### 2019-12-18 paper.tex
na eerste run
het loopt

\documentclass{article}

\usepackage{fenna-files/packages}
\usepackage{fenna-files/commands}
\bibliography{fenna-files/references}{}

\title{Dutch, PPs, ʀ-pronouns}
\author{Fenna Bergsma}
\date{\today}

\begin{document}

\maketitle

54586da0fa5bdbec34a4e83fcdf411ea6162a09a

\section{Introduction}

The puzzle is the following. In mismatching free relatives we sometimes see \tit{met wat} and sometimes \tit{waarmee}.

\ex.
\ag. Ik heb gekocht waar jij mee schildert.\\
 I have bought where you with paint\\
 `I bought what you are painting with.'
\bg. *Ik heb gekocht met wat jij schildert.\\
 I have bought with what you paint\\
 `I bought what you are painting with.'

\ex.
\ag. *Ik schilder waarmee jij hebt gekocht.\\
 I paint {where with} you have bought\\
 `I paint with what you bought.'
\bg. Ik schilder met wat jij hebt gekocht.\\
 I paint with what you have bought\\
 `I paint with what you bought.'

A few things should be noticed here. First, \tit{met wat} and \tit{waarmee} appear in a complementary distribution. Second, \tit{waar} in \tit{waarmee} means \tit{where}, but \tit{waarmee} does not express a location. Third, the preposition \tit{met} changes into \tit{mee}.

This paper: \tit{waarmee} is the default realization of an instrumental when all features form a constituent. If not, then \tit{met wat}. The \tit{r} in ʀ-pronouns does not necessarily express \tsc{locative}, in \tit{waarmee} is only expresses \tsc{thing}. The change of \tit{met} into \tit{mee} is a reflex of stranded features/a different spellout of features.

Unmarked examples are constructed and have been verified by native speakers.

\section{Conditions for \tit{waarmee} and \tit{met wat} to appear}

Repeating the first example from the introduction. What we see here is embedded clause verb requires its object to be an instrumental and the main clause verb wants an accusative object. \tit{waarmee} is correct weer, \tit{met wat} is not.

\ex.
\ag. Ik heb gekocht waar jij mee schildert.\\
 I have bought where you with paint\\
 `I bought what you are painting with.'
\bg. *Ik heb gekocht met wat jij schildert.\\
 I have bought with what you paint\\
 `I bought what you are painting with.'

 \tit{Waarmee} is ʀ-pronoun, a term introduced by \cite{riemsdijk1978}. ʀ-pronouns are not specific to the inanimate relative pronouns. No inanimate pronominal elements in Dutch is able to act as the object of a preposition. They are all replaced by an ʀ-pronoun. As suggested by the name, ʀ-pronouns always contain the morpheme \tit{r}.

 Dutch has the personal pronouns \tit{haar} `her', \tit{hem} `him' and \tit{het} `it' that can be used as animate and inanimate objects of verbs, as illustrated in \ref{ex:objverb}.

 \ex. Objects of verbs \label{ex:objverb}
 \ag. Ik zie haar/hem.\\
  I see her/him\\
  `I see her/him.'\label{ex:aniobj}
 \bg. Ik zie 't.\\
  I see it\\
  `I see it.'\label{ex:inaniobj}

The example in \ref{ex:prepani} shows that for animate objects the same pronouns (\tit{haar} `her' and \tit{hem} `him') appear as objects of prepositions. However, the inanimate personal pronoun \tit{het} `it' cannot be used as an object of a preposition, shown in \ref{ex:prephet}. Instead, an ʀ-pronoun appears. This is illustrated in \ref{ex:preper}.

\ex. Objects of prepositions \label{ex:objprep}
\ag. Ik schilder samen met haar/hem.\\
 I paint together with her/him\\
 `I am painting together with her/him.'\label{ex:prepani}
\bg. *Ik schilder met het.\\
 I paint with a brush\\
 `I am painting with it.'\label{ex:prephet}
\bg. Ik schilder er-mee.\\
 I paint \tit{er}-with\\
 `I am painting with it.'\label{ex:preper}

\tit{met} is not the only preposition with which this happens.

\ex.
\ag. Ik zit er-op.\\
 I sit it-on\\
 `I am sitting on it.
\bg. *Ik zit op 't.\\
 I sit on it\\
 `I am sitting on it.

 \ex.
 \ag. Hij zwemt er-in.\\
  He swims it-in\\
  `He is swimming in it.'
 \bg. *Hij zwemt in 't.\\
  He swims in it\\
  `He is swimming in it.'

\tit{Waarmee} and not \tit{met wat} also appears in other contexts. \ref{ex:headless} shows matching headless free relatives, \ref{ex:headed} shows headed relatives, \ref{ex:wh} gives wh-questions. The use of \tit{met wat} is ungrammatical here, and \tit{waarmee} should be chosen.

\ex. Matching headless relatives\label{ex:headless}
\ag. Ik schilder waar jij ook mee schildert.\\
 I paint \tit{w-aa-r} you also with paint\\
 `I am painting with what you are painting with too.'
\bg. *Ik schilder met wat jij ook schildert.\\
 I paint with what you also paint\\
 `I am painting with what you are painting with too.'

\ex. Headed relatives\label{ex:headed}
\ag. Ik schilder met de kwast waar-mee jij ook schildert.\\
 I paint with the brush \tit{w-aa-r}-with you also paint\\
 `I am painting with the brush that you are painting with too.'
\bg. *Ik schilder met de kwast met wat jij ook schildert.\\
 I paint with the brush with what you also paint\\
 `I am painting with the brush that you are painting with too.'

\ex. Wh-question\label{ex:wh}
\ag.  Waar-mee schilder jij?\\
 \tit{W-aa-r}-with paint you\\
 `What are you painting with?'
\bg. *Met wat schilder jij?\\
 With what paint you\\
 `What are you painting with?'

What this shows is that in principle \tit{waarmee} is used, it is the default. What is special about the examples in which \tit{met wat} is used then? I suggest that it is the constituency. \tit{Waarmee} needs to be a constituent. I repeated the \tit{waarmee} example. Here \tit{waar} and \tit{mee} are both part of the embedded clause. I show later that at some point in the derivation they were part of a proper constituent. They formed a constituent without any other elements.

\ex.
\ag. Ik heb gekocht [waar jij mee schildert].\\
 I have bought where you with paint\\
 `I bought what you are painting with.'
\bg. *Ik heb gekocht [met wat jij schildert].\\
 I have bought with what you paint\\
 `I bought what you are painting with.'

 Now I repeat the \tit{met wat} example. Here \tit{wat} is part of the embedded clause but \tit{met} is not. It belongs to the main clause. An embedded clause is finished before the main clause is built. At no point in the derivation can \tit{met} \tit{wat} form a proper constituent.

\ex.
\ag. *Ik schilder [waar]mee [jij hebt gekocht].\\
 I paint {where with} you have bought\\
 `I paint with what you bought.'
\bg. Ik schilder met [wat jij hebt gekocht].\\
 I paint with what you have bought\\
 `I paint with what you bought.'

There are actually more examples of \tit{wat} following \tit{met} in which \tit{met} and \tit{wat} do not form a constituent without containing any other elements. First, \tit{wat} is an indefinite that takes an NP complement, and only then it is combined with the \tit{met}. Second, \tit{wat} combines with \tit{voor} and then combines with an NP complement en then with \tit{met}. \tit{Met} and \tit{wat} are never a constituent to the exclusion of everything else.

\ex.
\ag. Ik wil graag thee met wat suiker.\\
 I want please tea with some sugar\\
 `I would like to have tea with some sugar.'
\bg. [Met [wat [voor [potloden]]] teken jij?\\
 with what for pencils draw you\\
 `What kind of pencils do you with?'

In conclusion:

\ex.
\a. *[[met] [wat]] $\rightarrow$ [waarmee]
\b. [met [wat X]]
\b. [met [wat [X]]]

\section{Connecting \tit{wat} to \tit{waar} and \tit{met} to \tit{mee}}

So, \tit{waarmee} and \tit{met wat} realize the same features but their spellouts differ.

\ex.
\ag. Ik heb gekocht [waar jij mee schildert].\\
 I have bought where you with paint\\
 `I bought what you are painting with.'
\bg. Ik schilder met [wat jij hebt gekocht].\\
 I paint with what you have bought\\
 `I paint with what you bought.'

A few things should be noted here. First, position of the elements: the regular pronoun follows the adposition and the ʀ-pronoun precedes the preposition. Second, the shape of the wh-pronoun: the ʀ-pronoun differs from the non-ʀ-pronoun in the lengthening of the vowel that the final consonant is \tit{r}. Third, the shape of the adposition: \tit{met} and \tit{tot} change in \tit{mee} and \tit{toe} when they combine with ʀ-pronouns.

Now let's look at it like this: \tit{waarmee} realizes particular features. Say \tit{waar} expresses A and B and \tit{mee} expresses C and D. Say, A B C and D. \tit{met wat} realizes the same features. Saying that \tit{wat} also realizes A and B and \tit{met} also C and D misses the point of having different realizations. So instead, say \tit{wat} only realizes A and \tit{met} realizes B, C and D. Or \tit{wat} realizes A, B and C and \tit{met} only realizes D. In both cases all features are expresses, but they are distributed differently, allowing for different realizations.\footnote{I did not address the ordering difference of the elements. Yes, this can lead to a difference in meaning.

\ex.
\ag. Ik klim in de boom.\\
 I climb in the tree\\
 `I am climbing in the tree.'
\bg. Ik klim de boom in\\
 I climb the tree in\\
 `I am climbing into the tree.'

Here, however, I will argue that the movement is driven by spellout and is meaningless.}

\begin{table}[ht]
	\center
	\caption {Distribution options}
	\begin{minipage}{0.27\linewidth}
		\begin{tabularx}{\textwidth}{cccc}
		\toprule
    \tsc{a}   & \tsc{b}            & \tsc{c}   & \tsc{d}                           \\
		\midrule
    \multicolumn{2}{c}{\tit{met}}  & \multicolumn{2}{c}{\cellcolor{Gray}\tit{wat}} \\
    \tit{mee} & \multicolumn{3}{c}{\cellcolor{Gray}\tit{waar}}                     \\
    \multicolumn{3}{c}{\tit{mee}}               & \cellcolor{Gray}{\tit{waar}}     \\
    \bottomrule
\end{tabularx}
\end{minipage}
\end{table}

I will argue for the last option, that \tit{met} spells out fewer features than \tit{mee}. The main argument for that comes from the fact that Dutch is a non-preposition stranding language, so prepositions cannot be moved out of the PP. Also, you cannot move the complement of a P to its spec, but you can subextract from them (Abels). And I show that ʀ-pronouns behave like clitic in how high they move.

In a nutshell, if all features are merged at once, we will always get an ʀ-pronoun. Due to spellout driven movement the ʀ-pronoun strands the features to be realizes by a preposition and a little more. The ʀ-pronoun is a clitic and moves high. The preposition + a little more realizes as \tit{mee} in case of \tit{waarmee}. Now if the features are not merged all at once, the regular spellout driven movements cannot take place, and we see \tit{met wat}. So, the answer of how constituency connects to change in phonological form lies in one of the core assumptions of nanosyntax: phrasal spellout spells out constituents.

\ex.
\a. \tit{waar} = w + a + r
\b. \tit{wat} = w + a + t

So the difference betwween \tit{t} and \tit{r} was actually the only difference we need to account for.

Dutch is a non P-stranding language.

\ex.
\ag. Met wie heb jij gedanst?\\
 with who have you danced\\
 `Whom did you dance with?'
\bg. *Wie heb jij gedanst met?\\
 who have you danced with\\
 `Whom did you dance with?'

Abels shows that extraction from a PP is not categorically excluded. It happens in Slavic.

--examples here--

What if ʀ-pronouns are actually clitic? And they pattern with Slavic in that they clitic can never follow Ps.

Do we have more reasons to believe that ʀ-pronouns are clitics? The non-wh ʀ-pronouns in Dutch are able to move very high, just like clitics and unlike regular pronouns in Dutch.\footnote{\ref{ex:hemaan} can also be excluded by saying that \tit{aan} and \tit{hem} cannot split.}

\ex.
\ag. Ik heb veel geld aan de badkamer uitgegeven.\\
 I have much money on the bathroom spent\\
 `I spent a lot of money on the bathroom.'
\bg. Ik heb er veel geld aan uitgegeven.\\
 I have there much money on spent\\
 `I spent a lof of money on it.'

\ex.
\ag. Ik heb veel geld aan mijn zoon uitgegeven.\\
 I have much money on my son spent\\
 `I spent a lof of money on my son'
\bg. Ik heb veel geld aan hem uitgegeven.\\
 I have much money on him spent\\
 `I spent a lot of money on him.'
\bg. *Ik heb \tbf{hem} veel geld aan uitgegeven.\\
 I have him much money on spent\\
 `I spent a lof of money on it.'\label{ex:hemaan}
\z.
\z.

This has shown that \tit{er} is small, smaller than regular pronouns. So we go for this option:

\begin{table}[ht]
	\center
	\caption {\tit{er} < \tit{'t}}
	\begin{minipage}{0.27\linewidth}
		\begin{tabularx}{\textwidth}{cccc}
		\toprule
    \tsc{a}   & \tsc{b}            & \tsc{c}   & \tsc{d}                           \\
		\midrule
    \multicolumn{2}{c}{\tit{met}}  & \multicolumn{2}{c}{\cellcolor{Gray}\tit{wat}} \\
    \multicolumn{3}{c}{\tit{mee}}               & \cellcolor{Gray}{\tit{waar}}     \\
    \bottomrule
\end{tabularx}
\end{minipage}
\end{table}

As a result of \tit{waar} being small, \tit{mee} becomes big. And \tit{mee} spells out more features than \tit{met}.

Now the difference in distribution between \tit{met wat} and \tit{waarmee} is going to follow from spellout. If we get higher than dative case, we need prepositions. Making prepositions is a very 'costly' operation in the langauge, it is the last resort option in the spellout procedure. Dutch also has forms that are not only prepositions, but can also function as postpositions. They are less 'costly'. To avoid building a complex specifier, different spellout options are used. That is why we get the \tsc{r}-pronoun in the picture. \tsc{r}-pronouns can combine with these postpositions.

\section{Taking \tit{waarmee} and \tit{met wat} apart}

\tit{'t} `it' from \ref{ex:entryt} can be used as subject, direct object and indirect object.

\ex.
\ag. 't Staat in de hal.\\
 \tsc{3sg.n.nom} stands in the hallway\\
 `It is standing in the hallway.'
\bg. Ik zie 't.\\
 I see \tsc{3sg.n.acc}\\
 `I see it.'
\bg. Ik heb 't een klap gegeven.\\
 I have \tsc{3sg.n.dat} a hit given\\
 `I hit it.'

 Pronouns in other genders alternate between nominative (non-oblique) and accusative/dative (oblique) in these contexts.

 \ex.
 \ag. Hij staat in de hal.\\
  \tsc{3sg.m.nom} stands in the hallway\\
  `He is standing in the hallway.'
 \bg. Ik zie hem.\\
  I see \tsc{3sg.m.acc}\\
  `I see it.'
 \bg. Ik heb hem een klap gegeven.\\
  I have \tsc{3sg.m.acc} a hit given\\
  `I hit him.'

\ex. \begin{forest} boom
[\tsc{dat}P
    [\tsc{f}3]
    [\tsc{acc}P
        [\tsc{f}2]
        [\tsc{nom}P
            [\tsc{f}1]
            [\tsc{thingP}
                [\tsc{thing}, roof]
            ]
        ]
    ]
]
{\draw (.east) node[right]{⇔ \tit{(ə)t}}; }
\end{forest}\label{ex:entryt}

\tit{Er} can be used as a locative.

\exg. Ik ben er al geweest.\\
I am there already been\\
`I have already been there.'

\ex. \begin{forest} boom
[\tsc{loc}P
[\tsc{location}]
    [\tsc{thngP}
        [\tsc{thing}, roof]
    ]
]
{\draw (.east) node[right]{⇔ \tit{(ə)r}}; }
\end{forest}\label{ex:entryr}

\tit{Met} can be used for as instrumental or comitative.

\exg. Ik dans met hem.\\
 I dance with him\\
 `I am dancing with him.'

\ex. \begin{forest} boom
[\tsc{com}P
    [\tsc{f}5]
    [\tsc{ins}P
        [\tsc{f}4, roof]
    ]
]
{\draw (.east) node[right]{⇔ \tit{met}}; }
\end{forest}\label{ex:entrymet}

Either way, it combines with accusative/dative (oblique), which can be seen on the pronouns. But only for the comitative, because for the instrumental we are getting an ʀ-pronoun. Full DPs do not show any marking, leading me to postulate the zero marker up to the dative.

\ex.
\ag. Ik dans met de man.\\
 I dance with the man\\
 `I am dancing with the man.'
\bg. Ik schilder met een kwast.\\
 I paint with een brush\\
 `I am painting with een brush.'

\ex. \begin{forest} boom
[\tsc{datP}
   [\tsc{f}3]
   [\tsc{acc}P
       [\tsc{f}2]
       [\tsc{nom}P
           [\tsc{f}1]
           [\phantom{x}]
       ]
   ]
]
{\draw (.east) node[right]{⇔ \tit{∅}}; }
\end{forest}

So \tit{met} expresses \tsc{f}4, and \tit{(ə)r} expresses \tsc{thing} and \tsc{f}1 to \tsc{f}1. \tit{(ə)r} only expresses \tsc{thing}. \tit{Ermee} and \tit{met 't} express the same features, which leaves \tsc{f}1 to \tsc{f}4 for \tit{mee}.

\begin{table}[ht]
	\center
	\caption {\tit{met 't} and \tit{ermee}}
	\begin{minipage}{0.38\linewidth}
		\begin{tabularx}{\textwidth}{ccccc}
		\toprule
    \tsc{f}4   & \tsc{f}3 & \tsc{f}2  & \tsc{f}1                 & \tsc{thing}                 \\
		\midrule
    \tit{met}  & \multicolumn{4}{c}{\cellcolor{Gray}\tit{(ə)t}}                                \\
    \multicolumn{4}{c}{\tit{mee}}                                & \cellcolor{Gray}\tit{(ə)r}  \\
    \bottomrule
\end{tabularx}
\end{minipage}
\end{table}

\ex. \begin{forest} boom
[\tsc{com}P
    [\tsc{f}5]
    [\tsc{insP}
        [\tsc{f}4]
        [\tsc{dat}P
            [\tsc{f}3]
            [\tsc{acc}P
                [\tsc{f}2]
                [\tsc{nom}P
                    [\tsc{f}1]
                    [\phantom{x}]
                ]
            ]
        ]
    ]
]
{\draw (.east) node[right]{⇔ \tit{mee}}; }
\end{forest}\label{ex:entrymee1}

\tit{a}/\tit{aa} is distal, \tit{ie}/\tit{i} is proximal. Medial?

\ex.
\ag. h-ie-r\\
 here\\
 `here'
\bg. d-aa-r\\
 there\\
 `there'
\bg. d-i-t\\
 this\\
 `this'
\bg. d-a-t\\
 that\\
 `that'
\z.
\z.

\ex. \begin{forest}
[WP
    [W, roof]
]
{\draw (.east) node[right]{⇔ \tit{w}}; }
\end{forest}\label{ex:entryw}

WP is the interrogative/wh, whatever.

\ex. \begin{forest}
[\tsc{distP}
    [\tsc{deix3}]
    [\tsc{medP}
        [\tsc{deix2}]
        [\tsc{deix1}]
    ]
]
{\draw (.east) node[right]{⇔ \tit{a}}; }
\end{forest}\label{ex:entrya}
\z.

\section{Derivation}

Spellout

\ex. Merge F and
 \a. Spell out FP
 \b. If (a) fails, attempt movement of the spec of the complement of \tsc{f}, and retry (a)
 \b. If (b) fails, move the complement of \tsc{f}, and retry (a)

\ex. Cyclic Override\\
Lexicalisation at a node XP overrides any previous match at a phrase contained in XP.

\ex. Backtracking\\
When spellout fails, go back to the previous cycle, and try the next option for that cycle.

The functional sequence of \tit{ermee}.

\ex. \tsc{f}4 > \tsc{f}3 > \tsc{f}2 > \tsc{f}1 > \tsc{thing}

We start with \tsc{thing}. This is realized as \tit{(ə)r}, because it has less junk than \tit{(ə)t}.

\ex.
\begin{forest} boom
 [\tsc{thingP}
     [\tsc{thing}, roof]
 ]
{\draw (.east) node[right]{⇔ \tit{(ə)r}}; }
\end{forest}

\tsc{f}1 is merged. \tit{(ə)r} is no longer a candidate, but \tit{(ə)t} is. So the spellout is overridden.

\ex. \begin{forest} boom
[\tsc{nom}P
   [\tsc{f}1]
   [\tsc{thingP}
       [\tsc{thing}, roof]
   ]
]
{\draw (.east) node[right]{⇔ \tit{(ə)t}}; }
\end{forest}

\tsc{f}2 is merged, which can still be realizd by \tit{(ə)t}.

\ex. \begin{forest} boom
[\tsc{accP}
   [\tsc{f}2]
   [\tsc{nom}P
       [\tsc{f}1]
       [\tsc{thingP}
           [\tsc{thing}, roof]
       ]
   ]
]
{\draw (.east) node[right]{⇔ \tit{(ə)t}}; }
\end{forest}

Idem for \tsc{f}3.

\ex. \begin{forest} boom
[\tsc{datP}
    [\tsc{f}3]
    [\tsc{accP}
       [\tsc{f}2]
       [\tsc{nom}P
           [\tsc{f}1]
           [\tsc{thingP}
               [\tsc{thing}, roof]
           ]
       ]
    ]
]
{\draw (.east) node[right]{⇔ \tit{(ə)t}}; }
\end{forest}

Now \tsc{f}4 is merged. No candidate for phrasal spellout, no candidate after complement movement.

\ex.
\a. \begin{forest} boom
[\tsc{insP}
    [\tsc{f}4]
    [\tsc{datP}
        [\tsc{f}3]
        [\tsc{accP}
           [\tsc{f}2]
           [\tsc{nom}P
               [\tsc{f}1]
               [\tsc{thingP}
                   [\tsc{thing}, roof]
               ]
           ]
        ]
    ]
]
{\draw (.east) node[right]{⇔ }; }
\end{forest}
\b. \begin{forest} boom
[\phantom{x}
    [\tsc{datP}
        [\tsc{f}3]
        [\tsc{accP}
           [\tsc{f}2]
           [\tsc{nom}P
               [\tsc{f}1]
               [\tsc{thingP}
                   [\tsc{thing}, roof]
               ]
           ]
        ]
    ]
    {\draw (.east) node[right]{⇔ \tit{(ə)t}}; }
    [\tsc{insP}
        [\tsc{f}4]
    ]
    {\draw (.east) node[right]{⇔ }; }
]
\end{forest}

The next step in the algorithm is backtracking. We try the next option for the cycle in which \tsc{f}3 was merged. This option is complement movement. However, there is no lexical entry that fits, so we try the next option.

show here

The exact same happens for \tsc{f}2.

show here

Now for \tsc{f}1 it is different. There is a candidate when we try complement movemement, namely \tsc{thing} is realized as \tit{(ə)r} and \tsc{f}1 is spelled out as \tit{∅}

\ex. \begin{forest} boom
[\phantom{x}
   [\tsc{thingP}
       [\tsc{thing}, roof]
   ]
   {\draw (.east) node[right]{⇔ \tit{(ə)r}}; }
   [\tsc{nom}P
       [\tsc{f}1]
   ]
   {\draw (.east) node[right]{⇔ \tit{∅}}; }
]
\end{forest}

Merge \tsc{f}2, there is no candidate for phrasal spellout, we try spec to spec movement and get a match:

\ex. \begin{forest} boom
[\phantom{x}
   [\tsc{thingP}
       [\tsc{thing}, roof]
   ]
   {\draw (.east) node[right]{⇔ \tit{(ə)r}}; }
   [\tsc{acc}P
       [\tsc{f}2]
       [\tsc{nom}P
           [\tsc{f}1]
       ]
   ]
   {\draw (.east) node[right]{⇔ \tit{∅}}; }
 ]
\end{forest}

Idem for \tsc{f}3.

\ex. \begin{forest} boom
[\phantom{x}
   [\tsc{thingP}
       [\tsc{thing}, roof]
   ]
   {\draw (.east) node[right]{⇔ \tit{(ə)r}}; }
   [\tsc{dat}P
       [\tsc{f}3]
       [\tsc{acc}P
           [\tsc{f}2]
           [\tsc{nom}P
               [\tsc{f}1]
           ]
       ]
   ]
   {\draw (.east) node[right]{⇔ \tit{∅}}; }
]
\end{forest}

Now \tsc{f}4 is merged. No phrasal spellout, but there is a match after spec-to-spec movement. However, is is not \tit{∅} anymore, but the inserted morpheme is \tit{mee}.

\ex. \begin{forest} boom
[\phantom{x}
    [\tsc{thingP}
       [\tsc{thing}, roof]
    ]
    {\draw (.east) node[right]{⇔ \tit{(ə)r}}; }
    [\tsc{insP}
       [\tsc{f}4]
       [\tsc{dat}P
           [\tsc{f}3]
           [\tsc{acc}P
               [\tsc{f}2]
               [\tsc{nom}P
                   [\tsc{f}1]
               ]
           ]
       ]
    ]
    {\draw (.east) node[right]{⇔ \tit{mee}}; }
]
\end{forest}

Then show here that this does not happen if not all features form a proper constituent. Spellout can just not target a constituent.

Open issues:

\begin{itemize}
  \item I still need to incorporate \tit{a} and \tit{w}. They can either come before case or after it.
  \item Right now I do not capture the formal similarity between \tit{met} and \tit{mee}. I have ideas about that:
  \item Some adpositions do not change shape. They should be usable both as prepositions and postpositions. This should be reflected in their lexical entry. A prediction is that there exist adpositions that cannot be used as postpositions. Examples of that are: \tit{zonder}, \tit{midden}, \tit{sinds}, \tit{rond}, \tit{beneden}.
\end{itemize}

\section{Conclusion}

\printbibliography

\end{document}

### 2019-12-19 paper.tex
werkt t?
vanaf de desktop
voor meeting with pavel

@@
 \maketitle
-
-54586da0fa5bdbec34a4e83fcdf411ea6162a09a
 
@@
 
-What this shows is that in principle \tit{waarmee} is used, it is the default.
-What is special about the examples in which \tit{met wat} is used then?
-I suggest that it is the constituency.
-\tit{Waarmee} needs to be a constituent.
-I repeated the \tit{waarmee} example.
-Here \tit{waar} and \tit{mee} are both part of the embedded clause.
-I show later that at some point in the derivation they were part of a proper constituent.
-They formed a constituent without any other elements.
+What this shows is that in principle \tit{waarmee} is used, it is the default. There is something special about the examples in which \tit{met wat} is used.
+
+Now let us return to the mismatching headed relatives.
+The two predicates I used in these are \tit{kopen} `to buy' and \tit{schilderen}  `to paint'.
+\tit{Kopen} takes an accusative DP as its object.
+\tit{Schilderen} can take an instrumental PP as its object.\footnote{Of course, \tit{schilderen} also possibly takes an accusative DP, but I am focussing on the instrumental here.}
+
+\ex.
+\ag. Ik koop het schilderij.\\
+ I buy the painting\\
+ `I am buying the painting.'
+\bg. Ik schilder met een kwast.\\
+ I paint with a brush\\
+ `I am painting with a brush.'
+
+I repeat the example in which \tit{schildert} is in the embedded clause.
 
@@
 
+\tit{Schildert} wants the instrumental PP, so the embedded clause looks like this:
+
+\ex. [waar jij mee schildert]
+
+Here \tit{waar} and \tit{mee} are both part of the embedded clause. At a certain point in the derivation they formed a proper constituent, i.e. they formed a constituent without any other elements.
+
+\ex. \begin{forest} boom
+[
+    [waarmee]
+    [schildert]
+]
+\end{forest}
+
+\ex. \begin{forest} boom
+[
+    [jij]
+    [
+        [waarmee]
+        [schildert]
+    ]
+]
+\end{forest}
+
+\ex. \begin{forest} boom
+[
+    [jij]
+    [
+        [
+            [waar]
+            [mee]
+        ]
+        [schildert]
+    ]
+]
+\end{forest}
+
+now move \tit{waar}
+
+\ex. \begin{forest} boom
+[
+    [waar]
+    [
+        [jij]
+        [
+            [
+                [mee]
+            ]
+            [schildert]
+        ]
+    ]
+]
+\end{forest}
+
+or \tit{waarmee}
+
+\ex. \begin{forest} boom
+[
+    [
+        [waar]
+        [mee]
+    ]
+    [
+        [jij]
+        [
+            [schildert]
+        ]
+    ]
+]
+\end{forest}
+
+Then in the main clause \tit{gekocht} is merged, which selects for an accusative object. Somehow \tit{waarmee} can satisfy that requirement.
+
 Now I repeat the \tit{met wat} example.
-Here \tit{wat} is part of the embedded clause but \tit{met} is not.
-It belongs to the main clause.
-An embedded clause is finished before the main clause is built.
-At no point in the derivation can \tit{met} \tit{wat} form a proper constituent.
 
@@
  `I paint with what you bought.'
+
+\tit{Schildert} wants the instrumental PP, so the embedded clause looks like this:
+
+\ex. [waar jij mee schildert]
+
+Here \tit{wat} is part of the embedded clause but \tit{met} is not.
+It belongs to the main clause.
+An embedded clause is finished before the main clause is built.
+At no point in the derivation can \tit{met} \tit{wat} form a proper constituent.
 
@@
 \b. [met [wat [X]]]
+
+How do I connect constituency and different spellouts of the instrumental? Nano: only constituents can spellout. Something interevened. More examples of that.
+
+\section{internal structure of \tit{met wat} and \tit{waarmee}}
+
+start with \tit{met wat}.
+
+--here taking xxx apart--
+
+--but first introduce a bit of theory--
 

### 2019-12-20 paper.tex
after 20.12
not much more
but convinced pavel of complementary distribution
look for a place for sigma

@@
 \section{Introduction}
+
+Mismatching free relatives give a unique insight into the internal structure of r-pronouns.
 
@@
 If not, then \tit{met wat}.
-The \tit{r} in ʀ-pronouns does not necessarily express \tsc{locative}, in \tit{waarmee} is only expresses \tsc{thing}.
+The \tit{r} in ʀ-pronouns does not necessarily express \tsc{location}, in \tit{waarmee} is only expresses \tsc{thing}.
 The change of \tit{met} into \tit{mee} is a reflex of stranded features/a different spellout of features.
@@
 
-\section{Conditions for \tit{waarmee} and \tit{met wat} to appear}
+\section{\tit{\tsc{r}}-pronouns as default \\
+Distribution between \tit{waarmee} and \tit{met wat}}
 
@@
 
- \tit{Waarmee} is ʀ-pronoun, a term introduced by \cite{riemsdijk1978}.
+ \tit{Waarmee} is an ʀ-pronoun, a term introduced by \cite{riemsdijk1978}.
 ʀ-pronouns are not specific to the inanimate relative pronouns.
@@
 
-What this shows is that in principle \tit{waarmee} is used, it is the default. There is something special about the examples in which \tit{met wat} is used.
+What this shows is that ʀ-pronouns are not exceptions, but they are the default.
+There is something special about the examples in which \tit{met wat} is used.
+I suggest that the crucial difference lies in constituency.
+\tit{Waarmee} can only be used if the instrumental PP forms a proper constituent, i.e.
+a constituent to the exclusion of any other elements.
+In the examples from xx to xx above this is the case.
+
+There are actually more examples of \tit{wat} following \tit{met} in which \tit{met} and \tit{wat} do not form a constituent without containing any other elements.
+First, \tit{wat} is an indefinite that takes an NP complement, and only then it is combined with the \tit{met}.
+Second, \tit{wat} combines with \tit{voor} and then combines with an NP complement en then with \tit{met}.
+\tit{Met} and \tit{wat} are never a constituent to the exclusion of everything else.
+
+\ex.
+\ag. Ik wil graag thee met wat suiker.\\
+ I want please tea with some sugar\\
+ `I would like to have tea with some sugar.'
+\bg. [Met [wat [voor [potloden]]] teken jij?\\
+ with what for pencils draw you\\
+ `What kind of pencils do you with?'
+
+Let me now show how this applies to the examples with the mismatching relatives.
+
+I repeat the example in which \tit{schildert} is in the embedded clause.
+
+\ex.
+\ag. Ik heb gekocht [waar jij mee schildert].\\
+ I have bought where you with paint\\
+ `I bought what you are painting with.'
+\bg. Ik schilder met [wat jij hebt gekocht].\\
+ I paint with what you have bought\\
+ `I paint with what you bought.'
 
@@
 
-I repeat the example in which \tit{schildert} is in the embedded clause.
-
-\ex.
-\ag. Ik heb gekocht [waar jij mee schildert].\\
- I have bought where you with paint\\
- `I bought what you are painting with.'
-\bg. *Ik heb gekocht [met wat jij schildert].\\
- I have bought with what you paint\\
- `I bought what you are painting with.'
-
 \tit{Schildert} wants the instrumental PP, so the embedded clause looks like this:
 
-\ex. [waar jij mee schildert]
+\ex. \begin{forest} boom
+[
+    [
+        [gekocht, roof]
+    ]
+    [
+        [waar jij mee schildert, roof]
+    ]
+]
+\end{forest}
 
@@
 [
-    [waarmee]
-    [schildert]
-]
-\end{forest}
-
-\ex. \begin{forest} boom
     [
-    [jij]
-    [
-        [waarmee]
-        [schildert]
-    ]
-]
-\end{forest}
-
-\ex. \begin{forest} boom
-[
-    [jij]
-    [
-        [
-            [waar]
-            [mee]
-        ]
-        [schildert]
-    ]
-]
-\end{forest}
-
-now move \tit{waar}
-
-\ex. \begin{forest} boom
-[
-    [waar]
-    [
-        [jij]
-        [
-            [
-                [mee]
-            ]
-            [schildert]
-        ]
-    ]
-]
-\end{forest}
-
-or \tit{waarmee}
-
-\ex. \begin{forest} boom
-[
-    [
-        [waar]
-        [mee]
+        [met, roof]
     ]
     [
-        [jij]
-        [
-            [schildert]
-        ]
+        [wat jij hebt gekocht, roof]
     ]
@@
 Then in the main clause \tit{gekocht} is merged, which selects for an accusative object. Somehow \tit{waarmee} can satisfy that requirement.
-
-Now I repeat the \tit{met wat} example.
-
-\ex.
-\ag. *Ik schilder [waar]mee [jij hebt gekocht].\\
- I paint {where with} you have bought\\
- `I paint with what you bought.'
-\bg. Ik schilder met [wat jij hebt gekocht].\\
- I paint with what you have bought\\
- `I paint with what you bought.'
 
@@
 
-There are actually more examples of \tit{wat} following \tit{met} in which \tit{met} and \tit{wat} do not form a constituent without containing any other elements.
-First, \tit{wat} is an indefinite that takes an NP complement, and only then it is combined with the \tit{met}.
-Second, \tit{wat} combines with \tit{voor} and then combines with an NP complement en then with \tit{met}.
-\tit{Met} and \tit{wat} are never a constituent to the exclusion of everything else.
-
-\ex.
-\ag. Ik wil graag thee met wat suiker.\\
- I want please tea with some sugar\\
- `I would like to have tea with some sugar.'
-\bg. [Met [wat [voor [potloden]]] teken jij?\\
- with what for pencils draw you\\
- `What kind of pencils do you with?'
-
 In conclusion:
@@
 
-How do I connect constituency and different spellouts of the instrumental? Nano: only constituents can spellout. Something interevened. More examples of that.
+How do I connect constituency and different spellouts of the instrumental? Nano: only constituents can spell out.
 
 \section{internal structure of \tit{met wat} and \tit{waarmee}}
+
+Van Riemsdijk said that R-pronouns are pronouns and they orginate in the complement of P.
+Due to \tsc{r}-movement they move to the spec of PP, and due to suppletion they change form, coincidentally to something identical to the locative.
+Full DPs cannot move to the spec of PP because they do not have access to that spec.
+
+I claim that this movement is not a special r-movement, but a movement driven by spellout. The suppletion also follows from the regular spellout algorithm, and it is the locative that is inserted.
+
+Koopman's account differ from Van Riemsdijk's in that she assumes \tsc{r}-pronouns obligatorily move to specPlace.
+The fact that locatives and \tsc{r}-pronouns are syncretic is not a surprise.
+They occur in the same structural configuration.
+
+Place does not make a lot of sense in \tit{waarmee}, because we do not have a place here.
+
+Abels says that this movement from the complement to the spec is not allowed.
+He argues that, instead, that R-words are base generated as the specifiers of distinguished class of zero-place prepositions.
+\tsc{r} is the complement of P and is subextracted from the complement of P (which is allowed, because it is subextraction and not extraction of it as a whole.)
+
+I agree with Abels in that \tit{r} is substracted from the complement of the preposition.
+However, I say that \tit{r} is actually the pronoun.
+What he refers to as an \tsc{r}-word is in Dutch \tit{w-aa-}, which I also assume is merged later.
+
+I do not care whether \tit{w-} and \tit{-a-} are merged before or after.
+
+WHY DOES MEE MOVE? I DO NOT KNOW.
+BUT IT DOES.
+AND SO DOES WAAR.
+waar maybe because it is remnant movement?
 

### 2019-12-21 paper.tex
zaterdagochtend
werkt niet meer (op overleaf wel zo ongeveer!)
intro is bijna klaar, eerste sectie is halverwege

@@
 
-Mismatching free relatives give a unique insight into the internal structure of r-pronouns.
+hoi
 
-The puzzle is the following. In mismatching free relatives we sometimes see \tit{met wat} and sometimes \tit{waarmee}.
+The term \tsc{r}-pronoun \citep{riemsdijk1978} refers to a set of nominal elements that can strand prepositions in Dutch (and German).
+It is special because Dutch is a normally non-preposition stranding language.
+\tsc{R}-pronouns morphologically consist of a combination of a preposition and locative pronoun.
+In the example \ref{ex:klimerop} \tit{mee} `with' is the preposition and \tit{er} `there' is the locative pronoun.
 
-\ex.
-\ag. Ik heb gekocht waar jij mee schildert.\\
+\exg. Ik klim er-op.\\
+ I climb there-on\\
+ `I am climbing on it.'\label{ex:klimerop}
+
+This paper focuses on a single \tsc{r}-pronoun in a specific type of free relative construction, namely on the relative pronoun \tit{waarmee} `with what' in a free relative construction in which the predicates require different cases.
+The \tsc{r}-pronoun \tit{waarmee} `with what' is interesting for two reasons.
+First, just like for all \tsc{r}-pronouns, the wh-element is the locative, but there is no meaning component related to location in `with what'.
+Second, the preposition \tit{met} `with' changes into \tit{mee} `with' when it is combined withn \tsc{r}-pronoun.
+
+The construction I focus on is a free relative construction, in which the two predicates combine with different cases.
+I illustrate this in \ref{ex:gekochtwaarmee}.
+The predicate in the embedded clause, \tit{schildert} `paint', combines with an instrumental PP.
+The predicate in the main clause clause, \tit{gekocht} `bought' combines with an accusative DP.
+The \tsc{r}-pronoun \tit{waarmee} `with what' is used here.
+
+%%%%%%
+Footnote
+In this example \tit{mee} `with' is stranded and \tit{waar} `where' is moved to the left edge of the embedded clause.
+It is also possible for \tit{waar} `where' to bring \tit{mee} `with' along, as in \ref{ex:meealong} but it is regarded as less natural.
+
+\exg. Ik heb gekocht waar jij mee schildert.\\
  I have bought where you with paint\\
- `I bought what you are painting with.'
-\bg. *Ik heb gekocht met wat jij schildert.\\
- I have bought with what you paint\\
- `I bought what you are painting with.'
+ `I bought what you are painting with.'\label{ex:meealong}
+Footnote
+%%%%%%
 
-\ex.
+\exg. Ik heb gekocht waar jij mee schildert.\\
+ I have bought where you with paint\\
+ `I bought what you are painting with.'\label{ex:gekochtwaarmee}
+
+If one were to switch around the predicates between the clauses, the \tsc{r}-pronoun does not appear anymore.
+In \ref{ex:schildermet}, \tit{schilder} `paint' combines with an instrumental PP in the main clause and \tit{gekocht} `bought' combines with an accusative DP in the embedded clause.
+The use of an \tsc{r}-pronoun is ungrammatical, as indicated by the ungrammaticality of \ref{ex:schilderwaarmee}.
+Instead, a combination of the regular instrumental preposition \tit{met} `with' and the regular wh-pronoun \tit{was} `what' in used.
+
+\ex.\label{ex:schildermet}
 \ag. *Ik schilder waarmee jij hebt gekocht.\\
  I paint {where with} you have bought\\
- `I paint with what you bought.'
+ `I paint with what you bought.'\label{ex:schilderwaarmee}
 \bg. Ik schilder met wat jij hebt gekocht.\\
  I paint with what you have bought\\
- `I paint with what you bought.'
+ `I paint with what you bought.'\label{ex:schildermetwat}
 
-A few things should be noticed here.
-First, \tit{met wat} and \tit{waarmee} appear in a complementary distribution.
-Second, \tit{waar} in \tit{waarmee} means \tit{where}, but \tit{waarmee} does not express a location.
-Third, the preposition \tit{met} changes into \tit{mee}.
+The use of \tit{met wat} `with what' is ungrammatical in the context in which \tit{waarmee} `with what' appeared in \ref{ex:gekochtwaarmee}. This is illustrated in \ref{ex:gekochtmetwat}.
 
-This paper: \tit{waarmee} is the default realization of an instrumental when all features form a constituent.
-If not, then \tit{met wat}.
-The \tit{r} in ʀ-pronouns does not necessarily express \tsc{location}, in \tit{waarmee} is only expresses \tsc{thing}.
-The change of \tit{met} into \tit{mee} is a reflex of stranded features/a different spellout of features.
+\exg. *Ik heb gekocht met wat jij schildert.\\
+ I have bought with what you paint\\
+ `I bought what you are painting with.'\label{ex:gekochtmetwat}
 
+In this paper I show that distribution of \tit{waarmee} `with what' and \tit{met wat} `with what' in these free relative constructions gives us a unique insight into the internal structure of \tsc{r}-pronouns.
+In what follows I show that \tsc{r}-pronouns and regular preposition compete to spell out the same syntactic features.
+If all features form a constituent, the \tsc{r}-pronoun surfaces.
+If the constituent is interrupted, the preposition-pronoun combination shows up.
+This straightforwardly follows in a system in which spellout targets phrasal constituents: Nanosyntax \citep{starke2006}.
+
+This paper is structured as follows.
+First, I show that it really is constituency.
+Then I decompose \tsc{r}-pronouns, prepositions and regular pronouns.
+Last, I show in derivations that constituency connects to the choice for \tsc{r}-pronoun or preposition and regular pronoun.
 Unmarked examples are constructed and have been verified by native speakers.
 
-\section{\tit{\tsc{r}}-pronouns as default \\
-Distribution between \tit{waarmee} and \tit{met wat}}
+\section{\tsc{R}-pronouns as default}
 
-Repeating the first example from the introduction.
-What we see here is embedded clause verb requires its object to be an instrumental and the main clause verb wants an accusative object.
-\tit{waarmee} is correct weer, \tit{met wat} is not.
+In the introduction I discussed the distribution between \tit{waarmee} `with what' and \tit{met wat} `with what' in free relatives with predicates that combine with different cases.
+Table \ref{tbl:distribution} repeats the generalization.
+When the main clause predicate combines with an accusative and the embedded clause predicate with an instrumental, \tit{waarmee} is grammatical and \tit{met wat} is ungrammatical.
+When the main clause predicate combines with an instrumental and the embedded clause predicate with an accusative, \tit{waarmee} is ungrammatical and \tit{met wat} is used.
 
-\ex.
-\ag. Ik heb gekocht waar jij mee schildert.\\
- I have bought where you with paint\\
- `I bought what you are painting with.'
-\bg. *Ik heb gekocht met wat jij schildert.\\
- I have bought with what you paint\\
- `I bought what you are painting with.'
+\begin{table}[ht]
+	\center
+	\caption {Distribution between \tit{waarmee} and \tit{met wat}}
+	\begin{minipage}{0.27\linewidth}
+		\begin{tabularx}{\textwidth}{ccc}
+		\toprule
+                              & \tit{waarmee} & \tit{met wat} \\
+		\midrule
+    m:\tsc{acc}, e:\tsc{ins}  & ✓             & *             \\
+    m:\tsc{ins}, e:\tsc{acc}  & *             & ✓             \\
+    \bottomrule
+\end{tabularx}
+\end{minipage}
+\end{table}\label{tbl:distribution}
 
- \tit{Waarmee} is an ʀ-pronoun, a term introduced by \cite{riemsdijk1978}.
-ʀ-pronouns are not specific to the inanimate relative pronouns.
-No inanimate pronominal elements in Dutch is able to act as the object of a preposition.
-They are all replaced by an ʀ-pronoun.
-As suggested by the name, ʀ-pronouns always contain the morpheme \tit{r}.
-
+The goal of this section is to show that \tit{waarmee} is the default as instrumental relative pronoun.
+In order to do that, I discuss the distribution of \tsc{r}-pronouns and regular pronouns in more general.
 Dutch has the personal pronouns \tit{haar} `her', \tit{hem} `him' and \tit{het} `it' that can be used as animate and inanimate objects of verbs, as illustrated in \ref{ex:objverb}.
@@
 This is illustrated in \ref{ex:preper}.
+\ref{erprep} shows that the \tsc{r}-pronoun obligatorily moves to the left of the pronoun.
 
@@
 \bg. Ik schilder er-mee.\\
- I paint \tit{er}-with\\
+ I paint there-with\\
  `I am painting with it.'\label{ex:preper}
+\bg. *Ik schilder mee er.\\
+ I paint with-there\\
+ `I am painting with it.'\label{ex:erprep}
 
-\tit{met} is not the only preposition with which this happens.
+\tit{Met} is not the only preposition with which this happens.
+\tit{Op} `on' and \tit{in} `in' do not combine with the inanimate personal pronoun \tit{'t}, but the \tsc{r}-pronoun is used obligatorily.
 
@@
   `He is swimming in it.'
+
+A picture similar to the one for inanimate personal pronouns appears with wh-inanimates.
+
+object of verbs \tit{wat}.
+object of preposition with \tit{wat}
+
+then show they appear in the contexts below.
 
@@
 
+In sum, no inanimate pronominal elements in Dutch is able to act as the object of a preposition.
+It is always the \tsc{r}-pronoun that appears.
 What this shows is that ʀ-pronouns are not exceptions, but they are the default.
@@
 a constituent to the exclusion of any other elements.
+--explain here how they all form a constituent.
 In the examples from xx to xx above this is the case.
@@
 \ex.
-\ag. Ik heb gekocht [waar jij mee schildert].\\
+\ag. Ik heb gekocht waar jij mee schildert.\\
  I have bought where you with paint\\
  `I bought what you are painting with.'
-\bg. Ik schilder met [wat jij hebt gekocht].\\
+\bg. Ik schilder met wat jij hebt gekocht.\\
  I paint with what you have bought\\

### 2019-12-22 paper.tex
zondagavond
- referenties aangepast
- eerste sectie bijna af
- stuctuur voor rest van verhaal gedaan

@@
 
-hoi
-
 The term \tsc{r}-pronoun \citep{riemsdijk1978} refers to a set of nominal elements that can strand prepositions in Dutch (and German).
@@
 
-This paper focuses on a single \tsc{r}-pronoun in a specific type of free relative construction, namely on the relative pronoun \tit{waarmee} `with what' in a free relative construction in which the predicates require different cases.
-The \tsc{r}-pronoun \tit{waarmee} `with what' is interesting for two reasons.
+This paper focuses on a single \tsc{r}-pronoun in a specific type of free relative construction.
+The \tsc{r}-pronoun I focus on is the relative pronoun \tit{waarmee} `with what', which is interesting for two reasons.
 First, just like for all \tsc{r}-pronouns, the wh-element is the locative, but there is no meaning component related to location in `with what'.
-Second, the preposition \tit{met} `with' changes into \tit{mee} `with' when it is combined withn \tsc{r}-pronoun.
+Second, the preposition \tit{met} `with' changes into \tit{mee} `with when it is combined with an \tsc{r}-pronoun.
 
-The construction I focus on is a free relative construction, in which the two predicates combine with different cases.
+The construction I focus on is a mismatching free relative.
+This is a free relative construction in which the two predicates (the one in the main clause and the one in the embedded clause) combine with two different cases (i.e.
+the case requirements do not match).
 I illustrate this in \ref{ex:gekochtwaarmee}.
@@
 The \tsc{r}-pronoun \tit{waarmee} `with what' is used here.
-
-%%%%%%
-Footnote
-In this example \tit{mee} `with' is stranded and \tit{waar} `where' is moved to the left edge of the embedded clause.
-It is also possible for \tit{waar} `where' to bring \tit{mee} `with' along, as in \ref{ex:meealong} but it is regarded as less natural.
+\footnote{In this example \tit{mee} `with' is stranded and \tit{waar} `where' is moved to the left edge of the embedded clause.
+It is also possible for \tit{waar} `where' to bring \tit{mee} `with' along, as in \ref{ex:meealong} but it is regarded as slightly less natural.
 
@@
  `I bought what you are painting with.'\label{ex:meealong}
-Footnote
-%%%%%%
+\z.
+
+\phantom{x}
+}
 
@@
 If the constituent is interrupted, the preposition-pronoun combination shows up.
-This straightforwardly follows in a system in which spellout targets phrasal constituents: Nanosyntax \citep{starke2006}.
+This straightforwardly follows in a system in which spellout targets phrasal constituents: Nanosyntax \citep{starke2009}.
 
@@
 
-\section{\tsc{R}-pronouns as default}
+\section{The distribution between \tit{waarmee} and \tit{met wat}}
 
@@
 	\caption {Distribution between \tit{waarmee} and \tit{met wat}}
-	\begin{minipage}{0.27\linewidth}
+	\begin{minipage}{0.45\linewidth}
 		\begin{tabularx}{\textwidth}{ccc}
@@
 		\midrule
-    m:\tsc{acc}, e:\tsc{ins}  & ✓             & *             \\
-    m:\tsc{ins}, e:\tsc{acc}  & *             & ✓             \\
+    m:\tsc{acc}, e:\tsc{ins}  & ✔             & *             \\
+    m:\tsc{ins}, e:\tsc{acc}  & *             & ✔             \\
     \bottomrule
@@
 
-The goal of this section is to show that \tit{waarmee} is the default as instrumental relative pronoun.
-In order to do that, I discuss the distribution of \tsc{r}-pronouns and regular pronouns in more general.
+In this section I first show that \tsc{r}-pronouns are the default complement of a preposition.
+Next, I illustrate that a necessary requirement for an \tsc{r}-pronoun is that is forms a proper constituent.
+
+\subsection{\tsc{R}-pronouns as default}
+
+The goal of this section is to show that \tit{waarmee} `with what' is the default as instrumental relative pronoun.
+This generalization is not new, it has already been made \citet{riemsdijk1978,koopman2000}.
+In order to show that \tit{waarmee} `with what' is the default, I discuss the distribution of \tsc{r}-pronouns and regular pronouns in more general.
+I start with the personal pronouns and then return to the wh-pronouns.
+
 Dutch has the personal pronouns \tit{haar} `her', \tit{hem} `him' and \tit{het} `it' that can be used as animate and inanimate objects of verbs, as illustrated in \ref{ex:objverb}.
@@
 This is illustrated in \ref{ex:preper}.
-\ref{erprep} shows that the \tsc{r}-pronoun obligatorily moves to the left of the pronoun.
+\ref{ex:erprep} shows that the \tsc{r}-pronoun obligatorily moves to the left of the pronoun.
 
@@
 
-A picture similar to the one for inanimate personal pronouns appears with wh-inanimates.
+The situation of the inanimate wh-pronouns resembles the inanimate personal pronouns.
+\tit{Wat} `what' can function as an object of a verb (see \ref{ex:wat}), but not as an object of a preposition \ref{ex:metwat}.
+In that case, the \tsc{r}-pronoun \tit{waarmee} `with what' is appears, as shown in \ref{ex:waarmee}.
+\footnote{The sentence in \ref{ex:metwat} is unacceptable with neutral intonation.
+It becomes is only acceptable if \tit{wat} `what' is stressed, for example in a context in which the speaker questions the choice for the object hearer is painting with.}
 
-object of verbs \tit{wat}.
-object of preposition with \tit{wat}
+\ex.
+\ag. Wat zie jij?\\
+ what see you\\
+ `What do you see?'\label{ex:wat}
+\bg. *Met wat schilder jij?\\
+ With what paint you\\
+ `What are you painting with?'\label{ex:metwat}
+\bg. Waar schilder jij mee?\\
+ Where paint you with\\
+ `What are you painting with?'\label{ex:waarmee}
 
-then show they appear in the contexts below.
+\tit{Waarmee} `with what' and not \tit{met wat} `with what' does not only appear in wh-questions, but also in other contexts.
+\ref{ex:headed} gives an example of a headed relative, and \ref{ex:headless} shows a free relative in which both predicates combine with an instrumental PP.
+The use of \tit{met wat} `with what' is ungrammatical in both contexts, and \tit{waarmee} `with what' is used.
 
-\tit{Waarmee} and not \tit{met wat} also appears in other contexts.
-\ref{ex:headless} shows matching headless free relatives, \ref{ex:headed} shows headed relatives, \ref{ex:wh} gives wh-questions.
-The use of \tit{met wat} is ungrammatical here, and \tit{waarmee} should be chosen.
+\ex.\label{ex:headed}
+\ag. Ik schilder met de kwast waar jij ook mee schildert.\\
+ I paint with the brush where you also with paint\\
+ `I am painting with the brush that you are painting with too.'
+\bg. *Ik schilder met de kwast met wat jij ook schildert.\\
+ I paint with the brush with what you also paint\\
+ `I am painting with the brush that you are painting with too.'
 
-\ex. Matching headless relatives\label{ex:headless}
+ \ex.\label{ex:headless}
  \ag. Ik schilder waar jij ook mee schildert.\\
- I paint \tit{w-aa-r} you also with paint\\
+  I paint where you also with paint\\
   `I am painting with what you are painting with too.'
@@
 
-\ex. Headed relatives\label{ex:headed}
-\ag. Ik schilder met de kwast waar-mee jij ook schildert.\\
- I paint with the brush \tit{w-aa-r}-with you also paint\\
- `I am painting with the brush that you are painting with too.'
-\bg. *Ik schilder met de kwast met wat jij ook schildert.\\
- I paint with the brush with what you also paint\\
+Table \ref{tbl:inanimates} summarizes the distribution of inanimates in Dutch.
+Inanimate (personal and wh-)pronouns in Dutch can function as objects verbs, but they are ungrammatical as objects of prepositions.
+In these contexts, \tsc{r}-pronouns appear.
+
+\begin{table}[ht]
+	\center
+	\caption {Inanimates in Dutch}
+	\begin{minipage}{0.45\linewidth}
+		\begin{tabularx}{\textwidth}{ccc}
+		\toprule
+                        & pers. pronouns & wh-pronouns \\
+  	\midrule
+objects of verbs        & ət             & wat         \\
+objects of prepositions & er             & waar        \\
+\bottomrule
+\end{tabularx}
+\end{minipage}
+\end{table}\label{tbl:inanimates}
+
+The next section discusses the role of constituency in \tsc{r}-pronouns.
+
+\subsection{\tit{Waarmee} is a constituent, \tit{met wat} is not}
+
+Let me now return to the mismatching free relatives. I repeat the relevant grammatical examples in \ref{ex:grammatical}.
+
+\ex.\label{ex:grammatical}
+\ag. Ik heb gekocht waar jij mee schildert.\\
+ I have bought where you with paint\\
+ `I bought what you are painting with.'\label{ex:grammaticalwaar}
+\bg. Ik schilder met wat jij hebt gekocht.\\
+ I paint with what you have bought\\
+ `I paint with what you bought.'\label{ex:grammaticalwat}
+
+In this section I showed that ʀ-pronouns are expected in combinations with prepositions.
+This means that the use of \tit{waarmee} `with what' \ref{ex:grammaticalwaar} is not surprising.
+Something that is surprising is the use of \tit{met wat} `with what' in \ref{ex:grammaticalwat}, and this is the example something more needs to be said about.
+In the remainder of this section I argue that this `something more' is that the instrumental PP in \ref{ex:grammaticalwat} does not form a proper constituent, i.e.
+it is not a constituent to the exclusion of any other elements.
+The other side of the coin is that constructions with \tsc{r}-pronouns contain a PP that does form a proper constituent.
+
+Below I repeat the examples with instrumental PPs I discuss so far in this paper.
+
+\ex.
+\ag. Ik schilder er-mee.\\
+ I paint there-with\\
+ `I am painting with it.'\label{ex:const1}
+\bg. Waar schilder jij mee?\\
+ Where paint you with\\
+ `What are you painting with?'\label{ex:const2}
+\bg. Ik schilder met de kwast [waar jij ook mee schildert].\\
+ I paint with the brush {where with} you also paint\\
+ `I am painting with the brush that you are painting with too.'\label{ex:const3}
+\bg. Ik schilder [waar jij ook mee schildert].\\
+ I paint where you also with paint\\
+ `I am painting with what you are painting with too.'\label{ex:const4}
+
+In each of these examples the instrumental PP forms a constituent at a certain point in the derivation.
+In \ref{ex:const1}, the PP forms a proper constituent in the surface order, as shown in \ref{ex:const1stage}.
+In \ref{ex:const2}, the PP forms a proper constituent before wh- and V2- movement, shown in \ref{ex:const2stage}.
+The structure in \ref{ex:const3stage} represents a stage in the derivation of the embedded clauses in \ref{ex:const3} and \ref{ex:const4}.
+\footnote{I assume that the antecedent in a free relative is a phonologically empty element, in line with cf. \cite{bresnan1978a,groos1981,himmelreich2017}.}
+Again, in the stage, which comes before relative movement of the pronoun to the left periphery of the relative clause, the PP forms a proper constituent.
+
+\ex.
+\a. [[ik] [[schilder] [er-mee]]]\label{ex:const1stage}
+\b. [[jij] [[schilder] [[waar] [mee]]]]\label{ex:const2stage}
+\b. [[jij] [[ook] [[schilder] [[waar] [mee]]]]]\label{ex:const3stage}
+
+There is additional evidence for the fact that \tit{waarmee} `with what' forms a constituent in the constructions above.
+In the example in \ref{ex:const2}-\ref{ex:const4} only \tit{waar} `where' was fronted, but \ref{ex:constwaarmee} shows that also the phrase containing \tit{mee} `with' can be moved.
+As wh-movement can only target constituents, it follows that \tit{waar} `where' and \tit{mee} `with' have to form a constituent.
+
+\ex.\label{ex:constwaarmee}
+\ag. Waarmee schilder jij?\\
+ {where with} paint you\\
+ `What are you painting with?'
+\bg. Ik schilder [waarmee jij ook schildert].\\
+ I paint {where with} you also paint\\
+ `I am painting with what you are painting with too.'
+\bg. Ik schilder met de kwast [waarmee jij ook schildert].\\
+ I paint with the brush {where with} you also paint\\
  `I am painting with the brush that you are painting with too.'
 
-\ex. Wh-question\label{ex:wh}
-\ag.  Waar-mee schilder jij?\\
- \tit{W-aa-r}-with paint you\\
- `What are you painting with?'
-\bg. *Met wat schilder jij?\\
- With what paint you\\
- `What are you painting with?'
+\ref{ex:grammaticalwat} is not the only construction in which the string \tit{met wat} `with what' appears.
+I give examples of two more occurrences in \ref{ex:moremetwat}.
+In \ref{ex:watindef}, \tit{wat} `what' is the \tit{wat} `what' in the so-called \tit{wat voor} `what for'-construction \citep[cf.][]{corver1991}.
+In \ref{ex:watindef}, \tit{wat} appears as a quantifier, and it means `some'.
+In both construction \tit{wat} `what' takes a complement and \tit{met wat} `with what' do not form a proper constituent.
+The brackets within the examples indicate the constituency.
 
-In sum, no inanimate pronominal elements in Dutch is able to act as the object of a preposition.
-It is always the \tsc{r}-pronoun that appears.
-What this shows is that ʀ-pronouns are not exceptions, but they are the default.
-There is something special about the examples in which \tit{met wat} is used.
-I suggest that the crucial difference lies in constituency.
-\tit{Waarmee} can only be used if the instrumental PP forms a proper constituent, i.e.
-a constituent to the exclusion of any other elements.
---explain here how they all form a constituent.
-In the examples from xx to xx above this is the case.
+\ex.\label{ex:moremetwat}
+\ag. [Met [wat [voor [potloden]]] teken jij?\\
+ with what for pencils draw you\\
+ `What kind of pencils do you with?'\label{ex:watwasfur}
+\bg. Ik wil graag thee [met [wat [suiker]]].\\
+ I want please tea with some sugar\\
+ `I would like to have tea with some sugar.'\label{ex:watindef}
 
-There are actually more examples of \tit{wat} following \tit{met} in which \tit{met} and \tit{wat} do not form a constituent without containing any other elements.
-First, \tit{wat} is an indefinite that takes an NP complement, and only then it is combined with the \tit{met}.
-Second, \tit{wat} combines with \tit{voor} and then combines with an NP complement en then with \tit{met}.
-\tit{Met} and \tit{wat} are never a constituent to the exclusion of everything else.
+Let me now show how this applies to the examples with the mismatching free relatives.
+The two predicates I used in the free relatives are \tit{kopen} `to buy' and \tit{schilderen}  `to paint'.
+\tit{Kopen} `to buy' takes an accusative DP as its object, illustrated in \ref{ex:kopen}.
+\tit{Schilderen} `to paint' can take an instrumental PP as its object., shown in \ref{ex:schilderen}.\footnote{Of course, \tit{schilderen} also optionally takes an accusative DP, but I am focussing on the instrumental here.}
 
 \ex.
-\ag. Ik wil graag thee met wat suiker.\\
- I want please tea with some sugar\\
- `I would like to have tea with some sugar.'
-\bg. [Met [wat [voor [potloden]]] teken jij?\\
- with what for pencils draw you\\
- `What kind of pencils do you with?'
+\ag. Ik koop het schilderij.\\
+ I buy the painting\\
+ `I am buying the painting.'\label{ex:kopen}
+\bg. Ik schilder met een kwast.\\
+ I paint with a brush\\
+ `I am painting with a brush.'\label{ex:schilderen}
 
-Let me now show how this applies to the examples with the mismatching relatives.
+insert the zero thingy there
 
@@
 \ex.
-\ag. Ik heb gekocht waar jij mee schildert.\\
+\ag. Ik heb gekocht [waar jij mee schildert].\\
  I have bought where you with paint\\
  `I bought what you are painting with.'
-\bg. Ik schilder met wat jij hebt gekocht.\\
+\bg. Ik schilder met [wat jij hebt gekocht].\\
  I paint with what you have bought\\
@@
 
-Now let us return to the mismatching headed relatives.
-The two predicates I used in these are \tit{kopen} `to buy' and \tit{schilderen}  `to paint'.
-\tit{Kopen} takes an accusative DP as its object.
-\tit{Schilderen} can take an instrumental PP as its object.\footnote{Of course, \tit{schilderen} also possibly takes an accusative DP, but I am focussing on the instrumental here.}
+\tit{Schildert} wants the instrumental PP, so the embedded clause looks like this.
+Here \tit{waar} and \tit{mee} are both part of the embedded clause.
+At a certain point in the derivation they formed a proper constituent, i.e.
+they formed a constituent without any other elements.
 
-\ex.
-\ag. Ik koop het schilderij.\\
- I buy the painting\\
- `I am buying the painting.'
-\bg. Ik schilder met een kwast.\\
- I paint with a brush\\
- `I am painting with a brush.'
-
-\tit{Schildert} wants the instrumental PP, so the embedded clause looks like this:
-
-\ex. \begin{forest} boom
-[
-    [
-        [gekocht, roof]
-    ]
-    [
-        [waar jij mee schildert, roof]
-    ]
-]
-\end{forest}
-
-Here \tit{waar} and \tit{mee} are both part of the embedded clause. At a certain point in the derivation they formed a proper constituent, i.e. they formed a constituent without any other elements.
-
-\ex. \begin{forest} boom
-[
-    [
-        [met, roof]
-    ]
-    [
-        [wat jij hebt gekocht, roof]
-    ]
-]
-\end{forest}
-
-Then in the main clause \tit{gekocht} is merged, which selects for an accusative object. Somehow \tit{waarmee} can satisfy that requirement.
-
+Then in the main clause \tit{gekocht} is merged, which selects for an accusative object.
+Somehow \tit{waarmee} can satisfy that requirement.
 \tit{Schildert} wants the instrumental PP, so the embedded clause looks like this:
@@
 \ex.
-\a. *[[met] [wat]] $\rightarrow$ [waarmee]
+\a. *[[met] [wat]] → [waarmee]
 \b. [met [wat X]]
@@
 
-\section{internal structure of \tit{met wat} and \tit{waarmee}}
+\section{Connecting constituency and spellout}
+
+Intro: why *\tit{met wat}? Not a filter, not a different paradigm.
+
+\subsection{Korean negation and causative}
+
+\subsection{nanostory of that}
+
+\subsection{waarmee = parallel}
+
+\section{A finer decomposition}
+
+What I account for: w, a, why we see the locative
+
+What I don't: similarity between \tit{met} and \tit{mee}, that preps do not change form
+
+and i need to say something about the assumption i make for pronouns
 
@@
 --here taking xxx apart--
-
---but first introduce a bit of theory--
-
-\section{Connecting \tit{wat} to \tit{waar} and \tit{met} to \tit{mee}}
-
-So, \tit{waarmee} and \tit{met wat} realize the same features but their spellouts differ.
-
-\ex.
-\ag. Ik heb gekocht [waar jij mee schildert].\\
- I have bought where you with paint\\
- `I bought what you are painting with.'
-\bg. Ik schilder met [wat jij hebt gekocht].\\
- I paint with what you have bought\\
- `I paint with what you bought.'
-
-A few things should be noted here.
-First, position of the elements: the regular pronoun follows the adposition and the ʀ-pronoun precedes the preposition.
-Second, the shape of the wh-pronoun: the ʀ-pronoun differs from the non-ʀ-pronoun in the lengthening of the vowel that the final consonant is \tit{r}.
-Third, the shape of the adposition: \tit{met} and \tit{tot} change in \tit{mee} and \tit{toe} when they combine with ʀ-pronouns.
-
-Now let's look at it like this: \tit{waarmee} realizes particular features.
-Say \tit{waar} expresses A and B and \tit{mee} expresses C and D.
-Say, A B C and D.
-\tit{met wat} realizes the same features.
-Saying that \tit{wat} also realizes A and B and \tit{met} also C and D misses the point of having different realizations.
-So instead, say \tit{wat} only realizes A and \tit{met} realizes B, C and D.
-Or \tit{wat} realizes A, B and C and \tit{met} only realizes D.
-In both cases all features are expresses, but they are distributed differently, allowing for different realizations.\footnote{I did not address the ordering difference of the elements.
-Yes, this can lead to a difference in meaning.
-
-\ex.
-\ag. Ik klim in de boom.\\
- I climb in the tree\\
- `I am climbing in the tree.'
-\bg. Ik klim de boom in\\
- I climb the tree in\\
- `I am climbing into the tree.'
-
-Here, however, I will argue that the movement is driven by spellout and is meaningless.}
-
-\begin{table}[ht]
-	\center
-	\caption {Distribution options}
-	\begin{minipage}{0.27\linewidth}
-		\begin{tabularx}{\textwidth}{cccc}
-		\toprule
-    \tsc{a}   & \tsc{b}            & \tsc{c}   & \tsc{d}                           \\
-		\midrule
-    \multicolumn{2}{c}{\tit{met}}  & \multicolumn{2}{c}{\cellcolor{Gray}\tit{wat}} \\
-    \tit{mee} & \multicolumn{3}{c}{\cellcolor{Gray}\tit{waar}}                     \\
-    \multicolumn{3}{c}{\tit{mee}}               & \cellcolor{Gray}{\tit{waar}}     \\
-    \bottomrule
-\end{tabularx}
-\end{minipage}
-\end{table}
-
-I will argue for the last option, that \tit{met} spells out fewer features than \tit{mee}.
-The main argument for that comes from the fact that Dutch is a non-preposition stranding language, so prepositions cannot be moved out of the PP.
-Also, you cannot move the complement of a P to its spec, but you can subextract from them (Abels).
-And I show that ʀ-pronouns behave like clitic in how high they move.
-
-In a nutshell, if all features are merged at once, we will always get an ʀ-pronoun.
-Due to spellout driven movement the ʀ-pronoun strands the features to be realizes by a preposition and a little more.
-The ʀ-pronoun is a clitic and moves high.
-The preposition + a little more realizes as \tit{mee} in case of \tit{waarmee}.
-Now if the features are not merged all at once, the regular spellout driven movements cannot take place, and we see \tit{met wat}.
-So, the answer of how constituency connects to change in phonological form lies in one of the core assumptions of nanosyntax: phrasal spellout spells out constituents.
-
-\ex.
-\a. \tit{waar} = w + a + r
-\b. \tit{wat} = w + a + t
-
-So the difference betwween \tit{t} and \tit{r} was actually the only difference we need to account for.
-
-Dutch is a non P-stranding language.
-
-\ex.
-\ag. Met wie heb jij gedanst?\\
- with who have you danced\\
- `Whom did you dance with?'
-\bg. *Wie heb jij gedanst met?\\
- who have you danced with\\
- `Whom did you dance with?'
-
-Abels shows that extraction from a PP is not categorically excluded. It happens in Slavic.
-
---examples here--
-
-What if ʀ-pronouns are actually clitic? And they pattern with Slavic in that they clitic can never follow Ps.
-
-Do we have more reasons to believe that ʀ-pronouns are clitics?
-The non-wh ʀ-pronouns in Dutch are able to move very high, just like clitics and unlike regular pronouns in Dutch.\footnote{\ref{ex:hemaan} can also be excluded by saying that \tit{aan} and \tit{hem} cannot split.}
-
-\ex.
-\ag. Ik heb veel geld aan de badkamer uitgegeven.\\
- I have much money on the bathroom spent\\
- `I spent a lot of money on the bathroom.'
-\bg. Ik heb er veel geld aan uitgegeven.\\
- I have there much money on spent\\
- `I spent a lof of money on it.'
-
-\ex.
-\ag. Ik heb veel geld aan mijn zoon uitgegeven.\\
- I have much money on my son spent\\
- `I spent a lof of money on my son'
-\bg. Ik heb veel geld aan hem uitgegeven.\\
- I have much money on him spent\\
- `I spent a lot of money on him.'
-\bg. *Ik heb \tbf{hem} veel geld aan uitgegeven.\\
- I have him much money on spent\\
- `I spent a lof of money on it.'\label{ex:hemaan}
-\z.
-\z.
-
-This has shown that \tit{er} is small, smaller than regular pronouns. So we go for this option:
-
-\begin{table}[ht]
-	\center
-	\caption {\tit{er} < \tit{'t}}
-	\begin{minipage}{0.27\linewidth}
-		\begin{tabularx}{\textwidth}{cccc}
-		\toprule
-    \tsc{a}   & \tsc{b}            & \tsc{c}   & \tsc{d}                           \\
-		\midrule
-    \multicolumn{2}{c}{\tit{met}}  & \multicolumn{2}{c}{\cellcolor{Gray}\tit{wat}} \\
-    \multicolumn{3}{c}{\tit{mee}}               & \cellcolor{Gray}{\tit{waar}}     \\
-    \bottomrule
-\end{tabularx}
-\end{minipage}
-\end{table}
-
-As a result of \tit{waar} being small, \tit{mee} becomes big. And \tit{mee} spells out more features than \tit{met}.
-
-Now the difference in distribution between \tit{met wat} and \tit{waarmee} is going to follow from spellout.
-If we get higher than dative case, we need prepositions.
-Making prepositions is a very 'costly' operation in the langauge, it is the last resort option in the spellout procedure.
-Dutch also has forms that are not only prepositions, but can also function as postpositions.
-They are less 'costly'.
-To avoid building a complex specifier, different spellout options are used.
-That is why we get the \tsc{r}-pronoun in the picture.
-\tsc{r}-pronouns can combine with these postpositions.
-
-\section{Taking \tit{waarmee} and \tit{met wat} apart}
 
@@
 
+\section{Connecting \tit{wat} to \tit{waar} and \tit{met} to \tit{mee}}
+
+So, \tit{waarmee} and \tit{met wat} realize the same features but their spellouts differ.
+
+\ex.
+\ag. Ik heb gekocht [waar jij mee schildert].\\
+ I have bought where you with paint\\
+ `I bought what you are painting with.'
+\bg. Ik schilder met [wat jij hebt gekocht].\\
+ I paint with what you have bought\\
+ `I paint with what you bought.'
+
+A few things should be noted here.
+First, position of the elements: the regular pronoun follows the adposition and the ʀ-pronoun precedes the preposition.
+Second, the shape of the wh-pronoun: the ʀ-pronoun differs from the non-ʀ-pronoun in the lengthening of the vowel that the final consonant is \tit{r}.
+Third, the shape of the adposition: \tit{met} and \tit{tot} change in \tit{mee} and \tit{toe} when they combine with ʀ-pronouns.
+
+Now let's look at it like this: \tit{waarmee} realizes particular features.
+Say \tit{waar} expresses A and B and \tit{mee} expresses C and D.
+Say, A B C and D.
+\tit{met wat} realizes the same features.
+Saying that \tit{wat} also realizes A and B and \tit{met} also C and D misses the point of having different realizations.
+So instead, say \tit{wat} only realizes A and \tit{met} realizes B, C and D.
+Or \tit{wat} realizes A, B and C and \tit{met} only realizes D.
+In both cases all features are expresses, but they are distributed differently, allowing for different realizations.\footnote{I did not address the ordering difference of the elements.
+Yes, this can lead to a difference in meaning.
+
+\ex.
+\ag. Ik klim in de boom.\\
+ I climb in the tree\\
+ `I am climbing in the tree.'
+\bg. Ik klim de boom in\\
+ I climb the tree in\\
+ `I am climbing into the tree.'
+
+Here, however, I will argue that the movement is driven by spellout and is meaningless.}
+
+\begin{table}[ht]
+	\center
+	\caption {Distribution options}
+	\begin{minipage}{0.27\linewidth}
+		\begin{tabularx}{\textwidth}{cccc}
+		\toprule
+    \tsc{a}   & \tsc{b}            & \tsc{c}   & \tsc{d}                           \\
+		\midrule
+    \multicolumn{2}{c}{\tit{met}}  & \multicolumn{2}{c}{\cellcolor{Gray}\tit{wat}} \\
+    \tit{mee} & \multicolumn{3}{c}{\cellcolor{Gray}\tit{waar}}                     \\
+    \multicolumn{3}{c}{\tit{mee}}               & \cellcolor{Gray}{\tit{waar}}     \\
+    \bottomrule
+\end{tabularx}
+\end{minipage}
+\end{table}
+
+I will argue for the last option, that \tit{met} spells out fewer features than \tit{mee}.
+The main argument for that comes from the fact that Dutch is a non-preposition stranding language, so prepositions cannot be moved out of the PP.
+Also, you cannot move the complement of a P to its spec, but you can subextract from them (Abels).
+And I show that ʀ-pronouns behave like clitic in how high they move.
+
+In a nutshell, if all features are merged at once, we will always get an ʀ-pronoun.
+Due to spellout driven movement the ʀ-pronoun strands the features to be realizes by a preposition and a little more.
+The ʀ-pronoun is a clitic and moves high.
+The preposition + a little more realizes as \tit{mee} in case of \tit{waarmee}.
+Now if the features are not merged all at once, the regular spellout driven movements cannot take place, and we see \tit{met wat}.
+So, the answer of how constituency connects to change in phonological form lies in one of the core assumptions of nanosyntax: phrasal spellout spells out constituents.
+
+\ex.
+\a. \tit{waar} = w + a + r
+\b. \tit{wat} = w + a + t
+
+So the difference betwween \tit{t} and \tit{r} was actually the only difference we need to account for.
+
+Dutch is a non P-stranding language.
+
+\ex.
+\ag. Met wie heb jij gedanst?\\
+ with who have you danced\\
+ `Whom did you dance with?'
+\bg. *Wie heb jij gedanst met?\\
+ who have you danced with\\
+ `Whom did you dance with?'
+
+Abels shows that extraction from a PP is not categorically excluded. It happens in Slavic.
+
+--examples here--
+
+What if ʀ-pronouns are actually clitic? And they pattern with Slavic in that they clitic can never follow Ps.
+
+Do we have more reasons to believe that ʀ-pronouns are clitics?
+The non-wh ʀ-pronouns in Dutch are able to move very high, just like clitics and unlike regular pronouns in Dutch.\footnote{\ref{ex:hemaan} can also be excluded by saying that \tit{aan} and \tit{hem} cannot split.}
+
+\ex.
+\ag. Ik heb veel geld aan de badkamer uitgegeven.\\
+ I have much money on the bathroom spent\\
+ `I spent a lot of money on the bathroom.'
+\bg. Ik heb er veel geld aan uitgegeven.\\
+ I have there much money on spent\\
+ `I spent a lof of money on it.'
+
+\ex.
+\ag. Ik heb veel geld aan mijn zoon uitgegeven.\\
+ I have much money on my son spent\\
+ `I spent a lof of money on my son'
+\bg. Ik heb veel geld aan hem uitgegeven.\\
+ I have much money on him spent\\
+ `I spent a lot of money on him.'
+\bg. *Ik heb \tbf{hem} veel geld aan uitgegeven.\\
+ I have him much money on spent\\
+ `I spent a lof of money on it.'\label{ex:hemaan}
+\z.
+\z.
+
+This has shown that \tit{er} is small, smaller than regular pronouns. So we go for this option:
+
+\begin{table}[ht]
+	\center
+	\caption {\tit{er} < \tit{'t}}
+	\begin{minipage}{0.27\linewidth}
+		\begin{tabularx}{\textwidth}{cccc}
+		\toprule
+    \tsc{a}   & \tsc{b}            & \tsc{c}   & \tsc{d}                           \\
+		\midrule
+    \multicolumn{2}{c}{\tit{met}}  & \multicolumn{2}{c}{\cellcolor{Gray}\tit{wat}} \\
+    \multicolumn{3}{c}{\tit{mee}}               & \cellcolor{Gray}{\tit{waar}}     \\
+    \bottomrule
+\end{tabularx}
+\end{minipage}
+\end{table}
+
+As a result of \tit{waar} being small, \tit{mee} becomes big. And \tit{mee} spells out more features than \tit{met}.
+
+Now the difference in distribution between \tit{met wat} and \tit{waarmee} is going to follow from spellout.
+If we get higher than dative case, we need prepositions.
+Making prepositions is a very 'costly' operation in the langauge, it is the last resort option in the spellout procedure.
+Dutch also has forms that are not only prepositions, but can also function as postpositions.
+They are less 'costly'.
+To avoid building a complex specifier, different spellout options are used.
+That is why we get the \tsc{r}-pronoun in the picture.
+\tsc{r}-pronouns can combine with these postpositions.
+
 Open issues:

### 2019-12-23 paper.tex
maandagmiddag
sectie 2 ook af, alleen nog 3

@@
 
-\begin{table}[ht]
+\begin{table}[ht]\label{tbl:distribution}
 	\center
@@
 \end{minipage}
-\end{table}\label{tbl:distribution}
+\end{table}
 
@@
  `I am painting together with her/him.'\label{ex:prepani}
-\bg. *Ik schilder met het.\\
- I paint with a brush\\
+\bg. *Ik schilder met 't.\\
+ I paint with it\\
  `I am painting with it.'\label{ex:prephet}
@@
 
-\begin{table}[ht]
+\begin{table}[ht]\label{tbl:inanimates}
 	\center
 	\caption {Inanimates in Dutch}
-	\begin{minipage}{0.45\linewidth}
+	\begin{minipage}{0.7\linewidth}
 		\begin{tabularx}{\textwidth}{ccc}
@@
 \end{minipage}
-\end{table}\label{tbl:inanimates}
+\end{table}
 
@@
 \bg. Ik schilder met de kwast [waar jij ook mee schildert].\\
- I paint with the brush {where with} you also paint\\
+ I paint with the brush where you also with paint\\
  `I am painting with the brush that you are painting with too.'\label{ex:const3}
@@
 The structure in \ref{ex:const3stage} represents a stage in the derivation of the embedded clauses in \ref{ex:const3} and \ref{ex:const4}.
-\footnote{I assume that the antecedent in a free relative is a phonologically empty element, in line with cf. \cite{bresnan1978a,groos1981,himmelreich2017}.}
+\footnote{I assume that the antecedent in a free relative is a phonologically empty element, in line with cf.
+\cite{bresnan1978a,groos1981,himmelreich2017}.
+Under that view, \ref{ex:const3} and \ref{ex:const4} are identical, except for that in \ref{ex:const4} modifies phonologically empty element.}
 Again, in the stage, which comes before relative movement of the pronoun to the left periphery of the relative clause, the PP forms a proper constituent.
@@
 
-\ref{ex:grammaticalwat} is not the only construction in which the string \tit{met wat} `with what' appears.
+The mismatching free relative in \ref{ex:grammaticalwat} is not the only construction in which the string \tit{met wat} `with what' appears.
 I give examples of two more occurrences in \ref{ex:moremetwat}.
@@
 
-insert the zero thingy there
-
-I repeat the example in which \tit{schildert} is in the embedded clause.
-
-\ex.
-\ag. Ik heb gekocht [waar jij mee schildert].\\
+I repeat the mismatching free relative in which \tit{waarmee} `met wat' appears in \ref{ex:mismatchwaarmee}.
+The predicate \tit{schildert} `paints' combines in the embedded clause with the instrumental PP.
+The PP forms a proper constituent within the embedded clause, and the PP can be realized as the \tsc{r}-pronoun \tit{waarmee} `with what'.\footnote{I assume that the embedded clause modifies a phonologically empty noun here which is the DP argument of \tit{gekocht} `bought'.}
+
+\exg. Ik heb gekocht [waar jij mee schildert].\\
  I have bought where you with paint\\
- `I bought what you are painting with.'
-\bg. Ik schilder met [wat jij hebt gekocht].\\
+ `I bought what you are painting with.'\label{ex:mismatchwaarmee}
+
+Next, we arrive at the mismatching free relative in which \tit{waarmee} `with what' cannot be used, but \tit{met wat} `with what' appears.
+The embedded clause predicate \tit{gekocht} `bought' combines with an accusative DP.
+The accusative object of a verb is always \tit{wat} `what', as I showed in \ref{ex:wat}.
+The instrumental PP only comes into the picture in the main clause, when \tit{schilder} `paint' combines with an instrumental PP.
+At no point in the derivation does the PP form a proper constituent, and \tit{waarmee} `with what' does not surface.
+
+\exg. Ik schilder met [wat jij hebt gekocht].\\
  I paint with what you have bought\\
- `I paint with what you bought.'
-
-\tit{Schildert} wants the instrumental PP, so the embedded clause looks like this.
-Here \tit{waar} and \tit{mee} are both part of the embedded clause.
-At a certain point in the derivation they formed a proper constituent, i.e.
-they formed a constituent without any other elements.
-
-Then in the main clause \tit{gekocht} is merged, which selects for an accusative object.
-Somehow \tit{waarmee} can satisfy that requirement.
-\tit{Schildert} wants the instrumental PP, so the embedded clause looks like this:
-
-\ex. [waar jij mee schildert]
-
-Here \tit{wat} is part of the embedded clause but \tit{met} is not.
-It belongs to the main clause.
-An embedded clause is finished before the main clause is built.
-At no point in the derivation can \tit{met} \tit{wat} form a proper constituent.
-
-In conclusion:
-
-\ex.
-\a. *[[met] [wat]] → [waarmee]
-\b. [met [wat X]]
+ `I paint with what you bought.'\label{ex:mismatchmetwat}
+
+\ref{ex:summaryconst} summarizes what I showed in this section.
+\tit{Met wat} `with what' can never surface when \tit{met} `with' and \tit{wat} `what' form a proper constituent.
+It always becomes \tit{waarmee} `with what'.
+This is schematically shown in \ref{ex:waarmeefr}.
+There are other contexts in which \tit{met wat} `with what' appears.
+This can be either when \tit{wat} `what' takes a complement, or when \tit{wat} is part of the a clause that \tit{met} `with' is not a part of.This last option is schematically showed in \ref{ex:metwatfr}, and it represents the mismatching free relative in \ref{ex:mismatchmetwat}.
+
+\ex.\label{ex:summaryconst}
+\a. *[[met] [wat]] → [waarmee]\label{ex:waarmeefr}
 \b. [met [wat [X]]]
-
-How do I connect constituency and different spellouts of the instrumental? Nano: only constituents can spell out.
-
-\section{Connecting constituency and spellout}
-
-Intro: why *\tit{met wat}? Not a filter, not a different paradigm.
-
-\subsection{Korean negation and causative}
-
-\subsection{nanostory of that}
-
-\subsection{waarmee = parallel}
+\b. [met [[wat] [X]]]\label{ex:metwatfr}
+
+This section showed that being a proper constituent is a necessary requirement for \tit{waarmee} `with what' to surface.
+The next section elaborates on how proper constituency and spellout relate to each other.
+
+\section{\tit{Waarmee} as suppletion}
+
+\tit{Met} `with' is a preposition that combines with full DPs and animate pronouns.
+\tit{Wat} `what' is a wh-element that appears as subject or object.
+There is no principled reason why \tit{met wat} `with what' should be ruled out.
+Previous work on \tsc{r}-pronoun has not given many insights, other than \citet{riemsdijk1978} postulating a filter that prohibits the existence of constituents consisting of prepositions and wh-elements or \citet{koopman2000} who makes reference to a different paradigm.
+
+In this section I start with showing a similar instance in which proper constituency and spellout go hand in hand.
+Then I show how these facts can be straightforwardly follow from the spellout algorithm in Nanosyntax.
+The section ends with showing how this logic can be applied to \tit{waarmee} `with what' and \tit{met wat} `with what'.
+
+In what follows I show another instance in which proper constituency influences spellout, suppletive negative forms in Korean as discussed in \citet{chung2007}.
+The point is that suppletion only goes through when the relevant features form a proper constituent, and not when an additional feature intervenes.
+
+Sentences in Korean can be negated by the two negative prefixes \tit{ani} or \tit{mos}, as shown in \ref{ex:koreannegation}.
+
+\ex.\label{ex:koreannegation}
+\ag. ca -n -ta\\
+ sleep -\tsc{pres} -\tsc{decl}\\
+ `is sleeping'
+\bg. mos/an(i) ca -n -ta\\
+ \tsc{neg} sleep -\tsc{pres} -\tsc{decl}\\
+ `cannot sleep / is not sleeping' \hfill \citep{chung2007}
+
+The verb \tit{al-} `know' does not combine with any of the negative markers, but it it uses the suppletive stem \tit{molu.\tsc{neg}}. This is illustrated in \ref{ex:koreanknow}.
+
+\ex.\label{ex:koreanknow}
+\ag. al -n -ta\\
+know \tsc{-pres} \tsc{-decl}\\
+`know(s)'
+\bg. *mos/*an(i) al -n -ta\\
+\tsc{neg} know -\tsc{pres} -decl\tsc{}\\
+\bg. molu -n -ta\\
+\tsc{neg}.know -\tsc{pres} -\tsc{decl}\\
+`do(es) not / cannot know'\label{ex:molu} \hfill \citep{chung2007}
+
+When \tit{al-} `know' is causativized before it is negated, the regular stem is used again, shown in \ref{ex:knowcausneg}.
+\ref{ex:molucaus} illustrates that the suppletive stem \tit{molu-} is no longer grammatical.
+
+\ex.
+\ag. al -li-\\
+ know -\tsc{caus}\\
+ `let know, inform'
+\bg. ani/ mos al -li -ess -ta\\
+ \tsc{neg} \tsc{neg} know -\tsc{caus} -\tsc{past} -\tsc{decl}\\
+ `did not /could not inform'\label{ex:knowcausneg}
+\bg. *molu -li -ess -ta\\
+ \tsc{neg}.know -\tsc{caus} -\tsc{past} -\tsc{decl}\\\label{ex:molucaus} \hfill \citep{chung2007}
+
+\citet{chung2007} points out that it cannot be phonological adjacency of the negation and \tit{al-} `know' that causes the suppletion in \ref{ex:molu}.
+The reason for that is that in \ref{ex:knowcausneg} \tit{al-} also follows the negation, but there is no suppletion.
+\citet{chung2007} suggests crucial difference has to do with in proper constituency.
+The structure of \ref{ex:molu} is given in \ref{ex:structuremolu}: Neg and \tit{al-} `know' form a proper constituent.
+\ref{ex:structurenegmolu} represents the structure of \ref{ex:knowcausneg}.
+Neg and \tit{al-} `know' no longer form a proper constituent, because \tsc{caus} is also part of the structure as the sister of \tit{al-} `know'.
+
+\ex.
+%%%
+\a. \begin{forest} boom
+[
+    [Neg]
+    [know]
+]
+\end{forest}\label{ex:structuremolu}
+\b. \begin{forest} boom
+[
+    [Neg]
+    [
+        [know]
+        [\tsc{caus}]
+    ]
+]
+\end{forest}\label{ex:structurenegmolu}
+
+\citet{caha2009} uses this pattern to argue in favor of a model with phrasal spellout rather than inserting phonology into terminal nodes, specifically Nanosyntax \citep{starke2009}.
+The idea is that the lexicon contains syntactic structures that are linked to a particular piece of phonology.
+If Korean has a lexical entry as in \ref{ex:entrymolu}, this can be inserted into the syntactic tree in \ref{ex:structuremolu}.
+
+\ex. \begin{forest} boom
+[
+    [Neg]
+    [know]
+]
+  {\draw (.east) node[right]{⇔ \tit{molu}}; }
+\end{forest}\label{ex:entrymolu}
+
+Important is in the insertion process is the Superset Principle.
+
+\ex. The Superset Principle \citet{starke2009}: \\
+A lexically stored tree matches a syntactic node iff the lexically stored tree contains the syntactic node.
+
+This ensures \ref{ex:entrymolu} is not inserted into the structure in \ref{ex:structurenegmolu}, as \tsc{caus} is contained in the syntactic structure but not in the structure in the lexicon in \ref{ex:entrymolu}.
+
+The same logic can be applied to \tit{waarmee} `with what' and \tit{met wat} `with what'.
+The preposition and wh-element together form a proper constituent, as in \ref{ex:structurewaarmee}, or the embedded CP of the relative clause is a sister of the wh-element, as in \ref{ex:structuremetwat}.
+
+\ex.
+\a. \begin{forest} boom
+[
+    [P]
+    [Wh]
+]
+\end{forest}\label{ex:structurewaarmee}
+%%
+\b. \begin{forest} boom
+[
+    [P]
+    [
+        [Wh]
+        [CP
+            [...,roof]
+        ]
+    ]
+]
+\end{forest}\label{ex:structuremetwat}
+
+Assume we have a lexical entry for \tit{waarmee} `met wat' that look as \ref{ex:entrywaarmee}.
+This entry can only be inserted into \ref{ex:structurewaarmee}, because the lexical structure matches the syntactic structure.
+It cannot be into \ref{ex:structuremetwat}, because the lexical structure does not contain the CP.
+
+\ex. \begin{forest} boom
+[
+    [InsP]
+    [WhP]
+]
+  {\draw (.east) node[right]{⇔ \tit{waarmee}}; }
+\end{forest}\label{ex:entrywaarmee}
+
+What I have shown in this section is how proper constituency relates to a change in phonology.
+However, this analysis missed numerous phonological properties of \tit{waarmee} `with what' and \tit{met wat} `with what', e.g.
+that they both contain the morpheme \tit{wa}.
+Under the suppletion analysis above, one can the phonological form of \tit{waarmee} could just as well be completely phonologically unrelated.
+The point of presenting the problem like this is to illustrate that the distribution between \tit{waarmee} `with what' and \tit{met wat} `with what' can be captured as a matter of spellout.
+
+In the next section I decompose \tit{waarmee} `with what' and \tit{met wat} `with what'. I show that both spell out the same set of features, but the distribution is different.
 
 \section{A finer decomposition}
+
+In this section I investigate the internal structure of \tit{waarmee} `with what' and \tit{met wat} `with what' to capture the phonological similarities between the two forms.
+
+\begin{table}[ht]
+	\center
+	\caption {\tit{met 't} and \tit{ermee}}
+	\begin{minipage}{0.56\linewidth}
+		\begin{tabularx}{\textwidth}{ccccccc}
+		\toprule
+    \tsc{wh}          & \tsc{deix}                         & \tsc{f}4   & \tsc{f}3 & \tsc{f}2  & \tsc{f}1                 & \tsc{thing}                 \\
+		\midrule
+    \multirow{2}{*}{w}  & \multirow{2}{*}{a}               & \tit{met}  & \multicolumn{4}{c}{\cellcolor{Gray}\tit{(ə)t}}                                \\
+                      &                                    & \multicolumn{4}{c}{\tit{mee}}                                & \cellcolor{Gray}\tit{(ə)r}  \\
+    \bottomrule
+\end{tabularx}
+\end{minipage}
+\end{table}
+
+The \tsc{r}-pronoun I focus on is the relative pronoun \tit{waarmee} `with what', which is interesting for two reasons.
+First, just like for all \tsc{r}-pronouns, the wh-element is the locative, but there is no meaning component related to location in `with what'.
+Second, the preposition \tit{met} `with' changes into \tit{mee} `with when it is combined with an \tsc{r}-pronoun.
+
+What we do not capture is:
+formal similarities between waarmee and met wat. I will talk about w, a. What I will not talk about it: mee and met
+why we see the locative. I will talk about that.
 
@@
 Or \tit{wat} realizes A, B and C and \tit{met} only realizes D.
-In both cases all features are expresses, but they are distributed differently, allowing for different realizations.\footnote{I did not address the ordering difference of the elements.
-Yes, this can lead to a difference in meaning.
-
-\ex.
+In both cases all features are expresses, but they are distributed differently, allowing for different realizations.
+\footnote{I did not address the ordering difference of the wh-element and the adposition.
+A topic related to (but not relevant for) this paper is the different positioning of identical adpositions in Dutch.
+In \ref{ex:dutchin}, \tit{in} changes meaning dependent on whether it procedes or follows the DP, it is respectively locational or directional.
+
+\ex.\label{ex:dutchin}
 \ag. Ik klim in de boom.\\
@@
  `I am climbing in the tree.'
-\bg. Ik klim de boom in\\
+\bg. Ik klim de boom in.\\
  I climb the tree in\\
@@
 
-Here, however, I will argue that the movement is driven by spellout and is meaningless.}
-
-\begin{table}[ht]
-	\center
-	\caption {Distribution options}
-	\begin{minipage}{0.27\linewidth}
-		\begin{tabularx}{\textwidth}{cccc}
-		\toprule
-    \tsc{a}   & \tsc{b}            & \tsc{c}   & \tsc{d}                           \\
-		\midrule
-    \multicolumn{2}{c}{\tit{met}}  & \multicolumn{2}{c}{\cellcolor{Gray}\tit{wat}} \\
-    \tit{mee} & \multicolumn{3}{c}{\cellcolor{Gray}\tit{waar}}                     \\
-    \multicolumn{3}{c}{\tit{mee}}               & \cellcolor{Gray}{\tit{waar}}     \\
-    \bottomrule
-\end{tabularx}
-\end{minipage}
-\end{table}
+The different positioning of the adpositions in \tsc{r}-pronouns is driven by spellout and is, therefore, meaningless.}
 
@@
 
-\begin{table}[ht]
-	\center
-	\caption {\tit{er} < \tit{'t}}
-	\begin{minipage}{0.27\linewidth}
-		\begin{tabularx}{\textwidth}{cccc}
-		\toprule
-    \tsc{a}   & \tsc{b}            & \tsc{c}   & \tsc{d}                           \\
-		\midrule
-    \multicolumn{2}{c}{\tit{met}}  & \multicolumn{2}{c}{\cellcolor{Gray}\tit{wat}} \\
-    \multicolumn{3}{c}{\tit{mee}}               & \cellcolor{Gray}{\tit{waar}}     \\
-    \bottomrule
-\end{tabularx}
-\end{minipage}
-\end{table}
-
-As a result of \tit{waar} being small, \tit{mee} becomes big. And \tit{mee} spells out more features than \tit{met}.
-
 Now the difference in distribution between \tit{met wat} and \tit{waarmee} is going to follow from spellout.
@@
 
-\begin{itemize}
-  \item I still need to incorporate \tit{a} and \tit{w}. They can either come before case or after it.
-  \item Right now I do not capture the formal similarity between \tit{met} and \tit{mee}. I have ideas about that:
-  \item Some adpositions do not change shape.
-They should be usable both as prepositions and postpositions.
-This should be reflected in their lexical entry.
-A prediction is that there exist adpositions that cannot be used as postpositions.
-Examples of that are: \tit{zonder}, \tit{midden}, \tit{sinds}, \tit{rond}, \tit{beneden}.
-\end{itemize}
-
-\section{Conclusion}
+ still need to incorporate \tit{a} and \tit{w}. They can either come before case or after it.
+
+\section{Conclusion and open issues}
+
+In the analysis laid out above it is a coincidence that \tit{mee} `with' and \tit{met} `with' look so much alike.
+
+Another topic I do not discuss is that in almost all cases the preposition does not change form when it combines with an \tsc{r}-pronoun, e.g.
+\tit{in}.
+If this proposal is on the right track, such elements can be used as either a prefix and as a suffix.
+A lexical entry as in \ref{ex:presuf} would be a candidate for such an element.
+
+\ex. \begin{forest} boom
+[XP
+    [XP
+        [X,roof]
+    ]
+    [YP
+        [Y]
+        [\phantom{x}]
+    ]
+]
+{\draw (.east) node[right]{⇔ \tit{in}}; }
+\end{forest}\label{ex:presuf}
+
+I leave it to future research to determine whether this is a feasible solution.
 

### 2019-12-23 paper.tex
maandagavond
halverwege laatste sectie, conclusie moet ook nog

@@
 
-\subsection{\tsc{R}-pronouns as default}
+\subsection{\tsc{R}-pronouns as default}\label{sec:rdefault}
 
@@
 
-Important is in the insertion process is the Superset Principle.
-
-\ex. The Superset Principle \citet{starke2009}: \\
-A lexically stored tree matches a syntactic node iff the lexically stored tree contains the syntactic node.
-
+Spellout targets only constituent \citep{starke2009}.
 This ensures \ref{ex:entrymolu} is not inserted into the structure in \ref{ex:structurenegmolu}, as \tsc{caus} is contained in the syntactic structure but not in the structure in the lexicon in \ref{ex:entrymolu}.
@@
 In this section I investigate the internal structure of \tit{waarmee} `with what' and \tit{met wat} `with what' to capture the phonological similarities between the two forms.
+First, I identify \tit{w-} and \tit{-a-} as morphemes that appear in both expressions.
+Putting these two aside, I concentrate on \tit{ermee} `with it' and \tit{met 't} `with it'.
+I decompose these two expressions further, and end up arguing for a picture as shown in Table \ref{tbl:nofeatures}.
+The elements \tit{w-} and \tit{-a-} express the same syntactic structure in both expressions.
+The elements \tit{met} and \tit{'t} together also express the same features as \tit{mee} and \tit{er} together, but the distribution differs.
+\tit{Met} expresses less structure than \tit{mee} and \tit{'t} expresses more structure than \tit{er}.
+It becomes clear that the \tit{er} in fact corresponds to the locative \tit{r} in Dutch.
 
@@
 	\center
-	\caption {\tit{met 't} and \tit{ermee}}
+	\caption {\tit{met wat} and \tit{waarmee}}
 	\begin{minipage}{0.56\linewidth}
@@
 		\toprule
-    \tsc{wh}          & \tsc{deix}                         & \tsc{f}4   & \tsc{f}3 & \tsc{f}2  & \tsc{f}1                 & \tsc{thing}                 \\
-		\midrule
-    \multirow{2}{*}{w}  & \multirow{2}{*}{a}               & \tit{met}  & \multicolumn{4}{c}{\cellcolor{Gray}\tit{(ə)t}}                                \\
-                      &                                    & \multicolumn{4}{c}{\tit{mee}}                                & \cellcolor{Gray}\tit{(ə)r}  \\
+    \phantom{\tsc{wh}}  & \phantom{\tsc{deix}}                    & \phantom{\tsc{f}4}  & \phantom{\tsc{f}3} & \phantom{\tsc{f}2}  & \phantom{\tsc{f}1}  & \phantom{\tsc{thing}} \\
+		%\midrule
+    \tit{w}   & \multicolumn{1}{|c|}{\tit{a}}  & \tit{met} & \multicolumn{4}{|c}{\tit{(ə)t}}                \\\hline
+    \tit{w}   & \multicolumn{1}{|c|}{\tit{a}}  & \multicolumn{4}{c|}{\tit{mee}}               & \tit{(ə)r}  \\
     \bottomrule
@@
 \end{minipage}
-\end{table}
-
-The \tsc{r}-pronoun I focus on is the relative pronoun \tit{waarmee} `with what', which is interesting for two reasons.
-First, just like for all \tsc{r}-pronouns, the wh-element is the locative, but there is no meaning component related to location in `with what'.
-Second, the preposition \tit{met} `with' changes into \tit{mee} `with when it is combined with an \tsc{r}-pronoun.
-
-What we do not capture is:
-formal similarities between waarmee and met wat. I will talk about w, a. What I will not talk about it: mee and met
-why we see the locative. I will talk about that.
-
-What I account for: w, a, why we see the locative
-
-What I don't: similarity between \tit{met} and \tit{mee}, that preps do not change form
-
-and i need to say something about the assumption i make for pronouns
-
-Van Riemsdijk said that R-pronouns are pronouns and they orginate in the complement of P.
-Due to \tsc{r}-movement they move to the spec of PP, and due to suppletion they change form, coincidentally to something identical to the locative.
-Full DPs cannot move to the spec of PP because they do not have access to that spec.
-
-I claim that this movement is not a special r-movement, but a movement driven by spellout. The suppletion also follows from the regular spellout algorithm, and it is the locative that is inserted.
-
-Koopman's account differ from Van Riemsdijk's in that she assumes \tsc{r}-pronouns obligatorily move to specPlace.
-The fact that locatives and \tsc{r}-pronouns are syncretic is not a surprise.
-They occur in the same structural configuration.
-
-Place does not make a lot of sense in \tit{waarmee}, because we do not have a place here.
-
-Abels says that this movement from the complement to the spec is not allowed.
-He argues that, instead, that R-words are base generated as the specifiers of distinguished class of zero-place prepositions.
-\tsc{r} is the complement of P and is subextracted from the complement of P (which is allowed, because it is subextraction and not extraction of it as a whole.)
-
-I agree with Abels in that \tit{r} is substracted from the complement of the preposition.
-However, I say that \tit{r} is actually the pronoun.
-What he refers to as an \tsc{r}-word is in Dutch \tit{w-aa-}, which I also assume is merged later.
-
-I do not care whether \tit{w-} and \tit{-a-} are merged before or after.
-
-WHY DOES MEE MOVE? I DO NOT KNOW.
-BUT IT DOES.
-AND SO DOES WAAR.
-waar maybe because it is remnant movement?
-
-start with \tit{met wat}.
-
---here taking xxx apart--
-
-\tit{'t} `it' from \ref{ex:entryt} can be used as subject, direct object and indirect object.
-
-\ex.
+\end{table}\label{tbl:nofeatures}
+
+Finally, I put everything together and show how \tit{waarmee} `with what' is inserted if all features form a constituent, and \tit{met wat} `with what' if this is not the case.
+
+\subsection{Taking everything apart}
+
+In this section I decompose \tit{waarmee} `with what' and \tit{met wat} `with what'.
+The idea is that both expessions realize the same features, and \tit{waarmee} `with what' takes precedence when all features form a constituent.
+The morphemes I distinguish in \tit{waarmee} `with what' are \tit{w-}, \tit{-aa-}, \tit{-r} and \tit{-mee}.
+Within \tit{met wat} `with what' I distinguish \tit{met}, \tit{w-}, \tit{-a-} and \tit{-t}.
+\ref{ex:decompose} shows this as well.
+
+\ex.\label{ex:decompose}
+\a. w -aa -r -mee
+\b. met w -a -t
+
+Let me start with the morphemes \tit{w-} and \tit{-a-} that appear in both expressions.
+Exactly because they appear in both expression, I do not pay much attention to them.
+For \tit{w-} I follow \citet{hachem2015} in that \tit{w-} realizes a WP.
+
+\ex. \begin{forest}
+[WP
+    [W, roof]
+]
+{\draw (.east) node[right]{⇔ \tit{w}}; }
+\end{forest}\label{ex:entryw}
+
+The morpheme \tit{-a-} expresses deixis.
+Dutch distinguishes between proximal by using \tit{-ie-/-i-} and distal by using \tit{-aa-/-a-}, illustrated in \ref{ex:deixis}.
+I assume that lengthening or shortening of the vowel is a result of the final \tit{r}.
+
+\ex.\label{ex:deixis}
+\ag. h-ie-r\\
+ here\\
+\bg. d-aa-r\\
+ there\\
+\bg. d-i-t\\
+ this\\
+\bg. d-a-t\\
+ that\\
+ \z.
+
+In combination with wh-elements, the distal marker \tit{-a-} is used. For the purpose of this paper I simply let \tit{-a-} correspond to \tsc{deixP}.
+
+\ex. \begin{forest}
+[deixP
+    [deix, roof]
+]
+{\draw (.east) node[right]{⇔ \tit{a}}; }
+\end{forest}\label{ex:entrya}
+
+I put \tit{w-} and \tit{-a-} aside for now, assuming they spell out the same syntactic structure in \tit{waarmee} `with what' and \tit{met wat} `with what'.
+This leaves \tit{er-mee} `with it' and \tit{met 't} `with it'.\footnote{\tit{'rmee} `with it' is often precdeded by an /ε/, which I assume to be for phonological reasons.}
+
+\ex.
+\ag. (e)r -mee\\
+there with\\
+\b. met 't\\
+with it\\
+
+I repeat the examples from Section \ref{sec:rdefault} below that show that \tit{ermee} `with it' is used when it forms a proper constituent and \tit{met 't} `with it' is ungrammatical.
+
+\ex.
+\ag. Ik schilder er-mee.\\
+ I paint there-with\\
+ `I am painting with it.'\label{ex:jarmee}
+\bg. *Ik schilder met 't.\\
+ I paint with it\\
+ `I am painting with it.'\label{ex:neemett}
+
+In other words, both expessions realize the same features, and \tit{ermee} `with it' takes precedence when all features form a constituent.
+
+Let me continue with specifying the lexical entries for \tit{met 't} `with it'. \tit{'t} `it' can be used as subject, direct object and indirect object, as shown in \ref{ex:tsubobj}.
+
+\ex.\label{ex:tsubobj}
 \ag. 't Staat in de hal.\\
@@
 
- Pronouns in other genders alternate between nominative (non-oblique) and accusative/dative (oblique) in these contexts.
-
- \ex.
+Pronouns in other genders alternate between nominative (non-oblique) and accusative/dative (oblique) in these contexts, illustrated in \ref{ex:hemsubobj}.
+
+\ex.\label{ex:hemsubobj}
 \ag. Hij staat in de hal.\\
@@
 
+I assume that the inanimate personal pronoun minimally contains the ontological category \tsc{thing} \citep{kayne2005}.
+I leave possible number and gender features out because they do not play a role in this paper.
+For case, I follow \citet{caha2009} that case features case features are organized the containment relation in \ref{ex:casetree}.
+The higher, more complex cases contain the smaller, less complex cases.
+
+\ex. \label{ex:casetree}
+\begin{forest} boom
+[\tsc{comP}
+    [\tsc{f5}]
+    [\tsc{insP}
+        [\tsc{f4}]
+        [\tsc{datP}
+            [\tsc{f3}]
+            [\tsc{accP}
+                [\tsc{f2}]
+                [\tsc{nomP}
+                    [\tsc{f1}]
+                    [DP]
+                ]
+            ]
+        ]
+    ]
+]
+\end{forest}
+
+The morpheme \tit{'t} can act as nominative, accusative and dative, as I showed in \ref{ex:tsubobj}. Taking this all together, \tit{'t} should have the lexical entry given in \ref{ex:entryt}.
+
 \ex. \begin{forest} boom
@@
 
-\tit{Er} can be used as a locative.
-
-\exg. Ik ben er al geweest.\\
-I am there already been\\
-`I have already been there.'
-
-\ex. \begin{forest} boom
-[\tsc{loc}P
-[\tsc{location}]
-    [\tsc{thngP}
-        [\tsc{thing}, roof]
-    ]
-]
-{\draw (.east) node[right]{⇔ \tit{(ə)r}}; }
-\end{forest}\label{ex:entryr}
-
-\tit{Met} can be used for as instrumental or comitative.
+This lexical entry can lexicalize the \tsc{datP}, but also the \tsc{accP} and \tsc{nomP}. This is due to the Superset Princple.
+
+ \ex. The Superset Principle \citet{starke2009}: \\
+ A lexically stored tree matches a syntactic node iff the lexically stored tree contains the syntactic node.
+
+In other words, a lexically stored structure does not have to be identical to the syntactic structure. It is enough if the syntactic structure is contained in the lexically stored tree.
+
+\tit{Met} `with' can be used for as instrumental or comitative, as shown in \ref{ex:metinscom}.
 
@@
  I dance with him\\
- `I am dancing with him.'
+ `I am dancing with him.'\label{ex:metinscom}
+
+Again, due to the superset principle, \tit{met} `with' can be used for comitative and as instrumental case. It combines with the dative, so the lowest feature is \tsc{f4}.
 
@@
 
-Either way, it combines with accusative/dative (oblique), which can be seen on the pronouns.
-But only for the comitative, because for the instrumental we are getting an ʀ-pronoun.
-Full DPs do not show any marking, leading me to postulate the zero marker up to the dative.
-
-\ex.
-\ag. Ik dans met de man.\\
- I dance with the man\\
- `I am dancing with the man.'
-\bg. Ik schilder met een kwast.\\
- I paint with een brush\\
- `I am painting with een brush.'
-
-\ex. \begin{forest} boom
-[\tsc{datP}
-   [\tsc{f}3]
-   [\tsc{acc}P
-       [\tsc{f}2]
-       [\tsc{nom}P
-           [\tsc{f}1]
-           [\phantom{x}]
-       ]
-   ]
-]
-{\draw (.east) node[right]{⇔ \tit{∅}}; }
-\end{forest}
-
-So \tit{met} expresses \tsc{f}4, and \tit{(ə)r} expresses \tsc{thing} and \tsc{f}1 to \tsc{f}1.
+-------
+now we get to \tit{er-mee}. they have to be able to lexicalize the same features as in \tit{met 't}.
+-----
+
+ \tit{Er} `there' can be used as a locative.
+
+ \exg. Ik ben er al geweest.\\
+ I am there already been\\
+ `I have already been there.'
+
+I follow \cite{baunaz2018} in assuming that the ontological category \tsc{location} contains \tsc{thing}.\footnote{\citet{baunaz2018} place in addition \tsc{person} between \tsc{thing} and \tsc{location}, which I left out here.}
+
+ \ex. \begin{forest} boom
+ [\tsc{loc}P
+ [\tsc{location}]
+     [\tsc{thngP}
+         [\tsc{thing}, roof]
+     ]
+ ]
+ {\draw (.east) node[right]{⇔ \tit{(ə)r}}; }
+ \end{forest}\label{ex:entryr}
+
+So \tit{met} expresses \tsc{f}4 and \tsc{f5}, and \tit{(ə)r} expresses \tsc{thing} and \tsc{f}1 to \tsc{f}3.
 \tit{(ə)r} only expresses \tsc{thing}.
-\tit{Ermee} and \tit{met 't} express the same features, which leaves \tsc{f}1 to \tsc{f}4 for \tit{mee}.
-
-\begin{table}[ht]
-	\center
-	\caption {\tit{met 't} and \tit{ermee}}
-	\begin{minipage}{0.38\linewidth}
-		\begin{tabularx}{\textwidth}{ccccc}
-		\toprule
-    \tsc{f}4   & \tsc{f}3 & \tsc{f}2  & \tsc{f}1                 & \tsc{thing}                 \\
-		\midrule
-    \tit{met}  & \multicolumn{4}{c}{\cellcolor{Gray}\tit{(ə)t}}                                \\
-    \multicolumn{4}{c}{\tit{mee}}                                & \cellcolor{Gray}\tit{(ə)r}  \\
-    \bottomrule
-\end{tabularx}
-\end{minipage}
-\end{table}
+\tit{Ermee} and \tit{met 't} express the same features, which leaves \tsc{f}1 to \tsc{f}5 for \tit{mee}.
+
+And! Nanosyntax encodes the difference between prefixes and suffixes by the difference in the shape of the lexical tree. \tit{-mee} follows \tit{er}, so I am going to call it a suffix. So:
 
@@
 
-\tit{a}/\tit{aa} is distal, \tit{ie}/\tit{i} is proximal. Medial?
-
-\ex.
-\ag. h-ie-r\\
- here\\
- `here'
-\bg. d-aa-r\\
- there\\
- `there'
-\bg. d-i-t\\
- this\\
- `this'
-\bg. d-a-t\\
- that\\
- `that'
-\z.
-\z.
-
-\ex. \begin{forest}
-[WP
-    [W, roof]
-]
-{\draw (.east) node[right]{⇔ \tit{w}}; }
-\end{forest}\label{ex:entryw}
-
-WP is the interrogative/wh, whatever.
-
-\ex. \begin{forest}
-[\tsc{distP}
-    [\tsc{deix3}]
-    [\tsc{medP}
-        [\tsc{deix2}]
-        [\tsc{deix1}]
-    ]
-]
-{\draw (.east) node[right]{⇔ \tit{a}}; }
-\end{forest}\label{ex:entrya}
-\z.
-
-\section{Derivation}
+\begin{table}[ht]
+	\center
+	\caption {\tit{met wat} and \tit{waarmee}}
+	\begin{minipage}{0.56\linewidth}
+		\begin{tabularx}{\textwidth}{ccccccc}
+		\toprule
+    \phantom{\tsc{wh}}  & \phantom{\tsc{deix}}                    & \phantom{\tsc{f}4}  & \phantom{\tsc{f}3} & \phantom{\tsc{f}2}  & \phantom{\tsc{f}1}  & \phantom{\tsc{thing}} \\
+		%\midrule
+    \tit{w}   & \multicolumn{1}{|c|}{\tit{a}}  & \tit{met} & \multicolumn{4}{|c}{\tit{(ə)t}}                \\\hline
+    \tit{w}   & \multicolumn{1}{|c|}{\tit{a}}  & \multicolumn{4}{c|}{\tit{mee}}               & \tit{(ə)r}  \\
+    \bottomrule
+\end{tabularx}
+\end{minipage}
+\end{table}\label{tbl:nofeatures}
+
+% I do not care whether \tit{w-} and \tit{-a-} are merged before or after.
+%
+% WHY DOES MEE MOVE? I DO NOT KNOW.
+% BUT IT DOES.
+% AND SO DOES WAAR.
+% waar maybe because it is remnant movement?
+%
+%
+%
+% Either way, it combines with accusative/dative (oblique), which can be seen on the pronouns.
+But only for the comitative, because for the instrumental we are getting an ʀ-pronoun.
+Full DPs do not show any marking, leading me to postulate the zero marker up to the dative.
+%
+% \ex.
+% \ag. Ik dans met de man.\\
+%  I dance with the man\\
+%  `I am dancing with the man.'
+% \bg. Ik schilder met een kwast.\\
+%  I paint with een brush\\
+%  `I am painting with een brush.'
+%
+% \ex. \begin{forest} boom
+% [\tsc{datP}
+%    [\tsc{f}3]
+%    [\tsc{acc}P
+%        [\tsc{f}2]
+%        [\tsc{nom}P
+%            [\tsc{f}1]
+%            [\phantom{x}]
+%        ]
+%    ]
+% ]
+% {\draw (.east) node[right]{⇔ \tit{∅}}; }
+% \end{forest}»
+
+\subsection{Putting it back together}
 
 Spellout
+
+\ex. The Elsewhere Condition (\citealt{kiparsky1973}, formulated as in \citealt{caha2020}):\\
+When two entries can spell out a given node, the more specific entry wins. Under the Superset Principle governed insertion, the more specific entry is the one which has fewer unused features
+
+Spellout algorithm \citep{starke2018}
 
@@
 
-\ex. Cyclic Override\\
+\ex. Cyclic Override \citep{starke2018}:\\
 Lexicalisation at a node XP overrides any previous match at a phrase contained in XP.
 
-\ex. Backtracking\\
+\ex. Backtracking \citep{starke2018}:
 When spellout fails, go back to the previous cycle, and try the next option for that cycle.
+
+\ex. Spec Formation \citep{starke2018}:\\
+If Merge F has failed to spell out (even after backtracking), try to spawn a new derivation providing the feature F and merge that with the current derivation, projecting the feature F at the top node.
 
@@
 
-\section{Connecting \tit{wat} to \tit{waar} and \tit{met} to \tit{mee}}
-
-So, \tit{waarmee} and \tit{met wat} realize the same features but their spellouts differ.
-
-\ex.
-\ag. Ik heb gekocht [waar jij mee schildert].\\
- I have bought where you with paint\\
- `I bought what you are painting with.'
-\bg. Ik schilder met [wat jij hebt gekocht].\\
- I paint with what you have bought\\
- `I paint with what you bought.'
-
-A few things should be noted here.
-First, position of the elements: the regular pronoun follows the adposition and the ʀ-pronoun precedes the preposition.
-Second, the shape of the wh-pronoun: the ʀ-pronoun differs from the non-ʀ-pronoun in the lengthening of the vowel that the final consonant is \tit{r}.
-Third, the shape of the adposition: \tit{met} and \tit{tot} change in \tit{mee} and \tit{toe} when they combine with ʀ-pronouns.
-
-Now let's look at it like this: \tit{waarmee} realizes particular features.
-Say \tit{waar} expresses A and B and \tit{mee} expresses C and D.
-Say, A B C and D.
-\tit{met wat} realizes the same features.
-Saying that \tit{wat} also realizes A and B and \tit{met} also C and D misses the point of having different realizations.
-So instead, say \tit{wat} only realizes A and \tit{met} realizes B, C and D.
-Or \tit{wat} realizes A, B and C and \tit{met} only realizes D.
-In both cases all features are expresses, but they are distributed differently, allowing for different realizations.
-\footnote{I did not address the ordering difference of the wh-element and the adposition.
+I did not address the ordering difference of the wh-element and the adposition.
 A topic related to (but not relevant for) this paper is the different positioning of identical adpositions in Dutch.
@@
 
-The different positioning of the adpositions in \tsc{r}-pronouns is driven by spellout and is, therefore, meaningless.}
-
-I will argue for the last option, that \tit{met} spells out fewer features than \tit{mee}.
-The main argument for that comes from the fact that Dutch is a non-preposition stranding language, so prepositions cannot be moved out of the PP.
-Also, you cannot move the complement of a P to its spec, but you can subextract from them (Abels).
-And I show that ʀ-pronouns behave like clitic in how high they move.
-
-In a nutshell, if all features are merged at once, we will always get an ʀ-pronoun.
-Due to spellout driven movement the ʀ-pronoun strands the features to be realizes by a preposition and a little more.
-The ʀ-pronoun is a clitic and moves high.
-The preposition + a little more realizes as \tit{mee} in case of \tit{waarmee}.
-Now if the features are not merged all at once, the regular spellout driven movements cannot take place, and we see \tit{met wat}.
+The different positioning of the adpositions in \tsc{r}-pronouns is driven by spellout and is, therefore, meaningless.
+
+\section{Conclusion and discussion}
+
 So, the answer of how constituency connects to change in phonological form lies in one of the core assumptions of nanosyntax: phrasal spellout spells out constituents.
 
-\ex.
-\a. \tit{waar} = w + a + r
-\b. \tit{wat} = w + a + t
-
-So the difference betwween \tit{t} and \tit{r} was actually the only difference we need to account for.
-
-Dutch is a non P-stranding language.
-
-\ex.
-\ag. Met wie heb jij gedanst?\\
- with who have you danced\\
- `Whom did you dance with?'
-\bg. *Wie heb jij gedanst met?\\
- who have you danced with\\
- `Whom did you dance with?'
-
-Abels shows that extraction from a PP is not categorically excluded. It happens in Slavic.
-
---examples here--
-
-What if ʀ-pronouns are actually clitic? And they pattern with Slavic in that they clitic can never follow Ps.
-
-Do we have more reasons to believe that ʀ-pronouns are clitics?
-The non-wh ʀ-pronouns in Dutch are able to move very high, just like clitics and unlike regular pronouns in Dutch.\footnote{\ref{ex:hemaan} can also be excluded by saying that \tit{aan} and \tit{hem} cannot split.}
-
-\ex.
-\ag. Ik heb veel geld aan de badkamer uitgegeven.\\
- I have much money on the bathroom spent\\
- `I spent a lot of money on the bathroom.'
-\bg. Ik heb er veel geld aan uitgegeven.\\
- I have there much money on spent\\
- `I spent a lof of money on it.'
-
-\ex.
-\ag. Ik heb veel geld aan mijn zoon uitgegeven.\\
- I have much money on my son spent\\
- `I spent a lof of money on my son'
-\bg. Ik heb veel geld aan hem uitgegeven.\\
- I have much money on him spent\\
- `I spent a lot of money on him.'
-\bg. *Ik heb \tbf{hem} veel geld aan uitgegeven.\\
- I have him much money on spent\\
- `I spent a lof of money on it.'\label{ex:hemaan}
-\z.
-\z.
-
-This has shown that \tit{er} is small, smaller than regular pronouns. So we go for this option:
+Just like Abels said: no preposition stranding, but extraction from the PP is ok!
+
+Van Riemsdijk said that R-pronouns are pronouns and they orginate in the complement of P.
+Due to \tsc{r}-movement they move to the spec of PP, and due to suppletion they change form, coincidentally to something identical to the locative.
+Full DPs cannot move to the spec of PP because they do not have access to that spec.
+
+I claim that this movement is not a special r-movement, but a movement driven by spellout. The suppletion also follows from the regular spellout algorithm, and it is the locative that is inserted.
+
+Koopman's account differ from Van Riemsdijk's in that she assumes \tsc{r}-pronouns obligatorily move to specPlace.
+The fact that locatives and \tsc{r}-pronouns are syncretic is not a surprise.
+They occur in the same structural configuration.
+
+Place does not make a lot of sense in \tit{waarmee}, because we do not have a place here.
+
+Abels says that this movement from the complement to the spec is not allowed.
+He argues that, instead, that R-words are base generated as the specifiers of distinguished class of zero-place prepositions.
+\tsc{r} is the complement of P and is subextracted from the complement of P (which is allowed, because it is subextraction and not extraction of it as a whole.)
+
+I agree with Abels in that \tit{r} is substracted from the complement of the preposition.
+However, I say that \tit{r} is actually the pronoun.
+What he refers to as an \tsc{r}-word is in Dutch \tit{w-aa-}, which I also assume is merged later.
 
@@
 
-Open issues:
-
- still need to incorporate \tit{a} and \tit{w}. They can either come before case or after it.
-
-\section{Conclusion and open issues}
+Open ends
 
@@
         [Y]
-        [\phantom{x}]
     ]
@@
 
+still need to incorporate \tit{a} and \tit{w}. They can either come before case or after it.
+
 \printbibliography

### 2019-12-24 paper.tex
dinsdagochtend
en nu naar jan!

@@
 I put \tit{w-} and \tit{-a-} aside for now, assuming they spell out the same syntactic structure in \tit{waarmee} `with what' and \tit{met wat} `with what'.
-This leaves \tit{er-mee} `with it' and \tit{met 't} `with it'.\footnote{\tit{'rmee} `with it' is often precdeded by an /ε/, which I assume to be for phonological reasons.}
+This leaves \tit{er-mee} `with it' and \tit{met 't} `with it'.\footnote{\tit{'rmee} `with it' is often precdeded by an /ε/, which I assume to be for phonological reasons.
+The vowel can be dropped under the right phonological circumstances.
+
+\exg. Ik heb 'r niks mee te maken.\\
+ I have there nothing with to do\\
+ `I have nothing to do with it.'
+ \z.
+
+\phantom{x}
+}
 
@@
                     [\tsc{f1}]
-                    [DP]
+                    [DP
+                        [...,roof]
+                    ]
                 ]
@@
 
-In other words, a lexically stored structure does not have to be identical to the syntactic structure. It is enough if the syntactic structure is contained in the lexically stored tree.
-
-\tit{Met} `with' can be used for as instrumental or comitative, as shown in \ref{ex:metinscom}.
+In other words, a lexically stored structure does not have to be identical to the syntactic structure.
+It is enough if the syntactic structure is contained in the lexically stored tree.
+This has a as consequence that the lexical entry in \ref{ex:entryt} can also be inserted in \ref{ex:tacc} and \ref{ex:tnom}.
+
+\ex.
+\a. \begin{forest} boom
+[\tsc{acc}P
+    [\tsc{f}2]
+    [\tsc{nom}P
+        [\tsc{f}1]
+        [\tsc{thingP}
+            [\tsc{thing}, roof]
+        ]
+    ]
+]
+\end{forest}\label{ex:tacc}
+\b. \begin{forest} boom
+[\tsc{nom}P
+    [\tsc{f}1]
+    [\tsc{thingP}
+        [\tsc{thing}, roof]
+    ]
+]
+\end{forest}\label{ex:tnom}
+
+Continuing with \tit{met} `with', which I have shown in this paper can be used to express instrumental. It can also be used as comitative, as shown in \ref{ex:metinscom}.
 
@@
 
-Again, due to the superset principle, \tit{met} `with' can be used for comitative and as instrumental case. It combines with the dative, so the lowest feature is \tsc{f4}.
+Case features are in a containment relation and instrumental contains all case features down to \tsc{f1}.
+Some of these features are expressed by the preposition, and other by the DP they combine with.
+As pronouns in Dutch can realize up to \tsc{f3}, the preposition starts from \tsc{f4}.
 
@@
      [\tsc{f}5]
-     [\tsc{ins}P
-         [\tsc{f}4, roof]
-     ]
+     [\tsc{f}4]
  ]
@@
 
--------
-now we get to \tit{er-mee}. they have to be able to lexicalize the same features as in \tit{met 't}.
------
+In sum, the syntactic structure that \tit{met wat} `with what' realizes is the one in \ref{ex:stmetwat}.
+
+ ex. [ [ [ [ \tsc{thing} ] \tsc{f1} ] \tsc{f2} ] \tsc{f3} \tsc{f4} ]\label{ex:stmetwat}
+
+Let us now turn to \tit{ermee} `with it', which lexicalizes the same structure as \tit{met 't} `with it', but with a different distribution.
 
@@
 
-So \tit{met} expresses \tsc{f}4 and \tsc{f5}, and \tit{(ə)r} expresses \tsc{thing} and \tsc{f}1 to \tsc{f}3.
-\tit{(ə)r} only expresses \tsc{thing}.
-\tit{Ermee} and \tit{met 't} express the same features, which leaves \tsc{f}1 to \tsc{f}5 for \tit{mee}.
-
-And! Nanosyntax encodes the difference between prefixes and suffixes by the difference in the shape of the lexical tree. \tit{-mee} follows \tit{er}, so I am going to call it a suffix. So:
+Via the superset principle, \tit{er} can be used to realize the feature \tsc{thing} as well, as it is contained in \tsc{locP}.
+
+So far, \tit{er} `there' only realizes the feature \tsc{thing} from the structure in \ref{ex:stmetwat}.
+This leaves \tit{f1} to \tsc{f4} to be realized by \tit{-mee}.
+I give the lexical tree in \ref{ex:entrymee}.
 
@@
                     [\tsc{f}1]
-                    [\phantom{x}]
                 ]
@@
 {\draw (.east) node[right]{⇔ \tit{mee}}; }
-\end{forest}\label{ex:entrymee1}
+\end{forest}\label{ex:entrymee}
+
+Note that there are two differences between the lexical entry in \ref{ex:entrymet} and \ref{ex:entrymee}.
+First, the lexical entry for \tit{mee} `with' in \ref{ex:entrymee}, in addition to the one for \tit{met} `with' in \ref{ex:entrymet}, contains the features \tsc{f1}, \tsc{f2} and \tsc{f3}.
+Second, the lexical entry in \ref{ex:entrymet} has a binary bottom, and the lexical entry in \ref{ex:entrymee} has a unary bottom.
+Nanosyntax distinguishes prefixes and suffixes by distinguishing these types of lexical entries.
+This is the crucial differences needed for the Dutch instrumental.
+\tit{Met} `with' is a prefix (preposition), so it has a binary bottom, and \tit{-mee} `with' is a suffix, so it needs a unary bottom. In the next section I show how this works in a derivation.
+\footnote{For completeness, \tit{mee} `with' has to be blocked from combining with full DPs and animate pronouns (reference).
+For now I assume that these pronouns spell out an additional feature \tit{σ} that is not realized by \tit{mee} `with' but only by \tit{met} `with'.
+Full DPs combine in addition with a zero marker for dative case.
+This way \tit{mee} `with' does not compete with \tit{met} `anymore'.
+I left this features out in this paper, at is does not contribute to the main point.}
+\footnote{Giving \tit{met} `with' and \tit{mee} `with' two distinct lexical entries has as a consquence that the phonological overlap between them seems like a coincidence.
+I leave it for future research to capture this observation.}
+\footnote{I do not address the ordering difference of the wh-element and the adposition.
+A topic related to (but not relevant for) this paper is the different positioning of identical adpositions in Dutch.
+In \ref{ex:dutchin}, \tit{in} changes meaning dependent on whether it procedes or follows the DP, it is respectively locational or directional.
+
+\ex.\label{ex:dutchin}
+\ag. Ik klim in de boom.\\
+ I climb in the tree\\
+ `I am climbing in the tree.'
+\bg. Ik klim de boom in.\\
+ I climb the tree in\\
+ `I am climbing into the tree.'
+
+The different positioning of the adpositions in \tsc{r}-pronouns is driven by spellout and is, therefore, meaningless.
+However, the topic might be related.
+In almost all cases the preposition does not change form when it combines with an \tsc{r}-pronoun, e.g.
+\tit{in}.
+If this proposal is on the right track, such elements can be used as either a prefix and as a suffix.
+A lexical entry as in \ref{ex:presuf} would be a candidate for such an element.
+
+\ex. \begin{forest} boom
+[XP
+    [XP
+        [X,roof]
+    ]
+    [YP
+        [Y]
+    ]
+]
+{\draw (.east) node[right]{⇔ \tit{in}}; }
+\end{forest}\label{ex:presuf}
+
+I leave it to future research to determine whether this is a feasible solution.}
+
+Table \ref{tbl:withfeatures} gives an overview of the distribution of the features in \tit{met wat} `with what' and \tit{waarmee} `with what'.
+In both cases, \tit{w-} and \tit{-a-} are the realization of the same morpheme.
+The difference between the two expressions lies in the distribution of the case features.
+\tit{Mee} `with' realizes all of them, and \tit{met} `with' only the top two.
+The residues are realized by respectively \tit{er} `there' and \tit{'t} `it'.
 
@@
 		\toprule
-    \phantom{\tsc{wh}}  & \phantom{\tsc{deix}}                    & \phantom{\tsc{f}4}  & \phantom{\tsc{f}3} & \phantom{\tsc{f}2}  & \phantom{\tsc{f}1}  & \phantom{\tsc{thing}} \\
-		%\midrule
+    \tsc{wh}  & \tsc{deix}                     & \tsc{f}4  & \tsc{f}3 & \tsc{f}2  & \tsc{f}1  & \tsc{thing} \\
+		\midrule
     \tit{w}   & \multicolumn{1}{|c|}{\tit{a}}  & \tit{met} & \multicolumn{4}{|c}{\tit{(ə)t}}                \\\hline
@@
 \end{minipage}
-\end{table}\label{tbl:nofeatures}
+\end{table}\label{tbl:withfeatures}
+
+In the next section I put all features back together in a derivation and I show how \tit{waarmee} `with what' surfaces when all features form a constituent.
+\tit{Met wat} `with what' appears when the functional sequence is disrubted.
 
@@
 
-Spellout
+Before I show that \tit{waarmee} `with what' is used when all features form a proper constituent, I need to make some assumptions about the spellout process in Nanosyntax explicit.
+
+First of all, when two lexical entries are both candicates for spellout, the most specific is inserted, following the Elsewhere Condition:
 
@@
 
-Spellout algorithm \citep{starke2018}
-
-\ex. Merge F and
+Second, spellout happens in a cyclic derivation, following a spellout algorithm \citep{starke2018}.
+After each instance of merge, spellout takes place.
+If no spellout exist for the phrase created by the newly added feature, evacuations movements specified in the spellout algorithm take place.
+The algorithm is given in \ref{ex:spellout}.
+
+\ex. Merge F and \label{ex:spellout}
  \a. Spell out FP
@@
 
+When a new match is found, it overrides previous spellouts.
+
 \ex. Cyclic Override \citep{starke2018}:\\
@@
 
+If the spellout procedure in \ref{ex:spellout} fails, backtracking takes place.
+
 \ex. Backtracking \citep{starke2018}:
@@
 
+If backtracking also does not help, a specifier is constructed.
+
 \ex. Spec Formation \citep{starke2018}:\\
@@
 
-The functional sequence of \tit{ermee}.
-
-\ex. \tsc{f}4 > \tsc{f}3 > \tsc{f}2 > \tsc{f}1 > \tsc{thing}
-
-We start with \tsc{thing}. This is realized as \tit{(ə)r}, because it has less junk than \tit{(ə)t}.
+With this theoretical background in the back of our minds, we can turn to the derivation.
+I first show how \tit{ermee} `with it' is constructed.
+I leave out \tit{w-} and \tit{-a-}, because it unnessisarily complicates the story.
+\footnote{I assume the actual functional sequence to be \ref{ex:fseq}.
+
+\ex. [ [ [ [ [ [ \tsc{thing} ] \tsc{deix} ] W ] \tsc{f1} ] \tsc{f2} ] \tsc{f3} \tsc{f4} ]\label{ex:fseq}
+\z.
+
+\phantom{x}
+
+}
+
+We start with \tsc{thing}.
+The two candidates here are \ref{ex:entryt} and \ref{ex:entryr}.
+Following the Elsewhere Condition, \ref{ex:entryr} wins the competition because it contains less unused material.
 
@@
  ]
-{\draw (.east) node[right]{⇔ \tit{(ə)r}}; }
-\end{forest}
-
-\tsc{f}1 is merged. \tit{(ə)r} is no longer a candidate, but \tit{(ə)t} is. So the spellout is overridden.
-
-\ex. \begin{forest} boom
-[\tsc{nom}P
-   [\tsc{f}1]
-   [\tsc{thingP}
-       [\tsc{thing}, roof]
-   ]
-]
-{\draw (.east) node[right]{⇔ \tit{(ə)t}}; }
-\end{forest}
-
-\tsc{f}2 is merged, which can still be realizd by \tit{(ə)t}.
+{\draw (.east) node[right]{⇒ \tit{(ə)r}}; }
+\end{forest}\label{ex:thingspellout}
+
+In the next step, \tsc{f}1 is merged.
+\ref{ex:entryr} is no longer a candidate because it does not contain \tsc{f1}.
+\ref{ex:entryt} still is a candidate, because it contains all features in \ref{ex:thingf1}.
+The spellout is overridden and the structure is realized as \tit{'t}.
+
+\ex. \begin{forest} boom
+[\tsc{nom}P
+   [\tsc{f}1]
+   [\tsc{thingP}
+       [\tsc{thing}, roof]
+   ]
+]
+{\draw (.east) node[right]{⇒ \tit{(ə)t}}; }
+\end{forest}\label{ex:thingf1}
+
+Then \tsc{f}2 is merged. This structure can still be realizd by \tit{'t}.
 
@@
 ]
-{\draw (.east) node[right]{⇔ \tit{(ə)t}}; }
+{\draw (.east) node[right]{⇒ \tit{(ə)t}}; }
 \end{forest}
 
-Idem for \tsc{f}3.
+In the next step \tsc{f3} is merged, the structure is still spelled out as \tit{'t}.
 
@@
 ]
-{\draw (.east) node[right]{⇔ \tit{(ə)t}}; }
+{\draw (.east) node[right]{⇒ \tit{(ə)t}}; }
 \end{forest}
 
-Now \tsc{f}4 is merged. No candidate for phrasal spellout, no candidate after complement movement.
+Then \tsc{f4} is merged, as shown in \ref{ex:f4no}.
+\ref{ex:entryt} can no longer spell the structure out, because it does not contain \tsc{f4}.
+Moreover, there is no candidate to spell out the structure as it is, so evacuation movement takes place.
+According to the spellout algorithm, the first evacuation movement to be tried is spec-to-spec movement.
+However, there is no specfier in this structure, so this does not apply.
+The second movement option is complement movement.
+The complement of \tsc{f4} moves to the specifier of \tsc{insP}, resulting in the structure in \ref{ex:f4comp}.
+The lexicon does not contain an entry with \tsc{insP} which contains only \tsc{f4}.\footnote{\tit{Met} `with' is not a candidate, because the syntactic structure has a unary bottom and the lexical structure has a binary bottom.}
 
@@
 ]
-{\draw (.east) node[right]{⇔ }; }
-\end{forest}
+{\draw (.east) node[right]{⇒ }; }
+\end{forest}\label{ex:f4no}
 \b. \begin{forest} boom
-[\phantom{x}
+[\tsc{datP}
     [\tsc{datP}
@@
     ]
-    {\draw (.east) node[right]{⇔ \tit{(ə)t}}; }
+    {\draw (.east) node[right]{⇒ \tit{(ə)t}}; }
     [\tsc{insP}
@@
     ]
-    {\draw (.east) node[right]{⇔ }; }
+    {\draw (.east) node[right]{⇒ }; }
+]
+\end{forest}\label{ex:f4comp}
+
+As no match can be found, backtracking is triggered.
+The derivation goes back to the previous cycle, and the next option for that cycle is tried.
+In this case, that is after the merge of \tsc{f3}.
+There is no specifier, so there is no spec-to-spec movement.
+Complement movement is tried, showed in \ref{ex:f3comp}.
+However, there is no match in the lexicon for an \tsc{datP} that contains only \tsc{f3}.
+
+\begin{forest} boom
+[\tsc{accP}
+    [\tsc{accP}
+       [\tsc{f}2]
+       [\tsc{nom}P
+           [\tsc{f}1]
+           [\tsc{thingP}
+               [\tsc{thing}, roof]
+           ]
+       ]
+    ]
+    {\draw (.east) node[right]{⇒ \tit{(ə)t}}; }
+    [\tsc{datP}
+        [\tsc{f}3]
+    ]
+    {\draw (.east) node[right]{⇒ }; }
+]
+\end{forest}\label{ex:f3comp}
+
+Backtracking proceeds further, into the cycle in which \tsc{f2} was merged. Again there is no specifier to be moved, and complement movement does not give any results.
+
+The derivation ends up backtracking into the cycle in which \tsc{f1} was merged.
+At this stage, \tsc{thing} was realized as \tit{'r}.
+Here there is again no specifier, but complement movement provides a structure that is fit for a lexical entry, namely: \ref{ex:entrymee}.
+
+\ex. \begin{forest} boom
+[\tsc{nomP}
+   [\tsc{thingP}
+       [\tsc{thing}, roof]
+   ]
+   {\draw (.east) node[right]{⇒ \tit{(ə)r}}; }
+   [\tsc{nom}P
+       [\tsc{f}1]
+   ]
+   {\draw (.east) node[right]{⇒ \tit{mee}}; }
 ]
@@
 
-The next step in the algorithm is backtracking.
-We try the next option for the cycle in which \tsc{f}3 was merged.
-This option is complement movement.
-However, there is no lexical entry that fits, so we try the next option.
-
-show here
-
-The exact same happens for \tsc{f}2.
-
-show here
-
-Now for \tsc{f}1 it is different. There is a candidate when we try complement movemement, namely \tsc{thing} is realized as \tit{(ə)r} and \tsc{f}1 is spelled out as \tit{∅}
-
-\ex. \begin{forest} boom
-[\phantom{x}
-   [\tsc{thingP}
-       [\tsc{thing}, roof]
-   ]
-   {\draw (.east) node[right]{⇔ \tit{(ə)r}}; }
-   [\tsc{nom}P
-       [\tsc{f}1]
-   ]
-   {\draw (.east) node[right]{⇔ \tit{∅}}; }
-]
-\end{forest}
-
-Merge \tsc{f}2, there is no candidate for phrasal spellout, we try spec to spec movement and get a match:
-
-\ex. \begin{forest} boom
-[\phantom{x}
-   [\tsc{thingP}
-       [\tsc{thing}, roof]
-   ]
-   {\draw (.east) node[right]{⇔ \tit{(ə)r}}; }
+The feature \tsc{f}2 is merged again.
+The structure cannot be spelled out as a whole, so spec-to-spec movement is tried.
+In that configuation \tit{f2} can be realized together with \tsc{f1} as \tit{mee}.
+
+\ex. \begin{forest} boom
+[\tsc{accP}
+   [\tsc{thingP}
+       [\tsc{thing}, roof]
+   ]
+   {\draw (.east) node[right]{⇒ \tit{(ə)r}}; }
    [\tsc{acc}P
@@
    ]
-   {\draw (.east) node[right]{⇔ \tit{∅}}; }
+   {\draw (.east) node[right]{⇒ \tit{mee}}; }
  ]
@@
 
-Idem for \tsc{f}3.
-
-\ex. \begin{forest} boom
-[\phantom{x}
-   [\tsc{thingP}
-       [\tsc{thing}, roof]
-   ]
-   {\draw (.east) node[right]{⇔ \tit{(ə)r}}; }
-   [\tsc{dat}P
-       [\tsc{f}3]
-       [\tsc{acc}P
-           [\tsc{f}2]
-           [\tsc{nom}P
-               [\tsc{f}1]
-           ]
-       ]
-   ]
-   {\draw (.east) node[right]{⇔ \tit{∅}}; }
-]
-\end{forest}
-
-Now \tsc{f}4 is merged. No phrasal spellout, but there is a match after spec-to-spec movement. However, is is not \tit{∅} anymore, but the inserted morpheme is \tit{mee}.
-
-\ex. \begin{forest} boom
-[\phantom{x}
-    [\tsc{thingP}
-       [\tsc{thing}, roof]
-    ]
-    {\draw (.east) node[right]{⇔ \tit{(ə)r}}; }
+The same happens for \tsc{f3} and \tsc{f4}, and the complete structure is realizes as shown in \ref{ex:spelloutermee}.
+
+\ex. \begin{forest} boom
+[\tsc{insP}
+    [\tsc{thingP}
+       [\tsc{thing}, roof]
+    ]
+    {\draw (.east) node[right]{⇒ \tit{(ə)r}}; }
     [\tsc{insP}
@@
     ]
-    {\draw (.east) node[right]{⇔ \tit{mee}}; }
+    {\draw (.east) node[right]{⇒ \tit{mee}}; }
+]
+\end{forest}\label{ex:spelloutermee}
+
+Skipping over the irrelevant details of how \tit{w-} and \tit{-a-} end up in their positions, the structure for \tit{waarmee} `with what' look as in \ref{ex:spelloutwaarmee}.
+\footnote{I assume that WP and \tsc{deixP} are both complex specifiers that are created after \tsc{thing} is spelled out in \ref{ex:thingspellout}.
+In after each merge after that, backtracking always takes place, the complex specifier is detached from the structure and the case features are spelled out together with or as a suffix on \tsc{thing}.}
+\footnote{A consequence of analyzing \tit{mee} `with' as a suffix is that \tit{r} and \tit{-mee} always form a constituent to the exclusion of \tit{w-} and \tit{-a-}.
+This is problematic because \tit{waar} `where' can move leaving \tit{mee} `with' behind.
+The only way to resolve the situation would be to assume that \tit{mee} `with' is evacuated and \tit{waar} `where' remnant moves after that.}
+
+\ex. \begin{forest} boom
+[\tsc{WP}
+    [\tsc{WP}
+        [\tsc{W}, roof]
+    ]
+    {\draw (.east) node[right]{⇒ \tit{w}}; }
+    [\tsc{deixP}
+        [\tsc{deixP}
+            [\tsc{deix}, roof]
+        ]
+        {\draw (.east) node[right]{⇒ \tit{a}}; }
+        [\tit{insP}
+            [\tsc{thingP}
+               [\tsc{thing}, roof]
+            ]
+            {\draw (.east) node[right]{⇒ \tit{(ə)r}}; }
+            [\tsc{insP}
+               [\tsc{f}4]
+               [\tsc{dat}P
+                   [\tsc{f}3]
+                   [\tsc{acc}P
+                       [\tsc{f}2]
+                       [\tsc{nom}P
+                           [\tsc{f}1]
+                       ]
+                   ]
+               ]
+            ]
+            {\draw (.east) node[right]{⇒ \tit{mee}}; }
+        ]
+    ]
+]
+\end{forest}\label{ex:spelloutwaarmee}
+
+So far I showed how \tit{waarmee} `with what' is derived if all syntactic features form a constituent.
+Next I address how this is blocked when the features do not form a proper constituent, and how the spellout is then \tit{met wat} `with what'.
+
+I start in a situation in which \tit{wat} `what' is part of a syntactic structure with the rest of a relative clause as a sister.
+
+\ex. \begin{forest} boom
+[CP
+    [CP
+        [...,roof]
+    ]
+    [\tsc{WP}
+        [\tsc{WP}
+            [\tsc{W}, roof]
+        ]
+        {\draw (.east) node[right]{⇒ \tit{w}}; }
+        [\tsc{deixP}
+            [\tsc{deixP}
+                [\tsc{deix}, roof]
+            ]
+            {\draw (.east) node[right]{⇒ \tit{a}}; }
+            [\tsc{accP}
+               [\tsc{f}2]
+               [\tsc{nom}P
+                   [\tsc{f}1]
+                   [\tsc{thingP}
+                       [\tsc{thing}, roof]
+                   ]
+               ]
+            ]
+            {\draw (.east) node[right]{⇒ \tit{(ə)t}}; }
+        ]
+    ]
 ]
@@
 
-Then show here that this does not happen if not all features form a proper constituent. Spellout can just not target a constituent.
-
-I did not address the ordering difference of the wh-element and the adposition.
-A topic related to (but not relevant for) this paper is the different positioning of identical adpositions in Dutch.
-In \ref{ex:dutchin}, \tit{in} changes meaning dependent on whether it procedes or follows the DP, it is respectively locational or directional.
-
-\ex.\label{ex:dutchin}
-\ag. Ik klim in de boom.\\
- I climb in the tree\\
- `I am climbing in the tree.'
-\bg. Ik klim de boom in.\\
- I climb the tree in\\
- `I am climbing into the tree.'
-
-The different positioning of the adpositions in \tsc{r}-pronouns is driven by spellout and is, therefore, meaningless.
+If a dative feature is merged here, it will not be able to be spelled out.
+The only option to realize the features is to form to spawn a new derivation, to create a complex specifier.
+And that is exactly what forming the preposition \tit{met} `with' is.
 
@@
 
-So, the answer of how constituency connects to change in phonological form lies in one of the core assumptions of nanosyntax: phrasal spellout spells out constituents.
-
-Just like Abels said: no preposition stranding, but extraction from the PP is ok!
-
-Van Riemsdijk said that R-pronouns are pronouns and they orginate in the complement of P.
-Due to \tsc{r}-movement they move to the spec of PP, and due to suppletion they change form, coincidentally to something identical to the locative.
-Full DPs cannot move to the spec of PP because they do not have access to that spec.
-
-I claim that this movement is not a special r-movement, but a movement driven by spellout. The suppletion also follows from the regular spellout algorithm, and it is the locative that is inserted.
-
-Koopman's account differ from Van Riemsdijk's in that she assumes \tsc{r}-pronouns obligatorily move to specPlace.
-The fact that locatives and \tsc{r}-pronouns are syncretic is not a surprise.
-They occur in the same structural configuration.
-
-Place does not make a lot of sense in \tit{waarmee}, because we do not have a place here.
-
-Abels says that this movement from the complement to the spec is not allowed.
-He argues that, instead, that R-words are base generated as the specifiers of distinguished class of zero-place prepositions.
-\tsc{r} is the complement of P and is subextracted from the complement of P (which is allowed, because it is subextraction and not extraction of it as a whole.)
-
-I agree with Abels in that \tit{r} is substracted from the complement of the preposition.
-However, I say that \tit{r} is actually the pronoun.
-What he refers to as an \tsc{r}-word is in Dutch \tit{w-aa-}, which I also assume is merged later.
-
-Now the difference in distribution between \tit{met wat} and \tit{waarmee} is going to follow from spellout.
-If we get higher than dative case, we need prepositions.
-Making prepositions is a very 'costly' operation in the langauge, it is the last resort option in the spellout procedure.
-Dutch also has forms that are not only prepositions, but can also function as postpositions.
-They are less 'costly'.
-To avoid building a complex specifier, different spellout options are used.
-That is why we get the \tsc{r}-pronoun in the picture.
-\tsc{r}-pronouns can combine with these postpositions.
-
-Open ends
-
-In the analysis laid out above it is a coincidence that \tit{mee} `with' and \tit{met} `with' look so much alike.
-
-Another topic I do not discuss is that in almost all cases the preposition does not change form when it combines with an \tsc{r}-pronoun, e.g.
-\tit{in}.
-If this proposal is on the right track, such elements can be used as either a prefix and as a suffix.
-A lexical entry as in \ref{ex:presuf} would be a candidate for such an element.
-
-\ex. \begin{forest} boom
-[XP
-    [XP
-        [X,roof]
-    ]
-    [YP
-        [Y]
-    ]
-]
-{\draw (.east) node[right]{⇔ \tit{in}}; }
-\end{forest}\label{ex:presuf}
-
-I leave it to future research to determine whether this is a feasible solution.
-
-still need to incorporate \tit{a} and \tit{w}. They can either come before case or after it.
+In this paper, I discussed the distribution of \tit{waarmee} `met wat' and \tit{met wat} `with what' is mismatching free relatives.
+I showed that \tit{waarmee} `with what' appears when all features form a proper constituent, and \tit{met wat} `with what' if they do not.
+
+The described pattern follows from a core assumptions in Nanosyntax: phrasal spellout spells out constituents.
+Looking more into detail, \tit{waarmee} `with what' takes precedence over \tit{met wat} `with what' because \tit{mee} has the structure of a suffix.
+Following the spellout algorithm, \tit{'t} `it' is replaced by \tit{er}, so that it can combine with \tit{mee} `with'.
+The preposition \tit{met} `with' is only used if there is no other option to spell out the features.
+
+This proposal is in several aspects in accordance with earlier work.
+Just like \citet{riemsdijk1978}, I claim that \tsc{r}-pronouns originate as the complement of P.
+He argued that due to some kind of suppletion \tit{'t} `it' changes form to \tsc{er}, which is coincidentally also the locative in Dutch.
+In my proposal, this suppletion follows naturally from the regular spellout algorithm.
+Also, it is not a coincidence that the locative appears, as it is an item with little features that spells out \tsc{thing}.
+The current proposal differs from \citet{riemsdijk1978} in that it is not the whole complement of P is moved.
+Instead, only part of the complement of P is extracted, which is generally allowed, also in non-preposition stranding languages \citep{abels2003diss}.
 

### 2019-12-24 paper.tex
first draft
finished it

@@
 
-\title{Dutch, PPs, ʀ-pronouns}
+\title{\tit{Waarmee} vs. \tit{met wat}}
 \author{Fenna Bergsma}
@@
 The term \tsc{r}-pronoun \citep{riemsdijk1978} refers to a set of nominal elements that can strand prepositions in Dutch (and German).
-It is special because Dutch is a normally non-preposition stranding language.
+This is noteworthy because Dutch is a normally non-preposition stranding language.
 \tsc{R}-pronouns morphologically consist of a combination of a preposition and locative pronoun.
-In the example \ref{ex:klimerop} \tit{mee} `with' is the preposition and \tit{er} `there' is the locative pronoun.
+In the example \ref{ex:klimerop} \tit{op} `on' is the preposition and \tit{er} `there' is the locative pronoun.
 
@@
 First, just like for all \tsc{r}-pronouns, the wh-element is the locative, but there is no meaning component related to location in `with what'.
-Second, the preposition \tit{met} `with' changes into \tit{mee} `with when it is combined with an \tsc{r}-pronoun.
+Second, the preposition \tit{met} `with' changes into \tit{mee} `with' when it is combined with an \tsc{r}-pronoun.
 
@@
 The predicate in the main clause clause, \tit{gekocht} `bought' combines with an accusative DP.
-The \tsc{r}-pronoun \tit{waarmee} `with what' is used here.
-\footnote{In this example \tit{mee} `with' is stranded and \tit{waar} `where' is moved to the left edge of the embedded clause.
-It is also possible for \tit{waar} `where' to bring \tit{mee} `with' along, as in \ref{ex:meealong} but it is regarded as slightly less natural.
+The \tsc{r}-pronoun \tit{waarmee} `with what' is used here.\footnote{In this example \tit{mee} `with' is stranded and \tit{waar} `where' is moved to the left edge of the embedded clause.
+It is also possible for \tit{waar} `where' to bring \tit{mee} `with' along, as in \ref{ex:meealong}, but it is regarded as slightly less natural.
 
@@
 
-If one were to switch around the predicates between the clauses, the \tsc{r}-pronoun does not appear anymore.
+If the predicates are switched around between the clauses, the \tsc{r}-pronoun does not appear anymore.
 In \ref{ex:schildermet}, \tit{schilder} `paint' combines with an instrumental PP in the main clause and \tit{gekocht} `bought' combines with an accusative DP in the embedded clause.
@@
 
-In this paper I show that distribution of \tit{waarmee} `with what' and \tit{met wat} `with what' in these free relative constructions gives us a unique insight into the internal structure of \tsc{r}-pronouns.
+In this paper I show that distribution of \tit{waarmee} `with what' and \tit{met wat} `with what' in these free relative constructions gives us a good insight into the internal structure of \tsc{r}-pronouns.
 In what follows I show that \tsc{r}-pronouns and regular preposition compete to spell out the same syntactic features.
-If all features form a constituent, the \tsc{r}-pronoun surfaces.
-If the constituent is interrupted, the preposition-pronoun combination shows up.
+If all features form a proper constituent (i.e.
+a constituent to the exclusion of other features), the \tsc{r}-pronoun surfaces.
+If it is not a proper constituent, the preposition-pronoun combination shows up.
 This straightforwardly follows in a system in which spellout targets phrasal constituents: Nanosyntax \citep{starke2009}.
@@
 This paper is structured as follows.
-First, I show that it really is constituency.
-Then I decompose \tsc{r}-pronouns, prepositions and regular pronouns.
-Last, I show in derivations that constituency connects to the choice for \tsc{r}-pronoun or preposition and regular pronoun.
+In Section \ref{sec:distribution} I discuss the distribution of \tit{waarmee} `waarmee' and \tit{met wat} `with what'.
+I show that the \tsc{r}-pronoun surfaces when it forms a proper constituent, and \tit{met wat} `with what' when it does not.
+Section \ref{sec:suppletion} discusses how proper constituency relates to spellout by treating \tit{waarmee} `with what' as an instance of suppletion.
+In Section \ref{sec:finer}, I decompose \tit{waarmee} `with what' and \tit{met wat} `with what' to make sense of the phonological similarities, and I provide a more detailed analysis.
 Unmarked examples are constructed and have been verified by native speakers.
 
-\section{The distribution between \tit{waarmee} and \tit{met wat}}
+\section{The distribution between \tit{waarmee} and \tit{met wat}}\label{sec:distribution}
 
@@
 Table \ref{tbl:distribution} repeats the generalization.
-When the main clause predicate combines with an accusative and the embedded clause predicate with an instrumental, \tit{waarmee} is grammatical and \tit{met wat} is ungrammatical.
-When the main clause predicate combines with an instrumental and the embedded clause predicate with an accusative, \tit{waarmee} is ungrammatical and \tit{met wat} is used.
-
-\begin{table}[ht]\label{tbl:distribution}
+When the main clause predicate combines with an accusative and the embedded clause predicate with an instrumental, \tit{waarmee} `with what' is grammatical and \tit{met wat} `with what' is ungrammatical.
+When the main clause predicate combines with an instrumental and the embedded clause predicate with an accusative, \tit{waarmee} `with what' is ungrammatical and \tit{met wat} `with what' is used.
+
+\begin{table}[ht]
 	\center
@@
 \end{tabularx}
+\label{tbl:distribution}
 \end{minipage}
@@
 
- \ex. Objects of verbs \label{ex:objverb}
+ \ex. \label{ex:objverb}
  \ag. Ik zie haar/hem.\\
@@
 
-\ex. Objects of prepositions \label{ex:objprep}
+\ex. \label{ex:objprep}
 \ag. Ik schilder samen met haar/hem.\\
@@
 \bg. *Ik schilder mee er.\\
- I paint with-there\\
+ I paint with there\\
  `I am painting with it.'\label{ex:erprep}
@@
 \tit{Wat} `what' can function as an object of a verb (see \ref{ex:wat}), but not as an object of a preposition \ref{ex:metwat}.
-In that case, the \tsc{r}-pronoun \tit{waarmee} `with what' is appears, as shown in \ref{ex:waarmee}.
-\footnote{The sentence in \ref{ex:metwat} is unacceptable with neutral intonation.
-It becomes is only acceptable if \tit{wat} `what' is stressed, for example in a context in which the speaker questions the choice for the object hearer is painting with.}
+In that case, the \tsc{r}-pronoun \tit{waarmee} `with what' is appears, as shown in \ref{ex:waarmee}.\footnote{The sentence in \ref{ex:metwat} is unacceptable with neutral intonation.
+It becomes is only acceptable if \tit{wat} `what' is stressed, for example in a context in which the speaker is highly surprised about the choice for the object hearer is painting with.}
 
@@
 
-\begin{table}[ht]\label{tbl:inanimates}
+\begin{table}[ht]
 	\center
@@
   	\midrule
-objects of verbs        & ət             & wat         \\
+objects of verbs        & 't             & wat         \\
 objects of prepositions & er             & waar        \\
@@
 \end{tabularx}
+\label{tbl:inanimates}
 \end{minipage}
@@
 In \ref{ex:const2}, the PP forms a proper constituent before wh- and V2- movement, shown in \ref{ex:const2stage}.
-The structure in \ref{ex:const3stage} represents a stage in the derivation of the embedded clauses in \ref{ex:const3} and \ref{ex:const4}.
-\footnote{I assume that the antecedent in a free relative is a phonologically empty element, in line with cf.
+The structure in \ref{ex:const3stage} represents a stage in the derivation of the embedded clauses in \ref{ex:const3} and \ref{ex:const4}.\footnote{I assume that the antecedent in a free relative is a phonologically empty element, in line with cf.
 \cite{bresnan1978a,groos1981,himmelreich2017}.
@@
 \ex.\label{ex:constwaarmee}
-\ag. Waarmee schilder jij?\\
- {where with} paint you\\
+\ag. Waar-mee schilder jij?\\
+ {where-with} paint you\\
  `What are you painting with?'
-\bg. Ik schilder [waarmee jij ook schildert].\\
- I paint {where with} you also paint\\
+\bg. Ik schilder [waar-mee jij ook schildert].\\
+ I paint {where-with} you also paint\\
  `I am painting with what you are painting with too.'
-\bg. Ik schilder met de kwast [waarmee jij ook schildert].\\
- I paint with the brush {where with} you also paint\\
+\bg. Ik schilder met de kwast [waar-mee jij ook schildert].\\
+ I paint with the brush {where-with} you also paint\\
  `I am painting with the brush that you are painting with too.'
@@
 \tit{Kopen} `to buy' takes an accusative DP as its object, illustrated in \ref{ex:kopen}.
-\tit{Schilderen} `to paint' can take an instrumental PP as its object., shown in \ref{ex:schilderen}.\footnote{Of course, \tit{schilderen} also optionally takes an accusative DP, but I am focussing on the instrumental here.}
+\tit{Schilderen} `to paint' can take an instrumental PP as its object., shown in \ref{ex:schilderen}.\footnote{\tit{Schilderen} also optionally takes an accusative object, but I am focussing on the instrumental here.}
 
@@
 There are other contexts in which \tit{met wat} `with what' appears.
-This can be either when \tit{wat} `what' takes a complement, or when \tit{wat} is part of the a clause that \tit{met} `with' is not a part of.This last option is schematically showed in \ref{ex:metwatfr}, and it represents the mismatching free relative in \ref{ex:mismatchmetwat}.
+This can be either when \tit{wat} `what' takes a complement, or when \tit{wat} is part of the a clause that \tit{met} `with' is not a part of.
+This last option is schematically showed in \ref{ex:metwatfr}, and it represents the mismatching free relative in \ref{ex:mismatchmetwat}.
 
@@
 
-\section{\tit{Waarmee} as suppletion}
+\section{\tit{Waarmee} `with what' as suppletion}\label{sec:suppletion}
 
@@
 
-In what follows I show another instance in which proper constituency influences spellout, suppletive negative forms in Korean as discussed in \citet{chung2007}.
-The point is that suppletion only goes through when the relevant features form a proper constituent, and not when an additional feature intervenes.
+In what follows I show another instance in which proper constituency influences spellout, namely suppletive negative forms in Korean, as discussed by \citet{chung2007}.
+The point is that suppletion only goes through when the relevant features form a proper constituent, and not when an additional structure intervenes.
 
@@
 
-Spellout targets only constituent \citep{starke2009}.
-This ensures \ref{ex:entrymolu} is not inserted into the structure in \ref{ex:structurenegmolu}, as \tsc{caus} is contained in the syntactic structure but not in the structure in the lexicon in \ref{ex:entrymolu}.
+Since spellout targets constituent \citep{starke2009}, \ref{ex:entrymolu} is not inserted into the structure in \ref{ex:structurenegmolu}.
+\tsc{caus} is contained in the syntactic structure but not in the structure in the lexicon in \ref{ex:entrymolu}.
 
@@
 
-\section{A finer decomposition}
+\section{A finer decomposition}\label{sec:finer}
 
 In this section I investigate the internal structure of \tit{waarmee} `with what' and \tit{met wat} `with what' to capture the phonological similarities between the two forms.
-First, I identify \tit{w-} and \tit{-a-} as morphemes that appear in both expressions.
+First, I identify \tit{w} and \tit{a} as morphemes that appear in both expressions.
 Putting these two aside, I concentrate on \tit{ermee} `with it' and \tit{met 't} `with it'.
 I decompose these two expressions further, and end up arguing for a picture as shown in Table \ref{tbl:nofeatures}.
-The elements \tit{w-} and \tit{-a-} express the same syntactic structure in both expressions.
+The elements \tit{w} and \tit{a} express the same syntactic structure in both expressions.
 The elements \tit{met} and \tit{'t} together also express the same features as \tit{mee} and \tit{er} together, but the distribution differs.
@@
 		%\midrule
-    \tit{w}   & \multicolumn{1}{|c|}{\tit{a}}  & \tit{met} & \multicolumn{4}{|c}{\tit{(ə)t}}                \\\hline
-    \tit{w}   & \multicolumn{1}{|c|}{\tit{a}}  & \multicolumn{4}{c|}{\tit{mee}}               & \tit{(ə)r}  \\
+    \tit{w}   & \multicolumn{1}{|c|}{\tit{a}}  & \tit{met} & \multicolumn{4}{|c}{\tit{'t}}                \\\hline
+    \tit{w}   & \multicolumn{1}{|c|}{\tit{a}}  & \multicolumn{4}{c|}{\tit{mee}}               & \tit{er}  \\
     \bottomrule
 \end{tabularx}
+\label{tbl:nofeatures}
 \end{minipage}
-\end{table}\label{tbl:nofeatures}
+\end{table}
 
@@
 In this section I decompose \tit{waarmee} `with what' and \tit{met wat} `with what'.
-The idea is that both expessions realize the same features, and \tit{waarmee} `with what' takes precedence when all features form a constituent.
-The morphemes I distinguish in \tit{waarmee} `with what' are \tit{w-}, \tit{-aa-}, \tit{-r} and \tit{-mee}.
-Within \tit{met wat} `with what' I distinguish \tit{met}, \tit{w-}, \tit{-a-} and \tit{-t}.
+The idea is that both expressions realize the same features, and \tit{waarmee} `with what' takes precedence when all features form a constituent.
+The morphemes I distinguish in \tit{waarmee} `with what' are \tit{w}, \tit{-aa-}, \tit{-r} and \tit{mee}.
+Within \tit{met wat} `with what' I distinguish \tit{met}, \tit{w}, \tit{a} and \tit{-t}.
 \ref{ex:decompose} shows this as well.
@@
 
-Let me start with the morphemes \tit{w-} and \tit{-a-} that appear in both expressions.
+Let me start with the morphemes \tit{w} and \tit{a} that appear in both expressions.
 Exactly because they appear in both expression, I do not pay much attention to them.
-For \tit{w-} I follow \citet{hachem2015} in that \tit{w-} realizes a WP.
+For \tit{w} I follow \citet{hachem2015} in that \tit{w} realizes a WP.
 
@@
 
-The morpheme \tit{-a-} expresses deixis.
-Dutch distinguishes between proximal by using \tit{-ie-/-i-} and distal by using \tit{-aa-/-a-}, illustrated in \ref{ex:deixis}.
+The morpheme \tit{a} expresses deixis.
+Dutch distinguishes between proximal by using \tit{ie/i} and distal by using \tit{aa/a}, illustrated in \ref{ex:deixis}.
 I assume that lengthening or shortening of the vowel is a result of the final \tit{r}.
@@
 
-In combination with wh-elements, the distal marker \tit{-a-} is used. For the purpose of this paper I simply let \tit{-a-} correspond to \tsc{deixP}.
+In combination with wh-elements, the distal marker \tit{a} is used. For the purpose of this paper I simply let \tit{a} correspond to \tsc{deixP}.
 
@@
 
-I put \tit{w-} and \tit{-a-} aside for now, assuming they spell out the same syntactic structure in \tit{waarmee} `with what' and \tit{met wat} `with what'.
-This leaves \tit{er-mee} `with it' and \tit{met 't} `with it'.\footnote{\tit{'rmee} `with it' is often precdeded by an /ε/, which I assume to be for phonological reasons.
-The vowel can be dropped under the right phonological circumstances.
-
-\exg. Ik heb 'r niks mee te maken.\\
- I have there nothing with to do\\
+I put \tit{w} and \tit{a} aside for now, assuming they spell out the same syntactic structure in \tit{waarmee} `with what' and \tit{met wat} `with what'.
+This leaves \tit{er-mee} `with it' and \tit{met 't} `with it'.\footnote{I assume that the \tit{e} in \tit{ermee} `with it' is there for phonological reasons.
+The vowel is dropped under the right phonological circumstances.
+
+\exg. Ik he niks mee te maken.\\
+ I have there nothing with to make\\
  `I have nothing to do with it.'
@@
 \ex.
-\ag. (e)r -mee\\
+\ag. er -mee\\
 there with\\
@@
  ]
- {\draw (.east) node[right]{⇔ \tit{(ə)t}}; }
+ {\draw (.east) node[right]{⇔ \tit{'t}}; }
  \end{forest}\label{ex:entryt}
 
-This lexical entry can lexicalize the \tsc{datP}, but also the \tsc{accP} and \tsc{nomP}. This is due to the Superset Princple.
+This lexical entry can lexicalize the \tsc{datP}, but also the \tsc{accP} and \tsc{nomP}. This is due to the Superset Principle.
 
@@
 It is enough if the syntactic structure is contained in the lexically stored tree.
-This has a as consequence that the lexical entry in \ref{ex:entryt} can also be inserted in \ref{ex:tacc} and \ref{ex:tnom}.
+This has a as consequence that the lexical entry in \ref{ex:entryt} can also be inserted in syntactic structures as \ref{ex:tacc} and \ref{ex:tnom}.
 
@@
 
- ex. [ [ [ [ \tsc{thing} ] \tsc{f1} ] \tsc{f2} ] \tsc{f3} \tsc{f4} ]\label{ex:stmetwat}
+\ex. [ [ [ [ \tsc{thing} ] \tsc{f1} ] \tsc{f2} ] \tsc{f3} \tsc{f4} ]\label{ex:stmetwat}
 
@@
  ]
- {\draw (.east) node[right]{⇔ \tit{(ə)r}}; }
+ {\draw (.east) node[right]{⇔ \tit{er}}; }
  \end{forest}\label{ex:entryr}
 
-Via the superset principle, \tit{er} can be used to realize the feature \tsc{thing} as well, as it is contained in \tsc{locP}.
+Notice already here that, via the superset principle, \tit{er} can be used to realize the feature \tsc{thing} as well, as it is contained in \tsc{locP}.
 
 So far, \tit{er} `there' only realizes the feature \tsc{thing} from the structure in \ref{ex:stmetwat}.
-This leaves \tit{f1} to \tsc{f4} to be realized by \tit{-mee}.
+This leaves \tsc{f1} to \tsc{f4} to be realized by \tit{mee}.
 I give the lexical tree in \ref{ex:entrymee}.
@@
 This is the crucial differences needed for the Dutch instrumental.
-\tit{Met} `with' is a prefix (preposition), so it has a binary bottom, and \tit{-mee} `with' is a suffix, so it needs a unary bottom. In the next section I show how this works in a derivation.
-\footnote{For completeness, \tit{mee} `with' has to be blocked from combining with full DPs and animate pronouns (reference).
+\tit{Met} `with' is a prefix (preposition), so it has a binary bottom, and \tit{mee} `with' is a suffix, so it needs a unary bottom.
+In the next section I show how this works in a derivation.\footnote{For completeness, \tit{mee} `with' has to be blocked from combining with full DPs and animate pronouns (reference).
 For now I assume that these pronouns spell out an additional feature \tit{σ} that is not realized by \tit{mee} `with' but only by \tit{met} `with'.
@@
 This way \tit{mee} `with' does not compete with \tit{met} `anymore'.
-I left this features out in this paper, at is does not contribute to the main point.}
-\footnote{Giving \tit{met} `with' and \tit{mee} `with' two distinct lexical entries has as a consquence that the phonological overlap between them seems like a coincidence.
-I leave it for future research to capture this observation.}
-\footnote{I do not address the ordering difference of the wh-element and the adposition.
+I left this features out in this paper, at is does not contribute to the main point.}\footnote{Giving \tit{met} `with' and \tit{mee} `with' two distinct lexical entries has as a consequence that the phonological overlap between them seems like a coincidence.
+Moreover, in almost all cases the preposition does not change form when it combines with an \tsc{r}-pronoun, e.g.
+\tit{in}.
+If this proposal is on the right track, elements as \tit{in} can be used as either a prefix and as a suffix.
+A lexical entry as in \ref{ex:presuf} would be a candidate for such an element.
+
+\ex. \begin{forest} boom
+[XP
+    [XP
+        [X,roof]
+    ]
+    [YP
+        [Y]
+    ]
+]
+{\draw (.east) node[right]{⇔ \tit{in}}; }
+\end{forest}\label{ex:presuf}
+
+I leave it to future research to determine whether this is a feasible solution.}\footnote{I do not address the ordering difference of the wh-element and the adposition.
 A topic related to (but not relevant for) this paper is the different positioning of identical adpositions in Dutch.
-In \ref{ex:dutchin}, \tit{in} changes meaning dependent on whether it procedes or follows the DP, it is respectively locational or directional.
+In \ref{ex:dutchin}, \tit{in} changes meaning dependent on whether it proceeds or follows the DP, it is respectively locational or directional.
 
@@
 
-The different positioning of the adpositions in \tsc{r}-pronouns is driven by spellout and is, therefore, meaningless.
-However, the topic might be related.
-In almost all cases the preposition does not change form when it combines with an \tsc{r}-pronoun, e.g.
-\tit{in}.
-If this proposal is on the right track, such elements can be used as either a prefix and as a suffix.
-A lexical entry as in \ref{ex:presuf} would be a candidate for such an element.
-
-\ex. \begin{forest} boom
-[XP
-    [XP
-        [X,roof]
-    ]
-    [YP
-        [Y]
-    ]
-]
-{\draw (.east) node[right]{⇔ \tit{in}}; }
-\end{forest}\label{ex:presuf}
-
-I leave it to future research to determine whether this is a feasible solution.}
+The different positioning of the adpositions in \tsc{r}-pronouns is driven by spellout and is, therefore, meaningless.}
 
 Table \ref{tbl:withfeatures} gives an overview of the distribution of the features in \tit{met wat} `with what' and \tit{waarmee} `with what'.
-In both cases, \tit{w-} and \tit{-a-} are the realization of the same morpheme.
+In both cases, \tit{w} and \tit{a} are the realization of the same morpheme.
 The difference between the two expressions lies in the distribution of the case features.
@@
 		\midrule
-    \tit{w}   & \multicolumn{1}{|c|}{\tit{a}}  & \tit{met} & \multicolumn{4}{|c}{\tit{(ə)t}}                \\\hline
-    \tit{w}   & \multicolumn{1}{|c|}{\tit{a}}  & \multicolumn{4}{c|}{\tit{mee}}               & \tit{(ə)r}  \\
+    \tit{w}   & \multicolumn{1}{|c|}{\tit{a}}  & \tit{met} & \multicolumn{4}{|c}{\tit{'t}}                \\\hline
+    \tit{w}   & \multicolumn{1}{|c|}{\tit{a}}  & \multicolumn{4}{c|}{\tit{mee}}               & \tit{er}  \\
     \bottomrule
 \end{tabularx}
+\label{tbl:withfeatures}
 \end{minipage}
-\end{table}\label{tbl:withfeatures}
+\end{table}
 
 In the next section I put all features back together in a derivation and I show how \tit{waarmee} `with what' surfaces when all features form a constituent.
-\tit{Met wat} `with what' appears when the functional sequence is disrubted.
-
-% I do not care whether \tit{w-} and \tit{-a-} are merged before or after.
+\tit{Met wat} `with what' appears when the functional sequence is disrupted.
+
+% I do not care whether \tit{w} and \tit{a} are merged before or after.
 %
@@
 
-First of all, when two lexical entries are both candicates for spellout, the most specific is inserted, following the Elsewhere Condition:
+First of all, when two lexical entries are both candidates for spellout, the most specific is inserted, following the Elsewhere Condition:
 
@@
 After each instance of merge, spellout takes place.
-If no spellout exist for the phrase created by the newly added feature, evacuations movements specified in the spellout algorithm take place.
+If no spellout exist for the phrase created by the newly added feature, evacuation movements specified in the spellout algorithm take place.
 The algorithm is given in \ref{ex:spellout}.
@@
 
-\ex. Backtracking \citep{starke2018}:
+\ex. Backtracking \citep{starke2018}:\\
 When spellout fails, go back to the previous cycle, and try the next option for that cycle.
@@
 I first show how \tit{ermee} `with it' is constructed.
-I leave out \tit{w-} and \tit{-a-}, because it unnessisarily complicates the story.
-\footnote{I assume the actual functional sequence to be \ref{ex:fseq}.
+I leave out \tit{w} and \tit{a}, because it unnecessarily complicates the story.\footnote{I assume that the WP and \tsc{deixP} appear lower in the structure than the case features, so the functional sequence is as given in \ref{ex:fseq}.
 
@@
  ]
-{\draw (.east) node[right]{⇒ \tit{(ə)r}}; }
+{\draw (.east) node[right]{⇒ \tit{er}}; }
 \end{forest}\label{ex:thingspellout}
@@
 ]
-{\draw (.east) node[right]{⇒ \tit{(ə)t}}; }
+{\draw (.east) node[right]{⇒ \tit{'t}}; }
 \end{forest}\label{ex:thingf1}
 
-Then \tsc{f}2 is merged. This structure can still be realizd by \tit{'t}.
+Then \tsc{f}2 is merged. This structure can still be realized by \tit{'t}.
 
@@
 ]
-{\draw (.east) node[right]{⇒ \tit{(ə)t}}; }
+{\draw (.east) node[right]{⇒ \tit{'t}}; }
 \end{forest}
@@
 According to the spellout algorithm, the first evacuation movement to be tried is spec-to-spec movement.
-However, there is no specfier in this structure, so this does not apply.
+However, there is no specifier in this structure, so this does not apply.
 The second movement option is complement movement.
@@
     ]
-    {\draw (.east) node[right]{⇒ \tit{(ə)t}}; }
+    {\draw (.east) node[right]{⇒ \tit{'t}}; }
     [\tsc{insP}
@@
     ]
-    {\draw (.east) node[right]{⇒ \tit{(ə)t}}; }
+    {\draw (.east) node[right]{⇒ \tit{'t}}; }
     [\tsc{datP}
@@
 The derivation ends up backtracking into the cycle in which \tsc{f1} was merged.
-At this stage, \tsc{thing} was realized as \tit{'r}.
+At this stage, \tsc{thing} was realized as \tit{er}.
 Here there is again no specifier, but complement movement provides a structure that is fit for a lexical entry, namely: \ref{ex:entrymee}.
@@
    ]
-   {\draw (.east) node[right]{⇒ \tit{(ə)r}}; }
+   {\draw (.east) node[right]{⇒ \tit{er}}; }
    [\tsc{nom}P
@@
 The structure cannot be spelled out as a whole, so spec-to-spec movement is tried.
-In that configuation \tit{f2} can be realized together with \tsc{f1} as \tit{mee}.
+In that configuration \tsc{f2} can be realized together with \tsc{f1} as \tit{mee}.
 
@@
    ]
-   {\draw (.east) node[right]{⇒ \tit{(ə)r}}; }
+   {\draw (.east) node[right]{⇒ \tit{er}}; }
    [\tsc{acc}P
@@
     ]
-    {\draw (.east) node[right]{⇒ \tit{(ə)r}}; }
+    {\draw (.east) node[right]{⇒ \tit{er}}; }
     [\tsc{insP}
@@
 
-Skipping over the irrelevant details of how \tit{w-} and \tit{-a-} end up in their positions, the structure for \tit{waarmee} `with what' look as in \ref{ex:spelloutwaarmee}.
-\footnote{I assume that WP and \tsc{deixP} are both complex specifiers that are created after \tsc{thing} is spelled out in \ref{ex:thingspellout}.
-In after each merge after that, backtracking always takes place, the complex specifier is detached from the structure and the case features are spelled out together with or as a suffix on \tsc{thing}.}
-\footnote{A consequence of analyzing \tit{mee} `with' as a suffix is that \tit{r} and \tit{-mee} always form a constituent to the exclusion of \tit{w-} and \tit{-a-}.
+Skipping over the irrelevant details of how \tit{w} and \tit{a} end up in their positions, the structure for \tit{waarmee} `with what' look as in \ref{ex:spelloutwaarmee}.\footnote{I assume that WP and \tsc{deixP} are both complex specifiers that are created after \tsc{thing} is spelled out in \ref{ex:thingspellout}.
+In after each merge after that, backtracking always takes place, the complex specifier is detached from the structure and the case features are spelled out together with or as a suffix on \tsc{thing}.}\footnote{A consequence of analyzing \tit{mee} `with' as a suffix is that \tit{r} and \tit{mee} always form a constituent to the exclusion of \tit{w} and \tit{a}.
 This is problematic because \tit{waar} `where' can move leaving \tit{mee} `with' behind.
-The only way to resolve the situation would be to assume that \tit{mee} `with' is evacuated and \tit{waar} `where' remnant moves after that.}
+To resolve the situation I assume that \tit{mee} `with' is evacuated and \tit{waar} `where' remnant moves after that.}
 
@@
             ]
-            {\draw (.east) node[right]{⇒ \tit{(ə)r}}; }
+            {\draw (.east) node[right]{⇒ \tit{er}}; }
             [\tsc{insP}
@@
             ]
-            {\draw (.east) node[right]{⇒ \tit{(ə)t}}; }
+            {\draw (.east) node[right]{⇒ \tit{'t}}; }
         ]
@@
 Looking more into detail, \tit{waarmee} `with what' takes precedence over \tit{met wat} `with what' because \tit{mee} has the structure of a suffix.
-Following the spellout algorithm, \tit{'t} `it' is replaced by \tit{er}, so that it can combine with \tit{mee} `with'.
+Following the spellout algorithm, \tit{'t} `it' is replaced by \tit{er} `there', so that it can combine with \tit{mee} `with'.
 The preposition \tit{met} `with' is only used if there is no other option to spell out the features.

### 2020-01-11 paper.tex
only formatting
left to do
-move tables to end
-double + single spacing
-abstract
-personal details
-keywords
weg bij jan vandaan
eigenlijk alleen koreaan verwijderd en ossetic erbij
nu op naar prefix vs. suffix!

@@
-\documentclass{article}
+\documentclass[12pt]{article}
+
+\usepackage[margin=1in]{geometry}
+%\usepackage{setspace}
+%\doublespacing
 
@@
 
-\title{\tit{Waarmee} vs. \tit{met wat}}
+\title{\tit{Waarmee} vs. \tit{met wat}\\
+Constituency spellout, r-pronouns}
 \author{Fenna Bergsma}
@@
 \begin{document}
+
+\raggedright
 
@@
 
-This section showed that being a proper constituent is a necessary requirement for \tit{waarmee} `with what' to surface.
-The next section elaborates on how proper constituency and spellout relate to each other.
-
-\section{\tit{Waarmee} `with what' as suppletion}\label{sec:suppletion}
-
 \tit{Met} `with' is a preposition that combines with full DPs and animate pronouns.
@@
 
-In this section I start with showing a similar instance in which proper constituency and spellout go hand in hand.
-Then I show how these facts can be straightforwardly follow from the spellout algorithm in Nanosyntax.
-The section ends with showing how this logic can be applied to \tit{waarmee} `with what' and \tit{met wat} `with what'.
-
-In what follows I show another instance in which proper constituency influences spellout, namely suppletive negative forms in Korean, as discussed by \citet{chung2007}.
-The point is that suppletion only goes through when the relevant features form a proper constituent, and not when an additional structure intervenes.
-
-Sentences in Korean can be negated by the two negative prefixes \tit{ani} or \tit{mos}, as shown in \ref{ex:koreannegation}.
-
-\ex.\label{ex:koreannegation}
-\ag. ca -n -ta\\
- sleep -\tsc{pres} -\tsc{decl}\\
- `is sleeping'
-\bg. mos/an(i) ca -n -ta\\
- \tsc{neg} sleep -\tsc{pres} -\tsc{decl}\\
- `cannot sleep / is not sleeping' \hfill \citep{chung2007}
-
-The verb \tit{al-} `know' does not combine with any of the negative markers, but it it uses the suppletive stem \tit{molu.\tsc{neg}}. This is illustrated in \ref{ex:koreanknow}.
-
-\ex.\label{ex:koreanknow}
-\ag. al -n -ta\\
-know \tsc{-pres} \tsc{-decl}\\
-`know(s)'
-\bg. *mos/*an(i) al -n -ta\\
-\tsc{neg} know -\tsc{pres} -decl\tsc{}\\
-\bg. molu -n -ta\\
-\tsc{neg}.know -\tsc{pres} -\tsc{decl}\\
-`do(es) not / cannot know'\label{ex:molu} \hfill \citep{chung2007}
-
-When \tit{al-} `know' is causativized before it is negated, the regular stem is used again, shown in \ref{ex:knowcausneg}.
-\ref{ex:molucaus} illustrates that the suppletive stem \tit{molu-} is no longer grammatical.
-
-\ex.
-\ag. al -li-\\
- know -\tsc{caus}\\
- `let know, inform'
-\bg. ani/ mos al -li -ess -ta\\
- \tsc{neg} \tsc{neg} know -\tsc{caus} -\tsc{past} -\tsc{decl}\\
- `did not /could not inform'\label{ex:knowcausneg}
-\bg. *molu -li -ess -ta\\
- \tsc{neg}.know -\tsc{caus} -\tsc{past} -\tsc{decl}\\\label{ex:molucaus} \hfill \citep{chung2007}
-
-\citet{chung2007} points out that it cannot be phonological adjacency of the negation and \tit{al-} `know' that causes the suppletion in \ref{ex:molu}.
-The reason for that is that in \ref{ex:knowcausneg} \tit{al-} also follows the negation, but there is no suppletion.
-\citet{chung2007} suggests crucial difference has to do with in proper constituency.
-The structure of \ref{ex:molu} is given in \ref{ex:structuremolu}: Neg and \tit{al-} `know' form a proper constituent.
-\ref{ex:structurenegmolu} represents the structure of \ref{ex:knowcausneg}.
-Neg and \tit{al-} `know' no longer form a proper constituent, because \tsc{caus} is also part of the structure as the sister of \tit{al-} `know'.
-
-\ex.
-%%%
-\a. \begin{forest} boom
-[
-    [Neg]
-    [know]
-]
-\end{forest}\label{ex:structuremolu}
-\b. \begin{forest} boom
-[
-    [Neg]
-    [
-        [know]
-        [\tsc{caus}]
-    ]
-]
-\end{forest}\label{ex:structurenegmolu}
-
-\citet{caha2009} uses this pattern to argue in favor of a model with phrasal spellout rather than inserting phonology into terminal nodes, specifically Nanosyntax \citep{starke2009}.
-The idea is that the lexicon contains syntactic structures that are linked to a particular piece of phonology.
-If Korean has a lexical entry as in \ref{ex:entrymolu}, this can be inserted into the syntactic tree in \ref{ex:structuremolu}.
-
-\ex. \begin{forest} boom
-[
-    [Neg]
-    [know]
-]
-  {\draw (.east) node[right]{⇔ \tit{molu}}; }
-\end{forest}\label{ex:entrymolu}
-
-Since spellout targets constituent \citep{starke2009}, \ref{ex:entrymolu} is not inserted into the structure in \ref{ex:structurenegmolu}.
-\tsc{caus} is contained in the syntactic structure but not in the structure in the lexicon in \ref{ex:entrymolu}.
-
-The same logic can be applied to \tit{waarmee} `with what' and \tit{met wat} `with what'.
-The preposition and wh-element together form a proper constituent, as in \ref{ex:structurewaarmee}, or the embedded CP of the relative clause is a sister of the wh-element, as in \ref{ex:structuremetwat}.
-
-\ex.
-\a. \begin{forest} boom
-[
-    [P]
-    [Wh]
-]
-\end{forest}\label{ex:structurewaarmee}
-%%
-\b. \begin{forest} boom
-[
-    [P]
-    [
-        [Wh]
-        [CP
-            [...,roof]
-        ]
-    ]
-]
-\end{forest}\label{ex:structuremetwat}
-
-Assume we have a lexical entry for \tit{waarmee} `met wat' that look as \ref{ex:entrywaarmee}.
-This entry can only be inserted into \ref{ex:structurewaarmee}, because the lexical structure matches the syntactic structure.
-It cannot be into \ref{ex:structuremetwat}, because the lexical structure does not contain the CP.
-
-\ex. \begin{forest} boom
-[
-    [InsP]
-    [WhP]
-]
-  {\draw (.east) node[right]{⇔ \tit{waarmee}}; }
-\end{forest}\label{ex:entrywaarmee}
-
-What I have shown in this section is how proper constituency relates to a change in phonology.
-However, this analysis missed numerous phonological properties of \tit{waarmee} `with what' and \tit{met wat} `with what', e.g.
-that they both contain the morpheme \tit{wa}.
-Under the suppletion analysis above, one can the phonological form of \tit{waarmee} could just as well be completely phonologically unrelated.
-The point of presenting the problem like this is to illustrate that the distribution between \tit{waarmee} `with what' and \tit{met wat} `with what' can be captured as a matter of spellout.
-
 In the next section I decompose \tit{waarmee} `with what' and \tit{met wat} `with what'. I show that both spell out the same set of features, but the distribution is different.
 
-\section{A finer decomposition}\label{sec:finer}
-
-In this section I investigate the internal structure of \tit{waarmee} `with what' and \tit{met wat} `with what' to capture the phonological similarities between the two forms.
+\section{Taking \tit{waarmee} and \tit{met wat} apart}
+
+In this section I investigate the internal structure of \tit{waarmee} `with what' and \tit{met wat} `with what' to capture the phonological similarities and differences between the two forms.
 First, I identify \tit{w} and \tit{a} as morphemes that appear in both expressions.
@@
 The elements \tit{met} and \tit{'t} together also express the same features as \tit{mee} and \tit{er} together, but the distribution differs.
-\tit{Met} expresses less structure than \tit{mee} and \tit{'t} expresses more structure than \tit{er}.
-It becomes clear that the \tit{er} in fact corresponds to the locative \tit{r} in Dutch.
+\tit{Met} expresses less structure than \tit{mee}, and \tit{'t} expresses more structure than \tit{er}.
+\tit{Met} is shown to be an prefix, and \tit{mee} is a suffix.
+It also becomes clear that the \tit{er} in fact corresponds to the locative \tit{r} in Dutch.
 
@@
 
-Finally, I put everything together and show how \tit{waarmee} `with what' is inserted if all features form a constituent, and \tit{met wat} `with what' if this is not the case.
-
-\subsection{Taking everything apart}
-
-In this section I decompose \tit{waarmee} `with what' and \tit{met wat} `with what'.
  The idea is that both expressions realize the same features, and \tit{waarmee} `with what' takes precedence when all features form a constituent.
@@
 \tit{Met wat} `with what' appears when the functional sequence is disrupted.
+
+\section{Two mechanisms}
+
+\subsection{Suppletive obliques}
+
+\begin{table}[ht]
+	\center
+	\caption {Iron Ossetic pronoun and noun}
+	\begin{minipage}{0.56\linewidth}
+		\begin{tabularx}{\textwidth}{ccccccc}
+		\toprule
+              & 1.\tsc{sg}  & head    \\
+		\midrule
+    \tsc{nom} & æz          & sær-Ø   \\
+    \tsc{acc} & mæn-Ø       & sær-Ø   \\
+    \tsc{gen} & mæn (⁇?)    & sær-y   \\
+    \tsc{ins} & mæn-æj      & sær-æj  \\
+    \tsc{dat} & mæn-æn      & sær-æn  \\
+    \tsc{all} & mæn-mæ      & sær-mæ  \\
+    \tsc{ade} & mæn-yl      & sær-yl  \\
+    \tsc{eq}  & mæn-au      & sær-au  \\
+    \tsc{com} & mæn-imæ     & sær-imæ \\
+    \bottomrule
+\end{tabularx}
+\label{tbl:ossetic}
+\end{minipage}
+\end{table}
+
+now the question: is \tit{æz} a suppletive nominative or is \tit{mæn} the suppletive stem from the accusative on? ossetic has a way to tell: suspended affixation.
+
+What we see in (3-a) is an ordinary coordination of two phrases, each marked
+by a plural marker and a case marker. Suspended affixation is then illustrated in
+(3-b). It is a type of a coordination where the comitative case marker is located
+only on the second conjunct, with no change in interpretation. The first conjunct
+simply bears no case marker in such cases.
+
+\ex.
+\ag. bæx-t-imæ æmæ gæl-t-imæ\\
+horse-pl-com and ox-pl-com\\
+\bg. bæx-tæ æmæ gæl-t-imæ\\
+horse-pl and ox-pl-com\\
+`with horses and oxen' \hfill (Iron Ossetic, Erschler 2012: 165)
+
+doing this with 1\tsc{sg} shows that the bare stem is \tit{mæn}.
+
+\ex.
+\ag. mæn æmæ Zauyr-æn\\
+ 1.\tsc{sg} and Zaur-\tsc{dat}\\
+\bg. *æz æmæ Zauyr-æn\\
+ 1.\tbf{sg} and Zaur-\tsc{dat}\\
+ `me and Zaur' \hfill (Belyaev 2014: 39)
+
+\tit{mæn} is actually the caseless form, \tit{æz} is marked for nominative.
+
+my conclusion: Dutch has a suppletive form for nominative, accusative and dative. Then higher cases do not combine with that suppletive form, but with the unmarked form.
+
+'t
+'t
+'t
+er-van
+er-mee
+er-mee
+
+\subsection{Prefix or suffix}
+
+https://ling.auf.net/lingbuzz/001026
 
@@
 
-\subsection{Putting it back together}
+\section{Showing it in a derivation}
 

### 2020-01-12 paper.tex
doesnt compile anymore
look for mistake

@@
 
-\title{\tit{Waarmee} vs. \tit{met wat}\\
-Constituency spellout, r-pronouns}
+\title{How P inanimate pronoun becomes R-pronoun-P On waarmee in Dutch}
 \author{Fenna Bergsma}
@@
 
-\raggedright
-
 \maketitle
@@
 
+English has a sentence.
+This is ungrammatical in Dutch.
+We need an \tsc{r}-pronoun.
 The term \tsc{r}-pronoun \citep{riemsdijk1978} refers to a set of nominal elements that can strand prepositions in Dutch (and German).
@@
 
-\exg. Ik klim er-op.\\
+\ex. I climb on it.
+
+\ex.
+\ag. *Ik klim op 't.\\
+ I climb on it\\
+ `I climb on it.'\label{ex:klimopt}
+\bg. Ik klim er-op.\\
  I climb there-on\\
- `I am climbing on it.'\label{ex:klimerop}
-
-This paper focuses on a single \tsc{r}-pronoun in a specific type of free relative construction.
-The \tsc{r}-pronoun I focus on is the relative pronoun \tit{waarmee} `with what', which is interesting for two reasons.
+ `I climb on it.'\label{ex:klimerop}
+
+In Dutch it is impossible to have [P inanimate].
+But why?
+\citet{riemsdijk1978} postulating a filter that prohibits the existence of constituents consisting of prepositions and inanimates + some kind of allomoprhy.
+\citet{koopman2000} who makes reference to a different paradigm.
+Abels: base-generated somewhere else.
+
+This chapter is an in-depth study of the \tsc{r}-pronoun-postposition combination \tit{waarmee} `with what' in Dutch.
+This instance is interesting for two reasons.
 First, just like for all \tsc{r}-pronouns, the wh-element is the locative, but there is no meaning component related to location in `with what'.
@@
 
-The construction I focus on is a mismatching free relative.
+what I will show that r-pronouns are not a different construction to express the same meaning, but they realize the same features as regular P + pronoun combinations.
+It is a kind of allomorphy, just like Van Riemsdijk said.
+And not a different way to express the same function.
+
+Evidence from that comes from the complementary distribution of \tit{waarmee} and \tit{met wat} in mismatching free relatives.
+
 This is a free relative construction in which the two predicates (the one in the main clause and the one in the embedded clause) combine with two different cases (i.e.
@@
 This straightforwardly follows in a system in which spellout targets phrasal constituents: Nanosyntax \citep{starke2009}.
+--here more about the internal structure of r-pronouns, and the suffix prefix distinction--
 
@@
 I show that the \tsc{r}-pronoun surfaces when it forms a proper constituent, and \tit{met wat} `with what' when it does not.
-Section \ref{sec:suppletion} discusses how proper constituency relates to spellout by treating \tit{waarmee} `with what' as an instance of suppletion.
-In Section \ref{sec:finer}, I decompose \tit{waarmee} `with what' and \tit{met wat} `with what' to make sense of the phonological similarities, and I provide a more detailed analysis.
+I decompose \tit{waarmee} `with what' and \tit{met wat} `with what' to make sense of the phonological similarities, and I provide a more detailed analysis.
 Unmarked examples are constructed and have been verified by native speakers.
@@
 
-\tit{Met} `with' is a preposition that combines with full DPs and animate pronouns.
-\tit{Wat} `what' is a wh-element that appears as subject or object.
-There is no principled reason why \tit{met wat} `with what' should be ruled out.
-Previous work on \tsc{r}-pronoun has not given many insights, other than \citet{riemsdijk1978} postulating a filter that prohibits the existence of constituents consisting of prepositions and wh-elements or \citet{koopman2000} who makes reference to a different paradigm.
+\tit{Met} `with' is a preposition that combines with full DPs and animate pronouns. \tit{Wat} `what' is a wh-element that appears as subject or object.
 

### 2020-01-12 paper.tex
einde zondag
niet veel gedaan.. maar er is een mooi overzicht in het schrift! schrijven nu
einde zondag
begonnen met prefix/suffix

@@
 Second, the preposition \tit{met} `with' changes into \tit{mee} `with' when it is combined with an \tsc{r}-pronoun.
+To my knowledge, there is no account so far for this fact.
 
@@
 I decompose these two expressions further, and end up arguing for a picture as shown in Table \ref{tbl:nofeatures}.
+
 The elements \tit{w} and \tit{a} express the same syntactic structure in both expressions.
@@
 https://ling.auf.net/lingbuzz/001026
+
+It differs per language and within a language how high a DP can move.
+Everything below is a suffix on the noun, everything higher is a preposition.
+Consider German full DP.
+Moves as high as above the dative, instrumental is expressed with a preposition.
+
+\ex. mit ein loffel
+
+but like i said, it also differs within a language, for example look at bulgarian here!
+
+\ex.
+\ag. Tazi duma m-i e nepoznata.\\
+that word I-\tsc{dat} is unfamiliar\\
+`That word is unfamiliar to me.'
+\bg. Tazi duma e nepoznata sina mi.\\
+that word is unfamiliar son my\\
+`That word is unfamiliar my son.'
+\bg. Tazi duma e nepoznata na sina mi.\\
+that word is unfamiliar to son my\\
+`That word is unfamiliar to my son.'
 

### 2020-01-13 paper.tex
einde maandag
vanalles

@@
 
-\title{How P inanimate pronoun becomes R-pronoun-P On waarmee in Dutch}
+\title{From *[P pronoun\scsub{inanim}] to [\tsc{r}-pronoun-P]\\ On \tit{waarmee} in Dutch}
 \author{Fenna Bergsma}
@@
 \tsc{R}-pronouns morphologically consist of a combination of a preposition and locative pronoun.
-In the example \ref{ex:klimerop} \tit{op} `on' is the preposition and \tit{er} `there' is the locative pronoun.
+In the example \ref{ex:klimerop} \tit{op} `on' is the preposition and \tit{'r} `there' is the locative pronoun.
 
@@
  `I climb on it.'\label{ex:klimopt}
-\bg. Ik klim er-op.\\
- I climb there-on\\
+\bg. Ik klim 'r op.\\
+ I climb there on\\
  `I climb on it.'\label{ex:klimerop}
@@
 Second, the preposition \tit{met} `with' changes into \tit{mee} `with' when it is combined with an \tsc{r}-pronoun.
-To my knowledge, there is no account so far for this fact.
+This observervation has so far remained unexplained.
 
@@
 The predicate in the main clause clause, \tit{gekocht} `bought' combines with an accusative DP.
-The \tsc{r}-pronoun \tit{waarmee} `with what' is used here.\footnote{In this example \tit{mee} `with' is stranded and \tit{waar} `where' is moved to the left edge of the embedded clause.
-It is also possible for \tit{waar} `where' to bring \tit{mee} `with' along, as in \ref{ex:meealong}, but it is regarded as slightly less natural.
+The \tsc{r}-pronoun \tit{waarmee} `with what' is used here.\footnote{In this example, \tit{waar} `where' takes \tit{mee} `with' to the left edge of the embedded clause.
+It is also possible for \tit{mee} `with' to be stranded, and \tit{waar} `where' to be moved to the left edge of the embedded clause on its own.
 
 \exg. Ik heb gekocht waar jij mee schildert.\\
- I have bought where you with paint\\
+ I have bought waar you with paint\\
  `I bought what you are painting with.'\label{ex:meealong}
@@
 
-\exg. Ik heb gekocht waar jij mee schildert.\\
- I have bought where you with paint\\
+\exg. Ik heb gekocht waarmee jij schildert.\\
+ I have bought {where with} you paint\\
  `I bought what you are painting with.'\label{ex:gekochtwaarmee}
@@
  `I am painting with it.'\label{ex:prephet}
-\bg. Ik schilder er-mee.\\
+\bg. Ik schilder 'r mee.\\
  I paint there-with\\
  `I am painting with it.'\label{ex:preper}
-\bg. *Ik schilder mee er.\\
+\bg. *Ik schilder mee 'r.\\
  I paint with there\\
@@
 \ex.
-\ag. Ik zit er-op.\\
- I sit it-on\\
+\ag. Ik zit 'r op.\\
+ I sit there on\\
  `I am sitting on it.
@@
 \ex.
- \ag. Hij zwemt er-in.\\
-  He swims it-in\\
+ \ag. Hij zwemt 'r in.\\
+  he swims it-in\\
   `He is swimming in it.'
  \bg. *Hij zwemt in 't.\\
-  He swims in it\\
+  he swims in it\\
   `He is swimming in it.'
@@
 \bg. *Met wat schilder jij?\\
- With what paint you\\
+ with what paint you\\
  `What are you painting with?'\label{ex:metwat}
-\bg. Waar schilder jij mee?\\
- Where paint you with\\
+\bg. Waarmee schilder jij?\\
+ {where with} paint you with\\
  `What are you painting with?'\label{ex:waarmee}
@@
 \ex.\label{ex:headed}
-\ag. Ik schilder met de kwast waar jij ook mee schildert.\\
- I paint with the brush where you also with paint\\
+\ag. Ik schilder met de kwast waarmee jij ook schildert.\\
+ I paint with the brush {where with} you also paint\\
  `I am painting with the brush that you are painting with too.'
@@
  \ex.\label{ex:headless}
- \ag. Ik schilder waar jij ook mee schildert.\\
-  I paint where you also with paint\\
+ \ag. Ik schilder waarmee jij ook schildert.\\
+  I paint {where with} you also paint\\
   `I am painting with what you are painting with too.'
@@
 
-Table \ref{tbl:inanimates} summarizes the distribution of inanimates in Dutch.
-Inanimate (personal and wh-)pronouns in Dutch can function as objects verbs, but they are ungrammatical as objects of prepositions.
-In these contexts, \tsc{r}-pronouns appear.
-
-\begin{table}[ht]
-	\center
-	\caption {Inanimates in Dutch}
-	\begin{minipage}{0.7\linewidth}
-		\begin{tabularx}{\textwidth}{ccc}
-		\toprule
-                        & pers. pronouns & wh-pronouns \\
-  	\midrule
-objects of verbs        & 't             & wat         \\
-objects of prepositions & er             & waar        \\
-\bottomrule
-\end{tabularx}
-\label{tbl:inanimates}
-\end{minipage}
-\end{table}
+\tit{'t} `it' and \tit{wat} `what' do not combine with prepositions. They are substituted by respectively \tit{'r} `there' and \tit{waar} `where'.
 
@@
 \ex.\label{ex:grammatical}
-\ag. Ik heb gekocht waar jij mee schildert.\\
- I have bought where you with paint\\
+\ag. Ik heb gekocht waarmee jij schildert.\\
+ I have bought {where with} you paint\\
  `I bought what you are painting with.'\label{ex:grammaticalwaar}
@@
 \ex.
-\ag. Ik schilder er-mee.\\
- I paint there-with\\
+\ag. Ik schilder 'r mee.\\
+ I paint there with\\
  `I am painting with it.'\label{ex:const1}
-\bg. Waar schilder jij mee?\\
- Where paint you with\\
+\bg. Waarmee schilder jij?\\
+{where with} paint you with\\
  `What are you painting with?'\label{ex:const2}
-\bg. Ik schilder met de kwast [waar jij ook mee schildert].\\
- I paint with the brush where you also with paint\\
+\bg. Ik schilder met de kwast [waarmee jij ook schildert].\\
+ I paint with the brush {where with} you also paint\\
  `I am painting with the brush that you are painting with too.'\label{ex:const3}
-\bg. Ik schilder [waar jij ook mee schildert].\\
- I paint where you also with paint\\
+\bg. Ik schilder [waarmee jij ook schildert].\\
+ I paint {where with} you also paint\\
  `I am painting with what you are painting with too.'\label{ex:const4}
@@
 \ex.
-\a. [[ik] [[schilder] [er-mee]]]\label{ex:const1stage}
-\b. [[jij] [[schilder] [[waar] [mee]]]]\label{ex:const2stage}
-\b. [[jij] [[ook] [[schilder] [[waar] [mee]]]]]\label{ex:const3stage}
-
-There is additional evidence for the fact that \tit{waarmee} `with what' forms a constituent in the constructions above.
-In the example in \ref{ex:const2}-\ref{ex:const4} only \tit{waar} `where' was fronted, but \ref{ex:constwaarmee} shows that also the phrase containing \tit{mee} `with' can be moved.
+\a. [[ik] [[schilder] ['r mee]]]\label{ex:const1stage}
+\b. [[jij] [[schilder] [waarmee]]]\label{ex:const2stage}
+\b. [[jij] [[ook] [[schilder] [waarmee]]]]\label{ex:const3stage}
+
+%There is additional evidence for the fact that \tit{waarmee} `with what' forms a constituent in the constructions above.
+In the example in \ref{ex:const2}-\ref{ex:const4} only \tit{waar} `where' was fronted, but \ref{ex:constwaarmee} shows that also the phrase containing \tit{mee} with' can be moved.
 As wh-movement can only target constituents, it follows that \tit{waar} `where' and \tit{mee} `with' have to form a constituent.
 
-\ex.\label{ex:constwaarmee}
-\ag. Waar-mee schilder jij?\\
- {where-with} paint you\\
- `What are you painting with?'
-\bg. Ik schilder [waar-mee jij ook schildert].\\
- I paint {where-with} you also paint\\
- `I am painting with what you are painting with too.'
-\bg. Ik schilder met de kwast [waar-mee jij ook schildert].\\
- I paint with the brush {where-with} you also paint\\
- `I am painting with the brush that you are painting with too.'
+%\ex.\label{ex:constwaarmee}
+%\ag. Waar-mee schilder jij?\\
+ %{where-with} paint you\\
+ %`What are you painting with?'
+%\bg. Ik schilder [waar-mee jij ook schildert].\\
+ %I paint {where-with} you also paint\\
+ %`I am painting with what you are painting with too.'
+%\bg. Ik schilder met de kwast [waar-mee jij ook schildert].\\
+ %I paint with the brush {where-with} you also paint\\
+ %`I am painting with the brush that you are painting with too.'
 
@@
 \tit{Kopen} `to buy' takes an accusative DP as its object, illustrated in \ref{ex:kopen}.
-\tit{Schilderen} `to paint' can take an instrumental PP as its object., shown in \ref{ex:schilderen}.\footnote{\tit{Schilderen} also optionally takes an accusative object, but I am focussing on the instrumental here.}
+\tit{Schilderen} `to paint' can take an instrumental PP as its object., shown in \ref{ex:schilderen}.\footnote{\tit{Schilderen} also optionally takes an (accusative) object, but I am focussing on the instrumental object here.}
 
@@
 I repeat the mismatching free relative in which \tit{waarmee} `met wat' appears in \ref{ex:mismatchwaarmee}.
-The predicate \tit{schildert} `paints' combines in the embedded clause with the instrumental PP.
+The predicate \tit{schildert} `paints' combines in the embedded clause with the instrumental object.
 The PP forms a proper constituent within the embedded clause, and the PP can be realized as the \tsc{r}-pronoun \tit{waarmee} `with what'.\footnote{I assume that the embedded clause modifies a phonologically empty noun here which is the DP argument of \tit{gekocht} `bought'.}
 
-\exg. Ik heb gekocht [waar jij mee schildert].\\
- I have bought where you with paint\\
+\exg. Ik heb gekocht [waarmee jij schildert].\\
+ I have bought {where with} you paint\\
  `I bought what you are painting with.'\label{ex:mismatchwaarmee}
@@
 \ex.\label{ex:summaryconst}
-\a. *[[met] [wat]] → [waarmee]\label{ex:waarmeefr}
+\a. [[met] [wat]] → [waarmee]\label{ex:waarmeefr}
 \b. [met [wat [X]]]
@@
 
+Along the way I introduce some background
+
+Things to explain
+*P pronoun-inanimate
+
+\tit{r} is the locative
+\tit{met} changes form
+
+ The idea is that both expressions realize the same featu♦res, and \tit{waarmee} `with what' takes precedence when all features form a constituent.
+The morphemes I distinguish in \tit{waarmee} `with what' are \tit{w}, \tit{-aa-}, \tit{-r} and \tit{mee}.
+Within \tit{met wat} `with what' I distinguish \tit{met}, \tit{w}, \tit{a} and \tit{-t}.
+\ref{ex:decompose} shows this as well.
+
+\ex.\label{ex:decompose}
+\a. w -aa -r -mee
+\b. met w -a -t
+
 In this section I investigate the internal structure of \tit{waarmee} `with what' and \tit{met wat} `with what' to capture the phonological similarities and differences between the two forms.
 First, I identify \tit{w} and \tit{a} as morphemes that appear in both expressions.
-Putting these two aside, I concentrate on \tit{ermee} `with it' and \tit{met 't} `with it'.
+Putting these two aside, I concentrate on \tit{'rmee} `with it' and \tit{met 't} `with it'.
 I decompose these two expressions further, and end up arguing for a picture as shown in Table \ref{tbl:nofeatures}.
@@
 The elements \tit{w} and \tit{a} express the same syntactic structure in both expressions.
-The elements \tit{met} and \tit{'t} together also express the same features as \tit{mee} and \tit{er} together, but the distribution differs.
-\tit{Met} expresses less structure than \tit{mee}, and \tit{'t} expresses more structure than \tit{er}.
+The elements \tit{met} and \tit{'t} together also express the same features as \tit{mee} and \tit{'r} together, but the distribution differs.
+\tit{Met} expresses less structure than \tit{mee}, and \tit{'t} expresses more structure than \tit{'r}.
 \tit{Met} is shown to be an prefix, and \tit{mee} is a suffix.
-It also becomes clear that the \tit{er} in fact corresponds to the locative \tit{r} in Dutch.
+It also becomes clear that the \tit{'r} in fact corresponds to the locative \tit{r} in Dutch.
 
@@
     \tit{w}   & \multicolumn{1}{|c|}{\tit{a}}  & \tit{met} & \multicolumn{4}{|c}{\tit{'t}}                \\\hline
-    \tit{w}   & \multicolumn{1}{|c|}{\tit{a}}  & \multicolumn{4}{c|}{\tit{mee}}               & \tit{er}  \\
+    \tit{w}   & \multicolumn{1}{|c|}{\tit{a}}  & \multicolumn{4}{c|}{\tit{mee}}               & \tit{'r}  \\
     \bottomrule
@@
 
- The idea is that both expressions realize the same features, and \tit{waarmee} `with what' takes precedence when all features form a constituent.
-The morphemes I distinguish in \tit{waarmee} `with what' are \tit{w}, \tit{-aa-}, \tit{-r} and \tit{mee}.
-Within \tit{met wat} `with what' I distinguish \tit{met}, \tit{w}, \tit{a} and \tit{-t}.
-\ref{ex:decompose} shows this as well.
-
-\ex.\label{ex:decompose}
-\a. w -aa -r -mee
-\b. met w -a -t
+\subsection{Overlap: \tit{w-} and \tit{-a-}}
 
@@
 I assume that lengthening or shortening of the vowel is a result of the final \tit{r}.
+
+\ex. The Superset Principle \citet{starke2009}: \\
+A lexically stored tree matches a syntactic node iff the lexically stored tree contains the syntactic node.
+
+First of all, when two lexical entries are both candidates for spellout, the most specific is inserted, following the Elsewhere Condition:
+
+\ex. The Elsewhere Condition (\citealt{kiparsky1973}, formulated as in \citealt{caha2020}):\\
+When two entries can spell out a given node, the more specific entry wins. Under the Superset Principle governed insertion, the more specific entry is the one which has fewer unused features
 
@@
 I put \tit{w} and \tit{a} aside for now, assuming they spell out the same syntactic structure in \tit{waarmee} `with what' and \tit{met wat} `with what'.
-This leaves \tit{er-mee} `with it' and \tit{met 't} `with it'.\footnote{I assume that the \tit{e} in \tit{ermee} `with it' is there for phonological reasons.
+This leaves \tit{'r-mee} `with it' and \tit{met 't} `with it'.\footnote{I assume that the \tit{e} in \tit{'rmee} `with it' is there for phonological reasons.
 The vowel is dropped under the right phonological circumstances.
 
-\exg. Ik he niks mee te maken.\\
+\exg. Ik heb 'r niks mee te maken.\\
  I have there nothing with to make\\
@@
 \ex.
-\ag. er -mee\\
+\ag. 'r -mee\\
 there with\\
@@
 
-I repeat the examples from Section \ref{sec:rdefault} below that show that \tit{ermee} `with it' is used when it forms a proper constituent and \tit{met 't} `with it' is ungrammatical.
-
-\ex.
-\ag. Ik schilder er-mee.\\
+\subsection{Differences: \tit{'r} vs. \tit{'t} and \tit{met} vs. \tit{-mee}}
+
+Having put \tit{w-} and \tit{a} aside for now, the forms \tit{met 't} `with it` and \tit{'rmee} `with it' are left.
+Below I repeat examples from Section \ref{sec:rdefault} that show that \tit{met} `with` can express instrumental case, and \tit{'t} is an inanimate pronoun.
+\ref{ex:metdp} shows \tit{met} `with' combined with full DP.
+\ref{ex:tverb} shows \tit{'t} as the object of verbs.
+
+\ex.
+\ag. Ik schilder met een kwast.\\
+ I paint with a brush\\
+ `I am painting with a brush.'\label{ex:metdp}
+ \bg. Ik zie 't.\\
+  I see it\\
+  `I see it.'\label{ex:tverb}
+
+However, \tit{met} `with' and \tit{'t} `it' do not appear together if they form a proper constituent. Instead, \tit{'rmee} is used, as shown in \ref{ex:rmeeconst}.
+
+\ex.\label{ex:rmeeconst}
+\ag. Ik schilder 'r-mee.\\
  I paint there-with\\
@@
 
-In other words, both expessions realize the same features, and \tit{ermee} `with it' takes precedence when all features form a constituent.
+In this section I set up an account that makes the ungrammaticality of \tit{met 't} and the appearance of \tit{'rmee} follow from spellout.
+The analysis accounts for the following two observations, taking \tit{met 't} as the point of departure.
+First, \tit{met} `with' changes from being a preposition to being a suffix, and its form changes into \tit{mee}.
+This process is restricted to inanimate pronouns, and it does not apply to full DPs and animate pronouns.
+Second, \tit{'t} is replaced by \tit{'r}, a morpheme that is associated with the locative in Dutch.
+
+This section first discusses some basic facts about case and assumptions about Nanosyntax.
+Then I discuss the distinction between prefixes and suffixes, followed by a discussion on suppletion in pronouns.
+Finally, I specify the lexical entries for \tit{'rmee} `with it` and \tit{met 't} `with it` that account for the described facts.
+
+\subsubsection{Case and nanosyntax}
 
@@
 \bg. Ik heb hem een klap gegeven.\\
- I have \tsc{3sg.m.acc} a hit given\\
- `I hit him.'
+ I have \tsc{3sg.m.dat} a hit given\\
+ `I gave him a smack.'
 
@@
 I leave possible number and gender features out because they do not play a role in this paper.
-For case, I follow \citet{caha2009} that case features case features are organized the containment relation in \ref{ex:casetree}.
-The higher, more complex cases contain the smaller, less complex cases.
+
+The morpheme \tit{'t} can act as nominative, accusative and dative, as I showed in \ref{ex:tsubobj}. Taking this all together, \tit{'t} should have the lexical entry given in \ref{ex:entryt}.
+
+\ex. \begin{forest} boom
+ [\tsc{dat}P
+     [\tsc{f}3]
+     [\tsc{acc}P
+         [\tsc{f}2]
+         [\tsc{nom}P
+             [\tsc{f}1]
+             [\tsc{thingP}
+                 [\tsc{thing}, roof]
+             ]
+         ]
+     ]
+ ]
+ {\draw (.east) node[right]{⇔ \tit{'t}}; }
+ \end{forest}\label{ex:entryt}
+
+ IT CANNOT BE STRONG, but it is weak 't staat in de hal
+
+This lexical entry can lexicalize the \tsc{datP}, but also the \tsc{accP} and \tsc{nomP}, due to the Superset Principle.
+
+START WITH 'T IN DUTCH, JUST HOW I DID BEFORE. SUPERSET PRINCIPLE, CASE HIERARCHY, ALL OF IT
+
+THEN INTRODUCE PREFIX/SUFFIX DISTINCTION.
+
+I discuss the basics of spellout and case..
+
+\exg. mit ein-em Löffel\\
+with a-\tsc{dat.sg} spoon\\
+`with a spoon' \hfill (German)
+
+\ex. The preposition/suffix hierarchy
+\a. If the expression of a particular case in the Case sequence (below) involves a preposition, then all cases to its right do as well.
+\b. The Case sequence: \tsc{nom – acc – gen – dat – ins – com} \hfill \citep{2009}
+
+put this in syntax
 
@@
 
-The morpheme \tit{'t} can act as nominative, accusative and dative, as I showed in \ref{ex:tsubobj}. Taking this all together, \tit{'t} should have the lexical entry given in \ref{ex:entryt}.
-
-\ex. \begin{forest} boom
+now derive it with movements
+
+Spellout happens in a cyclic derivation, following a spellout algorithm \citep{starke2018}.
+After each instance of merge, spellout takes place.
+If no spellout exist for the phrase created by the newly added feature, evacuation movements specified in the spellout algorithm take place.
+The algorithm is given in \ref{ex:spellout}.
+
+\ex. Merge F and \label{ex:spellout}
+ \a. Spell out FP
+ \b. If (a) fails, attempt movement of the spec of the complement of \tsc{f}, and retry (a)
+ \b. If (b) fails, move the complement of \tsc{f}, and retry (a)
+
+When a new match is found, it overrides previous spellouts.
+
+\ex. Cyclic Override \citep{starke2018}:\\
+Lexicalisation at a node XP overrides any previous match at a phrase contained in XP.
+
+\ex.
+\a. \begin{forest} boom
+[\tsc{ins{}}
+    [\tsc{f5}, roof]
+]
+{\draw (.east) node[right]{⇔ \tit{mit}}; }
+\end{forest}\label{ex:mit}
+\b. \begin{forest} boom
 [\tsc{dat}P
@@
             [\tsc{f}1]
-             [\tsc{thingP}
-                 [\tsc{thing}, roof]
-             ]
-         ]
-     ]
- ]
- {\draw (.east) node[right]{⇔ \tit{'t}}; }
- \end{forest}\label{ex:entryt}
-
-This lexical entry can lexicalize the \tsc{datP}, but also the \tsc{accP} and \tsc{nomP}. This is due to the Superset Principle.
-
- \ex. The Superset Principle \citet{starke2009}: \\
- A lexically stored tree matches a syntactic node iff the lexically stored tree contains the syntactic node.
+        ]
+    ]
+]
+{\draw (.east) node[right]{⇔ \tit{-em}}; }
+\end{forest}\label{ex:em}
+
+If not match can be found, a specifier is constructed.
+
+\ex. Spec Formation \citep{starke2018}:\\
+If Merge F has failed to spell out (even after backtracking), try to spawn a new derivation providing the feature F and merge that with the current derivation, projecting the feature F at the top node.
+
+For case, I follow \citet{caha2009} that case features case features are organized the containment relation in \ref{ex:casetree}.
+The higher, more complex cases contain the smaller, less complex cases.
 
@@
 
-\ex.
-\a. \begin{forest} boom
-[\tsc{acc}P
-    [\tsc{f}2]
-    [\tsc{nom}P
-        [\tsc{f}1]
-        [\tsc{thingP}
-            [\tsc{thing}, roof]
-        ]
-    ]
-]
-\end{forest}\label{ex:tacc}
-\b. \begin{forest} boom
-[\tsc{nom}P
-    [\tsc{f}1]
-    [\tsc{thingP}
-        [\tsc{thing}, roof]
-    ]
-]
-\end{forest}\label{ex:tnom}
-
-Continuing with \tit{met} `with', which I have shown in this paper can be used to express instrumental. It can also be used as comitative, as shown in \ref{ex:metinscom}.
-
-\exg. Ik dans met hem.\\
- I dance with him\\
- `I am dancing with him.'\label{ex:metinscom}
-
-Case features are in a containment relation and instrumental contains all case features down to \tsc{f1}.
-Some of these features are expressed by the preposition, and other by the DP they combine with.
-As pronouns in Dutch can realize up to \tsc{f3}, the preposition starts from \tsc{f4}.
-
- \ex. \begin{forest} boom
- [\tsc{com}P
-     [\tsc{f}5]
-     [\tsc{f}4]
- ]
- {\draw (.east) node[right]{⇔ \tit{met}}; }
- \end{forest}\label{ex:entrymet}
-
-In sum, the syntactic structure that \tit{met wat} `with what' realizes is the one in \ref{ex:stmetwat}.
-
-\ex. [ [ [ [ \tsc{thing} ] \tsc{f1} ] \tsc{f2} ] \tsc{f3} \tsc{f4} ]\label{ex:stmetwat}
-
-Let us now turn to \tit{ermee} `with it', which lexicalizes the same structure as \tit{met 't} `with it', but with a different distribution.
-
-\tit{Er} `there' can be used as a locative.
-
-\exg. Ik ben er al geweest.\\
- I am there already been\\
- `I have already been there.'
-
-I follow \cite{baunaz2018} in assuming that the ontological category \tsc{location} contains \tsc{thing}.\footnote{\citet{baunaz2018} place in addition \tsc{person} between \tsc{thing} and \tsc{location}, which I left out here.}
-
- \ex. \begin{forest} boom
- [\tsc{loc}P
- [\tsc{location}]
-     [\tsc{thngP}
-         [\tsc{thing}, roof]
-     ]
- ]
- {\draw (.east) node[right]{⇔ \tit{er}}; }
- \end{forest}\label{ex:entryr}
-
-Notice already here that, via the superset principle, \tit{er} can be used to realize the feature \tsc{thing} as well, as it is contained in \tsc{locP}.
-
-So far, \tit{er} `there' only realizes the feature \tsc{thing} from the structure in \ref{ex:stmetwat}.
-This leaves \tsc{f1} to \tsc{f4} to be realized by \tit{mee}.
-I give the lexical tree in \ref{ex:entrymee}.
-
-\ex. \begin{forest} boom
-[\tsc{com}P
-    [\tsc{f}5]
-    [\tsc{insP}
-        [\tsc{f}4]
-        [\tsc{dat}P
-            [\tsc{f}3]
-            [\tsc{acc}P
-                [\tsc{f}2]
-                [\tsc{nom}P
-                    [\tsc{f}1]
-                ]
-            ]
-        ]
-    ]
-]
-{\draw (.east) node[right]{⇔ \tit{mee}}; }
-\end{forest}\label{ex:entrymee}
-
-Note that there are two differences between the lexical entry in \ref{ex:entrymet} and \ref{ex:entrymee}.
-First, the lexical entry for \tit{mee} `with' in \ref{ex:entrymee}, in addition to the one for \tit{met} `with' in \ref{ex:entrymet}, contains the features \tsc{f1}, \tsc{f2} and \tsc{f3}.
-Second, the lexical entry in \ref{ex:entrymet} has a binary bottom, and the lexical entry in \ref{ex:entrymee} has a unary bottom.
-Nanosyntax distinguishes prefixes and suffixes by distinguishing these types of lexical entries.
-This is the crucial differences needed for the Dutch instrumental.
-\tit{Met} `with' is a prefix (preposition), so it has a binary bottom, and \tit{mee} `with' is a suffix, so it needs a unary bottom.
-In the next section I show how this works in a derivation.\footnote{For completeness, \tit{mee} `with' has to be blocked from combining with full DPs and animate pronouns (reference).
-For now I assume that these pronouns spell out an additional feature \tit{σ} that is not realized by \tit{mee} `with' but only by \tit{met} `with'.
-Full DPs combine in addition with a zero marker for dative case.
-This way \tit{mee} `with' does not compete with \tit{met} `anymore'.
-I left this features out in this paper, at is does not contribute to the main point.}\footnote{Giving \tit{met} `with' and \tit{mee} `with' two distinct lexical entries has as a consequence that the phonological overlap between them seems like a coincidence.
-Moreover, in almost all cases the preposition does not change form when it combines with an \tsc{r}-pronoun, e.g.
-\tit{in}.
-If this proposal is on the right track, elements as \tit{in} can be used as either a prefix and as a suffix.
-A lexical entry as in \ref{ex:presuf} would be a candidate for such an element.
-
-\ex. \begin{forest} boom
-[XP
-    [XP
-        [X,roof]
-    ]
-    [YP
-        [Y]
-    ]
-]
-{\draw (.east) node[right]{⇔ \tit{in}}; }
-\end{forest}\label{ex:presuf}
-
-I leave it to future research to determine whether this is a feasible solution.}\footnote{I do not address the ordering difference of the wh-element and the adposition.
-A topic related to (but not relevant for) this paper is the different positioning of identical adpositions in Dutch.
-In \ref{ex:dutchin}, \tit{in} changes meaning dependent on whether it proceeds or follows the DP, it is respectively locational or directional.
-
-\ex.\label{ex:dutchin}
-\ag. Ik klim in de boom.\\
- I climb in the tree\\
- `I am climbing in the tree.'
-\bg. Ik klim de boom in.\\
- I climb the tree in\\
- `I am climbing into the tree.'
-
-The different positioning of the adpositions in \tsc{r}-pronouns is driven by spellout and is, therefore, meaningless.}
-
-Table \ref{tbl:withfeatures} gives an overview of the distribution of the features in \tit{met wat} `with what' and \tit{waarmee} `with what'.
-In both cases, \tit{w} and \tit{a} are the realization of the same morpheme.
-The difference between the two expressions lies in the distribution of the case features.
-\tit{Mee} `with' realizes all of them, and \tit{met} `with' only the top two.
-The residues are realized by respectively \tit{er} `there' and \tit{'t} `it'.
-
-\begin{table}[ht]
-	\center
-	\caption {\tit{met wat} and \tit{waarmee}}
-	\begin{minipage}{0.56\linewidth}
-		\begin{tabularx}{\textwidth}{ccccccc}
-		\toprule
-    \tsc{wh}  & \tsc{deix}                     & \tsc{f}4  & \tsc{f}3 & \tsc{f}2  & \tsc{f}1  & \tsc{thing} \\
-		\midrule
-    \tit{w}   & \multicolumn{1}{|c|}{\tit{a}}  & \tit{met} & \multicolumn{4}{|c}{\tit{'t}}                \\\hline
-    \tit{w}   & \multicolumn{1}{|c|}{\tit{a}}  & \multicolumn{4}{c|}{\tit{mee}}               & \tit{er}  \\
-    \bottomrule
-\end{tabularx}
-\label{tbl:withfeatures}
-\end{minipage}
-\end{table}
-
-In the next section I put all features back together in a derivation and I show how \tit{waarmee} `with what' surfaces when all features form a constituent.
-\tit{Met wat} `with what' appears when the functional sequence is disrupted.
-
-\section{Two mechanisms}
-
-\subsection{Suppletive obliques}
+Nanosyntax distinguishes prefixes and suffixes by distinguishing these types of lexical entries. This is the crucial difference needed for the Dutch instrumental.
+
+It differs per language and within a language how high a DP can move.
+Everything below is a suffix on the noun, everything higher is a preposition.
+Consider German full DP.
+Moves as high as above the dative, instrumental is expressed with a preposition.
+
+but like i said, it also differs within a language, for example look at bulgarian here!
+
+\ex.
+\ag. Tazi duma m-i e nepoznata.\\
+that word I-\tsc{dat} is unfamiliar\\
+`That word is unfamiliar to me.'
+\bg. Tazi duma e nepoznata sina mi.\\
+that word is unfamiliar son my\\
+`That word is unfamiliar my son.'
+\bg. Tazi duma e nepoznata na sina mi.\\
+that word is unfamiliar to son my\\
+`That word is unfamiliar to my son.'
+
+The same intuition will hold for Dutch.
+-mee is going to be a suffix that will be able to attach to 'r, but it will not to full DPs and animates.
+
+\subsubsection{Backtracking}
+
+If the spellout procedure in \ref{ex:spellout} fails, backtracking takes place.
+
+\ex. Backtracking \citep{starke2018}:\\
+When spellout fails, go back to the previous cycle, and try the next option for that cycle.
 
@@
 't
-er-van
-er-mee
-er-mee
-
-\subsection{Prefix or suffix}
-
-https://ling.auf.net/lingbuzz/001026
-
-It differs per language and within a language how high a DP can move.
-Everything below is a suffix on the noun, everything higher is a preposition.
-Consider German full DP.
-Moves as high as above the dative, instrumental is expressed with a preposition.
-
-\ex. mit ein loffel
-
-but like i said, it also differs within a language, for example look at bulgarian here!
-
-\ex.
-\ag. Tazi duma m-i e nepoznata.\\
-that word I-\tsc{dat} is unfamiliar\\
-`That word is unfamiliar to me.'
-\bg. Tazi duma e nepoznata sina mi.\\
-that word is unfamiliar son my\\
-`That word is unfamiliar my son.'
-\bg. Tazi duma e nepoznata na sina mi.\\
-that word is unfamiliar to son my\\
-`That word is unfamiliar to my son.'
+'r-van
+'r-mee
+'r-mee
+
+\subsubsection{The lexical entries}
+
+Continuing with \tit{met} `with', which I have shown in this paper can be used to express instrumental. It can also be used as comitative, as shown in \ref{ex:metinscom}.
+
+\exg. Ik dans met hem.\\
+ I dance with him\\
+ `I am dancing with him.'\label{ex:metinscom}
+
+Case features are in a containment relation and instrumental contains all case features down to \tsc{f1}.
+Some of these features are expressed by the preposition, and other by the DP they combine with.
+As pronouns in Dutch can realize up to \tsc{f3}, the preposition starts from \tsc{f4}.
+
+ \ex. \begin{forest} boom
+ [\tsc{com}P
+     [\tsc{f}5]
+     [\tsc{f}4]
+ ]
+ {\draw (.east) node[right]{⇔ \tit{met}}; }
+ \end{forest}\label{ex:entrymet}
+
+In sum, the syntactic structure that \tit{met wat} `with what' realizes is the one in \ref{ex:stmetwat}.
+
+\ex. [ [ [ [ \tsc{thing} ] \tsc{f1} ] \tsc{f2} ] \tsc{f3} \tsc{f4} ]\label{ex:stmetwat}
+
+Let us now turn to \tit{'rmee} `with it', which lexicalizes the same structure as \tit{met 't} `with it', but with a different distribution.
+
+\tit{'r} `there' can be used as a locative.
+
+\exg. Ik ben er al geweest.\\
+ I am there already been\\
+ `I have already been there.'
+
+I follow \cite{baunaz2018} in assuming that the ontological category \tsc{location} contains \tsc{thing}.
+
+\footnote{\citet{baunaz2018} place in addition \tsc{person} between \tsc{thing} and \tsc{location}, which I left out here.}
+
+ \ex. \begin{forest} boom
+ [\tsc{loc}P
+ [\tsc{location}]
+     [\tsc{thingP}
+         [\tsc{thing}, roof]
+     ]
+ ]
+ {\draw (.east) node[right]{⇔ \tit{'r}}; }
+ \end{forest}\label{ex:entryr}
+
+Notice already here that, via the superset principle, \tit{'r} can be used to realize the feature \tsc{thing} as well, as it is contained in \tsc{locP}.
+
+So far, \tit{'r} `there' only realizes the feature \tsc{thing} from the structure in \ref{ex:stmetwat}.
+This leaves \tsc{f1} to \tsc{f4} to be realized by \tit{mee}.
+I give the lexical tree in \ref{ex:entrymee}.
+
+\ex. \begin{forest} boom
+[\tsc{com}P
+    [\tsc{f}5]
+    [\tsc{insP}
+        [\tsc{f}4]
+        [\tsc{dat}P
+            [\tsc{f}3]
+            [\tsc{acc}P
+                [\tsc{f}2]
+                [\tsc{nom}P
+                    [\tsc{f}1]
+                ]
+            ]
+        ]
+    ]
+]
+{\draw (.east) node[right]{⇔ \tit{mee}}; }
+\end{forest}\label{ex:entrymee}
+
+Note that there are two differences between the lexical entry in \ref{ex:entrymet} and \ref{ex:entrymee}.
+First, the lexical entry for \tit{mee} `with' in \ref{ex:entrymee}, in addition to the one for \tit{met} `with' in \ref{ex:entrymet}, contains the features \tsc{f1}, \tsc{f2} and \tsc{f3}.
+Second, the lexical entry in \ref{ex:entrymet} has a binary bottom, and the lexical entry in \ref{ex:entrymee} has a unary bottom.
+\tit{Met} `with' is a prefix (preposition), so it has a binary bottom, and \tit{mee} `with' is a suffix, so it needs a unary bottom.
+In the next section I show how this works in a derivation.
+
+\footnote{For completeness, \tit{mee} `with' has to be blocked from combining with full DPs and animate pronouns (reference).
+For now I assume that these pronouns spell out an additional feature \tit{σ} that is not realized by \tit{mee} `with' but only by \tit{met} `with'.
+Full DPs combine in addition with a zero marker for dative case.
+This way \tit{mee} `with' does not compete with \tit{met} `anymore'.
+I left this features out in this paper, at is does not contribute to the main point.}
+
+\footnote{Giving \tit{met} `with' and \tit{mee} `with' two distinct lexical entries has as a consequence that the phonological overlap between them seems like a coincidence.
+Moreover, in almost all cases the preposition does not change form when it combines with an \tsc{r}-pronoun, e.g.
+\tit{in}.
+If this proposal is on the right track, elements as \tit{in} can be used as either a prefix and as a suffix.
+A lexical entry as in \ref{ex:presuf} would be a candidate for such an element.
+
+\ex. \begin{forest} boom
+[XP
+    [XP
+        [X,roof]
+    ]
+    [YP
+        [Y]
+    ]
+]
+{\draw (.east) node[right]{⇔ \tit{in}}; }
+\end{forest}\label{ex:presuf}
+
+I leave it to future research to determine whether this is a feasible solution.}
+
+\footnote{A topic related to this paper is the different positioning of identical adpositions in Dutch (see \citet{caha2010} for an account of German and Dutch and \citet{pretorius2017} for Afrikaans).
+In \ref{ex:dutchin}, \tit{in} changes meaning dependening on whether it proceeds or follows the DP, it is respectively locational or directional.
+
+\ex.\label{ex:dutchin}
+\ag. Ik klim in de boom.\\
+ I climb in the tree\\
+ `I am climbing in the tree.'
+\bg. Ik klim de boom in.\\
+ I climb the tree in\\
+ `I am climbing into the tree.'
+
+In \ref{ex:dutchin}, the movement of the adposition is driven by movement, and it is meaningful.
+The movement I discuss in this paper with \tsc{r}-pronouns is driven by spellout, and it is meaningless.}
+
+Table \ref{tbl:withfeatures} gives an overview of the distribution of the features in \tit{met wat} `with what' and \tit{waarmee} `with what'.
+In both cases, \tit{w} and \tit{a} are the realization of the same morpheme.
+The difference between the two expressions lies in the distribution of the case features.
+\tit{Mee} `with' realizes all of them, and \tit{met} `with' only the top two.
+The residues are realized by respectively \tit{'r} `there' and \tit{'t} `it'.
+
+\begin{table}[ht]
+	\center
+	\caption {\tit{met wat} and \tit{waarmee}}
+	\begin{minipage}{0.56\linewidth}
+		\begin{tabularx}{\textwidth}{ccccccc}
+		\toprule
+    \tsc{wh}  & \tsc{deix}                     & \tsc{f}4  & \tsc{f}3 & \tsc{f}2  & \tsc{f}1  & \tsc{thing} \\
+		\midrule
+    \tit{w}   & \multicolumn{1}{|c|}{\tit{a}}  & \tit{met} & \multicolumn{4}{|c}{\tit{'t}}                \\\hline
+    \tit{w}   & \multicolumn{1}{|c|}{\tit{a}}  & \multicolumn{4}{c|}{\tit{mee}}               & \tit{'r}  \\
+    \bottomrule
+\end{tabularx}
+\label{tbl:withfeatures}
+\end{minipage}
+\end{table}
+
+In the next section I put all features back together in a derivation and I show how \tit{waarmee} `with what' surfaces when all features form a constituent.
+\tit{Met wat} `with what' appears when the functional sequence is disrupted.
 
@@
 
-Before I show that \tit{waarmee} `with what' is used when all features form a proper constituent, I need to make some assumptions about the spellout process in Nanosyntax explicit.
-
-First of all, when two lexical entries are both candidates for spellout, the most specific is inserted, following the Elsewhere Condition:
-
-\ex. The Elsewhere Condition (\citealt{kiparsky1973}, formulated as in \citealt{caha2020}):\\
-When two entries can spell out a given node, the more specific entry wins. Under the Superset Principle governed insertion, the more specific entry is the one which has fewer unused features
-
-Second, spellout happens in a cyclic derivation, following a spellout algorithm \citep{starke2018}.
-After each instance of merge, spellout takes place.
-If no spellout exist for the phrase created by the newly added feature, evacuation movements specified in the spellout algorithm take place.
-The algorithm is given in \ref{ex:spellout}.
-
-\ex. Merge F and \label{ex:spellout}
- \a. Spell out FP
- \b. If (a) fails, attempt movement of the spec of the complement of \tsc{f}, and retry (a)
- \b. If (b) fails, move the complement of \tsc{f}, and retry (a)
-
-When a new match is found, it overrides previous spellouts.
-
-\ex. Cyclic Override \citep{starke2018}:\\
-Lexicalisation at a node XP overrides any previous match at a phrase contained in XP.
-
-If the spellout procedure in \ref{ex:spellout} fails, backtracking takes place.
-
-\ex. Backtracking \citep{starke2018}:\\
-When spellout fails, go back to the previous cycle, and try the next option for that cycle.
-
-If backtracking also does not help, a specifier is constructed.
-
-\ex. Spec Formation \citep{starke2018}:\\
-If Merge F has failed to spell out (even after backtracking), try to spawn a new derivation providing the feature F and merge that with the current derivation, projecting the feature F at the top node.
-
-With this theoretical background in the back of our minds, we can turn to the derivation.
-I first show how \tit{ermee} `with it' is constructed.
+Repeat spellout algorithm
+
+spellout
+backtracking
+complex spec
+
+I first show how \tit{'rmee} `with it' is constructed.
 I leave out \tit{w} and \tit{a}, because it unnecessarily complicates the story.\footnote{I assume that the WP and \tsc{deixP} appear lower in the structure than the case features, so the functional sequence is as given in \ref{ex:fseq}.
@@
  ]
-{\draw (.east) node[right]{⇒ \tit{er}}; }
+{\draw (.east) node[right]{⇒ \tit{'r}}; }
 \end{forest}\label{ex:thingspellout}
@@
 The derivation ends up backtracking into the cycle in which \tsc{f1} was merged.
-At this stage, \tsc{thing} was realized as \tit{er}.
+At this stage, \tsc{thing} was realized as \tit{'r}.
 Here there is again no specifier, but complement movement provides a structure that is fit for a lexical entry, namely: \ref{ex:entrymee}.
@@
    ]
-   {\draw (.east) node[right]{⇒ \tit{er}}; }
+   {\draw (.east) node[right]{⇒ \tit{'r}}; }
    [\tsc{nom}P
@@
    ]
-   {\draw (.east) node[right]{⇒ \tit{er}}; }
+   {\draw (.east) node[right]{⇒ \tit{'r}}; }
    [\tsc{acc}P
@@
 
-The same happens for \tsc{f3} and \tsc{f4}, and the complete structure is realizes as shown in \ref{ex:spelloutermee}.
+The same happens for \tsc{f3} and \tsc{f4}, and the complete structure is realizes as shown in \ref{ex:spellout'rmee}.
 
@@
     ]
-    {\draw (.east) node[right]{⇒ \tit{er}}; }
+    {\draw (.east) node[right]{⇒ \tit{'r}}; }
     [\tsc{insP}
@@
 ]
-\end{forest}\label{ex:spelloutermee}
-
-Skipping over the irrelevant details of how \tit{w} and \tit{a} end up in their positions, the structure for \tit{waarmee} `with what' look as in \ref{ex:spelloutwaarmee}.\footnote{I assume that WP and \tsc{deixP} are both complex specifiers that are created after \tsc{thing} is spelled out in \ref{ex:thingspellout}.
-In after each merge after that, backtracking always takes place, the complex specifier is detached from the structure and the case features are spelled out together with or as a suffix on \tsc{thing}.}\footnote{A consequence of analyzing \tit{mee} `with' as a suffix is that \tit{r} and \tit{mee} always form a constituent to the exclusion of \tit{w} and \tit{a}.
-This is problematic because \tit{waar} `where' can move leaving \tit{mee} `with' behind.
-To resolve the situation I assume that \tit{mee} `with' is evacuated and \tit{waar} `where' remnant moves after that.}
+\end{forest}\label{ex:spellout'rmee}
+
+Skipping over the irrelevant details of how \tit{w} and \tit{a} end up in their positions, the structure for \tit{waarmee} `with what' look as in \ref{ex:spelloutwaarmee}.
+\footnote{I assume that WP and \tsc{deixP} are both complex specifiers that are created after \tsc{thing} is spelled out in \ref{ex:thingspellout}.
+In after each merge after that, backtracking always takes place, the complex specifier is detached from the structure and the case features are spelled out together with or as a suffix on \tsc{thing}.}
 
@@
             ]
-            {\draw (.east) node[right]{⇒ \tit{er}}; }
+            {\draw (.east) node[right]{⇒ \tit{'r}}; }
             [\tsc{insP}
@@
 
+A consequence of analyzing \tit{mee} `with' as a suffix is that \tit{r} and \tit{mee} always form a constituent to the exclusion of \tit{w} and \tit{a}.
+At first sight this seems problematic, because it is possible for \tit{waar} `where', stranding \tit{mee} `with'.
+I repeat the relevant example in \ref{ex:meestranded}.
+
+\exg. Ik heb gekocht waar jij mee schildert.\\
+ I have bought waar you with paint\\
+ `I bought what you are painting with.'\label{ex:meestranded}
+
+There is no constituent in \ref{ex:spelloutwaarmee} that contains \tit{waar} but not \tit{mee}.
+To resolve this situation I follow \citet{noonan2017dutch} in assuming that the phrase containing the adposition (here \tit{mee}) syntactically moves to a position higher in the structure.
+The movement of the adposition has the typical distribution of that of verbal particles (cf.
+\citealt{riemsdijk1978,noonan2017dutch}, and it could possibly be triggered by the feature Σ, associated with weak pronouns.
+With \tit{mee} having moved out, the WP only contains features that are realized as \tit{waar}, and it moves to the left edge of the clause, resulting in the surface order in \ref{ex:meestranded}.
+
 So far I showed how \tit{waarmee} `with what' is derived if all syntactic features form a constituent.
@@
 Looking more into detail, \tit{waarmee} `with what' takes precedence over \tit{met wat} `with what' because \tit{mee} has the structure of a suffix.
-Following the spellout algorithm, \tit{'t} `it' is replaced by \tit{er} `there', so that it can combine with \tit{mee} `with'.
+Following the spellout algorithm, \tit{'t} `it' is replaced by \tit{'r} `there', so that it can combine with \tit{mee} `with'.
 The preposition \tit{met} `with' is only used if there is no other option to spell out the features.
@@
 Just like \citet{riemsdijk1978}, I claim that \tsc{r}-pronouns originate as the complement of P.
-He argued that due to some kind of suppletion \tit{'t} `it' changes form to \tsc{er}, which is coincidentally also the locative in Dutch.
+He argued that due to some kind of suppletion \tit{'t} `it' changes form to \tsc{'r}, which is coincidentally also the locative in Dutch.
 In my proposal, this suppletion follows naturally from the regular spellout algorithm.

### 2020-01-14 paper.tex
mid tuesday

@@
 
-\title{From *[P pronoun\scsub{inanim}] to [\tsc{r}-pronoun-P]\\ On \tit{waarmee} in Dutch}
+\title{No preposition with inanimate but an \tsc{r}-pronoun with postposition\\
+On \tit{waarmee} vs. \tit{met wat} in Dutch}
 \author{Fenna Bergsma}
@@
 
+In answering the question why [P inanimate] I look at an exception to the rule that *P inanimate pronoun. That exception is a mismatching free relative. Here the string \tit{met wat} does appear.
+
 what I will show that r-pronouns are not a different construction to express the same meaning, but they realize the same features as regular P + pronoun combinations.
@@
 This straightforwardly follows in a system in which spellout targets phrasal constituents: Nanosyntax \citep{starke2009}.
---here more about the internal structure of r-pronouns, and the suffix prefix distinction--
+--here more about the internal structure of r-pronouns, and the postposition preposition distinction--
 
@@
 Putting these two aside, I concentrate on \tit{'rmee} `with it' and \tit{met 't} `with it'.
-I decompose these two expressions further, and end up arguing for a picture as shown in Table \ref{tbl:nofeatures}.
 
@@
 \tit{Met} expresses less structure than \tit{mee}, and \tit{'t} expresses more structure than \tit{'r}.
-\tit{Met} is shown to be an prefix, and \tit{mee} is a suffix.
+\tit{Met} is shown to be an preposition, and \tit{mee} is a postposition.
 It also becomes clear that the \tit{'r} in fact corresponds to the locative \tit{r} in Dutch.
-
-\begin{table}[ht]
-	\center
-	\caption {\tit{met wat} and \tit{waarmee}}
-	\begin{minipage}{0.56\linewidth}
-		\begin{tabularx}{\textwidth}{ccccccc}
-		\toprule
-    \phantom{\tsc{wh}}  & \phantom{\tsc{deix}}                    & \phantom{\tsc{f}4}  & \phantom{\tsc{f}3} & \phantom{\tsc{f}2}  & \phantom{\tsc{f}1}  & \phantom{\tsc{thing}} \\
-		%\midrule
-    \tit{w}   & \multicolumn{1}{|c|}{\tit{a}}  & \tit{met} & \multicolumn{4}{|c}{\tit{'t}}                \\\hline
-    \tit{w}   & \multicolumn{1}{|c|}{\tit{a}}  & \multicolumn{4}{c|}{\tit{mee}}               & \tit{'r}  \\
-    \bottomrule
-\end{tabularx}
-\label{tbl:nofeatures}
-\end{minipage}
-\end{table}
 
@@
 Exactly because they appear in both expression, I do not pay much attention to them.
-For \tit{w} I follow \citet{hachem2015} in that \tit{w} realizes a WP.
+For \tit{w} I follow \citet{hachem2015} in that \tit{w} realizes a WP.\footnote{Throughout the paper, ⇔ indicates the pairing between a lexical tree and a phonological form in a lexical entry, and ⇒ indicates how a node in the syntactic structure is spelled out.}
 
@@
 I assume that lengthening or shortening of the vowel is a result of the final \tit{r}.
-
-\ex. The Superset Principle \citet{starke2009}: \\
-A lexically stored tree matches a syntactic node iff the lexically stored tree contains the syntactic node.
-
-First of all, when two lexical entries are both candidates for spellout, the most specific is inserted, following the Elsewhere Condition:
-
-\ex. The Elsewhere Condition (\citealt{kiparsky1973}, formulated as in \citealt{caha2020}):\\
-When two entries can spell out a given node, the more specific entry wins. Under the Superset Principle governed insertion, the more specific entry is the one which has fewer unused features
 
@@
 The analysis accounts for the following two observations, taking \tit{met 't} as the point of departure.
-First, \tit{met} `with' changes from being a preposition to being a suffix, and its form changes into \tit{mee}.
+First, \tit{met} `with' changes from being a preposition to being a postposition, and its form changes into \tit{mee}.
 This process is restricted to inanimate pronouns, and it does not apply to full DPs and animate pronouns.
@@
 This section first discusses some basic facts about case and assumptions about Nanosyntax.
-Then I discuss the distinction between prefixes and suffixes, followed by a discussion on suppletion in pronouns.
+Then I discuss the distinction between prepositiones and postpositiones, followed by a discussion on suppletion in pronouns.
 Finally, I specify the lexical entries for \tit{'rmee} `with it` and \tit{met 't} `with it` that account for the described facts.
 
-\subsubsection{Case and nanosyntax}
-
-Let me continue with specifying the lexical entries for \tit{met 't} `with it'. \tit{'t} `it' can be used as subject, direct object and indirect object, as shown in \ref{ex:tsubobj}.
+\subsubsection{\tit{'t} vs. \tit{'r}}
+
+Let me start with the lexical entry for \tit{'t}.
+\tit{'t} `it' can be used as subject (associated with nominative), direct object (associated in accusative) and indirect object (associated with dative), as shown in \ref{ex:tsubobj}.
 
@@
  \tsc{3sg.n.nom} stands in the hallway\\
- `It is standing in the hallway.'
+ `It is standing in the hallway.'\label{ex:tnoclitic}
 \bg. Ik zie 't.\\
@@
  I have \tsc{3sg.n.dat} a hit given\\
- `I hit it.'
-
-Pronouns in other genders alternate between nominative (non-oblique) and accusative/dative (oblique) in these contexts, illustrated in \ref{ex:hemsubobj}.
-
-\ex.\label{ex:hemsubobj}
-\ag. Hij staat in de hal.\\
- \tsc{3sg.m.nom} stands in the hallway\\
- `He is standing in the hallway.'
-\bg. Ik zie hem.\\
- I see \tsc{3sg.m.acc}\\
- `I see it.'
-\bg. Ik heb hem een klap gegeven.\\
- I have \tsc{3sg.m.dat} a hit given\\
- `I gave him a smack.'
-
-I assume that the inanimate personal pronoun minimally contains the ontological category \tsc{thing} \citep{kayne2005}.
-I leave possible number and gender features out because they do not play a role in this paper.
-
-The morpheme \tit{'t} can act as nominative, accusative and dative, as I showed in \ref{ex:tsubobj}. Taking this all together, \tit{'t} should have the lexical entry given in \ref{ex:entryt}.
-
-\ex. \begin{forest} boom
- [\tsc{dat}P
-     [\tsc{f}3]
-     [\tsc{acc}P
-         [\tsc{f}2]
-         [\tsc{nom}P
-             [\tsc{f}1]
-             [\tsc{thingP}
-                 [\tsc{thing}, roof]
-             ]
-         ]
-     ]
- ]
- {\draw (.east) node[right]{⇔ \tit{'t}}; }
- \end{forest}\label{ex:entryt}
-
- IT CANNOT BE STRONG, but it is weak 't staat in de hal
-
-This lexical entry can lexicalize the \tsc{datP}, but also the \tsc{accP} and \tsc{nomP}, due to the Superset Principle.
-
-START WITH 'T IN DUTCH, JUST HOW I DID BEFORE. SUPERSET PRINCIPLE, CASE HIERARCHY, ALL OF IT
-
-THEN INTRODUCE PREFIX/SUFFIX DISTINCTION.
-
-I discuss the basics of spellout and case..
-
-\exg. mit ein-em Löffel\\
-with a-\tsc{dat.sg} spoon\\
-`with a spoon' \hfill (German)
-
-\ex. The preposition/suffix hierarchy
-\a. If the expression of a particular case in the Case sequence (below) involves a preposition, then all cases to its right do as well.
-\b. The Case sequence: \tsc{nom – acc – gen – dat – ins – com} \hfill \citep{2009}
-
-put this in syntax
+ `I gave it a hit.'
+
+For case, I follow \citet{caha2009} that case features case features are organized the containment relation in \ref{ex:casetree}.
+The higher, more complex cases contain the smaller, less complex cases.
 
@@
 
-now derive it with movements
+ Following the distinctions from \citet{cardinaletti1996}, \tit{'t} `it' is a weak pronoun.
+It is not a clitic, because it can occur in sentence initial position, shown in \ref{ex:tnoclitic}.
+It is not a strong pronoun, because it cannot be coordinated, as indicated in  \ref{ex:tcoordinated}.
+\ref{ex:datcoordinated} shows that \tit{'t} `it' needs to combine with \tit{da-}/\tit{di-} to be able to be coordinated.
+
+ \ex.
+ \ag. *Hij en 't staan in de hoek.\\
+  he and it stand in the corner\\
+  `He and it are standing in the corner.'\label{ex:tcoordinated}
+ \bg. Hij en dit/dat staan in de hoek.\\
+  he and this/that stand in the corner\\
+  `He and it are standing in the corner.'\label{ex:datcoordinated}
+
+I assume that the \tit{'t} contains the ontological category \tsc{thing} \citep{kayne2005}.
+The feature Σ indicates that the pronoun is a weak pronoun.
+I leave possible number and gender features out because they do not play a role in this paper.
+The morpheme \tit{'t} can act as nominative, accusative and dative, as I showed in \ref{ex:tsubobj}.
+Taking this all together, \tit{'t} has the lexical entry given in \ref{ex:entryt}.
+
+\ex. \begin{forest} boom
+ [\tsc{dat}P
+     [\tsc{f}3]
+     [\tsc{acc}P
+         [\tsc{f}2]
+         [\tsc{nom}P
+             [\tsc{f}1]
+             [ΣP
+                 [Σ]
+                 [\tsc{thingP}
+                     [\tsc{thing}, roof]
+                 ]
+             ]
+         ]
+     ]
+ ]
+ {\draw (.east) node[right]{⇔ \tit{'t}}; }
+ \end{forest}\label{ex:entryt}
+
+ This lexical entry can lexicalize the \tsc{datP}, but also the \tsc{accP} and \tsc{nomP}. This is due to the Superset Princple.
+
+  \ex. The Superset Principle \citet{starke2009}: \\
+  A lexically stored tree matches a syntactic node iff the lexically stored tree contains the syntactic node.
+
+ In other words, a lexically stored structure does not have to be identical to the syntactic structure.
+It is enough if the syntactic structure is contained in the lexically stored tree.
+This has a as consequence that the lexical entry in \ref{ex:entryt} can also be inserted in \ref{ex:tacc} and \ref{ex:tnom}.
+
+ \ex.
+ \a. \begin{forest} boom
+ [\tsc{acc}P
+     [\tsc{f}2]
+     [\tsc{nom}P
+         [\tsc{f}1]
+         [\tsc{thingP}
+             [\tsc{thing}, roof]
+         ]
+     ]
+ ]
+ \end{forest}\label{ex:tacc}
+ \b. \begin{forest} boom
+ [\tsc{nom}P
+     [\tsc{f}1]
+     [\tsc{thingP}
+         [\tsc{thing}, roof]
+     ]
+ ]
+ \end{forest}\label{ex:tnom}
+
+Let me move on to \tit{'r}. \tit{'r} `there' can be used as a locative.
+
+ \exg. Ik ben er al geweest.\\
+  I am there already been\\
+  `I have already been there.'
+
+I follow \cite{baunaz2018} in assuming that the ontological category \tsc{location} contains \tsc{thing}.\footnote{\citet{baunaz2018} place in addition \tsc{person} between \tsc{thing} and \tsc{location}, which I left out here.}
+
+\ex. \begin{forest} boom
+[\tsc{loc}P
+    [\tsc{location}]
+    [\tsc{thingP}
+        [\tsc{thing}, roof]
+    ]
+]
+{\draw (.east) node[right]{⇔ \tit{'r}}; }
+\end{forest}\label{ex:entryr}
+
+Notice already here that, via the superset principle, \tit{'r} can be used to realize the feature \tsc{thing} as well, as it is contained in \tsc{locP}.
+Moreover, in a syntactic structure like in \ref{ex:rthing} the lexical entry \ref{ex:entryr} will be inserted and not \ref{ex:entryt}.
+
+\ex.
+\begin{forest} boom
+ [\tsc{thingP}
+     [\tsc{thing}, roof]
+ ]
+{\draw (.east) node[right]{⇒ \tit{'r}}; }
+\end{forest}\label{ex:rthing}
+
+This is due to the Elsewhere condition. The idea is that when two lexical entries are both candidates for spellout, the most specific is inserted.
+
+\ex. The Elsewhere Condition (\citealt{kiparsky1973}, formulated as in \citealt{caha2020}):\\
+When two entries can spell out a given node, the more specific entry wins. Under the Superset Principle governed insertion, the more specific entry is the one which has fewer unused features
+
+The syntactic structure in \ref{ex:entryr} only has \tsc{loc} as an unused feature, whereas \ref{ex:entryt} has Σ up to \tsc{f3}.
+
+\subsubsection{\tit{Mee} vs. \tit{met}}
+
+\ex. The preposition/postposition hierarchy
+\a. If the expression of a particular case in the Case sequence (below) involves a preposition, then all cases to its right do as well.
+\b. The Case sequence: \tsc{nom – acc – gen – dat – ins – com} \hfill \citep{2009}
+
+\exg. mit ein-em Löffel\\
+with a-\tsc{dat.sg} spoon\\
+`with a spoon' \hfill (German)
+
+There is variation, between languages but also within languages.
+
+\ex.
+\ag. Tazi duma m-i e nepoznata.\\
+that word I-\tsc{dat} is unfamiliar\\
+`That word is unfamiliar to me.'
+\bg. *Tazi duma e nepoznata sina mi.\\
+that word is unfamiliar son my\\
+`That word is unfamiliar my son.'
+\bg. Tazi duma e nepoznata na sina mi.\\
+that word is unfamiliar to son my\\
+`That word is unfamiliar to my son.'
+
+show lexical entry for this?
+
+Here pronouns can take a postposition, but full DPs cannot. In Dutch it was slightly different: inanimate pronouns can take the postposition, but animates and full DPs cannot.
 
@@
 
+The distinction between prepositions and postpositions.
+
 If not match can be found, a specifier is constructed.
@@
 
-Nanosyntax distinguishes prefixes and suffixes by distinguishing these types of lexical entries. This is the crucial difference needed for the Dutch instrumental.
+Nanosyntax distinguishes prepositiones and postpositiones by distinguishing these types of lexical entries. This is the crucial difference needed for the Dutch instrumental.
 
 It differs per language and within a language how high a DP can move.
-Everything below is a suffix on the noun, everything higher is a preposition.
+Everything below is a postposition on the noun, everything higher is a preposition.
 Consider German full DP.
@@
 
-\ex.
-\ag. Tazi duma m-i e nepoznata.\\
-that word I-\tsc{dat} is unfamiliar\\
-`That word is unfamiliar to me.'
-\bg. Tazi duma e nepoznata sina mi.\\
-that word is unfamiliar son my\\
-`That word is unfamiliar my son.'
-\bg. Tazi duma e nepoznata na sina mi.\\
-that word is unfamiliar to son my\\
-`That word is unfamiliar to my son.'
-
 The same intuition will hold for Dutch.
--mee is going to be a suffix that will be able to attach to 'r, but it will not to full DPs and animates.
+-mee is going to be a postposition that will be able to attach to 'r, but it will not to full DPs and animates.
 
@@
 
-\tit{'r} `there' can be used as a locative.
-
-\exg. Ik ben er al geweest.\\
- I am there already been\\
- `I have already been there.'
-
-I follow \cite{baunaz2018} in assuming that the ontological category \tsc{location} contains \tsc{thing}.
-
-\footnote{\citet{baunaz2018} place in addition \tsc{person} between \tsc{thing} and \tsc{location}, which I left out here.}
-
- \ex. \begin{forest} boom
- [\tsc{loc}P
- [\tsc{location}]
-     [\tsc{thingP}
-         [\tsc{thing}, roof]
-     ]
- ]
- {\draw (.east) node[right]{⇔ \tit{'r}}; }
- \end{forest}\label{ex:entryr}
-
-Notice already here that, via the superset principle, \tit{'r} can be used to realize the feature \tsc{thing} as well, as it is contained in \tsc{locP}.
-
 So far, \tit{'r} `there' only realizes the feature \tsc{thing} from the structure in \ref{ex:stmetwat}.
@@
 Second, the lexical entry in \ref{ex:entrymet} has a binary bottom, and the lexical entry in \ref{ex:entrymee} has a unary bottom.
-\tit{Met} `with' is a prefix (preposition), so it has a binary bottom, and \tit{mee} `with' is a suffix, so it needs a unary bottom.
-In the next section I show how this works in a derivation.
-
-\footnote{For completeness, \tit{mee} `with' has to be blocked from combining with full DPs and animate pronouns (reference).
+\tit{Met} `with' is a preposition (preposition), so it has a binary bottom, and \tit{mee} `with' is a postposition, so it needs a unary bottom.
+In the next section I show how this works in a derivation.\footnote{For completeness, \tit{mee} `with' has to be blocked from combining with full DPs and animate pronouns (reference).
 For now I assume that these pronouns spell out an additional feature \tit{σ} that is not realized by \tit{mee} `with' but only by \tit{met} `with'.
@@
 This way \tit{mee} `with' does not compete with \tit{met} `anymore'.
-I left this features out in this paper, at is does not contribute to the main point.}
-
-\footnote{Giving \tit{met} `with' and \tit{mee} `with' two distinct lexical entries has as a consequence that the phonological overlap between them seems like a coincidence.
+I left this features out in this paper, at is does not contribute to the main point.}$^,$\footnote{Giving \tit{met} `with' and \tit{mee} `with' two distinct lexical entries has as a consequence that the phonological overlap between them seems like a coincidence.
 Moreover, in almost all cases the preposition does not change form when it combines with an \tsc{r}-pronoun, e.g.
 \tit{in}.
-If this proposal is on the right track, elements as \tit{in} can be used as either a prefix and as a suffix.
+If this proposal is on the right track, elements as \tit{in} can be used as either a preposition and as a postposition.
 A lexical entry as in \ref{ex:presuf} would be a candidate for such an element.
@@
 
-I leave it to future research to determine whether this is a feasible solution.}
-
-\footnote{A topic related to this paper is the different positioning of identical adpositions in Dutch (see \citet{caha2010} for an account of German and Dutch and \citet{pretorius2017} for Afrikaans).
+I leave it to future research to determine whether this is a feasible solution.}$^,$\footnote{A topic related to this paper is the different positioning of identical adpositions in Dutch (see \citet{caha2010} for an account of German and Dutch and \citet{pretorius2017} for Afrikaans).
 In \ref{ex:dutchin}, \tit{in} changes meaning dependening on whether it proceeds or follows the DP, it is respectively locational or directional.
@@
 
-Skipping over the irrelevant details of how \tit{w} and \tit{a} end up in their positions, the structure for \tit{waarmee} `with what' look as in \ref{ex:spelloutwaarmee}.
-\footnote{I assume that WP and \tsc{deixP} are both complex specifiers that are created after \tsc{thing} is spelled out in \ref{ex:thingspellout}.
-In after each merge after that, backtracking always takes place, the complex specifier is detached from the structure and the case features are spelled out together with or as a suffix on \tsc{thing}.}
+Skipping over the irrelevant details of how \tit{w} and \tit{a} end up in their positions, the structure for \tit{waarmee} `with what' look as in \ref{ex:spelloutwaarmee}.\footnote{I assume that WP and \tsc{deixP} are both complex specifiers that are created after \tsc{thing} is spelled out in \ref{ex:thingspellout}.
+In after each merge after that, backtracking always takes place, the complex specifier is detached from the structure and the case features are spelled out together with or as a postposition on \tsc{thing}.}
 
@@
 
-A consequence of analyzing \tit{mee} `with' as a suffix is that \tit{r} and \tit{mee} always form a constituent to the exclusion of \tit{w} and \tit{a}.
+A consequence of analyzing \tit{mee} `with' as a postposition is that \tit{r} and \tit{mee} always form a constituent to the exclusion of \tit{w} and \tit{a}.
 At first sight this seems problematic, because it is possible for \tit{waar} `where', stranding \tit{mee} `with'.
@@
 The described pattern follows from a core assumptions in Nanosyntax: phrasal spellout spells out constituents.
-Looking more into detail, \tit{waarmee} `with what' takes precedence over \tit{met wat} `with what' because \tit{mee} has the structure of a suffix.
+Looking more into detail, \tit{waarmee} `with what' takes precedence over \tit{met wat} `with what' because \tit{mee} has the structure of a postposition.
 Following the spellout algorithm, \tit{'t} `it' is replaced by \tit{'r} `there', so that it can combine with \tit{mee} `with'.

### 2020-01-14 paper.tex
end of day tuesday
still too much to do

@@
 \tsc{R}-pronouns morphologically consist of a combination of a preposition and locative pronoun.
-In the example \ref{ex:klimerop} \tit{op} `on' is the preposition and \tit{'r} `there' is the locative pronoun.
+In the example \ref{ex:klimerop} \tit{op} `on' is the preposition and \tit{'r} `there' is the locative pronoun.\footnote{The \tsc{r}-pronoun in \ref{ex:klimerop} can be written as \tit{er}, \tit{der} and \tit{'r} and pronounced as respectively /ɛr/, /dər/ or /ər/ cf.
+\citet{wesseling2018}.
+For this paper I consider them to be allomorphs.
+In my examples I use \tit{'r}.}
 
@@
 First, just like for all \tsc{r}-pronouns, the wh-element is the locative, but there is no meaning component related to location in `with what'.
-Second, the preposition \tit{met} `with' changes into \tit{mee} `with' when it is combined with an \tsc{r}-pronoun.
-This observervation has so far remained unexplained.
+Second, the preposition \tit{met} `with' does not only turn into a postposition, but it also changes into \tit{mee} `with' when it is combined with an \tsc{r}-pronoun.\footnote{I do not have anything to say about the distinction between prefixes and prepositions, or suffixes and postpositions.} This last observervation has so far remained unexplained.
 
@@
 If the predicates are switched around between the clauses, the \tsc{r}-pronoun does not appear anymore.
-In \ref{ex:schildermet}, \tit{schilder} `paint' combines with an instrumental PP in the main clause and \tit{gekocht} `bought' combines with an accusative DP in the embedded clause.
+In \ref{ex:schildermet}, \tit{schilder} `paint' combines with an instrumental object in the main clause and \tit{gekocht} `bought' combines with an accusative object in the embedded clause.
 The use of an \tsc{r}-pronoun is ungrammatical, as indicated by the ungrammaticality of \ref{ex:schilderwaarmee}.
@@
 
-The morpheme \tit{a} expresses deixis.
+I assume the morpheme \tit{a} to be related to deixis.
 Dutch distinguishes between proximal by using \tit{ie/i} and distal by using \tit{aa/a}, illustrated in \ref{ex:deixis}.
@@
  \z.
-
-In combination with wh-elements, the distal marker \tit{a} is used. For the purpose of this paper I simply let \tit{a} correspond to \tsc{deixP}.
+ \z.
+
+The question remains open to why wh-elements only combine with the distal marker \tit{a}, and they do not combine with proximal marker \tit{i/ie}.
+
+\ex.
+\a. wat, waar
+\b. *wit, *wier
+
+For the purpose of this paper I simply let \tit{a} correspond to \tsc{deixP}.
 
@@
 I put \tit{w} and \tit{a} aside for now, assuming they spell out the same syntactic structure in \tit{waarmee} `with what' and \tit{met wat} `with what'.
-This leaves \tit{'r-mee} `with it' and \tit{met 't} `with it'.\footnote{I assume that the \tit{e} in \tit{'rmee} `with it' is there for phonological reasons.
-The vowel is dropped under the right phonological circumstances.
-
-\exg. Ik heb 'r niks mee te maken.\\
- I have there nothing with to make\\
- `I have nothing to do with it.'
- \z.
-
-\phantom{x}
-}
+This leaves \tit{'r-mee} `with it' and \tit{met 't} `with it'.
 

### 2020-01-14 paper.tex
during colloquium
added sigma in trees

@@
 
-\title{No preposition with inanimate but an \tsc{r}-pronoun with postposition\\
+\title{How [preposition inanimate] becomes [\tsc{r}-pronoun postposition]\\
 On \tit{waarmee} vs. \tit{met wat} in Dutch}
@@
 This is noteworthy because Dutch is a normally non-preposition stranding language.
-\tsc{R}-pronouns morphologically consist of a combination of a preposition and locative pronoun.
-In the example \ref{ex:klimerop} \tit{op} `on' is the preposition and \tit{'r} `there' is the locative pronoun.\footnote{The \tsc{r}-pronoun in \ref{ex:klimerop} can be written as \tit{er}, \tit{der} and \tit{'r} and pronounced as respectively /ɛr/, /dər/ or /ər/ cf.
-\citet{wesseling2018}.
-For this paper I consider them to be allomorphs.
-In my examples I use \tit{'r}.}
+In the example \ref{ex:klimerop} \tit{op} `on' is the preposition and \tit{'r} `there' is the locative pronoun.\footnote{The \tsc{r}-pronoun \tit{'r} in \ref{ex:klimerop} can be written as \tit{er}, \tit{der} and \tit{'r} and pronounced as respectively /ɛr/, /dər/ or /ər/.
+As far as I am aware, there is no clear meaning difference between these forms.
+See \citet{wesseling2018} for discussion.
+In my examples I use \tit{'r}, but the other two forms fit just as well.}
 
@@
 I illustrate this in \ref{ex:gekochtwaarmee}.
-The predicate in the embedded clause, \tit{schildert} `paint', combines with an instrumental PP.
+The predicate in the embedded clause, \tit{schildert} `paint', combines with an instrumental object.
 The predicate in the main clause clause, \tit{gekocht} `bought' combines with an accusative DP.
@@
 \tit{Waarmee} `with what' and not \tit{met wat} `with what' does not only appear in wh-questions, but also in other contexts.
-\ref{ex:headed} gives an example of a headed relative, and \ref{ex:headless} shows a free relative in which both predicates combine with an instrumental PP.
+\ref{ex:headed} gives an example of a headed relative, and \ref{ex:headless} shows a free relative in which both predicates combine with an instrumental object.
 The use of \tit{met wat} `with what' is ungrammatical in both contexts, and \tit{waarmee} `with what' is used.
@@
 Something that is surprising is the use of \tit{met wat} `with what' in \ref{ex:grammaticalwat}, and this is the example something more needs to be said about.
-In the remainder of this section I argue that this `something more' is that the instrumental PP in \ref{ex:grammaticalwat} does not form a proper constituent, i.e.
+In the remainder of this section I argue that this `something more' is that the instrumental object in \ref{ex:grammaticalwat} does not form a proper constituent, i.e.
 it is not a constituent to the exclusion of any other elements.
-The other side of the coin is that constructions with \tsc{r}-pronouns contain a PP that does form a proper constituent.
-
-Below I repeat the examples with instrumental PPs I discuss so far in this paper.
+The other side of the coin is that constructions with \tsc{r}-pronouns contain a object that does form a proper constituent.
+
+Below I repeat the examples with instrumentals I discussed so far in this paper.
 
@@
 
-In each of these examples the instrumental PP forms a constituent at a certain point in the derivation.
-In \ref{ex:const1}, the PP forms a proper constituent in the surface order, as shown in \ref{ex:const1stage}.
-In \ref{ex:const2}, the PP forms a proper constituent before wh- and V2- movement, shown in \ref{ex:const2stage}.
+In each of these examples the instrumental object forms a constituent at a certain point in the derivation.
+In \ref{ex:const1}, the instrumental object forms a proper constituent in the surface order, as shown in \ref{ex:const1stage}.
+In \ref{ex:const2}, the instrumental object forms a proper constituent before wh- and V2- movement, shown in \ref{ex:const2stage}.
 The structure in \ref{ex:const3stage} represents a stage in the derivation of the embedded clauses in \ref{ex:const3} and \ref{ex:const4}.\footnote{I assume that the antecedent in a free relative is a phonologically empty element, in line with cf.
@@
 Under that view, \ref{ex:const3} and \ref{ex:const4} are identical, except for that in \ref{ex:const4} modifies phonologically empty element.}
-Again, in the stage, which comes before relative movement of the pronoun to the left periphery of the relative clause, the PP forms a proper constituent.
+Again, in the stage, which comes before relative movement of the pronoun to the left periphery of the relative clause, the instrumental object forms a proper constituent.
 
@@
 \tit{Kopen} `to buy' takes an accusative DP as its object, illustrated in \ref{ex:kopen}.
-\tit{Schilderen} `to paint' can take an instrumental PP as its object., shown in \ref{ex:schilderen}.\footnote{\tit{Schilderen} also optionally takes an (accusative) object, but I am focussing on the instrumental object here.}
+\tit{Schilderen} `to paint' can take an instrumental as its object., shown in \ref{ex:schilderen}.\footnote{\tit{Schilderen} also optionally takes an (accusative) object, but I am focussing on the instrumental object here.}
 
@@
 The predicate \tit{schildert} `paints' combines in the embedded clause with the instrumental object.
-The PP forms a proper constituent within the embedded clause, and the PP can be realized as the \tsc{r}-pronoun \tit{waarmee} `with what'.\footnote{I assume that the embedded clause modifies a phonologically empty noun here which is the DP argument of \tit{gekocht} `bought'.}
+The instrumental object forms a proper constituent within the embedded clause, and the it can be realized as the \tsc{r}-pronoun and postposition \tit{waarmee} `with what'.\footnote{I assume that the embedded clause modifies a phonologically empty noun here which is the DP argument of \tit{gekocht} `bought'.}
 
@@
 The accusative object of a verb is always \tit{wat} `what', as I showed in \ref{ex:wat}.
-The instrumental PP only comes into the picture in the main clause, when \tit{schilder} `paint' combines with an instrumental PP.
-At no point in the derivation does the PP form a proper constituent, and \tit{waarmee} `with what' does not surface.
+The instrumental only comes into the picture in the main clause, when \tit{schilder} `paint' combines with an instrumental object.
+At no point in the derivation does the instrumental object form a proper constituent, and \tit{waarmee} `with what' does not surface.
 
@@
 
-\subsection{Differences: \tit{'r} vs. \tit{'t} and \tit{met} vs. \tit{-mee}}
+\subsection{Differences: \tit{'rmee} vs. \tit{met 't}}
 
@@
          [\tsc{f}1]
-         [\tsc{thingP}
-             [\tsc{thing}, roof]
+         [ΣP
+             [Σ]
+             [\tsc{thingP}
+                 [\tsc{thing}, roof]
+             ]
          ]
@@
      [\tsc{f}1]
-     [\tsc{thingP}
-         [\tsc{thing}, roof]
+     [ΣP
+         [Σ]
+         [\tsc{thingP}
+             [\tsc{thing}, roof]
+         ]
      ]
@@
 
-The syntactic structure in \ref{ex:entryr} only has \tsc{loc} as an unused feature, whereas \ref{ex:entryt} has Σ up to \tsc{f3}.
+The syntactic structure in \ref{ex:entryr} only has \tsc{loc} as an unused feature, whereas in \ref{ex:entryt} Σ up to \tsc{f3} remain unused.
 
@@
                     [\tsc{f}1]
+                    [ΣP
+                        [Σ]
+                    ]
                 ]
@@
 
-\ex. [ [ [ [ [ [ \tsc{thing} ] \tsc{deix} ] W ] \tsc{f1} ] \tsc{f2} ] \tsc{f3} \tsc{f4} ]\label{ex:fseq}
+\ex. [ [ [ [ [ [ [ \tsc{thing} ] \tsc{deix} ] W ] \tsc{f1} ] \tsc{f2} ] \tsc{f3} ] \tsc{f4} ]\label{ex:fseq}
 \z.
@@
    [\tsc{f}1]
-   [\tsc{thingP}
-       [\tsc{thing}, roof]
+   [ΣP
+       [Σ]
+       [\tsc{thingP}
+           [\tsc{thing}, roof]
+       ]
    ]
@@
        [\tsc{f}1]
-       [\tsc{thingP}
-           [\tsc{thing}, roof]
+       [ΣP
+           [Σ]
+           [\tsc{thingP}
+               [\tsc{thing}, roof]
+           ]
        ]
@@
            [\tsc{f}1]
-           [\tsc{thingP}
-               [\tsc{thing}, roof]
+           [ΣP
+               [Σ]
+               [\tsc{thingP}
+                   [\tsc{thing}, roof]
+               ]
            ]
@@
                [\tsc{f}1]
-               [\tsc{thingP}
-                   [\tsc{thing}, roof]
+               [ΣP
+                   [Σ]
+                   [\tsc{thingP}
+                       [\tsc{thing}, roof]
+                   ]
                ]
@@
 
-Backtracking proceeds further, into the cycle in which \tsc{f2} was merged. Again there is no specifier to be moved, and complement movement does not give any results.
-
-The derivation ends up backtracking into the cycle in which \tsc{f1} was merged.
+Backtracking proceeds further, into the cycle in which \tsc{f1} was merged. Again there is no specifier to be moved, and complement movement does not give any results.
+
+The derivation ends up backtracking into the cycle in which Σ was merged.
 At this stage, \tsc{thing} was realized as \tit{'r}.
@@
 \ex. \begin{forest} boom
+[ΣP
+   [\tsc{thingP}
+       [\tsc{thing}, roof]
+   ]
+   {\draw (.east) node[right]{⇒ \tit{'r}}; }
+   [ΣP
+       [Σ]
+   ]
+   {\draw (.east) node[right]{⇒ \tit{mee}}; }
+]
+\end{forest}
+
+The feature \tsc{f}1 is merged again. The structure cannot be spelled out as a whole, so spec-to-spec movement is tried. In that configuration \tsc{f1} can be realized together with Σ as \tit{mee}.
+
+\ex. \begin{forest} boom
 [\tsc{nomP}
@@
        [\tsc{f}1]
+       [ΣP
+           [Σ]
+       ]
    ]
@@
 
-The feature \tsc{f}2 is merged again.
-The structure cannot be spelled out as a whole, so spec-to-spec movement is tried.
-In that configuration \tsc{f2} can be realized together with \tsc{f1} as \tit{mee}.
-
-\ex. \begin{forest} boom
-[\tsc{accP}
-   [\tsc{thingP}
-       [\tsc{thing}, roof]
-   ]
-   {\draw (.east) node[right]{⇒ \tit{'r}}; }
-   [\tsc{acc}P
-       [\tsc{f}2]
-       [\tsc{nom}P
-           [\tsc{f}1]
-       ]
-   ]
-   {\draw (.east) node[right]{⇒ \tit{mee}}; }
- ]
-\end{forest}
-
-The same happens for \tsc{f3} and \tsc{f4}, and the complete structure is realizes as shown in \ref{ex:spellout'rmee}.
+The same happens for \tsc{f2}, \tsc{f3} and \tsc{f4}, and the complete structure is realizes as shown in \ref{ex:spellout'rmee}.
 
@@
                    [\tsc{f}1]
+                   [ΣP
+                       [Σ]
+                   ]
                ]
@@
                            [\tsc{f}1]
+                           [ΣP
+                               [Σ]
+                           ]
                        ]
@@
 [CP
-    [CP
-        [...,roof]
-    ]
     [\tsc{WP}
@@
                    [\tsc{f}1]
-                   [\tsc{thingP}
-                       [\tsc{thing}, roof]
+                   [ΣP
+                       [Σ]
+                       [\tsc{thingP}
+                           [\tsc{thing}, roof]
+                       ]
                    ]
@@
     ]
+    [CP
+        [...,roof]
+    ]
 ]
@@
 
-If a dative feature is merged here, it will not be able to be spelled out.
+Only after the wh-element is moved to the left edge of the clause, case features higher than the accusative are merged.
+
+When a dative feature is merged here, it will not be able to be spelled out.
 The only option to realize the features is to form to spawn a new derivation, to create a complex specifier.

### 2020-01-15 paper.tex
prefix vs suffix
kind of done, now still backtracking

@@
 
+ Pronouns in other genders alternate between nominative (non-oblique) and accusative/dative (oblique) in these contexts, illustrated in \ref{ex:hemsubobj}.
+
+ \ex.\label{ex:hemsubobj}
+ \ag. Hij staat in de hal.\\
+  \tsc{3sg.m.nom} stands in the hallway\\
+  `He is standing in the hallway.'
+ \bg. Ik zie hem.\\
+  I see \tsc{3sg.m.acc}\\
+  `I see it.'
+ \bg. Ik heb hem een klap gegeven.\\
+  I have \tsc{3sg.m.acc} a hit given\\ with both alternatives. I work the proposal out with't  realizing all cases.
+
 For case, I follow \citet{caha2009} that case features case features are organized the containment relation in \ref{ex:casetree}.
@@
 I leave possible number and gender features out because they do not play a role in this paper.
-The morpheme \tit{'t} can act as nominative, accusative and dative, as I showed in \ref{ex:tsubobj}.
-Taking this all together, \tit{'t} has the lexical entry given in \ref{ex:entryt}.
+The morpheme \tit{'t} can act as nominative, accusative and dative, as I showed in \ref{ex:tsubobj}.\footnote{ Another possibility is to claim that \tit{'t} can only spell out \tsc{thing} and Σ and it combines with a zero suffix for the cases up to dative.
+This could be the same zero marker that full DPs combine with.
+
+\ex.
+\ag. De kast-∅ staat in de hal.\\
+ the cabinet-\tsc{nom} stands in the hallway\\
+ `The cabinet is standing in the hallway.'
+\bg. Ik zie de kast-∅.\\
+ I see the cabinet-\tsc{acc}\\
+ `I see the cabinet.'
+\bg. Ik heb de kast-∅ een klap gegeven.\\
+ I have the cabinet-\tsc{dat} a hit given\\
+ `I gave the cabinet a hit.'
+
+The proposed account fares equally well with both alternatives.
+I work the proposal out with \tit{'t} realizing the cases up to the dative.} Taking this all together, \tit{'t} has the lexical entry given in \ref{ex:entryt}.
 
@@
 
-This is due to the Elsewhere condition. The idea is that when two lexical entries are both candidates for spellout, the most specific is inserted.
+This is due to the Elsewhere Condition. The idea is that when two lexical entries are both candidates for spellout, the most specific is inserted.
 
@@
 \subsubsection{\tit{Mee} vs. \tit{met}}
+
+Now we come to mee and met.
+the crucial distinction between these elements is that \tit{mee} is postposition and \tit{met} is a preposition.
+i show: (i) relation between these types of elements, (ii) how that is being modeled with movement, (iii) that post goes before pre (iv) how that is modeled in nano.
+
+I shows 't spells out all features. this does not always happen. languages also use prepositions/prefixes and postpositions/suffixes to express case. and the relation between them is not arbitrary.
 
@@
 
+can be modeled in the sense that a dp moves to a certain height.
+
 \exg. mit ein-em Löffel\\
@@
 
-There is variation, between languages but also within languages.
+in german, dp moves above the dp. go back to dutch, hard to say above dative, because instrumental sometimes pre sometimes post.
+
+There is variation, between languages but also within languages. another instance is bulgarian.
 
@@
 
-show lexical entry for this?
-
 Here pronouns can take a postposition, but full DPs cannot. In Dutch it was slightly different: inanimate pronouns can take the postposition, but animates and full DPs cannot.
+
+give lexical entry for that.
+say why it does not work with full DPs and with animates.
+
+so what happens with these instead?
+they get the prepostiion.
+prepositions have to be encoded differently in the syntax, because they ARE different, they occur before the expression.
+as you saw the -mee has a unary bottom, so it can only arise as a result of movement.
+pre elements have a binary bottom.
+
+i'm going to crucially rely on the order in the spellout algoritm
+
+MOVE TO LATER
 
@@
 Lexicalisation at a node XP overrides any previous match at a phrase contained in XP.
-
-\ex.
-\a. \begin{forest} boom
-[\tsc{ins{}}
-    [\tsc{f5}, roof]
-]
-{\draw (.east) node[right]{⇔ \tit{mit}}; }
-\end{forest}\label{ex:mit}
-\b. \begin{forest} boom
-[\tsc{dat}P
-    [\tsc{f}3]
-    [\tsc{acc}P
-        [\tsc{f}2]
-        [\tsc{nom}P
-            [\tsc{f}1]
-        ]
-    ]
-]
-{\draw (.east) node[right]{⇔ \tit{-em}}; }
-\end{forest}\label{ex:em}
-
-The distinction between prepositions and postpositions.
 

### 2020-01-15 paper.tex
woensdagochtend
bij jan nu, op naar huis. prefix/suffix gedaan. nog backtracking en dan t hele verhaal nog door. pfoe

@@
 For case, I follow \citet{caha2009} that case features case features are organized the containment relation in \ref{ex:casetree}.
-The higher, more complex cases contain the smaller, less complex cases.
+The higher, more complex cases contain the smaller, less complex cases.\footnote{there has been discussion on the genitive.
+starke on two accusatives and two datives.
+this paper: only small accusative and dative and genitive is above both of them.}
 
@@
  [\tsc{comP}
+     [\tsc{f6}]
+     [\tsc{insP}
          [\tsc{f5}]
-     [\tsc{insP}
+         [\tsc{genP}
              [\tsc{f4}]
@@
      ]
+ ]
  \end{forest}
@@
 
-Now we come to mee and met.
+The last two forms are \tit{mee} `with' and \tit{met} `with'.
+An important distinction between these two is that \tit{mee} appears after the element it combines with (\tsc{'r}), while \tit{met} appears before the element it combines with (\tit{'t}).
+I will analyze \tit{mee} as a postposition and \tit{met} as a preposition.
+In this section I discuss the relation between prepositions and postpositions, and how this is modeled with the case hierarchy in Nanosyntax \citep{caha2009}.
+
+%$Now we come to mee and met.
 the crucial distinction between these elements is that \tit{mee} is postposition and \tit{met} is a preposition.
@@
 
-I shows 't spells out all features. this does not always happen. languages also use prepositions/prefixes and postpositions/suffixes to express case. and the relation between them is not arbitrary.
+In the previous section I argued that \tit{'t} realizes case features up to \tsc{f3} (see \ref{ex:entryt}).
+However, case can also be expressed by prepositions (or prefixes) and postpositions (or suffixes).
+The division between which cases are expressed by prepositions and which are expressed by postpositions is not arbitrary.
 
@@
 \a. If the expression of a particular case in the Case sequence (below) involves a preposition, then all cases to its right do as well.
-\b. The Case sequence: \tsc{nom – acc – gen – dat – ins – com} \hfill \citep{2009}
-
-can be modeled in the sense that a dp moves to a certain height.
-
-\exg. mit ein-em Löffel\\
-with a-\tsc{dat.sg} spoon\\
-`with a spoon' \hfill (German)
-
-in german, dp moves above the dp. go back to dutch, hard to say above dative, because instrumental sometimes pre sometimes post.
-
-There is variation, between languages but also within languages. another instance is bulgarian.
-
-\ex.
+\b. The Case sequence: \tsc{nom – acc – dat – gen - ins – com} \hfill \citep{caha2009}
+
+The result of that is that a PP can contain a preposition and a suffix, as in \ref{ex:loffel}. The dative suffix is used with a genitive preposition.
+
+\exg. von ein-em Löffel\\
+von a-\tsc{dat.sg} spoon\\
+`of a spoon' \hfill (German)\label{ex:loffel}
+
+With the case hierarchy in nanosyntax this can be modeled by letting the DP move as high as above the \tsc{datP} in the syntactic structure.
+The features below the \tsc{datP} are realized as a suffix, and the features above \tsc{datP} are realized as a preposition.
+I gloss over the fact that \tit{-em} is realized on the article and not
+
+There is variation with respect to how high a DP can move in the structure, both between languages and within languages.
+An example from the latter comes from Bulgarian.
+\ref{ex:bulpron} shows that pronouns can take the suffix \tit{-i} to realize dative, but full DPs need a preposition \tit{na} `to'.
+
+\ex.\label{ex:bulgarian}
 \ag. Tazi duma m-i e nepoznata.\\
 that word I-\tsc{dat} is unfamiliar\\
-`That word is unfamiliar to me.'
-\bg. *Tazi duma e nepoznata sina mi.\\
-that word is unfamiliar son my\\
-`That word is unfamiliar my son.'
+`That word is unfamiliar to me.'\label{ex:bulpron}
 \bg. Tazi duma e nepoznata na sina mi.\\
 that word is unfamiliar to son my\\
-`That word is unfamiliar to my son.'
-
-Here pronouns can take a postposition, but full DPs cannot. In Dutch it was slightly different: inanimate pronouns can take the postposition, but animates and full DPs cannot.
-
-give lexical entry for that.
-say why it does not work with full DPs and with animates.
-
-so what happens with these instead?
-they get the prepostiion.
-prepositions have to be encoded differently in the syntax, because they ARE different, they occur before the expression.
-as you saw the -mee has a unary bottom, so it can only arise as a result of movement.
-pre elements have a binary bottom.
-
-i'm going to crucially rely on the order in the spellout algoritm
-
-MOVE TO LATER
-
-Spellout happens in a cyclic derivation, following a spellout algorithm \citep{starke2018}.
-After each instance of merge, spellout takes place.
-If no spellout exist for the phrase created by the newly added feature, evacuation movements specified in the spellout algorithm take place.
-The algorithm is given in \ref{ex:spellout}.
-
-\ex. Merge F and \label{ex:spellout}
- \a. Spell out FP
- \b. If (a) fails, attempt movement of the spec of the complement of \tsc{f}, and retry (a)
- \b. If (b) fails, move the complement of \tsc{f}, and retry (a)
-
-When a new match is found, it overrides previous spellouts.
-
-\ex. Cyclic Override \citep{starke2018}:\\
-Lexicalisation at a node XP overrides any previous match at a phrase contained in XP.
-
-If not match can be found, a specifier is constructed.
-
-\ex. Spec Formation \citep{starke2018}:\\
-If Merge F has failed to spell out (even after backtracking), try to spawn a new derivation providing the feature F and merge that with the current derivation, projecting the feature F at the top node.
-
-For case, I follow \citet{caha2009} that case features case features are organized the containment relation in \ref{ex:casetree}.
-The higher, more complex cases contain the smaller, less complex cases.
-
-In other words, a lexically stored structure does not have to be identical to the syntactic structure.
-It is enough if the syntactic structure is contained in the lexically stored tree.
-This has a as consequence that the lexical entry in \ref{ex:entryt} can also be inserted in syntactic structures as \ref{ex:tacc} and \ref{ex:tnom}.
-
-Nanosyntax distinguishes prepositiones and postpositiones by distinguishing these types of lexical entries. This is the crucial difference needed for the Dutch instrumental.
-
-It differs per language and within a language how high a DP can move.
-Everything below is a postposition on the noun, everything higher is a preposition.
-Consider German full DP.
-Moves as high as above the dative, instrumental is expressed with a preposition.
-
-but like i said, it also differs within a language, for example look at bulgarian here!
-
-The same intuition will hold for Dutch.
--mee is going to be a postposition that will be able to attach to 'r, but it will not to full DPs and animates.
+`That word is unfamiliar to my son.'\label{ex:buldpto}
+
+In Dutch the split is not between pronouns and full DPs but between inanimate pronouns on the one hand and animates and full DPs on the other hand.
+In Dutch, inanimate pronouns combine with the postposition \tit{-mee} (see \ref{ex:dutchina} and not with the preposition \tit{met} (see \ref{ex:dutchinmet}).
+Animate pronouns and full DPs, however, combine with the preposition met, as shown in \ref{ex:dutchan} and \ref{ex:dutchdp}.
+The use of the postposition \tit{-mee} is ungrammatical (see \ref{ex:dutchanmee} and \ref{ex:dutchdpmee}).
+
+\ex.
+\ag. Ik schilder 'r-mee.\\
+ I paint there-with\\
+ `I am painting with it.'\label{ex:dutchina}
+\bg. *Ik schilder met 't\\
+ I paint with it\\
+ `I am painting with it.'\label{ex:dutchinmet}
+\bg. Ik schilder samen met hem.\\
+ I paint together with him\\
+ `I am painting with him.'\label{ex:dutchan}
+\bg. *Ik schilder samen 'm-mee.\\
+ I paint together him-with\\
+ `I am painting together with him.'\label{ex:dutchanmee}
+\bg. Ik schilder samen met de man.\\
+ I paint together with the man\\
+ `I am painting together with the man.'\label{ex:dutchdp}
+\bg. *Ik schilder samen de man-mee.\\
+ I paint together the man-with\\
+ `I am painting together with the man.'\label{ex:dutchdpmee}
+
+The next issue I turn to is what the lexical entry of \tit{mee} looks like.
+This needs to capture three facts.
+\tit{Mee} combines with \tit{'r}, it is a postposition, and it does not combine with animates and full DPs.
+
+First, \tit{mee} expresses instrumental (and comitative) case and it combines with \tit{'r}.\footnote{For reasons of space I leave \tsc{f6} out of the lexical entries and discussion, even though \tit{mee} and \tit{met} can also express comitative.} So far, \tit{'r} `there' only realizes the feature \tsc{thing}.
+This leaves Σ and \tsc{f1} to \tsc{f5} to be realized by \tit{mee}.
+I give the lexical tree of \tit{mee} in \ref{ex:entrymee}.
+
+\ex. \begin{forest} boom
+    [\tsc{insP}
+        [\tsc{f}6]
+        [\tsc{genP}
+            [\tsc{f4}]
+            [\tsc{dat}P
+                [\tsc{f}3]
+                [\tsc{acc}P
+                    [\tsc{f}2]
+                    [\tsc{nom}P
+                        [\tsc{f}1]
+                        [ΣP
+                            [Σ]
+                        ]
+                    ]
+                ]
+            ]
+        ]
+    ]
+{\draw (.east) node[right]{⇔ \tit{mee}}; }
+\end{forest}\label{ex:entrymee}
+
+This leads us to the second point: \tit{mee} is a postposition.
+Notice that the foot of the structure has a singleton feature.
+Nanosyntax distinguishes pre-elements from post-elements by the shape of their lexical entry.
+As a result, the whether an element is pre or post is lexically stored as follows from the spellout procedure.
+I illustrate this in Section \ref{sec:derivation}.
+Post-elements have a unary bottom (i.e.
+the foot of the tree is a single feature), so they can only appear as the result of movement.
+Post-elements have a binary bottom (i.e.
+the foot of the tree consists of two features), so they cannot be a candidate as a result of movement.
+
+Why does \tit{mee} not combine with animates and full DPs?
+I claim that has to do with the bottom feature of the lexical entry of \tit{mee}.
+Full DPs do not take features related to pronominal strength.
+According to the Superset Principle, a lexical tree can also match a syntactic tree with a subpart of the features, but a tree can only shrink from the top, so \tit{mee} will always realize Σ.
+I have a less clear answer to why animates do not combine with \tit{mee}.
+The crucial difference between animates and inanimates if gender features.
+For now I assume that gender features are situated between Σ and \tsc{f1}.
+The lexical entry of \tit{mee} includes both these features, so any features are incompatible with \tit{mee}.
+So far I do not have independent evidence for placing gender features between features of pronominal strength and case, and I leave this for future research.
+
+So far I discussed \tit{mee} is a postposition, which follows \tit{'r} and is stored with a unary bottom.
+\tit{Met}, on the other hand, is a preposition, it precedes \tit{'t}, so it should be stored with a binary bottom.
+The highest case feature \tit{'t} can realize is \tsc{f3}, so the preposition realizes all higher cases up to \tsc{f5}.
+
+\ex. \begin{forest} boom
+[\tsc{ins}P
+    [\tsc{f}5]
+    [\tsc{f}4]
+]
+{\draw (.east) node[right]{⇔ \tit{met}}; }
+\end{forest}\label{ex:entrymet}
 
@@
 
-If the spellout procedure in \ref{ex:spellout} fails, backtracking takes place.
+If the spellout procedure in fails, backtracking takes place.
 
@@
 
- \ex. \begin{forest} boom
- [\tsc{com}P
-     [\tsc{f}5]
-     [\tsc{f}4]
- ]
- {\draw (.east) node[right]{⇔ \tit{met}}; }
- \end{forest}\label{ex:entrymet}
-
 In sum, the syntactic structure that \tit{met wat} `with what' realizes is the one in \ref{ex:stmetwat}.
@@
 Let us now turn to \tit{'rmee} `with it', which lexicalizes the same structure as \tit{met 't} `with it', but with a different distribution.
-
-So far, \tit{'r} `there' only realizes the feature \tsc{thing} from the structure in \ref{ex:stmetwat}.
-This leaves \tsc{f1} to \tsc{f4} to be realized by \tit{mee}.
-I give the lexical tree in \ref{ex:entrymee}.
-
-\ex. \begin{forest} boom
-[\tsc{com}P
-    [\tsc{f}5]
-    [\tsc{insP}
-        [\tsc{f}4]
-        [\tsc{dat}P
-            [\tsc{f}3]
-            [\tsc{acc}P
-                [\tsc{f}2]
-                [\tsc{nom}P
-                    [\tsc{f}1]
-                    [ΣP
-                        [Σ]
-                    ]
-                ]
-            ]
-        ]
-    ]
-]
-{\draw (.east) node[right]{⇔ \tit{mee}}; }
-\end{forest}\label{ex:entrymee}
 
@@
 
-\section{Showing it in a derivation}
+\section{Showing it in a derivation}\label{sec:derivation}
 

### 2020-01-15 paper.tex
mostly done
go though it again, fix all typos and intros and still go through texts from people

@@
 
-\title{How [preposition inanimate] becomes [\tsc{r}-pronoun postposition]\\
-On \tit{waarmee} vs. \tit{met wat} in Dutch}
+\title{The \tsc{r}-pronoun and postposition \tit{waarmee} in Dutch}
 \author{Fenna Bergsma}
@@
 First, just like for all \tsc{r}-pronouns, the wh-element is the locative, but there is no meaning component related to location in `with what'.
-Second, the preposition \tit{met} `with' does not only turn into a postposition, but it also changes into \tit{mee} `with' when it is combined with an \tsc{r}-pronoun.\footnote{I do not have anything to say about the distinction between prefixes and prepositions, or suffixes and postpositions.} This last observervation has so far remained unexplained.
+Second, the preposition \tit{met} `with' does not only turn into a postposition, but it also changes into \tit{-mee} `with' when it is combined with an \tsc{r}-pronoun.\footnote{I do not have anything to say about the distinction between prefixes and prepositions, or suffixes and postpositions.} This last observervation has so far remained unexplained.
 
@@
 The predicate in the main clause clause, \tit{gekocht} `bought' combines with an accusative DP.
-The \tsc{r}-pronoun \tit{waarmee} `with what' is used here.\footnote{In this example, \tit{waar} `where' takes \tit{mee} `with' to the left edge of the embedded clause.
-It is also possible for \tit{mee} `with' to be stranded, and \tit{waar} `where' to be moved to the left edge of the embedded clause on its own.
+The \tsc{r}-pronoun \tit{waarmee} `with what' is used here.\footnote{In this example, \tit{waar} `where' takes \tit{-mee} `with' to the left edge of the embedded clause.
+It is also possible for \tit{-mee} `with' to be stranded, and \tit{waar} `where' to be moved to the left edge of the embedded clause on its own.
 
@@
 In \ref{ex:const2}, the instrumental object forms a proper constituent before wh- and V2- movement, shown in \ref{ex:const2stage}.
-The structure in \ref{ex:const3stage} represents a stage in the derivation of the embedded clauses in \ref{ex:const3} and \ref{ex:const4}.\footnote{I assume that the antecedent in a free relative is a phonologically empty element, in line with cf.
-\cite{bresnan1978a,groos1981,himmelreich2017}.
-Under that view, \ref{ex:const3} and \ref{ex:const4} are identical, except for that in \ref{ex:const4} modifies phonologically empty element.}
+The structure in \ref{ex:const3stage} represents a stage in the derivation of the embedded clauses in \ref{ex:const3} and \ref{ex:const4}.
 Again, in the stage, which comes before relative movement of the pronoun to the left periphery of the relative clause, the instrumental object forms a proper constituent.
@@
 %There is additional evidence for the fact that \tit{waarmee} `with what' forms a constituent in the constructions above.
-In the example in \ref{ex:const2}-\ref{ex:const4} only \tit{waar} `where' was fronted, but \ref{ex:constwaarmee} shows that also the phrase containing \tit{mee} with' can be moved.
-As wh-movement can only target constituents, it follows that \tit{waar} `where' and \tit{mee} `with' have to form a constituent.
+In the example in \ref{ex:const2}-\ref{ex:const4} only \tit{waar} `where' was fronted, but \ref{ex:constwaarmee} shows that also the phrase containing \tit{-mee} with' can be moved.
+As wh-movement can only target constituents, it follows that \tit{waar} `where' and \tit{-mee} `with' have to form a constituent.
 
@@
 \tit{Kopen} `to buy' takes an accusative DP as its object, illustrated in \ref{ex:kopen}.
-\tit{Schilderen} `to paint' can take an instrumental as its object., shown in \ref{ex:schilderen}.\footnote{\tit{Schilderen} also optionally takes an (accusative) object, but I am focussing on the instrumental object here.}
+\tit{Schilderen} `to paint' can take an instrumental as its object, shown in \ref{ex:schilderen}.\footnote{\tit{Schilderen} also optionally takes an (accusative) object, but I am focussing on the instrumental object here.}
 
@@
 The predicate \tit{schildert} `paints' combines in the embedded clause with the instrumental object.
-The instrumental object forms a proper constituent within the embedded clause, and the it can be realized as the \tsc{r}-pronoun and postposition \tit{waarmee} `with what'.\footnote{I assume that the embedded clause modifies a phonologically empty noun here which is the DP argument of \tit{gekocht} `bought'.}
+The instrumental object forms a proper constituent within the embedded clause, and the it can be realized as the \tsc{r}-pronoun and postposition \tit{waarmee} `with what'.\footnote{I assume that the accusative case requirement of \tit{gekocht} `bought' is satisfying by grafting a subconstituent of \tit{waarmee} `with what' \citep{bergsma2019}.}
 
@@
 
- The idea is that both expressions realize the same featu♦res, and \tit{waarmee} `with what' takes precedence when all features form a constituent.
-The morphemes I distinguish in \tit{waarmee} `with what' are \tit{w}, \tit{-aa-}, \tit{-r} and \tit{mee}.
+ The idea is that both expressions realize the same features, and \tit{waarmee} `with what' takes precedence when all features form a constituent.
+The morphemes I distinguish in \tit{waarmee} `with what' are \tit{w}, \tit{-aa-}, \tit{-r} and \tit{-mee}.
 Within \tit{met wat} `with what' I distinguish \tit{met}, \tit{w}, \tit{a} and \tit{-t}.
@@
 The elements \tit{w} and \tit{a} express the same syntactic structure in both expressions.
-The elements \tit{met} and \tit{'t} together also express the same features as \tit{mee} and \tit{'r} together, but the distribution differs.
-\tit{Met} expresses less structure than \tit{mee}, and \tit{'t} expresses more structure than \tit{'r}.
-\tit{Met} is shown to be an preposition, and \tit{mee} is a postposition.
+The elements \tit{met} and \tit{'t} together also express the same features as \tit{-mee} and \tit{'r} together, but the distribution differs.
+\tit{Met} expresses less structure than \tit{-mee}, and \tit{'t} expresses more structure than \tit{'r}.
+\tit{Met} is shown to be an preposition, and \tit{-mee} is a postposition.
 It also becomes clear that the \tit{'r} in fact corresponds to the locative \tit{r} in Dutch.
@@
 The analysis accounts for the following two observations, taking \tit{met 't} as the point of departure.
-First, \tit{met} `with' changes from being a preposition to being a postposition, and its form changes into \tit{mee}.
+First, \tit{met} `with' changes from being a preposition to being a postposition, and its form changes into \tit{-mee}.
 This process is restricted to inanimate pronouns, and it does not apply to full DPs and animate pronouns.
@@
 
-This section first discusses some basic facts about case and assumptions about Nanosyntax.
-Then I discuss the distinction between prepositiones and postpositiones, followed by a discussion on suppletion in pronouns.
-Finally, I specify the lexical entries for \tit{'rmee} `with it` and \tit{met 't} `with it` that account for the described facts.
-
 \subsubsection{\tit{'t} vs. \tit{'r}}
+
+In this section I give the lexical entries for \tit{'t} and \tit{'r}, and I show that \tit{'r} is actually the base form and \tit{'t} a suppletive nominative, accusative and dative.
 
@@
 \ex. \begin{forest} boom
- [\tsc{dat}P
-     [\tsc{f}3]
-     [\tsc{acc}P
-         [\tsc{f}2]
-         [\tsc{nom}P
-             [\tsc{f}1]
+ [\tsc{datP}
+     [\tsc{f3}]
+     [\tsc{accP}
+         [\tsc{f2}]
+         [\tsc{nomP}
+             [\tsc{f1}]
              [ΣP
@@
  \a. \begin{forest} boom
- [\tsc{acc}P
-     [\tsc{f}2]
-     [\tsc{nom}P
-         [\tsc{f}1]
+ [\tsc{accP}
+     [\tsc{f2}]
+     [\tsc{nomP}
+         [\tsc{f1}]
          [ΣP
@@
  \b. \begin{forest} boom
- [\tsc{nom}P
-     [\tsc{f}1]
+ [\tsc{nomP}
+     [\tsc{f1}]
      [ΣP
@@
 
-\subsubsection{\tit{Mee} vs. \tit{met}}
-
-The last two forms are \tit{mee} `with' and \tit{met} `with'.
-An important distinction between these two is that \tit{mee} appears after the element it combines with (\tsc{'r}), while \tit{met} appears before the element it combines with (\tit{'t}).
-I will analyze \tit{mee} as a postposition and \tit{met} as a preposition.
+What this means is that the base form of the neuter singular pronoun in Dutch is actually \tit{'r} and \tit{'t} should be analyzed as a suppletive nominative, accusative and dative.
+The base form only shows up in the higher cases, from instrumental on, see Table \ref{tbl:dutchcases}.
+
+\begin{table}[ht]
+	\center
+	\caption {Fragment Dutch \tsc{n.sg}}
+	\begin{minipage}{0.56\linewidth}
+		\begin{tabularx}{\textwidth}{ccccccc}
+		\toprule
+              & \tsc{n.sg} \\
+		\midrule
+    \tsc{nom} & 't         \\
+    \tsc{acc} & 't         \\
+    \tsc{dat} & 't         \\
+    \tsc{gen} & 'r-van     \\
+    \tsc{ins} & -r-mee     \\
+    \bottomrule
+\end{tabularx}
+\label{tbl:dutchcases}
+\end{minipage}
+\end{table}
+
+A similar situation appears in Iron Ossetic, shown in \ref{tbl:ossetic}.
+In the first person singular of this language, it is only the nominative that is suppletive: \tit{æz}.
+The higher cases have the stem \tit{mæn} and they combine with the suffixes that nouns normally also combine with.
+
+\begin{table}[ht]
+	\center
+	\caption {Fragment Iron Ossetic 1.\tsc{sg} and noun \citep{erschler2012}}
+	\begin{minipage}{0.3\linewidth}
+		\begin{tabularx}{\textwidth}{ccccccc}
+		\toprule
+              & 1.\tsc{sg}  & head    \\
+		\midrule
+    \tsc{nom} & æz          & sær-∅   \\
+    \tsc{acc} & mæn-∅       & sær-∅   \\
+    \tsc{gen} & mæn (??)    & sær-y   \\
+    \tsc{ins} & mæn-æj      & sær-æj  \\
+    \tsc{dat} & mæn-æn      & sær-æn  \\
+    \bottomrule
+\end{tabularx}
+\label{tbl:ossetic}
+\end{minipage}
+\end{table}
+
+\citet{caha2019competition} uses evidence from a phenomenon called suspended affixation to argue that \tit{mæn} is a caseless stem and and \tit{æz}.
+Consider the ordinary coordination in \ref{ex:horseoxboth}.
+Both conjuncts are marked by a plural marker and a case marker.
+Suspended affixation is shown in \ref{ex:horseoxone}.
+Here the case marker only appears on the second conjunct and not on the first one without changing the interpretation.
+\tit{Bæx-tæ} `horse-\tsc{pl}' in \ref{ex:horseoxone} does not carry any case marking here.
+
+\ex.
+\ag. bæx-t-imæ æmæ gæl-t-imæ\\
+horse-\tsc{pl-com} and ox-\tsc{pl-com}\\\label{ex:horseoxboth}
+\bg. bæx-tæ æmæ gæl-t-imæ\\
+horse-\tsc{pl} and ox-\tsc{pl-com}\\
+`with horses and oxen' \hfill (Iron Ossetic, \citep[165]{erschler2012})\label{ex:horseoxone}
+
+\ref{ex:suspendedme} gives examples of the first person singular in a suspended affixation contexts.
+It shows that it is \tit{mæn} that appears as a caseless first conjunct and that the use of \tit{æz} is ungrammatical.
+This means that \tit{mæn} is the bare stem that combines with case markers, and \tit{æz} the suppletive nominative.
+In Section \ref{sec:derivation} I show how a derivation with this type of elements works in nanosyntax.
+
+\ex.\label{ex:suspendedme}
+\ag. mæn æmæ Zauyr-æn\\
+ 1.\tsc{sg} and Zaur-\tsc{dat}\\\label{ex:izaurboth}
+\bg. *æz æmæ Zauyr-æn\\
+ 1.\tbf{sg} and Zaur-\tsc{dat}\\
+ `me and Zaur' \hfill (\citealt[39]{беляев2014} after \citealt{caha2019competition})\label{ex:izaurone}
+
+The point of showing the Ossetic example is that Dutch is not unique in having suppletive forms that are less marked (in this case nominative, accusative and dative), and higher cases that are a combination of a suffix and a base form.
+
+\subsubsection{\tit{-mee} vs. \tit{met}}
+
+The last two forms to specify lexical entries for are \tit{-mee} `with' and \tit{met} `with'.
+An important distinction between these two is that \tit{-mee} appears after the element it combines with (\tsc{'r}), while \tit{met} appears before the element it combines with (\tit{'t}).
+I will analyze \tit{-mee} as a postposition and \tit{met} as a preposition.
 In this section I discuss the relation between prepositions and postpositions, and how this is modeled with the case hierarchy in Nanosyntax \citep{caha2009}.
-
-%$Now we come to mee and met.
-the crucial distinction between these elements is that \tit{mee} is postposition and \tit{met} is a preposition.
-i show: (i) relation between these types of elements, (ii) how that is being modeled with movement, (iii) that post goes before pre (iv) how that is modeled in nano.
 
@@
 
-\exg. von ein-em Löffel\\
-von a-\tsc{dat.sg} spoon\\
-`of a spoon' \hfill (German)\label{ex:loffel}
+\exg. (die Farbe) von ein -em Löffel\\
+the color of a -\tsc{dat.sg} spoon\\
+`(the color) of a spoon' \hfill (German)\label{ex:loffel}
 
@@
 The features below the \tsc{datP} are realized as a suffix, and the features above \tsc{datP} are realized as a preposition.
-I gloss over the fact that \tit{-em} is realized on the article and not
 
@@
 \ex.\label{ex:bulgarian}
-\ag. Tazi duma m-i e nepoznata.\\
-that word I-\tsc{dat} is unfamiliar\\
+\ag. Tazi duma m -i e nepoznata.\\
+that word I -\tsc{dat} is unfamiliar\\
 `That word is unfamiliar to me.'\label{ex:bulpron}
@@
 that word is unfamiliar to son my\\
-`That word is unfamiliar to my son.'\label{ex:buldpto}
+`That word is unfamiliar to my son.'\label{ex:buldpto} \hfill \citep[39]{caha2009}
 
@@
 In Dutch, inanimate pronouns combine with the postposition \tit{-mee} (see \ref{ex:dutchina} and not with the preposition \tit{met} (see \ref{ex:dutchinmet}).
-Animate pronouns and full DPs, however, combine with the preposition met, as shown in \ref{ex:dutchan} and \ref{ex:dutchdp}.
-The use of the postposition \tit{-mee} is ungrammatical (see \ref{ex:dutchanmee} and \ref{ex:dutchdpmee}).
 
@@
  `I am painting with it.'\label{ex:dutchinmet}
-\bg. Ik schilder samen met hem.\\
+
+Animate pronouns and full DPs, however, combine with the preposition met, as shown in \ref{ex:dutchan} and \ref{ex:dutchdp}.
+The use of the postposition \tit{-mee} is ungrammatical (see \ref{ex:dutchanmee} and \ref{ex:dutchdpmee}).
+
+\ex.
+\ag. Ik schilder samen met hem.\\
  I paint together with him\\
  `I am painting with him.'\label{ex:dutchan}
+\bg. Ik schilder samen met de man.\\
+ I paint together with the man\\
+ `I am painting together with the man.'\label{ex:dutchdp}
 \bg. *Ik schilder samen 'm-mee.\\
@@
  `I am painting together with him.'\label{ex:dutchanmee}
-\bg. Ik schilder samen met de man.\\
- I paint together with the man\\
- `I am painting together with the man.'\label{ex:dutchdp}
 \bg. *Ik schilder samen de man-mee.\\
@@
 
-The next issue I turn to is what the lexical entry of \tit{mee} looks like.
+ In other words, inanimates can move higher than animates and full DPs in Dutch.
+To be more precise, the inanimate \tit{'t} is replaced by \tit{'r}, and this element can move as high as above the dative to combine with \tit{-mee}.
+Later I return to what it is that prevents animates and full DPs from being combined with \tit{-mee}.
+
+First I show to is what the lexical entry of \tit{-mee} looks like.
 This needs to capture three facts.
-\tit{Mee} combines with \tit{'r}, it is a postposition, and it does not combine with animates and full DPs.
-
-First, \tit{mee} expresses instrumental (and comitative) case and it combines with \tit{'r}.\footnote{For reasons of space I leave \tsc{f6} out of the lexical entries and discussion, even though \tit{mee} and \tit{met} can also express comitative.} So far, \tit{'r} `there' only realizes the feature \tsc{thing}.
-This leaves Σ and \tsc{f1} to \tsc{f5} to be realized by \tit{mee}.
-I give the lexical tree of \tit{mee} in \ref{ex:entrymee}.
+\tit{-mee} combines with \tit{'r}, and it is a postposition.
+First, \tit{-mee} expresses instrumental (and comitative) case and it combines with \tit{'r}.\footnote{For reasons of space I leave \tsc{f6} out of the lexical entries and discussion, even though \tit{-mee} and \tit{met} can also express comitative.}
+So far, \tit{'r} `there' only realizes the feature \tsc{thing}. This leaves Σ and \tsc{f1} to \tsc{f5} to be realized by \tit{-mee}. I give the lexical tree of \tit{-mee} in \ref{ex:entrymee}.
 
@@
     [\tsc{insP}
-        [\tsc{f}6]
+        [\tsc{f6}]
         [\tsc{genP}
             [\tsc{f4}]
-            [\tsc{dat}P
-                [\tsc{f}3]
-                [\tsc{acc}P
-                    [\tsc{f}2]
-                    [\tsc{nom}P
-                        [\tsc{f}1]
-                        [ΣP
-                            [Σ]
-                        ]
-                    ]
-                ]
-            ]
-        ]
-    ]
-{\draw (.east) node[right]{⇔ \tit{mee}}; }
+            [\tsc{datP}
+                [\tsc{f3}]
+                [\tsc{accP}
+                    [\tsc{f2}]
+                    [\tsc{nomP}
+                        [\tsc{f1}]
+                        [ΣP
+                            [Σ]
+                        ]
+                    ]
+                ]
+            ]
+        ]
+    ]
+{\draw (.east) node[right]{⇔ \tit{-mee}}; }
 \end{forest}\label{ex:entrymee}
 
-This leads us to the second point: \tit{mee} is a postposition.
+This leads us to the second point: \tit{-mee} is a postposition.
 Notice that the foot of the structure has a singleton feature.
-Nanosyntax distinguishes pre-elements from post-elements by the shape of their lexical entry.
+Nanosyntax distinguishes pre-elements from post-elements by the shape of their lexical entry \citep{starke2018}.
 As a result, the whether an element is pre or post is lexically stored as follows from the spellout procedure.
@@
 
-Why does \tit{mee} not combine with animates and full DPs?
-I claim that has to do with the bottom feature of the lexical entry of \tit{mee}.
+Why does \tit{-mee} not combine with animates and full DPs?
+I claim that has to do with the bottom feature of the lexical entry of \tit{-mee}.
 Full DPs do not take features related to pronominal strength.
-According to the Superset Principle, a lexical tree can also match a syntactic tree with a subpart of the features, but a tree can only shrink from the top, so \tit{mee} will always realize Σ.
-I have a less clear answer to why animates do not combine with \tit{mee}.
+According to the Superset Principle, a lexical tree can also match a syntactic tree with a subpart of the features, but a tree can only shrink from the top, so \tit{-mee} will always realize Σ.
+I have a less clear answer to why animates do not combine with \tit{-mee}.
 The crucial difference between animates and inanimates if gender features.
 For now I assume that gender features are situated between Σ and \tsc{f1}.
-The lexical entry of \tit{mee} includes both these features, so any features are incompatible with \tit{mee}.
+The lexical entry of \tit{-mee} includes both these features, so any features are incompatible with \tit{-mee}.
 So far I do not have independent evidence for placing gender features between features of pronominal strength and case, and I leave this for future research.
 
-So far I discussed \tit{mee} is a postposition, which follows \tit{'r} and is stored with a unary bottom.
+So far I discussed \tit{-mee} is a postposition, which follows \tit{'r} and is stored with a unary bottom.
 \tit{Met}, on the other hand, is a preposition, it precedes \tit{'t}, so it should be stored with a binary bottom.
 The highest case feature \tit{'t} can realize is \tsc{f3}, so the preposition realizes all higher cases up to \tsc{f5}.
-
-\ex. \begin{forest} boom
-[\tsc{ins}P
-    [\tsc{f}5]
-    [\tsc{f}4]
+I give the lexical entry for \tit{met} in \ref{ex:entrymet}.
+
+\ex. \begin{forest} boom
+[\tsc{insP}
+    [\tsc{f5}]
+    [\tsc{f4}]
 ]
@@
 
-\subsubsection{Backtracking}
-
-If the spellout procedure in fails, backtracking takes place.
+In the next section I put all features back together in a derivation and I show how \tit{waarmee} `with what' surfaces when all features form a constituent.
+\tit{Met wat} `with what' appears when the functional sequence is disrupted.
+
+\section{In a derivation}\label{sec:derivation}
+
+Before I show that \tit{waarmee} `with what' is used when all features form a proper constituent, I need to make some assumptions about the spellout process in Nanosyntax explicit.
+Spellout happens in a cyclic derivation, following a spellout algorithm \citep{starke2018}.
+After each instance of merge, spellout takes place.
+If no spellout exist for the phrase created by the newly added feature, evacuation movements specified in the spellout algorithm take place.
+The algorithm is given in \ref{ex:spellout}.
+
+\ex. Merge F and \label{ex:spellout}
+ \a. Spell out FP
+ \b. If (a) fails, attempt movement of the spec of the complement of \tsc{f}, and retry (a)
+ \b. If (b) fails, move the complement of \tsc{f}, and retry (a)
+
+When a new match is found, it overrides previous spellouts.
+
+\ex. Cyclic Override \citep{starke2018}:\\
+Lexicalisation at a node XP overrides any previous match at a phrase contained in XP.
+
+If the spellout procedure in \ref{ex:spellout} fails, backtracking takes place.
+This is a crucial operation to get from the suppletive nominative, accusative and dative \tit{'t} to the base form \tit{'r}.
 
 \ex. Backtracking \citep{starke2018}:\\
-When spellout fails, go back to the previous cycle, and try the next option for that cycle.
-
-\begin{table}[ht]
-	\center
-	\caption {Iron Ossetic pronoun and noun}
-	\begin{minipage}{0.56\linewidth}
-		\begin{tabularx}{\textwidth}{ccccccc}
-		\toprule
-              & 1.\tsc{sg}  & head    \\
-		\midrule
-    \tsc{nom} & æz          & sær-Ø   \\
-    \tsc{acc} & mæn-Ø       & sær-Ø   \\
-    \tsc{gen} & mæn (⁇?)    & sær-y   \\
-    \tsc{ins} & mæn-æj      & sær-æj  \\
-    \tsc{dat} & mæn-æn      & sær-æn  \\
-    \tsc{all} & mæn-mæ      & sær-mæ  \\
-    \tsc{ade} & mæn-yl      & sær-yl  \\
-    \tsc{eq}  & mæn-au      & sær-au  \\
-    \tsc{com} & mæn-imæ     & sær-imæ \\
-    \bottomrule
-\end{tabularx}
-\label{tbl:ossetic}
-\end{minipage}
-\end{table}
-
-now the question: is \tit{æz} a suppletive nominative or is \tit{mæn} the suppletive stem from the accusative on? ossetic has a way to tell: suspended affixation.
-
-What we see in (3-a) is an ordinary coordination of two phrases, each marked
-by a plural marker and a case marker. Suspended affixation is then illustrated in
-(3-b). It is a type of a coordination where the comitative case marker is located
-only on the second conjunct, with no change in interpretation. The first conjunct
-simply bears no case marker in such cases.
-
-\ex.
-\ag. bæx-t-imæ æmæ gæl-t-imæ\\
-horse-pl-com and ox-pl-com\\
-\bg. bæx-tæ æmæ gæl-t-imæ\\
-horse-pl and ox-pl-com\\
-`with horses and oxen' \hfill (Iron Ossetic, Erschler 2012: 165)
-
-doing this with 1\tsc{sg} shows that the bare stem is \tit{mæn}.
-
-\ex.
-\ag. mæn æmæ Zauyr-æn\\
- 1.\tsc{sg} and Zaur-\tsc{dat}\\
-\bg. *æz æmæ Zauyr-æn\\
- 1.\tbf{sg} and Zaur-\tsc{dat}\\
- `me and Zaur' \hfill (Belyaev 2014: 39)
-
-\tit{mæn} is actually the caseless form, \tit{æz} is marked for nominative.
-
-my conclusion: Dutch has a suppletive form for nominative, accusative and dative. Then higher cases do not combine with that suppletive form, but with the unmarked form.
-
-'t
-'t
-'t
-'r-van
-'r-mee
-'r-mee
-
-\subsubsection{The lexical entries}
-
-Continuing with \tit{met} `with', which I have shown in this paper can be used to express instrumental. It can also be used as comitative, as shown in \ref{ex:metinscom}.
-
-\exg. Ik dans met hem.\\
- I dance with him\\
- `I am dancing with him.'\label{ex:metinscom}
-
-Case features are in a containment relation and instrumental contains all case features down to \tsc{f1}.
-Some of these features are expressed by the preposition, and other by the DP they combine with.
-As pronouns in Dutch can realize up to \tsc{f3}, the preposition starts from \tsc{f4}.
-
-In sum, the syntactic structure that \tit{met wat} `with what' realizes is the one in \ref{ex:stmetwat}.
-
-\ex. [ [ [ [ \tsc{thing} ] \tsc{f1} ] \tsc{f2} ] \tsc{f3} \tsc{f4} ]\label{ex:stmetwat}
-
-Let us now turn to \tit{'rmee} `with it', which lexicalizes the same structure as \tit{met 't} `with it', but with a different distribution.
-
-Note that there are two differences between the lexical entry in \ref{ex:entrymet} and \ref{ex:entrymee}.
-First, the lexical entry for \tit{mee} `with' in \ref{ex:entrymee}, in addition to the one for \tit{met} `with' in \ref{ex:entrymet}, contains the features \tsc{f1}, \tsc{f2} and \tsc{f3}.
-Second, the lexical entry in \ref{ex:entrymet} has a binary bottom, and the lexical entry in \ref{ex:entrymee} has a unary bottom.
-\tit{Met} `with' is a preposition (preposition), so it has a binary bottom, and \tit{mee} `with' is a postposition, so it needs a unary bottom.
-In the next section I show how this works in a derivation.\footnote{For completeness, \tit{mee} `with' has to be blocked from combining with full DPs and animate pronouns (reference).
-For now I assume that these pronouns spell out an additional feature \tit{σ} that is not realized by \tit{mee} `with' but only by \tit{met} `with'.
-Full DPs combine in addition with a zero marker for dative case.
-This way \tit{mee} `with' does not compete with \tit{met} `anymore'.
-I left this features out in this paper, at is does not contribute to the main point.}$^,$\footnote{Giving \tit{met} `with' and \tit{mee} `with' two distinct lexical entries has as a consequence that the phonological overlap between them seems like a coincidence.
+When spellout fails, go back to the previous cycle, and try the next option for that cycle.\label{ex:backtracking}
+
+If backtracking also does not help, a specifier is constructed. This is what happens when the preposition \tit{met} is inserted.
+
+\ex. Spec Formation \citep{starke2018}:\\
+If Merge F has failed to spell out (even after backtracking), try to spawn a new derivation providing the feature F and merge that with the current derivation, projecting the feature F at the top node.
+
+I first show how \tit{'rmee} `with it' is constructed.
+I leave out \tit{w} and \tit{a}, because it unnecessarily complicates the story.\footnote{I assume that the WP and \tsc{deixP} appear lower in the structure than the case features, so the functional sequence is as given in \ref{ex:fseq}.
+
+\ex. [ [ [ [ [ [ [ \tsc{thing} ] \tsc{deix} ] W ] \tsc{f1} ] \tsc{f2} ] \tsc{f3} ] \tsc{f4} ]\label{ex:fseq}
+\z.
+
+\phantom{x}
+
+}
+
+We start with \tsc{thing}.
+The two candidates here are \ref{ex:entryt} and \ref{ex:entryr}.
+Following the Elsewhere Condition, \ref{ex:entryr} wins the competition because it contains less unused material.
+
+\ex.
+\begin{forest} boom
+ [\tsc{thingP}
+     [\tsc{thing}, roof]
+ ]
+{\draw (.east) node[right]{⇒ \tit{'r}}; }
+\end{forest}\label{ex:thingspellout}
+
+In the next step, Σ is merged.
+\ref{ex:entryr} is no longer a candidate because it does not contain Σ.
+\ref{ex:entryt} still is a candidate, because it contains all features in \ref{ex:thingf1}.
+The spellout is overridden and the structure is realized as \tit{'t}.
+
+\ex. \begin{forest} boom
+[ΣP
+   [Σ]
+   [\tsc{thingP}
+       [\tsc{thing}, roof]
+   ]
+]
+{\draw (.east) node[right]{⇒ \tit{'t}}; }
+\end{forest}\label{ex:thingf1}
+
+Then \tsc{f1} is merged. This structure can still be realized by \tit{'t}.
+
+\ex. \begin{forest} boom
+[\tsc{nomP}
+   [\tsc{f1}]
+   [ΣP
+       [Σ]
+       [\tsc{thingP}
+           [\tsc{thing}, roof]
+       ]
+   ]
+]
+{\draw (.east) node[right]{⇒ \tit{'t}}; }
+\end{forest}
+
+The same holds for the next two steps in which \tsc{f2} and \tsc{f3} are merged: the structure can still be spelled out as \tit{'t}.
+
+\ex. \begin{forest} boom
+[\tsc{datP}
+    [\tsc{f3}]
+    [\tsc{accP}
+       [\tsc{f2}]
+       [\tsc{nomP}
+           [\tsc{f1}]
+           [ΣP
+               [Σ]
+               [\tsc{thingP}
+                   [\tsc{thing}, roof]
+               ]
+           ]
+       ]
+    ]
+]
+{\draw (.east) node[right]{⇒ \tit{'t}}; }
+\end{forest}
+
+Then \tsc{f4} is merged, as shown in \ref{ex:f4no}.
+\ref{ex:entryt} can no longer spell out the structure, because it does not contain \tsc{f4}.
+There is also no other candidate to spell out the structure as it is.
+
+\ex. \begin{forest} boom
+[\tsc{insP}
+    [\tsc{f4}]
+    [\tsc{datP}
+        [\tsc{f3}]
+        [\tsc{accP}
+           [\tsc{f2}]
+           [\tsc{nomP}
+               [\tsc{f1}]
+               [ΣP
+                   [Σ]
+                   [\tsc{thingP}
+                       [\tsc{thing}, roof]
+                   ]
+               ]
+           ]
+        ]
+    ]
+]
+{\draw (.east) node[right]{⇒ }; }
+\end{forest}\label{ex:f4no}
+
+According to the spellout algorithm in \ref{ex:spellout}, it should be attempted to move of the spec of the complement of \tsc{f4}.
+However, there is no specifier in \ref{ex:f4no}, so this does not apply.
+The second movement option is complement movement.
+The complement of \tsc{f4} moves to the specifier of \tsc{insP}, resulting in the structure in \ref{ex:f4comp}.
+The lexicon does not contain an entry with \tsc{insP} which contains only \tsc{f4}.\footnote{\tit{Met} `with' is not a candidate, because the syntactic structure has a unary bottom and the lexical structure has a binary bottom.}
+
+\ex. \begin{forest} boom
+[\tsc{datP}
+    [\tsc{datP}
+        [\tsc{f3}]
+        [\tsc{accP}
+           [\tsc{f2}]
+           [\tsc{nomP}
+               [\tsc{f1}]
+               [ΣP
+                   [Σ]
+                   [\tsc{thingP}
+                       [\tsc{thing}, roof]
+                   ]
+               ]
+           ]
+        ]
+    ]
+    {\draw (.east) node[right]{⇒ \tit{'t}}; }
+    [\tsc{insP}
+        [\tsc{f4}]
+    ]
+    {\draw (.east) node[right]{⇒ }; }
+]
+\end{forest}\label{ex:f4comp}
+
+As I formulated in the introduction of this section, the operation called Backtracking is triggered (see \ref{ex:backtracking}).
+This means that the derivation goes back to the previous cycle, and the next option for that cycle is tried.
+In this case, the previous cycle is the one in which \tsc{f3} is merged.
+The next option for that cycle is spec-to-spec movement.
+As there is no specifier, this does not apply.
+The option after that is complement movement, shown in \ref{ex:f3comp}.
+However, there is no match in the lexicon for an \tsc{datP} that contains only \tsc{f3}.
+
+\ex. \begin{forest} boom
+[\tsc{accP}
+    [\tsc{accP}
+       [\tsc{f2}]
+       [\tsc{nomP}
+           [\tsc{f1}]
+           [ΣP
+               [Σ]
+               [\tsc{thingP}
+                   [\tsc{thing}, roof]
+               ]
+           ]
+       ]
+    ]
+    {\draw (.east) node[right]{⇒ \tit{'t}}; }
+    [\tsc{datP}
+        [\tsc{f3}]
+    ]
+    {\draw (.east) node[right]{⇒ }; }
+]
+\end{forest}\label{ex:f3comp}
+
+This means that backtracking proceeds further, into the cycle in which \tsc{f2} was merged.
+Again, spec-to-spec movement does not apply because there is no specifier, and complement movement can be tried, but there is no fitting lexical entry available.
+The same holds for the cycle in which \tsc{f1} is merged.
+
+The situation changes when the derivation comes to the cycle in which Σ was merged.
+At this stage, \tsc{thing} was realized as \tit{'r}.
+Again there was no specifier, no spec-to-spec movement does not apply.
+However, complement movement provides a structure that is a match for the lexical entry in \ref{ex:entrymee}: \tit{-mee}.
+
+\ex. \begin{forest} boom
+[ΣP
+   [\tsc{thingP}
+       [\tsc{thing}, roof]
+   ]
+   {\draw (.east) node[right]{⇒ \tit{'r}}; }
+   [ΣP
+       [Σ]
+   ]
+   {\draw (.east) node[right]{⇒ \tit{-mee}}; }
+]
+\end{forest}
+
+From this point on the previously unmerged features are merged again one by one. First, \tsc{f1} is merged again, shown in \ref{ex:f1again}. No match exists for this syntactic structure.
+
+\ex. \begin{forest} boom
+[\tsc{nomP}
+    [\tsc{f1}]
+    [ΣP
+       [\tsc{thingP}
+           [\tsc{thing}, roof]
+       ]
+       [ΣP
+           [Σ]
+       ]
+    ]
+]
+{\draw (.east) node[right]{⇒}; }
+\end{forest}\label{ex:f1again}
+
+Following the spellout algorithm, the next step is spec-to-spec movement is tried. The result is shown in \ref{ex:f1spec}. In that configuration \tsc{f1} can be realized together with Σ as \tit{-mee}.
+
+\ex. \begin{forest} boom
+[\tsc{nomP}
+   [\tsc{thingP}
+       [\tsc{thing}, roof]
+   ]
+   {\draw (.east) node[right]{⇒ \tit{'r}}; }
+   [\tsc{nomP}
+       [\tsc{f1}]
+       [ΣP
+           [Σ]
+       ]
+   ]
+   {\draw (.east) node[right]{⇒ \tit{-mee}}; }
+ ]
+\end{forest}\label{ex:f1spec}
+
+The same happens for \tsc{f2}, \tsc{f3} and \tsc{f4}.
+The features are merged one at a time, there is no spellout after merging the feature, but there is a spellout after spec-to-spec movement.
+I show the situation after \tsc{f4} is realized as  \ref{ex:spellout'rmee}.
+
+\ex. \begin{forest} boom
+[\tsc{insP}
+    [\tsc{thingP}
+       [\tsc{thing}, roof]
+    ]
+    {\draw (.east) node[right]{⇒ \tit{'r}}; }
+    [\tsc{insP}
+       [\tsc{f4}]
+       [\tsc{datP}
+           [\tsc{f3}]
+           [\tsc{accP}
+               [\tsc{f2}]
+               [\tsc{nomP}
+                   [\tsc{f1}]
+                   [ΣP
+                       [Σ]
+                   ]
+               ]
+           ]
+       ]
+    ]
+    {\draw (.east) node[right]{⇒ \tit{-mee}}; }
+]
+\end{forest}\label{ex:spellout'rmee}
+
+I skip over the details of how \tit{w} and \tit{a} end up in their positions.\footnote{I assume that WP and \tsc{deixP} are both complex specifiers that are created after \tsc{thing} is spelled out in \ref{ex:thingspellout}.
+After each instance of merge after that, backtracking always takes place, the complex specifier is detached from the structure and the case features are spelled out together with or as a postposition on \tsc{thing}.} The final result of the structure for \tit{waarmee} `with what' look as in \ref{ex:spelloutwaarmee}.
+
+\ex. \begin{forest} boom
+[\tsc{WP}
+    [\tsc{WP}
+        [\tsc{W}, roof]
+    ]
+    {\draw (.east) node[right]{⇒ \tit{w}}; }
+    [\tsc{deixP}
+        [\tsc{deixP}
+            [\tsc{deix}, roof]
+        ]
+        {\draw (.east) node[right]{⇒ \tit{a}}; }
+        [\tsc{insP}
+            [\tsc{thingP}
+               [\tsc{thing}, roof]
+            ]
+            {\draw (.east) node[right]{⇒ \tit{'r}}; }
+            [\tsc{insP}
+               [\tsc{f4}]
+               [\tsc{datP}
+                   [\tsc{f3}]
+                   [\tsc{accP}
+                       [\tsc{f2}]
+                       [\tsc{nomP}
+                           [\tsc{f1}]
+                           [ΣP
+                               [Σ]
+                           ]
+                       ]
+                   ]
+               ]
+            ]
+            {\draw (.east) node[right]{⇒ \tit{-mee}}; }
+        ]
+    ]
+]
+\end{forest}\label{ex:spelloutwaarmee}
+
+A consequence of analyzing \tit{-mee} `with' as a postposition is that \tit{r} and \tit{-mee} always form a constituent to the exclusion of \tit{w} and \tit{a}.
+At first sight this seems problematic, because it is possible for \tit{waar} `where', stranding \tit{-mee} `with'.
+I repeat the relevant example in \ref{ex:meestranded}.
+
+\exg. Ik heb gekocht waar jij mee schildert.\\
+ I have bought waar you with paint\\
+ `I bought what you are painting with.'\label{ex:meestranded}
+
+There is no constituent in \ref{ex:spelloutwaarmee} that contains \tit{waar} but not \tit{-mee}.
+To resolve this situation I follow \citet{noonan2017dutch} in assuming that the phrase containing the adposition (here \tit{-mee}) syntactically moves to a position higher in the structure.
+The movement of the adposition has the typical distribution of that of verbal particles (cf.
+\citealt{riemsdijk1978,noonan2017dutch}, and it could possibly be triggered by the feature Σ, associated with weak pronouns.
+With \tit{-mee} having moved out, the WP only contains features that are realized as \tit{waar}, and it moves to the left edge of the clause, resulting in the surface order in \ref{ex:meestranded}.
+
+So far I showed how \tit{waarmee} `with what' is derived if all syntactic features form a constituent.
+Next I address how \tit{waarmee} is blocked and \tit{met wat} `with what' appears when the features do not form a proper constituent is derived.
+An example of a situation in which all features do not form a constituent is given in \ref{ex:noconst}.
+
+\exg. Ik schilder met wat jij hebt gekocht.\\
+ I paint with what you have bought\\
+ `I paint with what you bought.'\label{ex:noconst}
+
+I start at the point on which \tit{wat} `what' is part of a syntactic structure with the rest of a relative clause as a sister.
+
+\ex. \begin{forest} boom
+[CP
+    [\tsc{WP}
+        [\tsc{WP}
+            [\tsc{W}, roof]
+        ]
+        {\draw (.east) node[right]{⇒ \tit{w}}; }
+        [\tsc{deixP}
+            [\tsc{deixP}
+                [\tsc{deix}, roof]
+            ]
+            {\draw (.east) node[right]{⇒ \tit{a}}; }
+            [\tsc{accP}
+               [\tsc{f2}]
+               [\tsc{nomP}
+                   [\tsc{f1}]
+                   [ΣP
+                       [Σ]
+                       [\tsc{thingP}
+                           [\tsc{thing}, roof]
+                       ]
+                   ]
+               ]
+            ]
+            {\draw (.east) node[right]{⇒ \tit{'t}}; }
+        ]
+    ]
+    [CP
+        [...,roof]
+    ]
+]
+\end{forest}
+
+\ex. \begin{forest} boom
+[\tsc{NP}
+    [NP
+        [NP, roof]
+    ]
+    {\draw (.east) node[right]{⇒ \tit{∅}}; }
+    [CP
+        [\tsc{WP}
+            [\tsc{WP}
+                [\tsc{W}, roof]
+            ]
+            {\draw (.east) node[right]{⇒ \tit{w}}; }
+            [\tsc{deixP}
+                [\tsc{deixP}
+                    [\tsc{deix}, roof]
+                ]
+                {\draw (.east) node[right]{⇒ \tit{a}}; }
+                [\tsc{accP}
+                   [\tsc{f2}]
+                   [\tsc{nomP}
+                       [\tsc{f1}]
+                       [ΣP
+                           [Σ]
+                           [\tsc{thingP}
+                               [\tsc{thing}, roof]
+                           ]
+                       ]
+                   ]
+                ]
+                {\draw (.east) node[right]{⇒ \tit{'t}}; }
+            ]
+        ]
+        [CP
+            [...,roof]
+        ]
+    ]
+]
+\end{forest}
+
+After that, \tsc{f4} is merged. here
+
+When a dative feature is merged here, it will not be able to be spelled out.
+The only option to realize the features is to form to spawn a new derivation, to create a complex specifier.
+And that is exactly what forming the preposition \tit{met} `with' is.
+
+\section{Conclusion and discussion}
+
+In this paper, I discussed the distribution of \tit{waarmee} `met wat' and \tit{met wat} `with what' is mismatching free relatives.
+I showed that \tit{waarmee} `with what' appears when all features form a proper constituent, and \tit{met wat} `with what' if they do not.
+
+The described pattern follows from a core assumptions in Nanosyntax: phrasal spellout spells out constituents.
+Looking more into detail, \tit{waarmee} `with what' takes precedence over \tit{met wat} `with what' because \tit{-mee} has the structure of a postposition.
+Following the spellout algorithm, \tit{'t} `it' is replaced by \tit{'r} `there', so that it can combine with \tit{-mee} `with'.
+The preposition \tit{met} `with' is only used if there is no other option to spell out the features.
+
+This proposal is in several aspects in accordance with earlier work.
+Just like \citet{riemsdijk1978}, I claim that \tsc{r}-pronouns originate as the complement of P.
+He argued that due to some kind of suppletion \tit{'t} `it' changes form to \tsc{'r}, which is coincidentally also the locative in Dutch.
+In my proposal, this suppletion follows naturally from the regular spellout algorithm.
+Also, it is not a coincidence that the locative appears, as it is an item with little features that spells out \tsc{thing}.
+The current proposal differs from \citet{riemsdijk1978} in that it is not the whole complement of P is moved.
+Instead, only part of the complement of P is extracted, which is generally allowed, also in non-preposition stranding languages \citep{abels2003diss}.
+
+Giving \tit{met} `with' and \tit{-mee} `with' two distinct lexical entries has as a consequence that the phonological overlap between them seems like a coincidence.
 Moreover, in almost all cases the preposition does not change form when it combines with an \tsc{r}-pronoun, e.g.
@@
 
-I leave it to future research to determine whether this is a feasible solution.}$^,$\footnote{A topic related to this paper is the different positioning of identical adpositions in Dutch (see \citet{caha2010} for an account of German and Dutch and \citet{pretorius2017} for Afrikaans).
+I leave it to future research to determine whether this is a feasible solution.
+
+A topic related to this paper is the different positioning of identical adpositions in Dutch (see \citet{caha2010} for an account of German and Dutch and \citet{pretorius2017} for Afrikaans).
 In \ref{ex:dutchin}, \tit{in} changes meaning dependening on whether it proceeds or follows the DP, it is respectively locational or directional.
@@
 In \ref{ex:dutchin}, the movement of the adposition is driven by movement, and it is meaningful.
-The movement I discuss in this paper with \tsc{r}-pronouns is driven by spellout, and it is meaningless.}
-
-Table \ref{tbl:withfeatures} gives an overview of the distribution of the features in \tit{met wat} `with what' and \tit{waarmee} `with what'.
-In both cases, \tit{w} and \tit{a} are the realization of the same morpheme.
-The difference between the two expressions lies in the distribution of the case features.
-\tit{Mee} `with' realizes all of them, and \tit{met} `with' only the top two.
-The residues are realized by respectively \tit{'r} `there' and \tit{'t} `it'.
-
-\begin{table}[ht]
-	\center
-	\caption {\tit{met wat} and \tit{waarmee}}
-	\begin{minipage}{0.56\linewidth}
-		\begin{tabularx}{\textwidth}{ccccccc}
-		\toprule
-    \tsc{wh}  & \tsc{deix}                     & \tsc{f}4  & \tsc{f}3 & \tsc{f}2  & \tsc{f}1  & \tsc{thing} \\
-		\midrule
-    \tit{w}   & \multicolumn{1}{|c|}{\tit{a}}  & \tit{met} & \multicolumn{4}{|c}{\tit{'t}}                \\\hline
-    \tit{w}   & \multicolumn{1}{|c|}{\tit{a}}  & \multicolumn{4}{c|}{\tit{mee}}               & \tit{'r}  \\
-    \bottomrule
-\end{tabularx}
-\label{tbl:withfeatures}
-\end{minipage}
-\end{table}
-
-In the next section I put all features back together in a derivation and I show how \tit{waarmee} `with what' surfaces when all features form a constituent.
-\tit{Met wat} `with what' appears when the functional sequence is disrupted.
-
-% I do not care whether \tit{w} and \tit{a} are merged before or after.
-%
-% WHY DOES MEE MOVE? I DO NOT KNOW.
-% BUT IT DOES.
-% AND SO DOES WAAR.
-% waar maybe because it is remnant movement?
-%
-%
-%
-% Either way, it combines with accusative/dative (oblique), which can be seen on the pronouns.
-But only for the comitative, because for the instrumental we are getting an ʀ-pronoun.
-Full DPs do not show any marking, leading me to postulate the zero marker up to the dative.
-%
-% \ex.
-% \ag. Ik dans met de man.\\
-%  I dance with the man\\
-%  `I am dancing with the man.'
-% \bg. Ik schilder met een kwast.\\
-%  I paint with een brush\\
-%  `I am painting with een brush.'
-%
-% \ex. \begin{forest} boom
-% [\tsc{datP}
-%    [\tsc{f}3]
-%    [\tsc{acc}P
-%        [\tsc{f}2]
-%        [\tsc{nom}P
-%            [\tsc{f}1]
-%            [\phantom{x}]
-%        ]
-%    ]
-% ]
-% {\draw (.east) node[right]{⇔ \tit{∅}}; }
-% \end{forest}»
-
-\section{Showing it in a derivation}\label{sec:derivation}
-
-Repeat spellout algorithm
-
-spellout
-backtracking
-complex spec
-
-I first show how \tit{'rmee} `with it' is constructed.
-I leave out \tit{w} and \tit{a}, because it unnecessarily complicates the story.\footnote{I assume that the WP and \tsc{deixP} appear lower in the structure than the case features, so the functional sequence is as given in \ref{ex:fseq}.
-
-\ex. [ [ [ [ [ [ [ \tsc{thing} ] \tsc{deix} ] W ] \tsc{f1} ] \tsc{f2} ] \tsc{f3} ] \tsc{f4} ]\label{ex:fseq}
-\z.
-
-\phantom{x}
-
-}
-
-We start with \tsc{thing}.
-The two candidates here are \ref{ex:entryt} and \ref{ex:entryr}.
-Following the Elsewhere Condition, \ref{ex:entryr} wins the competition because it contains less unused material.
-
-\ex.
-\begin{forest} boom
- [\tsc{thingP}
-     [\tsc{thing}, roof]
- ]
-{\draw (.east) node[right]{⇒ \tit{'r}}; }
-\end{forest}\label{ex:thingspellout}
-
-In the next step, \tsc{f}1 is merged.
-\ref{ex:entryr} is no longer a candidate because it does not contain \tsc{f1}.
-\ref{ex:entryt} still is a candidate, because it contains all features in \ref{ex:thingf1}.
-The spellout is overridden and the structure is realized as \tit{'t}.
-
-\ex. \begin{forest} boom
-[\tsc{nom}P
-   [\tsc{f}1]
-   [ΣP
-       [Σ]
-       [\tsc{thingP}
-           [\tsc{thing}, roof]
-       ]
-   ]
-]
-{\draw (.east) node[right]{⇒ \tit{'t}}; }
-\end{forest}\label{ex:thingf1}
-
-Then \tsc{f}2 is merged. This structure can still be realized by \tit{'t}.
-
-\ex. \begin{forest} boom
-[\tsc{accP}
-   [\tsc{f}2]
-   [\tsc{nom}P
-       [\tsc{f}1]
-       [ΣP
-           [Σ]
-           [\tsc{thingP}
-               [\tsc{thing}, roof]
-           ]
-       ]
-   ]
-]
-{\draw (.east) node[right]{⇒ \tit{'t}}; }
-\end{forest}
-
-In the next step \tsc{f3} is merged, the structure is still spelled out as \tit{'t}.
-
-\ex. \begin{forest} boom
-[\tsc{datP}
-    [\tsc{f}3]
-    [\tsc{accP}
-       [\tsc{f}2]
-       [\tsc{nom}P
-           [\tsc{f}1]
-           [ΣP
-               [Σ]
-               [\tsc{thingP}
-                   [\tsc{thing}, roof]
-               ]
-           ]
-       ]
-    ]
-]
-{\draw (.east) node[right]{⇒ \tit{'t}}; }
-\end{forest}
-
-Then \tsc{f4} is merged, as shown in \ref{ex:f4no}.
-\ref{ex:entryt} can no longer spell the structure out, because it does not contain \tsc{f4}.
-Moreover, there is no candidate to spell out the structure as it is, so evacuation movement takes place.
-According to the spellout algorithm, the first evacuation movement to be tried is spec-to-spec movement.
-However, there is no specifier in this structure, so this does not apply.
-The second movement option is complement movement.
-The complement of \tsc{f4} moves to the specifier of \tsc{insP}, resulting in the structure in \ref{ex:f4comp}.
-The lexicon does not contain an entry with \tsc{insP} which contains only \tsc{f4}.\footnote{\tit{Met} `with' is not a candidate, because the syntactic structure has a unary bottom and the lexical structure has a binary bottom.}
-
-\ex.
-\a. \begin{forest} boom
-[\tsc{insP}
-    [\tsc{f}4]
-    [\tsc{datP}
-        [\tsc{f}3]
-        [\tsc{accP}
-           [\tsc{f}2]
-           [\tsc{nom}P
-               [\tsc{f}1]
-               [ΣP
-                   [Σ]
-                   [\tsc{thingP}
-                       [\tsc{thing}, roof]
-                   ]
-               ]
-           ]
-        ]
-    ]
-]
-{\draw (.east) node[right]{⇒ }; }
-\end{forest}\label{ex:f4no}
-\b. \begin{forest} boom
-[\tsc{datP}
-    [\tsc{datP}
-        [\tsc{f}3]
-        [\tsc{accP}
-           [\tsc{f}2]
-           [\tsc{nom}P
-               [\tsc{f}1]
-               [ΣP
-                   [Σ]
-                   [\tsc{thingP}
-                       [\tsc{thing}, roof]
-                   ]
-               ]
-           ]
-        ]
-    ]
-    {\draw (.east) node[right]{⇒ \tit{'t}}; }
-    [\tsc{insP}
-        [\tsc{f}4]
-    ]
-    {\draw (.east) node[right]{⇒ }; }
-]
-\end{forest}\label{ex:f4comp}
-
-As no match can be found, backtracking is triggered.
-The derivation goes back to the previous cycle, and the next option for that cycle is tried.
-In this case, that is after the merge of \tsc{f3}.
-There is no specifier, so there is no spec-to-spec movement.
-Complement movement is tried, showed in \ref{ex:f3comp}.
-However, there is no match in the lexicon for an \tsc{datP} that contains only \tsc{f3}.
-
-\begin{forest} boom
-[\tsc{accP}
-    [\tsc{accP}
-       [\tsc{f}2]
-       [\tsc{nom}P
-           [\tsc{f}1]
-           [ΣP
-               [Σ]
-               [\tsc{thingP}
-                   [\tsc{thing}, roof]
-               ]
-           ]
-       ]
-    ]
-    {\draw (.east) node[right]{⇒ \tit{'t}}; }
-    [\tsc{datP}
-        [\tsc{f}3]
-    ]
-    {\draw (.east) node[right]{⇒ }; }
-]
-\end{forest}\label{ex:f3comp}
-
-Backtracking proceeds further, into the cycle in which \tsc{f1} was merged. Again there is no specifier to be moved, and complement movement does not give any results.
-
-The derivation ends up backtracking into the cycle in which Σ was merged.
-At this stage, \tsc{thing} was realized as \tit{'r}.
-Here there is again no specifier, but complement movement provides a structure that is fit for a lexical entry, namely: \ref{ex:entrymee}.
-
-\ex. \begin{forest} boom
-[ΣP
-   [\tsc{thingP}
-       [\tsc{thing}, roof]
-   ]
-   {\draw (.east) node[right]{⇒ \tit{'r}}; }
-   [ΣP
-       [Σ]
-   ]
-   {\draw (.east) node[right]{⇒ \tit{mee}}; }
-]
-\end{forest}
-
-The feature \tsc{f}1 is merged again. The structure cannot be spelled out as a whole, so spec-to-spec movement is tried. In that configuration \tsc{f1} can be realized together with Σ as \tit{mee}.
-
-\ex. \begin{forest} boom
-[\tsc{nomP}
-   [\tsc{thingP}
-       [\tsc{thing}, roof]
-   ]
-   {\draw (.east) node[right]{⇒ \tit{'r}}; }
-   [\tsc{nom}P
-       [\tsc{f}1]
-       [ΣP
-           [Σ]
-       ]
-   ]
-   {\draw (.east) node[right]{⇒ \tit{mee}}; }
- ]
-\end{forest}
-
-The same happens for \tsc{f2}, \tsc{f3} and \tsc{f4}, and the complete structure is realizes as shown in \ref{ex:spellout'rmee}.
-
-\ex. \begin{forest} boom
-[\tsc{insP}
-    [\tsc{thingP}
-       [\tsc{thing}, roof]
-    ]
-    {\draw (.east) node[right]{⇒ \tit{'r}}; }
-    [\tsc{insP}
-       [\tsc{f}4]
-       [\tsc{dat}P
-           [\tsc{f}3]
-           [\tsc{acc}P
-               [\tsc{f}2]
-               [\tsc{nom}P
-                   [\tsc{f}1]
-                   [ΣP
-                       [Σ]
-                   ]
-               ]
-           ]
-       ]
-    ]
-    {\draw (.east) node[right]{⇒ \tit{mee}}; }
-]
-\end{forest}\label{ex:spellout'rmee}
-
-Skipping over the irrelevant details of how \tit{w} and \tit{a} end up in their positions, the structure for \tit{waarmee} `with what' look as in \ref{ex:spelloutwaarmee}.\footnote{I assume that WP and \tsc{deixP} are both complex specifiers that are created after \tsc{thing} is spelled out in \ref{ex:thingspellout}.
-In after each merge after that, backtracking always takes place, the complex specifier is detached from the structure and the case features are spelled out together with or as a postposition on \tsc{thing}.}
-
-\ex. \begin{forest} boom
-[\tsc{WP}
-    [\tsc{WP}
-        [\tsc{W}, roof]
-    ]
-    {\draw (.east) node[right]{⇒ \tit{w}}; }
-    [\tsc{deixP}
-        [\tsc{deixP}
-            [\tsc{deix}, roof]
-        ]
-        {\draw (.east) node[right]{⇒ \tit{a}}; }
-        [\tit{insP}
-            [\tsc{thingP}
-               [\tsc{thing}, roof]
-            ]
-            {\draw (.east) node[right]{⇒ \tit{'r}}; }
-            [\tsc{insP}
-               [\tsc{f}4]
-               [\tsc{dat}P
-                   [\tsc{f}3]
-                   [\tsc{acc}P
-                       [\tsc{f}2]
-                       [\tsc{nom}P
-                           [\tsc{f}1]
-                           [ΣP
-                               [Σ]
-                           ]
-                       ]
-                   ]
-               ]
-            ]
-            {\draw (.east) node[right]{⇒ \tit{mee}}; }
-        ]
-    ]
-]
-\end{forest}\label{ex:spelloutwaarmee}
-
-A consequence of analyzing \tit{mee} `with' as a postposition is that \tit{r} and \tit{mee} always form a constituent to the exclusion of \tit{w} and \tit{a}.
-At first sight this seems problematic, because it is possible for \tit{waar} `where', stranding \tit{mee} `with'.
-I repeat the relevant example in \ref{ex:meestranded}.
-
-\exg. Ik heb gekocht waar jij mee schildert.\\
- I have bought waar you with paint\\
- `I bought what you are painting with.'\label{ex:meestranded}
-
-There is no constituent in \ref{ex:spelloutwaarmee} that contains \tit{waar} but not \tit{mee}.
-To resolve this situation I follow \citet{noonan2017dutch} in assuming that the phrase containing the adposition (here \tit{mee}) syntactically moves to a position higher in the structure.
-The movement of the adposition has the typical distribution of that of verbal particles (cf.
-\citealt{riemsdijk1978,noonan2017dutch}, and it could possibly be triggered by the feature Σ, associated with weak pronouns.
-With \tit{mee} having moved out, the WP only contains features that are realized as \tit{waar}, and it moves to the left edge of the clause, resulting in the surface order in \ref{ex:meestranded}.
-
-So far I showed how \tit{waarmee} `with what' is derived if all syntactic features form a constituent.
-Next I address how this is blocked when the features do not form a proper constituent, and how the spellout is then \tit{met wat} `with what'.
-
-I start in a situation in which \tit{wat} `what' is part of a syntactic structure with the rest of a relative clause as a sister.
-
-\ex. \begin{forest} boom
-[CP
-    [\tsc{WP}
-        [\tsc{WP}
-            [\tsc{W}, roof]
-        ]
-        {\draw (.east) node[right]{⇒ \tit{w}}; }
-        [\tsc{deixP}
-            [\tsc{deixP}
-                [\tsc{deix}, roof]
-            ]
-            {\draw (.east) node[right]{⇒ \tit{a}}; }
-            [\tsc{accP}
-               [\tsc{f}2]
-               [\tsc{nom}P
-                   [\tsc{f}1]
-                   [ΣP
-                       [Σ]
-                       [\tsc{thingP}
-                           [\tsc{thing}, roof]
-                       ]
-                   ]
-               ]
-            ]
-            {\draw (.east) node[right]{⇒ \tit{'t}}; }
-        ]
-    ]
-    [CP
-        [...,roof]
-    ]
-]
-\end{forest}
-
-Only after the wh-element is moved to the left edge of the clause, case features higher than the accusative are merged.
-
-When a dative feature is merged here, it will not be able to be spelled out.
-The only option to realize the features is to form to spawn a new derivation, to create a complex specifier.
-And that is exactly what forming the preposition \tit{met} `with' is.
-
-\section{Conclusion and discussion}
-
-In this paper, I discussed the distribution of \tit{waarmee} `met wat' and \tit{met wat} `with what' is mismatching free relatives.
-I showed that \tit{waarmee} `with what' appears when all features form a proper constituent, and \tit{met wat} `with what' if they do not.
-
-The described pattern follows from a core assumptions in Nanosyntax: phrasal spellout spells out constituents.
-Looking more into detail, \tit{waarmee} `with what' takes precedence over \tit{met wat} `with what' because \tit{mee} has the structure of a postposition.
-Following the spellout algorithm, \tit{'t} `it' is replaced by \tit{'r} `there', so that it can combine with \tit{mee} `with'.
-The preposition \tit{met} `with' is only used if there is no other option to spell out the features.
-
-This proposal is in several aspects in accordance with earlier work.
-Just like \citet{riemsdijk1978}, I claim that \tsc{r}-pronouns originate as the complement of P.
-He argued that due to some kind of suppletion \tit{'t} `it' changes form to \tsc{'r}, which is coincidentally also the locative in Dutch.
-In my proposal, this suppletion follows naturally from the regular spellout algorithm.
-Also, it is not a coincidence that the locative appears, as it is an item with little features that spells out \tsc{thing}.
-The current proposal differs from \citet{riemsdijk1978} in that it is not the whole complement of P is moved.
-Instead, only part of the complement of P is extracted, which is generally allowed, also in non-preposition stranding languages \citep{abels2003diss}.
+The movement I discuss in this paper with \tsc{r}-pronouns is driven by spellout, and it is meaningless.
 

### 2020-01-15 paper.tex
klaar voor woensdag
meeste werkt, alleen nog intro en conclusie en structuur en alles doornemen

@@
 Let me start with the morphemes \tit{w} and \tit{a} that appear in both expressions.
-Exactly because they appear in both expression, I do not pay much attention to them.
-For \tit{w} I follow \citet{hachem2015} in that \tit{w} realizes a WP.\footnote{Throughout the paper, ⇔ indicates the pairing between a lexical tree and a phonological form in a lexical entry, and ⇒ indicates how a node in the syntactic structure is spelled out.}
+I assume that they correspond to the same syntactic structure in both \tit{waarmee} and \tit{met wat}.
+As I am interested in the differencs between the two expression, I do not discuss the featural content of \tit{w} and \tit{a} into depth.
+
+For \tit{w} I follow \citet{hachem2015} who investigated \tit{d} and \tit{w} elements in German and Dutch.
+In her work, \tit{d} establishes a definite reference and \tit{w} triggers the construction of a set of alternatives in the sense of \citet{rooth1992} (see \citealt{hachem2015} for discussion).\footnote{Throughout the paper, ⇔ indicates the pairing between a lexical tree and a phonological form in a lexical entry, and ⇒ indicates how a node in the syntactic structure is spelled out.}
 
@@
 
-I assume the morpheme \tit{a} to be related to deixis.
-Dutch distinguishes between proximal by using \tit{ie/i} and distal by using \tit{aa/a}, illustrated in \ref{ex:deixis}.
-I assume that lengthening or shortening of the vowel is a result of the final \tit{r}.
+I follow several authors (cf.
+\citealt{lander2016,noonan2017dutch,wesseling2018}) in assuming the morpheme \tit{a} to be related to deixis.
+Dutch distinguishes between proximal by using \tit{ie} (/i:/) and \tit{i} (/ɪ/) and distal by using \tit{aa} (/aː/) and \tit{a} (/ɑ/), illustrated in \ref{ex:deixis}.\footnote{A question that remains open is why wh-elements only combine with the distal marker \tit{a}, and not with proximal marker \tit{i/ie}.} I analyze the transformation from /ɪ/ into /i:/ and /ɑ/ into /aː/ as a result of the final r.
 
@@
 
-The question remains open to why wh-elements only combine with the distal marker \tit{a}, and they do not combine with proximal marker \tit{i/ie}.
-
-\ex.
-\a. wat, waar
-\b. *wit, *wier
-
 For the purpose of this paper I simply let \tit{a} correspond to \tsc{deixP}.
@@
 
-Having put \tit{w-} and \tit{a} aside for now, the forms \tit{met 't} `with it` and \tit{'rmee} `with it' are left.
+In this section I discuss the forms \tit{met 't} `with it` and \tit{'rmee} `with it'.
 Below I repeat examples from Section \ref{sec:rdefault} that show that \tit{met} `with` can express instrumental case, and \tit{'t} is an inanimate pronoun.
@@
 An important distinction between these two is that \tit{-mee} appears after the element it combines with (\tsc{'r}), while \tit{met} appears before the element it combines with (\tit{'t}).
-I will analyze \tit{-mee} as a postposition and \tit{met} as a preposition.
-In this section I discuss the relation between prepositions and postpositions, and how this is modeled with the case hierarchy in Nanosyntax \citep{caha2009}.
+I will analyze \tit{-mee} as a postposition and \tit{met} as a preposition.\footnote{A topic related to this paper is the different positioning of identical adpositions in Dutch (see \citet{caha2010} for an account of German and Dutch and \citet{pretorius2017} for Afrikaans).
+In \ref{ex:dutchin}, \tit{in} changes meaning dependening on whether it proceeds or follows the DP, it is respectively locational or directional.
+
+\ex.\label{ex:dutchin}
+\ag. Ik klim in de boom.\\
+ I climb in the tree\\
+ `I am climbing in the tree.'
+\bg. Ik klim de boom in.\\
+ I climb the tree in\\
+ `I am climbing into the tree.'
+
+In \ref{ex:dutchin}, the movement of the adposition is driven by movement, and it is meaningful.
+The movement I discuss in this paper with \tsc{r}-pronouns is driven by spellout, and it is meaningless.} In this section I discuss the relation between prepositions and postpositions, and how this is modeled with the case hierarchy in Nanosyntax \citep{caha2009}.
 
@@
 \ex. Spec Formation \citep{starke2018}:\\
-If Merge F has failed to spell out (even after backtracking), try to spawn a new derivation providing the feature F and merge that with the current derivation, projecting the feature F at the top node.
+If Merge F has failed to spell out (even after backtracking), try to spawn a new derivation providing the feature F and merge that with the current derivation, projecting the feature F at the top node.\label{ex:specformation}
 
@@
 I start at the point on which \tit{wat} `what' is part of a syntactic structure with the rest of a relative clause as a sister.
+Even though \tsc{f3} is not part of the embedded clause, I already added it to the structure.
+While it is unclear why, syncretic forms seem to behave differently in that they seem to resolve case conflicts in free relatives and related phenomena (cf.
+\citealt{groos1981,pullum1986,ingria1990}).
+I give the syntactic structure from which are start in \ref{ex:metwatst}.
 
@@
             {\draw (.east) node[right]{⇒ \tit{a}}; }
+            [\tsc{datP}
+                [\tsc{f3}]
                 [\tsc{accP}
@@
                 ]
+            ]
             {\draw (.east) node[right]{⇒ \tit{'t}}; }
@@
 ]
-\end{forest}
-
-\ex. \begin{forest} boom
-[\tsc{NP}
-    [NP
-        [NP, roof]
-    ]
-    {\draw (.east) node[right]{⇒ \tit{∅}}; }
+\end{forest}\label{ex:metwatst}
+
+At this point \tsc{f4} is merged, as shown in \ref{ex:f4metwat}.
+Because of the presence of the CP, there is no possibility for \tsc{f4} to be spelled out, even after the regular movements and backtracking.
+
+\ex. \begin{forest} boom
+[\tsc{genP}
+    [\tsc{f4}]
     [CP
@@
 ]
-\end{forest}
-
-After that, \tsc{f4} is merged. here
-
-When a dative feature is merged here, it will not be able to be spelled out.
-The only option to realize the features is to form to spawn a new derivation, to create a complex specifier.
-And that is exactly what forming the preposition \tit{met} `with' is.
+\end{forest}\label{ex:f4metwat}
+
+The last resort possibility to spell out features is set in motion: a complex specifier is created, as described in \ref{ex:specformation}. This is illustrated in \ref{ex:metmetwat}.
+
+\ex. \begin{forest} boom
+[\tsc{insP}
+    [\tsc{insP}
+        [\tsc{f5}]
+        [\tsc{f4}]
+    ]
+    {\draw (.east) node[right]{⇒ \tit{met}}; }
+    [CP
+        [\tsc{WP}
+            [\tsc{WP}
+                [\tsc{W}, roof]
+            ]
+            {\draw (.east) node[right]{⇒ \tit{w}}; }
+            [\tsc{deixP}
+                [\tsc{deixP}
+                    [\tsc{deix}, roof]
+                ]
+                {\draw (.east) node[right]{⇒ \tit{a}}; }
+                [\tsc{accP}
+                   [\tsc{f2}]
+                   [\tsc{nomP}
+                       [\tsc{f1}]
+                       [ΣP
+                           [Σ]
+                           [\tsc{thingP}
+                               [\tsc{thing}, roof]
+                           ]
+                       ]
+                   ]
+                ]
+                {\draw (.east) node[right]{⇒ \tit{'t}}; }
+            ]
+        ]
+        [CP
+            [...,roof]
+        ]
+    ]
+]
+\end{forest}\label{ex:metmetwat}
+
+This section showed how the instrumental inanimate relative pronoun is realized as \tit{waarmee} `with what' when all syntactic features form a constituent.
+It also showed how \tit{met wat} `with what' appears when all features do not form a proper constituent, and other features intervene.
 
@@
 Giving \tit{met} `with' and \tit{-mee} `with' two distinct lexical entries has as a consequence that the phonological overlap between them seems like a coincidence.
-Moreover, in almost all cases the preposition does not change form when it combines with an \tsc{r}-pronoun, e.g.
+This can be questioned, because there is only one more preposition that changes form when it appears postpositionally.
+This preposition is \tit{tot} `to', and it changes into \tit{toe} as a postposition.
+It has in common with \tit{met} `with' that it is the only preposition in Dutch that has the phonological structure CVt.
+For now I take the phonological resemblance to be a relic from the past without having any influence on the synchronic data.
+
+n all the other cases the preposition does not change form when it combines with an \tsc{r}-pronoun, e.g.
 \tit{in}.
 If this proposal is on the right track, elements as \tit{in} can be used as either a preposition and as a postposition.
-A lexical entry as in \ref{ex:presuf} would be a candidate for such an element.
-
-\ex. \begin{forest} boom
-[XP
+The lexical entry should then be usable as pre-element and as post-element, so it needs to have a binary bottom and a unary foot at the same time.
+The lexical entry in \ref{ex:presuf} would be a candidate for such an element.
+YP can be inserted as a post-element, and XP can be inserted via the Superset Princple as a pre-element.
+
+\ex. \begin{forest} boom
+[YP
     [XP
@@
 
-A topic related to this paper is the different positioning of identical adpositions in Dutch (see \citet{caha2010} for an account of German and Dutch and \citet{pretorius2017} for Afrikaans).
-In \ref{ex:dutchin}, \tit{in} changes meaning dependening on whether it proceeds or follows the DP, it is respectively locational or directional.
-
-\ex.\label{ex:dutchin}
-\ag. Ik klim in de boom.\\
- I climb in the tree\\
- `I am climbing in the tree.'
-\bg. Ik klim de boom in.\\
- I climb the tree in\\
- `I am climbing into the tree.'
-
-In \ref{ex:dutchin}, the movement of the adposition is driven by movement, and it is meaningful.
-The movement I discuss in this paper with \tsc{r}-pronouns is driven by spellout, and it is meaningless.
-
 \printbibliography

### 2020-01-16 paper.tex
bij jan vandaan
intro ver af

@@
 
-English has a sentence.
-This is ungrammatical in Dutch.
-We need an \tsc{r}-pronoun.
-The term \tsc{r}-pronoun \citep{riemsdijk1978} refers to a set of nominal elements that can strand prepositions in Dutch (and German).
-This is noteworthy because Dutch is a normally non-preposition stranding language.
-In the example \ref{ex:klimerop} \tit{op} `on' is the preposition and \tit{'r} `there' is the locative pronoun.\footnote{The \tsc{r}-pronoun \tit{'r} in \ref{ex:klimerop} can be written as \tit{er}, \tit{der} and \tit{'r} and pronounced as respectively /ɛr/, /dər/ or /ər/.
+Dutch has the preposition \tit{met} `with' that expresses instrumental case.
+In \ref{ex:metdp}, \tit{met} `with' is combined with a full DP.
+The inanimate pronoun in Dutch is \tit{'t} `it'.\footnote{The longer form that is mostly used in writing is \tit{het} `it'.
+I will use the spoken variant \tit{'t} throughout this paper.} \ref{ex:tverb} illustrates that \tit{'t} `it' can be used as the object of a verb.
+
+\ex.
+\ag. Ik schilder met een kwast.\\
+ I paint with a brush\\
+ `I am painting with a brush.'\label{ex:metdp}
+ \bg. Ik zie 't.\\
+  I see it\\
+  `I see it.'\label{ex:tverb}
+
+\tit{Met} `with' and \tit{'t} `it' do not appear together, as illustrated in \ref{ex:neemett}.
+Instead, Dutch uses the \tsc{r}-pronoun \tit{'r} and the postposition \tit{mee}, as shown in \ref{ex:jarmee}.\footnote{The \tsc{r}-pronoun \tit{'r} in \ref{ex:klimerop} can be written as \tit{er}, \tit{der} and \tit{'r} and pronounced as respectively /ɛr/, /dər/ or /ər/.
 As far as I am aware, there is no clear meaning difference between these forms.
 See \citet{wesseling2018} for discussion.
-In my examples I use \tit{'r}, but the other two forms fit just as well.}
-
-\ex. I climb on it.
-
-\ex.
-\ag. *Ik klim op 't.\\
- I climb on it\\
- `I climb on it.'\label{ex:klimopt}
-\bg. Ik klim 'r op.\\
- I climb there on\\
- `I climb on it.'\label{ex:klimerop}
-
-In Dutch it is impossible to have [P inanimate].
-But why?
-\citet{riemsdijk1978} postulating a filter that prohibits the existence of constituents consisting of prepositions and inanimates + some kind of allomoprhy.
-\citet{koopman2000} who makes reference to a different paradigm.
-Abels: base-generated somewhere else.
-
-This chapter is an in-depth study of the \tsc{r}-pronoun-postposition combination \tit{waarmee} `with what' in Dutch.
+In my examples I use \tit{'r}, but the other two forms fit just as well.}$^,$\footnote{In this paper I do not make any claims about the distinction between prefixes and prepositions, or suffixes and postpositions.}
+
+\ex.\label{ex:rmeeconst}
+\ag. *Ik schilder met 't.\\
+ I paint with it\\
+ `I am painting with it.'\label{ex:neemett}
+\bg. Ik schilder 'r -mee.\\
+ I paint there -with\\
+ `I am painting with it.'\label{ex:jarmee}
+
+\tsc{R}-pronouns \citep{riemsdijk1978,koopman1994} are nominal elements that are syncretic with locative pronouns, which in Dutch means they contain the morpheme \tit{r}.
+The adposition it combines with obligatorily follows the \tsc{r}-pronoun, compare \ref{ex:jarmee} and \ref{ex:neemeer}.
+Notice also that the preposition \tit{met} `with' has changed form into \tit{mee} `with' when it appears as a postposition (see \ref{ex:metdp} and \ref{ex:jarmee}).
+
+\exg. *Ik schilder mee 'r.\\
+ I paint with there\\
+ `I am painting with it.'\label{ex:neemeer}
+
+This chapter is concerned with the question of how to correctly rule out the construction in \ref{ex:neemett} and to let the \tsc{r}-pronoun construction in \ref{ex:jarmee} appear.
+I argue that \tsc{r}-pronouns are not something special, but a consequence of regular spellout.
+Just like \citet{riemsdijk1978} I analyze \tsc{r}-pronouns and postpositions as a type of allomorphy.
+What is different is that spellout rules out the ungrammaticality of the preposition and inanimate pronoun, rather than the stipulation of a filter.
+
+This chapter is an in-depth study of the instrumental \tsc{r}-pronoun-postposition combination \tit{'r -mee} `with it' and \tit{waarmee} `with what' in Dutch.
 This instance is interesting for two reasons.
-First, just like for all \tsc{r}-pronouns, the wh-element is the locative, but there is no meaning component related to location in `with what'.
-Second, the preposition \tit{met} `with' does not only turn into a postposition, but it also changes into \tit{-mee} `with' when it is combined with an \tsc{r}-pronoun.\footnote{I do not have anything to say about the distinction between prefixes and prepositions, or suffixes and postpositions.} This last observervation has so far remained unexplained.
-
-In answering the question why [P inanimate] I look at an exception to the rule that *P inanimate pronoun. That exception is a mismatching free relative. Here the string \tit{met wat} does appear.
-
-what I will show that r-pronouns are not a different construction to express the same meaning, but they realize the same features as regular P + pronoun combinations.
-It is a kind of allomorphy, just like Van Riemsdijk said.
-And not a different way to express the same function.
+First, just like for all \tsc{r}-pronouns, the \tsc{r}-pronoun is syncretic with the locative.
+In many of the \tsc{r}-pronoun-postpositions combinations, the meaning component of the locative is intuitive, as many prepositions express locations, directions etc.
+However, an instrumental expresses an instrument and does not have a meaning component assosicated with location.
+The second reason why I focus on this particular \tsc{r}-pronoun and postposition has to do with the form of the adposition.
+The preposition \tit{met} `with' does not only turn into a postposition, but it also changes into \tit{-mee} `with' when it is combined with an \tsc{r}-pronoun.\footnote{I do not have anything to say about the distinction between prefixes and prepositions, or suffixes and postpositions.} This last observervation has so far remained unexplained.
+
+%%here the basic idea%%
+When all features form a proper constituent, then the \tsc{r}-pronoun surfaces. When there is a complement or whatever, it does not work.
+In what follows I show that \tsc{r}-pronouns and regular preposition compete to spell out the same syntactic features.
+If all features form a proper constituent (i.e.
+a constituent to the exclusion of other features), the \tsc{r}-pronoun surfaces.
+If it is not a proper constituent, the preposition-pronoun combination shows up.
+This straightforwardly follows in a system in which spellout targets phrasal constituents: Nanosyntax \citep{starke2009}.
+--here more about the internal structure of r-pronouns, and the postposition preposition distinction--
+
+%%here the structure of the paper%%
+This paper is structured as follows.
+In Section \ref{sec:distribution} I discuss the distribution of \tit{waarmee} `waarmee' and \tit{met wat} `with what'.
+I show that the \tsc{r}-pronoun surfaces when it forms a proper constituent, and \tit{met wat} `with what' when it does not.
+I decompose \tit{waarmee} `with what' and \tit{met wat} `with what' to make sense of the phonological similarities, and I provide a more detailed analysis.
+Unmarked examples are constructed and have been verified by native speakers.
+
+\section{\tsc{R}-pronouns are proper constituents}\label{sec:distribution}
+
+\subsection{\tsc{R}-pronouns as default}\label{sec:rdefault}
+
+The goal of this section is to show that \tit{waarmee} `with what' is the default as instrumental relative pronoun, a shown in a.o.
+\citet{riemsdijk1978,koopman2000}.
+In order to show that \tit{waarmee} `with what' is the default, I discuss the distribution of \tsc{r}-pronouns and regular pronouns in more general.
+I start with the personal pronouns and then return to the wh-pronouns.
+
+Dutch has the personal pronouns \tit{haar} `her', \tit{hem} `him' and \tit{het} `it' that can be used as animate and inanimate objects of verbs, as illustrated in \ref{ex:objverb}.
+
+ \ex. \label{ex:objverb}
+ \ag. Ik zie haar/hem.\\
+  I see her/him\\
+  `I see her/him.'\label{ex:aniobj}
+ \bg. Ik zie 't.\\
+  I see it\\
+  `I see it.'\label{ex:inaniobj}
+
+The example in \ref{ex:prepani} shows that for animate objects the same pronouns (\tit{haar} `her' and \tit{hem} `him') appear as objects of prepositions.
+However, the inanimate personal pronoun \tit{het} `it' cannot be used as an object of a preposition, shown in \ref{ex:prephet}.
+Instead, an ʀ-pronoun appears.
+This is illustrated in \ref{ex:preper}.
+\ref{ex:erprep} shows that the \tsc{r}-pronoun obligatorily moves to the left of the pronoun.
+
+\ex. \label{ex:objprep}
+\ag. Ik schilder samen met haar/hem.\\
+ I paint together with her/him\\
+ `I am painting together with her/him.'\label{ex:prepani}
+\bg. *Ik schilder met 't.\\
+ I paint with it\\
+ `I am painting with it.'\label{ex:prephet}
+\bg. Ik schilder 'r mee.\\
+ I paint there -with\\
+ `I am painting with it.'\label{ex:preper}
+\bg. *Ik schilder mee 'r.\\
+ I paint with there\\
+ `I am painting with it.'\label{ex:erprep}
+
+\tit{Met} is not the only preposition with which this happens.
+\tit{Op} `on' and \tit{in} `in' do not combine with the inanimate personal pronoun \tit{'t}, but the \tsc{r}-pronoun is used obligatorily.
+
+\ex.
+\ag. Ik zit 'r op.\\
+ I sit there on\\
+ `I am sitting on it.
+\bg. *Ik zit op 't.\\
+ I sit on it\\
+ `I am sitting on it.
+
+\ex.
+ \ag. Hij zwemt 'r in.\\
+  he swims it-in\\
+  `He is swimming in it.'
+ \bg. *Hij zwemt in 't.\\
+  he swims in it\\
+  `He is swimming in it.'
+
+The situation of the inanimate wh-pronouns resembles the inanimate personal pronouns.
+\tit{Wat} `what' can function as an object of a verb (see \ref{ex:wat}), but not as an object of a preposition \ref{ex:metwat}.
+In that case, the \tsc{r}-pronoun \tit{waarmee} `with what' is appears, as shown in \ref{ex:waarmee}.\footnote{The sentence in \ref{ex:metwat} is unacceptable with neutral intonation.
+It becomes is only acceptable if \tit{wat} `what' is stressed, for example in a context in which the speaker is highly surprised about the choice for the object hearer is painting with.}
+
+\ex.
+\ag. Wat zie jij?\\
+ what see you\\
+ `What do you see?'\label{ex:wat}
+\bg. *Met wat schilder jij?\\
+ with what paint you\\
+ `What are you painting with?'\label{ex:metwat}
+\bg. Waarmee schilder jij?\\
+ {where with} paint you with\\
+ `What are you painting with?'\label{ex:waarmee}
+
+\tit{Waarmee} `with what' and not \tit{met wat} `with what' does not only appear in wh-questions, but also in other contexts.
+\ref{ex:headed} gives an example of a headed relative, and \ref{ex:headless} shows a free relative in which both predicates combine with an instrumental object.
+The use of \tit{met wat} `with what' is ungrammatical in both contexts, and \tit{waarmee} `with what' is used.
+
+\ex.\label{ex:headed}
+\ag. Ik schilder met de kwast waarmee jij ook schildert.\\
+ I paint with the brush {where with} you also paint\\
+ `I am painting with the brush that you are painting with too.'
+\bg. *Ik schilder met de kwast met wat jij ook schildert.\\
+ I paint with the brush with what you also paint\\
+ `I am painting with the brush that you are painting with too.'
+
+ \ex.\label{ex:headless}
+ \ag. Ik schilder waarmee jij ook schildert.\\
+  I paint {where with} you also paint\\
+  `I am painting with what you are painting with too.'
+ \bg. *Ik schilder met wat jij ook schildert.\\
+  I paint with what you also paint\\
+  `I am painting with what you are painting with too.'
+
+\tit{'t} `it' and \tit{wat} `what' do not combine with prepositions. They are substituted by respectively \tit{'r} `there' and \tit{waar} `where'.
+
+The next section discusses the role of constituency in \tsc{r}-pronouns.
+
+\subsection{\tit{Met wat} `with what' shows up}
+
+Sometimes \tit{met wat} shows up!
 
@@
  `I bought what you are painting with.'\label{ex:gekochtmetwat}
-
-In this paper I show that distribution of \tit{waarmee} `with what' and \tit{met wat} `with what' in these free relative constructions gives us a good insight into the internal structure of \tsc{r}-pronouns.
-In what follows I show that \tsc{r}-pronouns and regular preposition compete to spell out the same syntactic features.
-If all features form a proper constituent (i.e.
-a constituent to the exclusion of other features), the \tsc{r}-pronoun surfaces.
-If it is not a proper constituent, the preposition-pronoun combination shows up.
-This straightforwardly follows in a system in which spellout targets phrasal constituents: Nanosyntax \citep{starke2009}.
---here more about the internal structure of r-pronouns, and the postposition preposition distinction--
-
-This paper is structured as follows.
-In Section \ref{sec:distribution} I discuss the distribution of \tit{waarmee} `waarmee' and \tit{met wat} `with what'.
-I show that the \tsc{r}-pronoun surfaces when it forms a proper constituent, and \tit{met wat} `with what' when it does not.
-I decompose \tit{waarmee} `with what' and \tit{met wat} `with what' to make sense of the phonological similarities, and I provide a more detailed analysis.
-Unmarked examples are constructed and have been verified by native speakers.
-
-\section{The distribution between \tit{waarmee} and \tit{met wat}}\label{sec:distribution}
 
@@
 
-\subsection{\tsc{R}-pronouns as default}\label{sec:rdefault}
-
-The goal of this section is to show that \tit{waarmee} `with what' is the default as instrumental relative pronoun.
-This generalization is not new, it has already been made \citet{riemsdijk1978,koopman2000}.
-In order to show that \tit{waarmee} `with what' is the default, I discuss the distribution of \tsc{r}-pronouns and regular pronouns in more general.
-I start with the personal pronouns and then return to the wh-pronouns.
-
-Dutch has the personal pronouns \tit{haar} `her', \tit{hem} `him' and \tit{het} `it' that can be used as animate and inanimate objects of verbs, as illustrated in \ref{ex:objverb}.
-
- \ex. \label{ex:objverb}
- \ag. Ik zie haar/hem.\\
-  I see her/him\\
-  `I see her/him.'\label{ex:aniobj}
- \bg. Ik zie 't.\\
-  I see it\\
-  `I see it.'\label{ex:inaniobj}
-
-The example in \ref{ex:prepani} shows that for animate objects the same pronouns (\tit{haar} `her' and \tit{hem} `him') appear as objects of prepositions.
-However, the inanimate personal pronoun \tit{het} `it' cannot be used as an object of a preposition, shown in \ref{ex:prephet}.
-Instead, an ʀ-pronoun appears.
-This is illustrated in \ref{ex:preper}.
-\ref{ex:erprep} shows that the \tsc{r}-pronoun obligatorily moves to the left of the pronoun.
-
-\ex. \label{ex:objprep}
-\ag. Ik schilder samen met haar/hem.\\
- I paint together with her/him\\
- `I am painting together with her/him.'\label{ex:prepani}
-\bg. *Ik schilder met 't.\\
- I paint with it\\
- `I am painting with it.'\label{ex:prephet}
-\bg. Ik schilder 'r mee.\\
- I paint there-with\\
- `I am painting with it.'\label{ex:preper}
-\bg. *Ik schilder mee 'r.\\
- I paint with there\\
- `I am painting with it.'\label{ex:erprep}
-
-\tit{Met} is not the only preposition with which this happens.
-\tit{Op} `on' and \tit{in} `in' do not combine with the inanimate personal pronoun \tit{'t}, but the \tsc{r}-pronoun is used obligatorily.
-
-\ex.
-\ag. Ik zit 'r op.\\
- I sit there on\\
- `I am sitting on it.
-\bg. *Ik zit op 't.\\
- I sit on it\\
- `I am sitting on it.
-
-\ex.
- \ag. Hij zwemt 'r in.\\
-  he swims it-in\\
-  `He is swimming in it.'
- \bg. *Hij zwemt in 't.\\
-  he swims in it\\
-  `He is swimming in it.'
-
-The situation of the inanimate wh-pronouns resembles the inanimate personal pronouns.
-\tit{Wat} `what' can function as an object of a verb (see \ref{ex:wat}), but not as an object of a preposition \ref{ex:metwat}.
-In that case, the \tsc{r}-pronoun \tit{waarmee} `with what' is appears, as shown in \ref{ex:waarmee}.\footnote{The sentence in \ref{ex:metwat} is unacceptable with neutral intonation.
-It becomes is only acceptable if \tit{wat} `what' is stressed, for example in a context in which the speaker is highly surprised about the choice for the object hearer is painting with.}
-
-\ex.
-\ag. Wat zie jij?\\
- what see you\\
- `What do you see?'\label{ex:wat}
-\bg. *Met wat schilder jij?\\
- with what paint you\\
- `What are you painting with?'\label{ex:metwat}
-\bg. Waarmee schilder jij?\\
- {where with} paint you with\\
- `What are you painting with?'\label{ex:waarmee}
-
-\tit{Waarmee} `with what' and not \tit{met wat} `with what' does not only appear in wh-questions, but also in other contexts.
-\ref{ex:headed} gives an example of a headed relative, and \ref{ex:headless} shows a free relative in which both predicates combine with an instrumental object.
-The use of \tit{met wat} `with what' is ungrammatical in both contexts, and \tit{waarmee} `with what' is used.
-
-\ex.\label{ex:headed}
-\ag. Ik schilder met de kwast waarmee jij ook schildert.\\
- I paint with the brush {where with} you also paint\\
- `I am painting with the brush that you are painting with too.'
-\bg. *Ik schilder met de kwast met wat jij ook schildert.\\
- I paint with the brush with what you also paint\\
- `I am painting with the brush that you are painting with too.'
-
- \ex.\label{ex:headless}
- \ag. Ik schilder waarmee jij ook schildert.\\
-  I paint {where with} you also paint\\
-  `I am painting with what you are painting with too.'
- \bg. *Ik schilder met wat jij ook schildert.\\
-  I paint with what you also paint\\
-  `I am painting with what you are painting with too.'
-
-\tit{'t} `it' and \tit{wat} `what' do not combine with prepositions. They are substituted by respectively \tit{'r} `there' and \tit{waar} `where'.
-
-The next section discusses the role of constituency in \tsc{r}-pronouns.
-
-\subsection{\tit{Waarmee} is a constituent, \tit{met wat} is not}
-
 Let me now return to the mismatching free relatives. I repeat the relevant grammatical examples in \ref{ex:grammatical}.
@@
 
-In this section I showed that ʀ-pronouns are expected in combinations with prepositions.
+In the preceding section I showed that ʀ-pronouns are expected in combinations with prepositions.
 This means that the use of \tit{waarmee} `with what' \ref{ex:grammaticalwaar} is not surprising.
@@
 %\ex.\label{ex:constwaarmee}
-%\ag. Waar-mee schilder jij?\\
- %{where-with} paint you\\
+%\ag. Waar -mee schilder jij?\\
+ %{where -with} paint you\\
  %`What are you painting with?'
-%\bg. Ik schilder [waar-mee jij ook schildert].\\
- %I paint {where-with} you also paint\\
+%\bg. Ik schilder [waar -mee jij ook schildert].\\
+ %I paint {where -with} you also paint\\
  %`I am painting with what you are painting with too.'
-%\bg. Ik schilder met de kwast [waar-mee jij ook schildert].\\
- %I paint with the brush {where-with} you also paint\\
+%\bg. Ik schilder met de kwast [waar -mee jij ook schildert].\\
+ %I paint with the brush {where -with} you also paint\\
  %`I am painting with the brush that you are painting with too.'
@@
 I put \tit{w} and \tit{a} aside for now, assuming they spell out the same syntactic structure in \tit{waarmee} `with what' and \tit{met wat} `with what'.
-This leaves \tit{'r-mee} `with it' and \tit{met 't} `with it'.
+This leaves \tit{'r -mee} `with it' and \tit{met 't} `with it'.
 
@@
 with it\\
+\z.
+\z.
 
@@
 In this section I discuss the forms \tit{met 't} `with it` and \tit{'rmee} `with it'.
-Below I repeat examples from Section \ref{sec:rdefault} that show that \tit{met} `with` can express instrumental case, and \tit{'t} is an inanimate pronoun.
-\ref{ex:metdp} shows \tit{met} `with' combined with full DP.
-\ref{ex:tverb} shows \tit{'t} as the object of verbs.
-
-\ex.
-\ag. Ik schilder met een kwast.\\
- I paint with a brush\\
- `I am painting with a brush.'\label{ex:metdp}
- \bg. Ik zie 't.\\
-  I see it\\
-  `I see it.'\label{ex:tverb}
-
-However, \tit{met} `with' and \tit{'t} `it' do not appear together if they form a proper constituent. Instead, \tit{'rmee} is used, as shown in \ref{ex:rmeeconst}.
-
-\ex.\label{ex:rmeeconst}
-\ag. Ik schilder 'r-mee.\\
- I paint there-with\\
- `I am painting with it.'\label{ex:jarmee}
-\bg. *Ik schilder met 't.\\
- I paint with it\\
- `I am painting with it.'\label{ex:neemett}
-
-In this section I set up an account that makes the ungrammaticality of \tit{met 't} and the appearance of \tit{'rmee} follow from spellout.
+I set up an account that makes the ungrammaticality of \tit{met 't} and the appearance of \tit{'rmee} follow from spellout.
 The analysis accounts for the following two observations, taking \tit{met 't} as the point of departure.
@@
     \tsc{gen} & 'r-van     \\
-    \tsc{ins} & -r-mee     \\
+    \tsc{ins} & -r -mee     \\
     \bottomrule
@@
 \ex.
-\ag. Ik schilder 'r-mee.\\
- I paint there-with\\
+\ag. Ik schilder 'r -mee.\\
+ I paint there -with\\
  `I am painting with it.'\label{ex:dutchina}

### 2020-01-16 paper.tex
klaar, alleen nog lezen
pfoe, wat een bevalling

@@
 
-Dutch has the preposition \tit{met} `with' that expresses instrumental case.
+Dutch has the preposition \tit{met} `with' that expresses the instrumental.
 In \ref{ex:metdp}, \tit{met} `with' is combined with a full DP.
@@
 \tit{Met} `with' and \tit{'t} `it' do not appear together, as illustrated in \ref{ex:neemett}.
-Instead, Dutch uses the \tsc{r}-pronoun \tit{'r} and the postposition \tit{mee}, as shown in \ref{ex:jarmee}.\footnote{The \tsc{r}-pronoun \tit{'r} in \ref{ex:klimerop} can be written as \tit{er}, \tit{der} and \tit{'r} and pronounced as respectively /ɛr/, /dər/ or /ər/.
+Instead, Dutch uses the \tsc{r}-pronoun \tit{'r} `there' and the postposition \tit{mee} `with', as shown in \ref{ex:jarmee}.\footnote{The \tsc{r}-pronoun \tit{'r} in \ref{ex:jarmee} can be written as \tit{er}, \tit{der} and \tit{'r} and pronounced as respectively /ɛr/, /dər/ or /ər/.
 As far as I am aware, there is no clear meaning difference between these forms.
@@
 \tsc{R}-pronouns \citep{riemsdijk1978,koopman1994} are nominal elements that are syncretic with locative pronouns, which in Dutch means they contain the morpheme \tit{r}.
-The adposition it combines with obligatorily follows the \tsc{r}-pronoun, compare \ref{ex:jarmee} and \ref{ex:neemeer}.
-Notice also that the preposition \tit{met} `with' has changed form into \tit{mee} `with' when it appears as a postposition (see \ref{ex:metdp} and \ref{ex:jarmee}).
+The adpositions they combine with obligatorily follow the \tsc{r}-pronoun, see \ref{ex:jarmee} and \ref{ex:neemeer}.
+Notice also that the preposition \tit{met} `with' differs phonologically from the postposition \tit{mee} `with` (see \ref{ex:metdp} and \ref{ex:jarmee}).
 
@@
 
-This chapter is concerned with the question of how to correctly rule out the construction in \ref{ex:neemett} and to let the \tsc{r}-pronoun construction in \ref{ex:jarmee} appear.
-I argue that \tsc{r}-pronouns are not something special, but a consequence of regular spellout.
-Just like \citet{riemsdijk1978} I analyze \tsc{r}-pronouns and postpositions as a type of allomorphy.
-What is different is that spellout rules out the ungrammaticality of the preposition and inanimate pronoun, rather than the stipulation of a filter.
-
-This chapter is an in-depth study of the instrumental \tsc{r}-pronoun-postposition combination \tit{'r -mee} `with it' and \tit{waarmee} `with what' in Dutch.
+The main question I address in this chapter is how to correctly rule out \tit{met 't} `with it' in \ref{ex:neemett}, and let the \tsc{r}-pronoun and postposition in \ref{ex:jarmee} appear.
+I argue that \tsc{r}-pronouns are not something special, but a consequence of regular spellout mechanisms.
+Just like \citet{riemsdijk1978} I analyze \tsc{r}-pronouns and postpositions as a type of allomorph of the preposition and pronoun.
+The crucial difference in the current approach is that spellout rules out the ungrammaticality of the preposition and pronoun, and not the stipulation of a filter.
+
+This chapter is an in-depth study of the instrumental \tsc{r}-pronoun and postposition \tit{'r -mee} `with it' and \tit{waarmee} `with what' in Dutch.
 This instance is interesting for two reasons.
 First, just like for all \tsc{r}-pronouns, the \tsc{r}-pronoun is syncretic with the locative.
-In many of the \tsc{r}-pronoun-postpositions combinations, the meaning component of the locative is intuitive, as many prepositions express locations, directions etc.
-However, an instrumental expresses an instrument and does not have a meaning component assosicated with location.
+In many of the \tsc{r}-pronouns and postpositions, the meaning component of the locative is intuitive, as many prepositions express locations, directions etc.
+However, an instrumental expresses an instrument, which does not have a meaning component assosicated with location.
+Ideally, an analysis treats the syncretism not as accidental but allows for the locative meaning to be absent.
 The second reason why I focus on this particular \tsc{r}-pronoun and postposition has to do with the form of the adposition.
-The preposition \tit{met} `with' does not only turn into a postposition, but it also changes into \tit{-mee} `with' when it is combined with an \tsc{r}-pronoun.\footnote{I do not have anything to say about the distinction between prefixes and prepositions, or suffixes and postpositions.} This last observervation has so far remained unexplained.
-
-%%here the basic idea%%
-When all features form a proper constituent, then the \tsc{r}-pronoun surfaces. When there is a complement or whatever, it does not work.
-In what follows I show that \tsc{r}-pronouns and regular preposition compete to spell out the same syntactic features.
-If all features form a proper constituent (i.e.
-a constituent to the exclusion of other features), the \tsc{r}-pronoun surfaces.
-If it is not a proper constituent, the preposition-pronoun combination shows up.
-This straightforwardly follows in a system in which spellout targets phrasal constituents: Nanosyntax \citep{starke2009}.
---here more about the internal structure of r-pronouns, and the postposition preposition distinction--
-
-%%here the structure of the paper%%
+The preposition \tit{met} `with' does not only turn into a postposition, but it also changes into \tit{-mee} `with' when it is combined with an \tsc{r}-pronoun.
+This last observervation has so far remained unexplained.
+
+The main generalization is that the instrumental \tsc{r}-pronoun and postposition \tit{waarmee} `with what' takes precedence over the instrumental preposition and inanimate pronoun \tit{met wat} `with what'.
+This generalization is subject to an important condition: the instrumental object needs to form a proper constituent i.e.
+a constituent to the exclusion of other features.
+When this condition is not met, the preposition and pronoun appear.
+This can straightforwardly follow in a system in which spellout targets phrasal constituents: Nanosyntax \citep{starke2009}.
+I work this idea out capturing the following observations.
+First, \tsc{r}-pronouns are syncretic with locatives.
+Second, regular pronouns appear with prepoositions, \tsc{r}-pronouns with postpositions.
+Third, the instrumental preposition and postposition differ in form (\tit{met} vs.
+\tit{mee}).
+
 This paper is structured as follows.
-In Section \ref{sec:distribution} I discuss the distribution of \tit{waarmee} `waarmee' and \tit{met wat} `with what'.
-I show that the \tsc{r}-pronoun surfaces when it forms a proper constituent, and \tit{met wat} `with what' when it does not.
-I decompose \tit{waarmee} `with what' and \tit{met wat} `with what' to make sense of the phonological similarities, and I provide a more detailed analysis.
+In Section \ref{sec:distribution} I discuss the condition that \tsc{r}-pronouns and postpositions are subject too: they need to form a proper constituent.
+I show that \tsc{r}-pronouns and postpositions and prepositions and pronouns are in complementary distribution, depending on whether all features form a proper constituent or not.
+In Section \ref{sec:takingapart} I decompose \tit{waarmee} `with what' and \tit{met wat} `with what', and I connect them to parts of syntactic structure.
+Section \ref{sec:derivation} shows in a derivation how \tit{waarmee} `with what' is derived and the role that constituency plays.
+Section \ref{sec:conclusion} concludes and discusses possible extensions of the analysis.
+All examples in this paper are from Dutch, unless indicated otherwise.
 Unmarked examples are constructed and have been verified by native speakers.
@@
 
+The goal of this section is to show that \tsc{r}-pronouns and postpositions appear when all features that are to be spelled out form a proper constituent, i.e.
+that all features form a constituent to the exclusion of any other features.
+I start the section by showing that \tit{'rmee} `with it' and \tit{waarmee} `with what` are the default, that normally they appear instead of \tit{met 't} `with it' and \tit{met wat} `with what`.
+Then I show an exception, in which \tit{met wat} `with what` has to be used and \tit{waarmee} `with what` cannot.
+I argue that the crucial difference between the exception and other cases is that in the exception the features do not form a proper constituent.
+
 \subsection{\tsc{R}-pronouns as default}\label{sec:rdefault}
 
-The goal of this section is to show that \tit{waarmee} `with what' is the default as instrumental relative pronoun, a shown in a.o.
-\citet{riemsdijk1978,koopman2000}.
-In order to show that \tit{waarmee} `with what' is the default, I discuss the distribution of \tsc{r}-pronouns and regular pronouns in more general.
-I start with the personal pronouns and then return to the wh-pronouns.
-
-Dutch has the personal pronouns \tit{haar} `her', \tit{hem} `him' and \tit{het} `it' that can be used as animate and inanimate objects of verbs, as illustrated in \ref{ex:objverb}.
+In what follows I discuss the distribution of \tsc{r}-pronouns and regular pronouns in general \citep{riemsdijk1978,koopman2000}. I start with the personal pronouns and then return to the wh-pronouns.
+
+Dutch has the accusative personal pronouns \tit{haar} `her', \tit{hem} `him' and \tit{het} `it' that can be used as animate and inanimate objects of verbs, as illustrated in \ref{ex:objverb}.
 
@@
 The example in \ref{ex:prepani} shows that for animate objects the same pronouns (\tit{haar} `her' and \tit{hem} `him') appear as objects of prepositions.
-However, the inanimate personal pronoun \tit{het} `it' cannot be used as an object of a preposition, shown in \ref{ex:prephet}.
-Instead, an ʀ-pronoun appears.
+Repeating from the introduction, the inanimate personal pronoun \tit{het} `it' cannot be used as an object of a preposition, shown in \ref{ex:prephet}.
+Instead, an \tsc{r}-pronoun appears.
 This is illustrated in \ref{ex:preper}.
-\ref{ex:erprep} shows that the \tsc{r}-pronoun obligatorily moves to the left of the pronoun.
+\ref{ex:erprep} shows that the \tsc{r}-pronoun obligatorily has moved to the left of the adposition.
 
@@
 \tit{Met} is not the only preposition with which this happens.
-\tit{Op} `on' and \tit{in} `in' do not combine with the inanimate personal pronoun \tit{'t}, but the \tsc{r}-pronoun is used obligatorily.
+For example, \tit{op} `on' and \tit{in} `in' are two prepositions that also do not combine with the inanimate personal pronoun \tit{'t}, but the \tsc{r}-pronoun and postposition is used obligatorily.
 
@@
 
-The situation of the inanimate wh-pronouns resembles the inanimate personal pronouns.
+The situation of the inanimate wh-pronouns resembles the one of the inanimate personal pronouns.
 \tit{Wat} `what' can function as an object of a verb (see \ref{ex:wat}), but not as an object of a preposition \ref{ex:metwat}.
-In that case, the \tsc{r}-pronoun \tit{waarmee} `with what' is appears, as shown in \ref{ex:waarmee}.\footnote{The sentence in \ref{ex:metwat} is unacceptable with neutral intonation.
-It becomes is only acceptable if \tit{wat} `what' is stressed, for example in a context in which the speaker is highly surprised about the choice for the object hearer is painting with.}
+In that case, the \tsc{r}-pronoun and postposition \tit{waarmee} `with what' appears, as shown in \ref{ex:waarmee}.\footnote{The sentence in \ref{ex:metwat} is unacceptable with neutral intonation.
+It becomes acceptable if \tit{wat} `what' is stressed, for example in a context in which the speaker is highly surprised about the choice of the object the hearer is painting with.}
 
@@
 
-\tit{'t} `it' and \tit{wat} `what' do not combine with prepositions. They are substituted by respectively \tit{'r} `there' and \tit{waar} `where'.
-
-The next section discusses the role of constituency in \tsc{r}-pronouns.
+In sum, \tit{'t} `it' and \tit{wat} `what' do not combine with prepositions. They are substituted by respectively \tit{'r} `there' and \tit{waar} `where'.
 
@@
 
-Sometimes \tit{met wat} shows up!
-
-Evidence from that comes from the complementary distribution of \tit{waarmee} and \tit{met wat} in mismatching free relatives.
-
-This is a free relative construction in which the two predicates (the one in the main clause and the one in the embedded clause) combine with two different cases (i.e.
+This section discusses an exception to what is shown in the previous section.
+I show an instance in which \tit{met wat} `with what' has to be used instead of \tit{waarmee} `with what'.
+This instance comes from a mismatching free relative construction.
+
+A mismatching free relative is a free relative construction in which the two predicates (the one in the main clause and the one in the embedded clause) combine with two different cases (i.e.
 the case requirements do not match).
-I illustrate this in \ref{ex:gekochtwaarmee}.
+I give an example in which the \tsc{r}-pronoun and postposition appears before I get to the exception.
+Consider \ref{ex:gekochtwaarmee}.
 The predicate in the embedded clause, \tit{schildert} `paint', combines with an instrumental object.
-The predicate in the main clause clause, \tit{gekocht} `bought' combines with an accusative DP.
-The \tsc{r}-pronoun \tit{waarmee} `with what' is used here.\footnote{In this example, \tit{waar} `where' takes \tit{-mee} `with' to the left edge of the embedded clause.
+The predicate in the main clause clause, \tit{gekocht} `bought' combines with an accusative object.
+The \tsc{r}-pronoun and postposition \tit{waarmee} `with what' is used here.
+The use of \tit{met wat} `with what' is ungrammatical in this context, illustrated in \ref{ex:gekochtmetwat}.\footnote{In this example, \tit{waar} `where' takes \tit{-mee} `with' to the left edge of the embedded clause.
 It is also possible for \tit{-mee} `with' to be stranded, and \tit{waar} `where' to be moved to the left edge of the embedded clause on its own.
@@
 
-\exg. Ik heb gekocht waarmee jij schildert.\\
+\ex.
+\ag. Ik heb gekocht waarmee jij schildert.\\
  I have bought {where with} you paint\\
  `I bought what you are painting with.'\label{ex:gekochtwaarmee}
-
-If the predicates are switched around between the clauses, the \tsc{r}-pronoun does not appear anymore.
+\bg. *Ik heb gekocht met wat jij schildert.\\
+ I have bought with what you paint\\
+ `I bought what you are painting with.'\label{ex:gekochtmetwat}
+
+If the predicates are switched around between the clauses, the \tsc{r}-pronoun and postposition do not appear anymore.
 In \ref{ex:schildermet}, \tit{schilder} `paint' combines with an instrumental object in the main clause and \tit{gekocht} `bought' combines with an accusative object in the embedded clause.
-The use of an \tsc{r}-pronoun is ungrammatical, as indicated by the ungrammaticality of \ref{ex:schilderwaarmee}.
-Instead, a combination of the regular instrumental preposition \tit{met} `with' and the regular wh-pronoun \tit{was} `what' in used.
+The use of an \tsc{r}-pronoun and postposition is ungrammatical, as indicated by \ref{ex:schilderwaarmee}.
+Instead, a combination of the regular instrumental preposition \tit{met} `with' and the regular wh-pronoun \tit{wat} `what' in used.
 
@@
 
-The use of \tit{met wat} `with what' is ungrammatical in the context in which \tit{waarmee} `with what' appeared in \ref{ex:gekochtwaarmee}. This is illustrated in \ref{ex:gekochtmetwat}.
-
-\exg. *Ik heb gekocht met wat jij schildert.\\
- I have bought with what you paint\\
- `I bought what you are painting with.'\label{ex:gekochtmetwat}
-
-In the introduction I discussed the distribution between \tit{waarmee} `with what' and \tit{met wat} `with what' in free relatives with predicates that combine with different cases.
-Table \ref{tbl:distribution} repeats the generalization.
+Table \ref{tbl:distribution} summarizes the pattern.
 When the main clause predicate combines with an accusative and the embedded clause predicate with an instrumental, \tit{waarmee} `with what' is grammatical and \tit{met wat} `with what' is ungrammatical.
@@
 
-In this section I first show that \tsc{r}-pronouns are the default complement of a preposition.
-Next, I illustrate that a necessary requirement for an \tsc{r}-pronoun is that is forms a proper constituent.
-
-Let me now return to the mismatching free relatives. I repeat the relevant grammatical examples in \ref{ex:grammatical}.
-
-\ex.\label{ex:grammatical}
-\ag. Ik heb gekocht waarmee jij schildert.\\
- I have bought {where with} you paint\\
- `I bought what you are painting with.'\label{ex:grammaticalwaar}
-\bg. Ik schilder met wat jij hebt gekocht.\\
- I paint with what you have bought\\
- `I paint with what you bought.'\label{ex:grammaticalwat}
-
-In the preceding section I showed that ʀ-pronouns are expected in combinations with prepositions.
-This means that the use of \tit{waarmee} `with what' \ref{ex:grammaticalwaar} is not surprising.
-Something that is surprising is the use of \tit{met wat} `with what' in \ref{ex:grammaticalwat}, and this is the example something more needs to be said about.
-In the remainder of this section I argue that this `something more' is that the instrumental object in \ref{ex:grammaticalwat} does not form a proper constituent, i.e.
+In the remainder of this section I argue that the crucial point of \ref{ex:schildermetwat} is that the instrumental object does not form a proper constituent, i.e.
 it is not a constituent to the exclusion of any other elements.
-The other side of the coin is that constructions with \tsc{r}-pronouns contain a object that does form a proper constituent.
+The other side of the coin is that constructions with \tsc{r}-pronouns and postpositions contain an instrumental object that does form a proper constituent.
 
@@
 
-In each of these examples the instrumental object forms a constituent at a certain point in the derivation.
+In each of these examples the instrumental object forms a proper constituent at a certain point in the derivation.
 In \ref{ex:const1}, the instrumental object forms a proper constituent in the surface order, as shown in \ref{ex:const1stage}.
@@
 
-%There is additional evidence for the fact that \tit{waarmee} `with what' forms a constituent in the constructions above.
-In the example in \ref{ex:const2}-\ref{ex:const4} only \tit{waar} `where' was fronted, but \ref{ex:constwaarmee} shows that also the phrase containing \tit{-mee} with' can be moved.
-As wh-movement can only target constituents, it follows that \tit{waar} `where' and \tit{-mee} `with' have to form a constituent.
-
-%\ex.\label{ex:constwaarmee}
-%\ag. Waar -mee schilder jij?\\
- %{where -with} paint you\\
- %`What are you painting with?'
-%\bg. Ik schilder [waar -mee jij ook schildert].\\
- %I paint {where -with} you also paint\\
- %`I am painting with what you are painting with too.'
-%\bg. Ik schilder met de kwast [waar -mee jij ook schildert].\\
- %I paint with the brush {where -with} you also paint\\
- %`I am painting with the brush that you are painting with too.'
+Let me now show how this applies to the examples with the mismatching free relatives.
+The two predicates I used in the free relatives are \tit{kopen} `to buy' and \tit{schilderen}  `to paint'.
+\tit{Kopen} `to buy' takes an accusative DP as its object, illustrated in \ref{ex:kopen}.
+\tit{Schilderen} `to paint' can take an instrumental as its object, shown in \ref{ex:schilderen}.\footnote{\tit{Schilderen} also optionally takes an (accusative) object, but I am focussing on the instrumental object here.}
+
+\ex.
+\ag. Ik koop het schilderij.\\
+ I buy the painting\\
+ `I am buying the painting.'\label{ex:kopen}
+\bg. Ik schilder met een kwast.\\
+ I paint with a brush\\
+ `I am painting with a brush.'\label{ex:schilderen}
+
+I repeat the mismatching free relative in which \tit{waarmee} `with what' appears in \ref{ex:mismatchwaarmee}.
+The predicate \tit{schildert} `paints' combines in the embedded clause with the instrumental object.
+The instrumental object forms a proper constituent within the embedded clause, and the it can be realized as the \tsc{r}-pronoun and postposition \tit{waarmee} `with what'.\footnote{I assume that the accusative case requirement of \tit{gekocht} `bought' is satisfying by grafting a subconstituent of \tit{waarmee} `with what' \citep{bergsma2019}.}
+
+\exg. Ik heb gekocht [waarmee jij schildert].\\
+ I have bought {where with} you paint\\
+ `I bought what you are painting with.'\label{ex:mismatchwaarmee}
+
+Next, we arrive at the mismatching free relative in which \tit{waarmee} `with what' cannot be used, but \tit{met wat} `with what' appears.
+The embedded clause predicate \tit{gekocht} `bought' combines with an accusative DP.
+The accusative object of a verb is always \tit{wat} `what', as I showed in \ref{ex:wat}.
+The instrumental only comes into the picture in the main clause, when \tit{schilder} `paint' combines with an instrumental object.
+At no point in the derivation does the instrumental object form a proper constituent, and \tit{waarmee} `with what' does not surface.
+
+\exg. Ik schilder met [wat jij hebt gekocht].\\
+ I paint with what you have bought\\
+ `I paint with what you bought.'\label{ex:mismatchmetwat}
 
@@
  In \ref{ex:watindef}, \tit{wat} appears as a quantifier, and it means `some'.
-In both construction \tit{wat} `what' takes a complement and \tit{met wat} `with what' do not form a proper constituent.
+In both constructions \tit{wat} `what' takes a complement and \tit{met wat} `with what' do not form a proper constituent.
 The brackets within the examples indicate the constituency.
@@
 
-Let me now show how this applies to the examples with the mismatching free relatives.
-The two predicates I used in the free relatives are \tit{kopen} `to buy' and \tit{schilderen}  `to paint'.
-\tit{Kopen} `to buy' takes an accusative DP as its object, illustrated in \ref{ex:kopen}.
-\tit{Schilderen} `to paint' can take an instrumental as its object, shown in \ref{ex:schilderen}.\footnote{\tit{Schilderen} also optionally takes an (accusative) object, but I am focussing on the instrumental object here.}
-
-\ex.
-\ag. Ik koop het schilderij.\\
- I buy the painting\\
- `I am buying the painting.'\label{ex:kopen}
-\bg. Ik schilder met een kwast.\\
- I paint with a brush\\
- `I am painting with a brush.'\label{ex:schilderen}
-
-I repeat the mismatching free relative in which \tit{waarmee} `met wat' appears in \ref{ex:mismatchwaarmee}.
-The predicate \tit{schildert} `paints' combines in the embedded clause with the instrumental object.
-The instrumental object forms a proper constituent within the embedded clause, and the it can be realized as the \tsc{r}-pronoun and postposition \tit{waarmee} `with what'.\footnote{I assume that the accusative case requirement of \tit{gekocht} `bought' is satisfying by grafting a subconstituent of \tit{waarmee} `with what' \citep{bergsma2019}.}
-
-\exg. Ik heb gekocht [waarmee jij schildert].\\
- I have bought {where with} you paint\\
- `I bought what you are painting with.'\label{ex:mismatchwaarmee}
-
-Next, we arrive at the mismatching free relative in which \tit{waarmee} `with what' cannot be used, but \tit{met wat} `with what' appears.
-The embedded clause predicate \tit{gekocht} `bought' combines with an accusative DP.
-The accusative object of a verb is always \tit{wat} `what', as I showed in \ref{ex:wat}.
-The instrumental only comes into the picture in the main clause, when \tit{schilder} `paint' combines with an instrumental object.
-At no point in the derivation does the instrumental object form a proper constituent, and \tit{waarmee} `with what' does not surface.
-
-\exg. Ik schilder met [wat jij hebt gekocht].\\
- I paint with what you have bought\\
- `I paint with what you bought.'\label{ex:mismatchmetwat}
-
 \ref{ex:summaryconst} summarizes what I showed in this section.
 \tit{Met wat} `with what' can never surface when \tit{met} `with' and \tit{wat} `what' form a proper constituent.
-It always becomes \tit{waarmee} `with what'.
-This is schematically shown in \ref{ex:waarmeefr}.
-There are other contexts in which \tit{met wat} `with what' appears.
-This can be either when \tit{wat} `what' takes a complement, or when \tit{wat} is part of the a clause that \tit{met} `with' is not a part of.
-This last option is schematically showed in \ref{ex:metwatfr}, and it represents the mismatching free relative in \ref{ex:mismatchmetwat}.
+It always becomes \tit{waarmee} `with what', as shown in \ref{ex:waarmeefr}.
 
@@
 \a. [[met] [wat]] → [waarmee]\label{ex:waarmeefr}
-\b. [met [wat [X]]]
+\b. [met [wat [X]]]\label{ex:metwatx}
 \b. [met [[wat] [X]]]\label{ex:metwatfr}
 
-\tit{Met} `with' is a preposition that combines with full DPs and animate pronouns. \tit{Wat} `what' is a wh-element that appears as subject or object.
-
-In the next section I decompose \tit{waarmee} `with what' and \tit{met wat} `with what'. I show that both spell out the same set of features, but the distribution is different.
-
-\section{Taking \tit{waarmee} and \tit{met wat} apart}
-
-Along the way I introduce some background
-
-Things to explain
-*P pronoun-inanimate
-
-\tit{r} is the locative
-\tit{met} changes form
-
- The idea is that both expressions realize the same features, and \tit{waarmee} `with what' takes precedence when all features form a constituent.
-The morphemes I distinguish in \tit{waarmee} `with what' are \tit{w}, \tit{-aa-}, \tit{-r} and \tit{-mee}.
-Within \tit{met wat} `with what' I distinguish \tit{met}, \tit{w}, \tit{a} and \tit{-t}.
-\ref{ex:decompose} shows this as well.
+\tit{Met wat} `with what' can appear when the instrumental object does not form a proper constituent.
+This can be either when \tit{wat} `what' takes a complement before it combines with \tit{met} `with', as shown in \ref{ex:metwatx}, representing the examples in \ref{ex:moremetwat}.
+The other option is that \tit{wat} `what' is part of the a clause that \tit{met} `with' is not a part of, schematitized as \ref{ex:metwatfr} as an illustration of \ref{ex:mismatchmetwat}.
+
+\section{Decomposing \tit{waarmee} and \tit{met wat}}\label{sec:takingapart}
+
+In this section I decompose \tit{waarmee} `with what' and \tit{met wat} `met wat' into smaller units, and I connect them to parts of syntactic structure.
+Both spell out the same set of features but the distribution is different.
+I decompose \tit{waarmee} and \tit{met wat} as I show in \ref{ex:decompose}.
+Earlier works have decomposed these pronouns in similar ways (cf.
+\citet{hachem2015,noonan2017dutch,wesseling2018}).
 
 \ex.\label{ex:decompose}
-\a. w -aa -r -mee
-\b. met w -a -t
-
-In this section I investigate the internal structure of \tit{waarmee} `with what' and \tit{met wat} `with what' to capture the phonological similarities and differences between the two forms.
-First, I identify \tit{w} and \tit{a} as morphemes that appear in both expressions.
+\ag. w -aa -r -mee\\
+\tsc{w} -\tsc{deix} -\tsc{loc} -\tsc{ins}\\
+\bg. met w -a -t\\
+\tsc{ins} \tsc{w} -\tsc{deix} -\tsc{n.sg}\\
+\z.
+\z.
+
+In this section I first identify \tit{w} and \tit{a} as morphemes that appear in both expressions.
 Putting these two aside, I concentrate on \tit{'rmee} `with it' and \tit{met 't} `with it'.
-
-The elements \tit{w} and \tit{a} express the same syntactic structure in both expressions.
-The elements \tit{met} and \tit{'t} together also express the same features as \tit{-mee} and \tit{'r} together, but the distribution differs.
-\tit{Met} expresses less structure than \tit{-mee}, and \tit{'t} expresses more structure than \tit{'r}.
-\tit{Met} is shown to be an preposition, and \tit{-mee} is a postposition.
-It also becomes clear that the \tit{'r} in fact corresponds to the locative \tit{r} in Dutch.
+Along the way I introduce some necessary theoretical background on Nanosyntax.
 
@@
 Let me start with the morphemes \tit{w} and \tit{a} that appear in both expressions.
-I assume that they correspond to the same syntactic structure in both \tit{waarmee} and \tit{met wat}.
+I assume that they correspond to the same syntactic structure in both \tit{waarmee} `with what' and \tit{met wat} `with what'.
 As I am interested in the differencs between the two expression, I do not discuss the featural content of \tit{w} and \tit{a} into depth.
@@
 \ex. \begin{forest}
-[WP
+[\tsc{wP}
     [W, roof]
@@
 \ex. \begin{forest}
-[deixP
-    [deix, roof]
+[\tsc{deixP}
+    [\tsc{deix}, roof]
 ]
@@
 I set up an account that makes the ungrammaticality of \tit{met 't} and the appearance of \tit{'rmee} follow from spellout.
-The analysis accounts for the following two observations, taking \tit{met 't} as the point of departure.
-First, \tit{met} `with' changes from being a preposition to being a postposition, and its form changes into \tit{-mee}.
+The analysis accounts for the following three observations, taking \tit{met 't} as the point of departure.
+First, \tit{met} `with' changes from being a preposition to being a postposition.
 This process is restricted to inanimate pronouns, and it does not apply to full DPs and animate pronouns.
-Second, \tit{'t} is replaced by \tit{'r}, a morpheme that is associated with the locative in Dutch.
+Second, \tit{met} changes form into \tit{-mee}.
+Third, \tit{'t} is replaced by \tit{'r}, a morpheme that is associated with the locative in Dutch.
 
@@
 Let me start with the lexical entry for \tit{'t}.
-\tit{'t} `it' can be used as subject (associated with nominative), direct object (associated in accusative) and indirect object (associated with dative), as shown in \ref{ex:tsubobj}.
+\tit{'t} `it' can be used as a subject (associated with nominative), direct object (associated in accusative) and indirect object (associated with dative), as shown in \ref{ex:tsubobj}.
 
@@
  \bg. Ik heb hem een klap gegeven.\\
-  I have \tsc{3sg.m.acc} a hit given\\ with both alternatives. I work the proposal out with't  realizing all cases.
-
-For case, I follow \citet{caha2009} that case features case features are organized the containment relation in \ref{ex:casetree}.
-The higher, more complex cases contain the smaller, less complex cases.\footnote{there has been discussion on the genitive.
-starke on two accusatives and two datives.
-this paper: only small accusative and dative and genitive is above both of them.}
+  I have \tsc{3sg.m.dat} a hit given\\
+  `I gave him a hit.'
+
+For case, I follow \citet{caha2009} that case features are organized as in the containment relation in \ref{ex:casetree}.
+The higher, more complex cases contain the smaller, less complex cases.\footnote{I follow \citet{starke2017} in that there are two types of accusatives and datives.
+In this paper I only include the S-\tsc{acc} and S-\tsc{dat}, which are placed below the \tsc{gen}.}
 
@@
 
- Following the distinctions from \citet{cardinaletti1996}, \tit{'t} `it' is a weak pronoun.
+ Following the distinctions from \citet{cardinaletti1996}, I assume \tit{'t} `it' is a weak pronoun.
 It is not a clitic, because it can occur in sentence initial position, shown in \ref{ex:tnoclitic}.
@@
 It is enough if the syntactic structure is contained in the lexically stored tree.
-This has a as consequence that the lexical entry in \ref{ex:entryt} can also be inserted in \ref{ex:tacc} and \ref{ex:tnom}.
+This has as a consequence that the lexical entry in \ref{ex:entryt} can also be inserted in \ref{ex:tacc} and \ref{ex:tnom}.
 
@@
 
-I follow \cite{baunaz2018} in assuming that the ontological category \tsc{location} contains \tsc{thing}.\footnote{\citet{baunaz2018} place in addition \tsc{person} between \tsc{thing} and \tsc{location}, which I left out here.}
+I follow \citet{baunaz2018} in assuming that the ontological category \tsc{location} contains \tsc{thing}.\footnote{\citet{baunaz2018} place in addition \tsc{person} between \tsc{thing} and \tsc{location}, which I have left out here.}
 
@@
 \ex. The Elsewhere Condition (\citealt{kiparsky1973}, formulated as in \citealt{caha2020}):\\
-When two entries can spell out a given node, the more specific entry wins. Under the Superset Principle governed insertion, the more specific entry is the one which has fewer unused features
+When two entries can spell out a given node, the more specific entry wins. Under the Superset Principle governed insertion, the more specific entry is the one which has fewer unused features.
 
@@
 	\caption {Fragment Dutch \tsc{n.sg}}
-	\begin{minipage}{0.56\linewidth}
+	\begin{minipage}{0.17\linewidth}
 		\begin{tabularx}{\textwidth}{ccccccc}
@@
     \tsc{acc} & mæn-∅       & sær-∅   \\
+    \tsc{dat} & mæn-æn      & sær-æn  \\
     \tsc{gen} & mæn (??)    & sær-y   \\
     \tsc{ins} & mæn-æj      & sær-æj  \\
-    \tsc{dat} & mæn-æn      & sær-æn  \\
     \bottomrule
@@
 This means that \tit{mæn} is the bare stem that combines with case markers, and \tit{æz} the suppletive nominative.
-In Section \ref{sec:derivation} I show how a derivation with this type of elements works in nanosyntax.
+In Section \ref{sec:derivation} I show how a derivation with this type of elements works in Nanosyntax.
 
@@
 In \ref{ex:dutchin}, the movement of the adposition is driven by movement, and it is meaningful.
-The movement I discuss in this paper with \tsc{r}-pronouns is driven by spellout, and it is meaningless.} In this section I discuss the relation between prepositions and postpositions, and how this is modeled with the case hierarchy in Nanosyntax \citep{caha2009}.
+The movement of \tsc{r}-pronouns I discuss in this paper is driven by spellout, which is meaningless.} In this section I discuss the relation between prepositions and postpositions, and how this is modeled with the case hierarchy in Nanosyntax \citep{caha2009}.
 
@@
 \ex. The preposition/postposition hierarchy
-\a. If the expression of a particular case in the Case sequence (below) involves a preposition, then all cases to its right do as well.
+\a. If the expression of a particular case in the case sequence (below) involves a preposition, then all cases to its right do as well.
 \b. The Case sequence: \tsc{nom – acc – dat – gen - ins – com} \hfill \citep{caha2009}
@@
 
-With the case hierarchy in nanosyntax this can be modeled by letting the DP move as high as above the \tsc{datP} in the syntactic structure.
+With the case hierarchy in Nanosyntax this can be modeled by letting the DP move as high as above the \tsc{datP} in the syntactic structure.
 The features below the \tsc{datP} are realized as a suffix, and the features above \tsc{datP} are realized as a preposition.
@@
 After each instance of merge, spellout takes place.
-If no spellout exist for the phrase created by the newly added feature, evacuation movements specified in the spellout algorithm take place.
+If no spellout exists for the phrase created by the newly added feature, evacuation movements specified in the spellout algorithm take place.
 The algorithm is given in \ref{ex:spellout}.
@@
 \ex. Merge F and \label{ex:spellout}
- \a. Spell out FP
- \b. If (a) fails, attempt movement of the spec of the complement of \tsc{f}, and retry (a)
- \b. If (b) fails, move the complement of \tsc{f}, and retry (a)
+ \a. Spell out FP.
+ \b. If (a) fails, attempt movement of the spec of the complement of \tsc{f}, and retry (a).
+ \b. If (b) fails, move the complement of \tsc{f}, and retry (a).
 
@@
 
+With this theoretical background in place, we can turn to the derivation.
 I first show how \tit{'rmee} `with it' is constructed.
-I leave out \tit{w} and \tit{a}, because it unnecessarily complicates the story.\footnote{I assume that the WP and \tsc{deixP} appear lower in the structure than the case features, so the functional sequence is as given in \ref{ex:fseq}.
+I leave out \tit{w} and \tit{a}, because it unnecessarily complicates the story.\footnote{I assume that the \tsc{wP} and \tsc{deixP} appear lower in the structure than the case features, so the functional sequence is as given in \ref{ex:fseq}.
 
@@
 Again there was no specifier, no spec-to-spec movement does not apply.
-However, complement movement provides a structure that is a match for the lexical entry in \ref{ex:entrymee}: \tit{-mee}.
+However, complement movement provides a structure that is a match for the lexical entry in \ref{ex:entrymee}: \tit{-mee}.\footnote{This picture resembles the proposal of \citep{abels2003diss} in that not the whole complement of P is moves but only a part is extracted.
+The current analysis differs in that the movement is not syntactically driven but by spellout.}
 
@@
 
-I skip over the details of how \tit{w} and \tit{a} end up in their positions.\footnote{I assume that WP and \tsc{deixP} are both complex specifiers that are created after \tsc{thing} is spelled out in \ref{ex:thingspellout}.
-After each instance of merge after that, backtracking always takes place, the complex specifier is detached from the structure and the case features are spelled out together with or as a postposition on \tsc{thing}.} The final result of the structure for \tit{waarmee} `with what' look as in \ref{ex:spelloutwaarmee}.
-
-\ex. \begin{forest} boom
-[\tsc{WP}
-    [\tsc{WP}
-        [\tsc{W}, roof]
+I skip over the details of how \tit{w} and \tit{a} end up in their positions.\footnote{I assume that \tsc{wP} and \tsc{deixP} are both complex specifiers that are created after \tsc{thing} is spelled out in \ref{ex:thingspellout}.
+After each instance of merge after that, backtracking takes place, the complex specifier is detached from the structure and the case features are spelled out together with or as a postposition on \tsc{thing}.} The final result of the structure for \tit{waarmee} `with what' look as in \ref{ex:spelloutwaarmee}.
+
+\ex. \begin{forest} boom
+[\tsc{\tsc{wP}}
+    [\tsc{\tsc{wP}}
+        [\tsc{w}, roof]
     ]
@@
 There is no constituent in \ref{ex:spelloutwaarmee} that contains \tit{waar} but not \tit{-mee}.
-To resolve this situation I follow \citet{noonan2017dutch} in assuming that the phrase containing the adposition (here \tit{-mee}) syntactically moves to a position higher in the structure.
+To resolve this situation I follow \citet{noonan2017dutch} in assuming that the phrase containing the adposition (here \tit{-mee}) can syntactically move to a position higher in the structure.
+Evidence that \tit{mee} `with' has moved comes from the ungrammaticality of \ref{ex:meeend}.
+This shows that \tit{mee} `with' cannot be stranded in its base position (see \ref{ex:const3stage}).
+
+\exg. *Ik heb gekocht waar jij schildert mee.\\
+ I have bought waar you paint with\\
+ `I bought what you are painting with.'\label{ex:meeend}
+
 The movement of the adposition has the typical distribution of that of verbal particles (cf.
-\citealt{riemsdijk1978,noonan2017dutch}, and it could possibly be triggered by the feature Σ, associated with weak pronouns.
-With \tit{-mee} having moved out, the WP only contains features that are realized as \tit{waar}, and it moves to the left edge of the clause, resulting in the surface order in \ref{ex:meestranded}.
+\citealt{riemsdijk1978,noonan2017dutch}, and it could possibly be triggered by the feature Σ (which is contained in \tit{mee} `with`), associated with weak pronouns.
+With \tit{-mee} having moved out, the \tsc{wP} only contains features that are realized as \tit{waar}, and it moves to the left edge of the clause, resulting in the surface order in \ref{ex:meestranded}.
 
 So far I showed how \tit{waarmee} `with what' is derived if all syntactic features form a constituent.
-Next I address how \tit{waarmee} is blocked and \tit{met wat} `with what' appears when the features do not form a proper constituent is derived.
+Next I address how \tit{waarmee} `with what' is blocked and \tit{met wat} `with what' appears when the features do not form a proper constituent is derived.
 An example of a situation in which all features do not form a constituent is given in \ref{ex:noconst}.
@@
 [CP
-    [\tsc{WP}
-        [\tsc{WP}
-            [\tsc{W}, roof]
+    [\tsc{\tsc{wP}}
+        [\tsc{\tsc{wP}}
+            [\tsc{w}, roof]
         ]
@@
     [CP
-        [\tsc{WP}
-            [\tsc{WP}
-                [\tsc{W}, roof]
+        [\tsc{\tsc{wP}}
+            [\tsc{\tsc{wP}}
+                [\tsc{w}, roof]
             ]
@@
 
-\section{Conclusion and discussion}
-
-In this paper, I discussed the distribution of \tit{waarmee} `met wat' and \tit{met wat} `with what' is mismatching free relatives.
-I showed that \tit{waarmee} `with what' appears when all features form a proper constituent, and \tit{met wat} `with what' if they do not.
-
-The described pattern follows from a core assumptions in Nanosyntax: phrasal spellout spells out constituents.
-Looking more into detail, \tit{waarmee} `with what' takes precedence over \tit{met wat} `with what' because \tit{-mee} has the structure of a postposition.
-Following the spellout algorithm, \tit{'t} `it' is replaced by \tit{'r} `there', so that it can combine with \tit{-mee} `with'.
-The preposition \tit{met} `with' is only used if there is no other option to spell out the features.
-
-This proposal is in several aspects in accordance with earlier work.
-Just like \citet{riemsdijk1978}, I claim that \tsc{r}-pronouns originate as the complement of P.
-He argued that due to some kind of suppletion \tit{'t} `it' changes form to \tsc{'r}, which is coincidentally also the locative in Dutch.
-In my proposal, this suppletion follows naturally from the regular spellout algorithm.
-Also, it is not a coincidence that the locative appears, as it is an item with little features that spells out \tsc{thing}.
-The current proposal differs from \citet{riemsdijk1978} in that it is not the whole complement of P is moved.
-Instead, only part of the complement of P is extracted, which is generally allowed, also in non-preposition stranding languages \citep{abels2003diss}.
-
+\section{Conclusion and discussion}\label{sec:conclusion}
+
+In this paper, I discussed the instrumental \tsc{r}-pronoun and postposition \tit{waarmee} `with what' in Dutch.
+The main intuition is that this form that appears when features of an instrumental inanimate object form a proper constituent.
+The form cannot appear, and \tit{met wat} `with what` surfaces instead, when all features do not form a proper constituent.
+The described pattern follows from a core assumption in Nanosyntax: phrasal spellout spells out constituents \citep{starke2009}.
+The distribution of \tit{r}-pronouns and postpositions and prepositions and pronouns follows from regular spellout mechanisms.
+
+Under this analysis, there is no need for a filter that rules out a combination of a preposition and an inanimate pronoun.
+As long as the to be spelled out features form a proper constituent, the spellout algorithm ensures the \tsc{r}-pronoun and postposition takes precedence over the other form.
+The fact that locatives are syncretic with \tsc{r}-pronouns is not a coincidence as well.
+The lexicon contains a single entry for a locative, which is the one used for \tsc{r}-pronouns as well.
+The change in placement of the adposition is a consequence of spellout too.
+\tit{Mee} `with' is a postposition and is stored differently from the preposition \tit{met} `with', which leads to the correct placement with different constituency.
+The fact that \tit{met} `with' and \tit{mee} `with' differ phonologically can also be captured by storing them as two separate lexical entries.
+
+In the remainder of this section I discuss how this analysis can be extended to other adpositions in Dutch.
 Giving \tit{met} `with' and \tit{-mee} `with' two distinct lexical entries has as a consequence that the phonological overlap between them seems like a coincidence.
@@
 
-n all the other cases the preposition does not change form when it combines with an \tsc{r}-pronoun, e.g.
+In all other cases the adposition does not change form when it combines with an \tsc{r}-pronoun, e.g.
 \tit{in}.
-If this proposal is on the right track, elements as \tit{in} can be used as either a preposition and as a postposition.
+If this proposal is on the right track, elements as \tit{in} can be used as either a preposition or as a postposition.
 The lexical entry should then be usable as pre-element and as post-element, so it needs to have a binary bottom and a unary foot at the same time.

### 2020-01-16 paper.tex
leaving jan's place
refereces in place

@@
 
-\title{The \tsc{r}-pronoun and postposition \tit{waarmee} in Dutch}
+\title{The \tsc{r}-pronoun and postposition \tit{waar-mee} in Dutch}
 \author{Fenna Bergsma}
@@
 
-This chapter is an in-depth study of the instrumental \tsc{r}-pronoun and postposition \tit{'r -mee} `with it' and \tit{waarmee} `with what' in Dutch.
+This chapter is an in-depth study of the instrumental \tsc{r}-pronoun and postposition \tit{'r-mee} `with it' and \tit{waar-mee} `with what' in Dutch.
 This instance is interesting for two reasons.
@@
 
-The main generalization is that the instrumental \tsc{r}-pronoun and postposition \tit{waarmee} `with what' takes precedence over the instrumental preposition and inanimate pronoun \tit{met wat} `with what'.
+The main generalization is that the instrumental \tsc{r}-pronoun and postposition \tit{waar-mee} `with what' takes precedence over the instrumental preposition and inanimate pronoun \tit{met wat} `with what'.
 This generalization is subject to an important condition: the instrumental object needs to form a proper constituent i.e.
@@
 I show that \tsc{r}-pronouns and postpositions and prepositions and pronouns are in complementary distribution, depending on whether all features form a proper constituent or not.
-In Section \ref{sec:takingapart} I decompose \tit{waarmee} `with what' and \tit{met wat} `with what', and I connect them to parts of syntactic structure.
-Section \ref{sec:derivation} shows in a derivation how \tit{waarmee} `with what' is derived and the role that constituency plays.
+In Section \ref{sec:takingapart} I decompose \tit{waar-mee} `with what' and \tit{met wat} `with what', and I connect them to parts of syntactic structure.
+Section \ref{sec:derivation} shows in a derivation how \tit{waar-mee} `with what' is derived and the role that constituency plays.
 Section \ref{sec:conclusion} concludes and discusses possible extensions of the analysis.
@@
 that all features form a constituent to the exclusion of any other features.
-I start the section by showing that \tit{'rmee} `with it' and \tit{waarmee} `with what` are the default, that normally they appear instead of \tit{met 't} `with it' and \tit{met wat} `with what`.
-Then I show an exception, in which \tit{met wat} `with what` has to be used and \tit{waarmee} `with what` cannot.
+I start the section by showing that \tit{'rmee} `with it' and \tit{waar-mee} `with what` are the default, that normally they appear instead of \tit{met 't} `with it' and \tit{met wat} `with what`.
+Then I show an exception, in which \tit{met wat} `with what` has to be used and \tit{waar-mee} `with what` cannot.
 I argue that the crucial difference between the exception and other cases is that in the exception the features do not form a proper constituent.
@@
  `I am painting with it.'\label{ex:prephet}
-\bg. Ik schilder 'r mee.\\
+\bg. Ik schilder 'r -mee.\\
  I paint there -with\\
@@
 \tit{Wat} `what' can function as an object of a verb (see \ref{ex:wat}), but not as an object of a preposition \ref{ex:metwat}.
-In that case, the \tsc{r}-pronoun and postposition \tit{waarmee} `with what' appears, as shown in \ref{ex:waarmee}.\footnote{The sentence in \ref{ex:metwat} is unacceptable with neutral intonation.
+In that case, the \tsc{r}-pronoun and postposition \tit{waar-mee} `with what' appears, as shown in \ref{ex:waar-mee}.\footnote{The sentence in \ref{ex:metwat} is unacceptable with neutral intonation.
 It becomes acceptable if \tit{wat} `what' is stressed, for example in a context in which the speaker is highly surprised about the choice of the object the hearer is painting with.}
@@
  `What are you painting with?'\label{ex:metwat}
-\bg. Waarmee schilder jij?\\
- {where with} paint you with\\
- `What are you painting with?'\label{ex:waarmee}
-
-\tit{Waarmee} `with what' and not \tit{met wat} `with what' does not only appear in wh-questions, but also in other contexts.
+\bg. Waar -mee schilder jij?\\
+ where with paint you with\\
+ `What are you painting with?'\label{ex:waar-mee}
+
+\tit{Waar-mee} `with what' and not \tit{met wat} `with what' does not only appear in wh-questions, but also in other contexts.
 \ref{ex:headed} gives an example of a headed relative, and \ref{ex:headless} shows a free relative in which both predicates combine with an instrumental object.
-The use of \tit{met wat} `with what' is ungrammatical in both contexts, and \tit{waarmee} `with what' is used.
+The use of \tit{met wat} `with what' is ungrammatical in both contexts, and \tit{waar-mee} `with what' is used.
 
 \ex.\label{ex:headed}
-\ag. Ik schilder met de kwast waarmee jij ook schildert.\\
- I paint with the brush {where with} you also paint\\
+\ag. Ik schilder met de kwast waar -mee jij ook schildert.\\
+ I paint with the brush where with you also paint\\
  `I am painting with the brush that you are painting with too.'
@@
  \ex.\label{ex:headless}
- \ag. Ik schilder waarmee jij ook schildert.\\
-  I paint {where with} you also paint\\
+ \ag. Ik schilder waar -mee jij ook schildert.\\
+  I paint where with you also paint\\
   `I am painting with what you are painting with too.'
@@
 This section discusses an exception to what is shown in the previous section.
-I show an instance in which \tit{met wat} `with what' has to be used instead of \tit{waarmee} `with what'.
+I show an instance in which \tit{met wat} `with what' has to be used instead of \tit{waar-mee} `with what'.
 This instance comes from a mismatching free relative construction.
@@
 I give an example in which the \tsc{r}-pronoun and postposition appears before I get to the exception.
-Consider \ref{ex:gekochtwaarmee}.
+Consider \ref{ex:gekochtwaar-mee}.
 The predicate in the embedded clause, \tit{schildert} `paint', combines with an instrumental object.
 The predicate in the main clause clause, \tit{gekocht} `bought' combines with an accusative object.
-The \tsc{r}-pronoun and postposition \tit{waarmee} `with what' is used here.
+The \tsc{r}-pronoun and postposition \tit{waar-mee} `with what' is used here.
 The use of \tit{met wat} `with what' is ungrammatical in this context, illustrated in \ref{ex:gekochtmetwat}.\footnote{In this example, \tit{waar} `where' takes \tit{-mee} `with' to the left edge of the embedded clause.
@@
 \ex.
-\ag. Ik heb gekocht waarmee jij schildert.\\
- I have bought {where with} you paint\\
- `I bought what you are painting with.'\label{ex:gekochtwaarmee}
+\ag. Ik heb gekocht waar -mee jij schildert.\\
+ I have bought where with you paint\\
+ `I bought what you are painting with.'\label{ex:gekochtwaar-mee}
 \bg. *Ik heb gekocht met wat jij schildert.\\
@@
 In \ref{ex:schildermet}, \tit{schilder} `paint' combines with an instrumental object in the main clause and \tit{gekocht} `bought' combines with an accusative object in the embedded clause.
-The use of an \tsc{r}-pronoun and postposition is ungrammatical, as indicated by \ref{ex:schilderwaarmee}.
+The use of an \tsc{r}-pronoun and postposition is ungrammatical, as indicated by \ref{ex:schilderwaar-mee}.
 Instead, a combination of the regular instrumental preposition \tit{met} `with' and the regular wh-pronoun \tit{wat} `what' in used.
@@
 \ex.\label{ex:schildermet}
-\ag. *Ik schilder waarmee jij hebt gekocht.\\
- I paint {where with} you have bought\\
- `I paint with what you bought.'\label{ex:schilderwaarmee}
+\ag. *Ik schilder waar -mee jij hebt gekocht.\\
+ I paint where with you have bought\\
+ `I paint with what you bought.'\label{ex:schilderwaar-mee}
 \bg. Ik schilder met wat jij hebt gekocht.\\
@@
 Table \ref{tbl:distribution} summarizes the pattern.
-When the main clause predicate combines with an accusative and the embedded clause predicate with an instrumental, \tit{waarmee} `with what' is grammatical and \tit{met wat} `with what' is ungrammatical.
-When the main clause predicate combines with an instrumental and the embedded clause predicate with an accusative, \tit{waarmee} `with what' is ungrammatical and \tit{met wat} `with what' is used.
+When the main clause predicate combines with an accusative and the embedded clause predicate with an instrumental, \tit{waar-mee} `with what' is grammatical and \tit{met wat} `with what' is ungrammatical.
+When the main clause predicate combines with an instrumental and the embedded clause predicate with an accusative, \tit{waar-mee} `with what' is ungrammatical and \tit{met wat} `with what' is used.
 
@@
 	\center
-	\caption {Distribution between \tit{waarmee} and \tit{met wat}}
+	\caption {Distribution between \tit{waar-mee} and \tit{met wat}}
 	\begin{minipage}{0.45\linewidth}
@@
 		\toprule
-                              & \tit{waarmee} & \tit{met wat} \\
+                              & \tit{waar-mee} & \tit{met wat} \\
 		\midrule
@@
 \ex.
-\ag. Ik schilder 'r mee.\\
+\ag. Ik schilder 'r -mee.\\
  I paint there with\\
  `I am painting with it.'\label{ex:const1}
-\bg. Waarmee schilder jij?\\
-{where with} paint you with\\
+\bg. Waar -mee schilder jij?\\
+where with paint you with\\
  `What are you painting with?'\label{ex:const2}
-\bg. Ik schilder met de kwast [waarmee jij ook schildert].\\
- I paint with the brush {where with} you also paint\\
+\bg. Ik schilder met de kwast [waar -mee jij ook schildert].\\
+ I paint with the brush where with you also paint\\
  `I am painting with the brush that you are painting with too.'\label{ex:const3}
-\bg. Ik schilder [waarmee jij ook schildert].\\
- I paint {where with} you also paint\\
+\bg. Ik schilder [waar -mee jij ook schildert].\\
+ I paint where with you also paint\\
  `I am painting with what you are painting with too.'\label{ex:const4}
@@
 \ex.
-\a. [[ik] [[schilder] ['r mee]]]\label{ex:const1stage}
-\b. [[jij] [[schilder] [waarmee]]]\label{ex:const2stage}
-\b. [[jij] [[ook] [[schilder] [waarmee]]]]\label{ex:const3stage}
+\a. [[ik] [[schilder] ['r -mee]]]\label{ex:const1stage}
+\b. [[jij] [[schilder] [waar-mee]]]\label{ex:const2stage}
+\b. [[jij] [[ook] [[schilder] [waar-mee]]]]\label{ex:const3stage}
 
@@
 
-I repeat the mismatching free relative in which \tit{waarmee} `with what' appears in \ref{ex:mismatchwaarmee}.
+I repeat the mismatching free relative in which \tit{waar-mee} `with what' appears in \ref{ex:mismatchwaar-mee}.
 The predicate \tit{schildert} `paints' combines in the embedded clause with the instrumental object.
-The instrumental object forms a proper constituent within the embedded clause, and the it can be realized as the \tsc{r}-pronoun and postposition \tit{waarmee} `with what'.\footnote{I assume that the accusative case requirement of \tit{gekocht} `bought' is satisfying by grafting a subconstituent of \tit{waarmee} `with what' \citep{bergsma2019}.}
-
-\exg. Ik heb gekocht [waarmee jij schildert].\\
- I have bought {where with} you paint\\
- `I bought what you are painting with.'\label{ex:mismatchwaarmee}
-
-Next, we arrive at the mismatching free relative in which \tit{waarmee} `with what' cannot be used, but \tit{met wat} `with what' appears.
+The instrumental object forms a proper constituent within the embedded clause, and the it can be realized as the \tsc{r}-pronoun and postposition \tit{waar-mee} `with what'.\footnote{I assume that the accusative case requirement of \tit{gekocht} `bought' is satisfying by grafting a subconstituent of \tit{waar-mee} `with what' \citep{bergsma2019}.}
+
+\exg. Ik heb gekocht [waar -mee jij schildert].\\
+ I have bought where with you paint\\
+ `I bought what you are painting with.'\label{ex:mismatchwaar-mee}
+
+Next, we arrive at the mismatching free relative in which \tit{waar-mee} `with what' cannot be used, but \tit{met wat} `with what' appears.
 The embedded clause predicate \tit{gekocht} `bought' combines with an accusative DP.
@@
 The instrumental only comes into the picture in the main clause, when \tit{schilder} `paint' combines with an instrumental object.
-At no point in the derivation does the instrumental object form a proper constituent, and \tit{waarmee} `with what' does not surface.
+At no point in the derivation does the instrumental object form a proper constituent, and \tit{waar-mee} `with what' does not surface.
 
@@
 
- The mismatching free relative in \ref{ex:grammaticalwat} is not the only construction in which the string \tit{met wat} `with what' appears.
+ The mismatching free relative in \ref{ex:mismatchmetwat} is not the only construction in which the string \tit{met wat} `with what' appears.
 I give examples of two more occurrences in \ref{ex:moremetwat}.
@@
 \tit{Met wat} `with what' can never surface when \tit{met} `with' and \tit{wat} `what' form a proper constituent.
-It always becomes \tit{waarmee} `with what', as shown in \ref{ex:waarmeefr}.
+It always becomes \tit{waar-mee} `with what', as shown in \ref{ex:waar-meefr}.
 
 \ex.\label{ex:summaryconst}
-\a. [[met] [wat]] → [waarmee]\label{ex:waarmeefr}
+\a. [[met] [wat]] → [waar-mee]\label{ex:waar-meefr}
 \b. [met [wat [X]]]\label{ex:metwatx}
@@
 
-\section{Decomposing \tit{waarmee} and \tit{met wat}}\label{sec:takingapart}
-
-In this section I decompose \tit{waarmee} `with what' and \tit{met wat} `met wat' into smaller units, and I connect them to parts of syntactic structure.
+\section{Decomposing \tit{waar-mee} and \tit{met wat}}\label{sec:takingapart}
+
+In this section I decompose \tit{waar-mee} `with what' and \tit{met wat} `met wat' into smaller units, and I connect them to parts of syntactic structure.
 Both spell out the same set of features but the distribution is different.
-I decompose \tit{waarmee} and \tit{met wat} as I show in \ref{ex:decompose}.
+I decompose \tit{waar-mee} and \tit{met wat} as I show in \ref{ex:decompose}.
 Earlier works have decomposed these pronouns in similar ways (cf.
@@
 Let me start with the morphemes \tit{w} and \tit{a} that appear in both expressions.
-I assume that they correspond to the same syntactic structure in both \tit{waarmee} `with what' and \tit{met wat} `with what'.
+I assume that they correspond to the same syntactic structure in both \tit{waar-mee} `with what' and \tit{met wat} `with what'.
 As I am interested in the differencs between the two expression, I do not discuss the featural content of \tit{w} and \tit{a} into depth.
@@
 
-I put \tit{w} and \tit{a} aside for now, assuming they spell out the same syntactic structure in \tit{waarmee} `with what' and \tit{met wat} `with what'.
-This leaves \tit{'r -mee} `with it' and \tit{met 't} `with it'.
+I put \tit{w} and \tit{a} aside for now, assuming they spell out the same syntactic structure in \tit{waar-mee} `with what' and \tit{met wat} `with what'.
+This leaves \tit{'r-mee} `with it' and \tit{met 't} `with it'.
 
@@
 
-In the next section I put all features back together in a derivation and I show how \tit{waarmee} `with what' surfaces when all features form a constituent.
+In the next section I put all features back together in a derivation and I show how \tit{waar-mee} `with what' surfaces when all features form a constituent.
 \tit{Met wat} `with what' appears when the functional sequence is disrupted.
@@
 
-Before I show that \tit{waarmee} `with what' is used when all features form a proper constituent, I need to make some assumptions about the spellout process in Nanosyntax explicit.
+Before I show that \tit{waar-mee} `with what' is used when all features form a proper constituent, I need to make some assumptions about the spellout process in Nanosyntax explicit.
 Spellout happens in a cyclic derivation, following a spellout algorithm \citep{starke2018}.
@@
 I skip over the details of how \tit{w} and \tit{a} end up in their positions.\footnote{I assume that \tsc{wP} and \tsc{deixP} are both complex specifiers that are created after \tsc{thing} is spelled out in \ref{ex:thingspellout}.
-After each instance of merge after that, backtracking takes place, the complex specifier is detached from the structure and the case features are spelled out together with or as a postposition on \tsc{thing}.} The final result of the structure for \tit{waarmee} `with what' look as in \ref{ex:spelloutwaarmee}.
+After each instance of merge after that, backtracking takes place, the complex specifier is detached from the structure and the case features are spelled out together with or as a postposition on \tsc{thing}.} The final result of the structure for \tit{waar-mee} `with what' look as in \ref{ex:spelloutwaar-mee}.
 
@@
 ]
-\end{forest}\label{ex:spelloutwaarmee}
+\end{forest}\label{ex:spelloutwaar-mee}
 
@@
 
-There is no constituent in \ref{ex:spelloutwaarmee} that contains \tit{waar} but not \tit{-mee}.
+There is no constituent in \ref{ex:spelloutwaar-mee} that contains \tit{waar} but not \tit{-mee}.
 To resolve this situation I follow \citet{noonan2017dutch} in assuming that the phrase containing the adposition (here \tit{-mee}) can syntactically move to a position higher in the structure.
@@
 
-So far I showed how \tit{waarmee} `with what' is derived if all syntactic features form a constituent.
-Next I address how \tit{waarmee} `with what' is blocked and \tit{met wat} `with what' appears when the features do not form a proper constituent is derived.
+So far I showed how \tit{waar-mee} `with what' is derived if all syntactic features form a constituent.
+Next I address how \tit{waar-mee} `with what' is blocked and \tit{met wat} `with what' appears when the features do not form a proper constituent is derived.
 An example of a situation in which all features do not form a constituent is given in \ref{ex:noconst}.
@@
 
-This section showed how the instrumental inanimate relative pronoun is realized as \tit{waarmee} `with what' when all syntactic features form a constituent.
+This section showed how the instrumental inanimate relative pronoun is realized as \tit{waar-mee} `with what' when all syntactic features form a constituent.
 It also showed how \tit{met wat} `with what' appears when all features do not form a proper constituent, and other features intervene.
@@
 
-In this paper, I discussed the instrumental \tsc{r}-pronoun and postposition \tit{waarmee} `with what' in Dutch.
+In this paper, I discussed the instrumental \tsc{r}-pronoun and postposition \tit{waar-mee} `with what' in Dutch.
 The main intuition is that this form that appears when features of an instrumental inanimate object form a proper constituent.

### 2020-01-16 paper.tex
submitted to christina
BAM

@@
 \title{The \tsc{r}-pronoun and postposition \tit{waar-mee} in Dutch}
-\author{Fenna Bergsma}
+\author{Fenna Bergsma\\Goethe-Universität Frankfurt}
 \date{\today}
@@
 
-The main question I address in this chapter is how to correctly rule out \tit{met 't} `with it' in \ref{ex:neemett}, and let the \tsc{r}-pronoun and postposition in \ref{ex:jarmee} appear.
+The main question I address in this paper is how to correctly rule out \tit{met 't} `with it' in \ref{ex:neemett}, and let the \tsc{r}-pronoun and postposition in \ref{ex:jarmee} appear.
 I argue that \tsc{r}-pronouns are not something special, but a consequence of regular spellout mechanisms.
-Just like \citet{riemsdijk1978} I analyze \tsc{r}-pronouns and postpositions as a type of allomorph of the preposition and pronoun.
-The crucial difference in the current approach is that spellout rules out the ungrammaticality of the preposition and pronoun, and not the stipulation of a filter.
-
-This chapter is an in-depth study of the instrumental \tsc{r}-pronoun and postposition \tit{'r-mee} `with it' and \tit{waar-mee} `with what' in Dutch.
+Just like \citet{riemsdijk1978} I analyze an \tsc{r}-pronoun and postposition as a type of allomorph of the preposition and pronoun.
+The crucial difference in the current approach is that spellout rules out the ungrammaticality of the preposition and pronoun and not the stipulation of a filter.
+
+This paper is focuses on the instrumental \tsc{r}-pronoun and postposition \tit{'r-mee} `with it' and \tit{waar-mee} `with what' in Dutch.
 This instance is interesting for two reasons.
@@
 In many of the \tsc{r}-pronouns and postpositions, the meaning component of the locative is intuitive, as many prepositions express locations, directions etc.
-However, an instrumental expresses an instrument, which does not have a meaning component assosicated with location.
+However, an instrumental expresses an instrument, which does not have a meaning component associated with location.
 Ideally, an analysis treats the syncretism not as accidental but allows for the locative meaning to be absent.
@@
 The preposition \tit{met} `with' does not only turn into a postposition, but it also changes into \tit{-mee} `with' when it is combined with an \tsc{r}-pronoun.
-This last observervation has so far remained unexplained.
+This last observation has so far remained unexplained.
 
@@
 First, \tsc{r}-pronouns are syncretic with locatives.
-Second, regular pronouns appear with prepoositions, \tsc{r}-pronouns with postpositions.
+Second, regular pronouns appear with prepositions, \tsc{r}-pronouns with postpositions.
 Third, the instrumental preposition and postposition differ in form (\tit{met} vs.
@@
 
-The goal of this section is to show that \tsc{r}-pronouns and postpositions appear when all features that are to be spelled out form a proper constituent, i.e.
+The goal of this section is to show that \tsc{r}-pronouns and postpositions appear when all relevant features form a proper constituent, i.e.
 that all features form a constituent to the exclusion of any other features.
@@
 Then I show an exception, in which \tit{met wat} `with what` has to be used and \tit{waar-mee} `with what` cannot.
-I argue that the crucial difference between the exception and other cases is that in the exception the features do not form a proper constituent.
+I argue that the crucial difference between the exception and other cases is that in the exception the relevant features do not form a proper constituent.
 
@@
 
-In what follows I discuss the distribution of \tsc{r}-pronouns and regular pronouns in general \citep{riemsdijk1978,koopman2000}. I start with the personal pronouns and then return to the wh-pronouns.
-
-Dutch has the accusative personal pronouns \tit{haar} `her', \tit{hem} `him' and \tit{het} `it' that can be used as animate and inanimate objects of verbs, as illustrated in \ref{ex:objverb}.
+In what follows I discuss the distribution of \tsc{r}-pronouns and regular pronouns in general \citep{riemsdijk1978,koopman1994}. I start with the personal pronouns and then return to the wh-pronouns.
+
+Dutch has the accusative personal pronouns \tit{haar} `her', \tit{hem} `him' and \tit{'t} `it' that can be used as animate and inanimate objects of verbs, as illustrated in \ref{ex:objverb}.
 
@@
 
-The example in \ref{ex:prepani} shows that for animate objects the same pronouns (\tit{haar} `her' and \tit{hem} `him') appear as objects of prepositions.
-Repeating from the introduction, the inanimate personal pronoun \tit{het} `it' cannot be used as an object of a preposition, shown in \ref{ex:prephet}.
+Example \ref{ex:prepani} shows that for animate objects the same pronouns (\tit{haar} `her' and \tit{hem} `him') appear as objects of prepositions.
+Repeating from the introduction, the inanimate personal pronoun \tit{'t} `it' cannot be used as an object of a preposition, shown in \ref{ex:prephet}.
 Instead, an \tsc{r}-pronoun appears.
 This is illustrated in \ref{ex:preper}.
-\ref{ex:erprep} shows that the \tsc{r}-pronoun obligatorily has moved to the left of the adposition.
+\ref{ex:erprep} shows that the \tsc{r}-pronoun has moved obligatorily to the left of the adposition.
 
@@
 \tit{Met} is not the only preposition with which this happens.
-For example, \tit{op} `on' and \tit{in} `in' are two prepositions that also do not combine with the inanimate personal pronoun \tit{'t}, but the \tsc{r}-pronoun and postposition is used obligatorily.
+For example, \tit{op} `on' and \tit{in} `in' also do not combine with the inanimate personal pronoun \tit{'t}, but the \tsc{r}-pronoun and postposition are used obligatorily.
 
@@
   he swims it-in\\
-  `He is swimming in it.'
+  `He is swimming there it.'
  \bg. *Hij zwemt in 't.\\
@@
 the case requirements do not match).
-I give an example in which the \tsc{r}-pronoun and postposition appears before I get to the exception.
+I give an example in which the \tsc{r}-pronoun and postposition appear before I get to the exception.
 Consider \ref{ex:gekochtwaar-mee}.
 The predicate in the embedded clause, \tit{schildert} `paint', combines with an instrumental object.
-The predicate in the main clause clause, \tit{gekocht} `bought' combines with an accusative object.
+The predicate in the main clause, \tit{gekocht} `bought' combines with an accusative object.
 The \tsc{r}-pronoun and postposition \tit{waar-mee} `with what' is used here.
@@
 
-If the predicates are switched around between the clauses, the \tsc{r}-pronoun and postposition do not appear anymore.
+If the predicates are switched between the clauses, the \tsc{r}-pronoun and postposition do not appear anymore.
 In \ref{ex:schildermet}, \tit{schilder} `paint' combines with an instrumental object in the main clause and \tit{gekocht} `bought' combines with an accusative object in the embedded clause.
@@
 The two predicates I used in the free relatives are \tit{kopen} `to buy' and \tit{schilderen}  `to paint'.
-\tit{Kopen} `to buy' takes an accusative DP as its object, illustrated in \ref{ex:kopen}.
-\tit{Schilderen} `to paint' can take an instrumental as its object, shown in \ref{ex:schilderen}.\footnote{\tit{Schilderen} also optionally takes an (accusative) object, but I am focussing on the instrumental object here.}
+\tit{Kopen} `to buy' takes an accusative object, illustrated in \ref{ex:kopen}.
+\tit{Schilderen} `to paint' can take an instrumental as its object, shown in \ref{ex:schilderen}.\footnote{\tit{Schilderen} also optionally takes an (accusative) object, but I am focusing on the instrumental object here.}
 
@@
 
-Next, we arrive at the mismatching free relative in which \tit{waar-mee} `with what' cannot be used, but \tit{met wat} `with what' appears.
-The embedded clause predicate \tit{gekocht} `bought' combines with an accusative DP.
+Next, I arrive at the mismatching free relative in which \tit{waar-mee} `with what' cannot be used, but \tit{met wat} `with what' appears.
+The embedded clause predicate \tit{gekocht} `bought' combines with an accusative object.
 The accusative object of a verb is always \tit{wat} `what', as I showed in \ref{ex:wat}.
@@
 I give examples of two more occurrences in \ref{ex:moremetwat}.
-In \ref{ex:watindef}, \tit{wat} `what' is the \tit{wat} `what' in the so-called \tit{wat voor} `what for'-construction \citep[cf.][]{corver1991}.
+In \ref{ex:watwasfur}, \tit{wat} `what' is the \tit{wat} `what' in the so-called \tit{wat voor} `what for'-construction \citep[cf.][]{corver1991}.
  In \ref{ex:watindef}, \tit{wat} appears as a quantifier, and it means `some'.
@@
 It always becomes \tit{waar-mee} `with what', as shown in \ref{ex:waar-meefr}.
+\tit{Met wat} `with what' can appear when the instrumental object does not form a proper constituent.
+This can be either when \tit{wat} `what' takes a complement before it combines with \tit{met} `with', as shown in \ref{ex:metwatx}, representing the examples in \ref{ex:moremetwat}.
+The other option is that \tit{wat} `what' is part of the a clause that \tit{met} `with' is not a part of, schematized as \ref{ex:metwatfr} as an illustration of \ref{ex:mismatchmetwat}.
 
@@
 
-\tit{Met wat} `with what' can appear when the instrumental object does not form a proper constituent.
-This can be either when \tit{wat} `what' takes a complement before it combines with \tit{met} `with', as shown in \ref{ex:metwatx}, representing the examples in \ref{ex:moremetwat}.
-The other option is that \tit{wat} `what' is part of the a clause that \tit{met} `with' is not a part of, schematitized as \ref{ex:metwatfr} as an illustration of \ref{ex:mismatchmetwat}.
-
 \section{Decomposing \tit{waar-mee} and \tit{met wat}}\label{sec:takingapart}
 
-In this section I decompose \tit{waar-mee} `with what' and \tit{met wat} `met wat' into smaller units, and I connect them to parts of syntactic structure.
-Both spell out the same set of features but the distribution is different.
+In this section I decompose \tit{waar-mee} `with what' and \tit{met wat} `met wat' into smaller units, which I connect to parts of syntactic structure.
+\tit{Waar-mee} `with what' and \tit{met wat} `met wat' spell out the same set of features but the distribution is different.
 I decompose \tit{waar-mee} and \tit{met wat} as I show in \ref{ex:decompose}.
 Earlier works have decomposed these pronouns in similar ways (cf.
-\citet{hachem2015,noonan2017dutch,wesseling2018}).
+\citealt{hachem2015,noonan2017dutch,wesseling2018}).
 
@@
 
-Let me start with the morphemes \tit{w} and \tit{a} that appear in both expressions.
-I assume that they correspond to the same syntactic structure in both \tit{waar-mee} `with what' and \tit{met wat} `with what'.
-As I am interested in the differencs between the two expression, I do not discuss the featural content of \tit{w} and \tit{a} into depth.
+Let me start with the morphemes \tit{w} and \tit{a} that appear in both \tit{waar-mee} `with what' and \tit{met wat} `met wat'.
+I assume that they correspond to the same syntactic structure in both.
+As I am interested in the differences between the two expressions, I do not discuss the featural content of \tit{w} and \tit{a} into depth.
 
@@
 I follow several authors (cf.
-\citealt{lander2016,noonan2017dutch,wesseling2018}) in assuming the morpheme \tit{a} to be related to deixis.
-Dutch distinguishes between proximal by using \tit{ie} (/i:/) and \tit{i} (/ɪ/) and distal by using \tit{aa} (/aː/) and \tit{a} (/ɑ/), illustrated in \ref{ex:deixis}.\footnote{A question that remains open is why wh-elements only combine with the distal marker \tit{a}, and not with proximal marker \tit{i/ie}.} I analyze the transformation from /ɪ/ into /i:/ and /ɑ/ into /aː/ as a result of the final r.
+\citealt{lander2016,noonan2017dutch,wesseling2018}) that assume the morpheme \tit{a} is related to deixis.
+Dutch distinguishes between proximal by using \tit{ie} (/i:/) and \tit{i} (/ɪ/) and distal by using \tit{aa} (/aː/) and \tit{a} (/ɑ/), illustrated in \ref{ex:deixis}.\footnote{A question that remains open is why wh-elements combine with the distal marker \tit{a}, and they cannot with the proximal marker \tit{i/ie}.} I analyze the transformation from /ɪ/ into /i:/ and /ɑ/ into /aː/ as a result of the final r.
 
@@
 
-For the purpose of this paper I simply let \tit{a} correspond to \tsc{deixP}.
+For the purpose of this paper I let \tit{a} correspond to \tsc{deixP}.
 
@@
 
-For case, I follow \citet{caha2009} that case features are organized as in the containment relation in \ref{ex:casetree}.
-The higher, more complex cases contain the smaller, less complex cases.\footnote{I follow \citet{starke2017} in that there are two types of accusatives and datives.
-In this paper I only include the S-\tsc{acc} and S-\tsc{dat}, which are placed below the \tsc{gen}.}
+For case, I follow \citet{caha2009} in that case features are organized as in the containment relation in \ref{ex:casetree}.
+The higher, more complex cases contain the smaller, less complex cases.
+For the purpose of this paper, I only show case features relevant for the argument.
 
@@
  \begin{forest} boom
- [\tsc{comP}
-     [\tsc{f6}]
  [\tsc{insP}
-         [\tsc{f5}]
-         [\tsc{genP}
      [\tsc{f4}]
@@
                  [DP
-                             [...,roof]
-                         ]
-                     ]
+                     [..,roof]
                  ]
@@
 
+\ref{ex:entryt} shows the lexical entry for \tit{'t} `it'.
 I assume that the \tit{'t} contains the ontological category \tsc{thing} \citep{kayne2005}.
 The feature Σ indicates that the pronoun is a weak pronoun.
-I leave possible number and gender features out because they do not play a role in this paper.
+For reasons of space I let singular be the absence of number and neuter the absence of gender.
 The morpheme \tit{'t} can act as nominative, accusative and dative, as I showed in \ref{ex:tsubobj}.\footnote{ Another possibility is to claim that \tit{'t} can only spell out \tsc{thing} and Σ and it combines with a zero suffix for the cases up to dative.
@@
 
-The proposed account fares equally well with both alternatives.
-I work the proposal out with \tit{'t} realizing the cases up to the dative.} Taking this all together, \tit{'t} has the lexical entry given in \ref{ex:entryt}.
+The proposed account fares equally well with both alternatives. I work the proposal out with \tit{'t} realizing the cases up to the dative.}
 
@@
 
- This lexical entry can lexicalize the \tsc{datP}, but also the \tsc{accP} and \tsc{nomP}. This is due to the Superset Princple.
+ This lexical entry can lexicalize the \tsc{datP}, but also the \tsc{accP} and \tsc{nomP}. This is due to the Superset Principle.
 
@@
 
- \exg. Ik ben er al geweest.\\
+ \exg. Ik ben 'r al geweest.\\
   I am there already been\\
@@
 
-Notice already here that, via the superset principle, \tit{'r} can be used to realize the feature \tsc{thing} as well, as it is contained in \tsc{locP}.
+Notice here that, via the Superset Principle, \tit{'r} can be used to realize the feature \tsc{thing} as well, as it is contained in \tsc{locP}.
 Moreover, in a syntactic structure like in \ref{ex:rthing} the lexical entry \ref{ex:entryr} will be inserted and not \ref{ex:entryt}.
@@
 
-What this means is that the base form of the neuter singular pronoun in Dutch is actually \tit{'r} and \tit{'t} should be analyzed as a suppletive nominative, accusative and dative.
+This means that the caseless base form of the neuter singular pronoun in Dutch is actually \tit{'r} and \tit{'t} should be analyzed as a suppletive nominative, accusative and dative.
 The base form only shows up in the higher cases, from instrumental on, see Table \ref{tbl:dutchcases}.
@@
     \tsc{dat} & 't         \\
-    \tsc{gen} & 'r-van     \\
     \tsc{ins} & -r -mee    \\
@@
 
-A similar situation appears in Iron Ossetic, shown in \ref{tbl:ossetic}.
+A similar situation appears in Iron Ossetic, shown in Table \ref{tbl:ossetic}.
 In the first person singular of this language, it is only the nominative that is suppletive: \tit{æz}.
@@
     \tsc{dat} & mæn-æn      & sær-æn  \\
-    \tsc{gen} & mæn (??)    & sær-y   \\
     \tsc{ins} & mæn-æj      & sær-æj  \\
@@
 horse-\tsc{pl} and ox-\tsc{pl-com}\\
-`with horses and oxen' \hfill (Iron Ossetic, \citep[165]{erschler2012})\label{ex:horseoxone}
+`with horses and oxen' \hfill (Iron Ossetic, \citealt[165]{erschler2012})\label{ex:horseoxone}
 
@@
  1.\tbf{sg} and Zaur-\tsc{dat}\\
- `me and Zaur' \hfill (\citealt[39]{беляев2014} after \citealt{caha2019competition})\label{ex:izaurone}
-
-The point of showing the Ossetic example is that Dutch is not unique in having suppletive forms that are less marked (in this case nominative, accusative and dative), and higher cases that are a combination of a suffix and a base form.
+ `me and Zaur' \hfill (Iron Ossetic, \citealt[39]{беляев2014} after \citealt{caha2019competition})\label{ex:izaurone}
+
+The point of showing the Ossetic example is that Dutch is not unique in having suppletive forms that are less marked (in this case nominative, accusative and dative), and higher cases that are a combination of a suffix and a caseless base form.
 
@@
 I will analyze \tit{-mee} as a postposition and \tit{met} as a preposition.\footnote{A topic related to this paper is the different positioning of identical adpositions in Dutch (see \citet{caha2010} for an account of German and Dutch and \citet{pretorius2017} for Afrikaans).
-In \ref{ex:dutchin}, \tit{in} changes meaning dependening on whether it proceeds or follows the DP, it is respectively locational or directional.
+In \ref{ex:dutchin}, \tit{in} `in' changes meaning depending on whether it proceeds or follows the DP, it is respectively locational or directional.
 
@@
 \a. If the expression of a particular case in the case sequence (below) involves a preposition, then all cases to its right do as well.
-\b. The Case sequence: \tsc{nom – acc – dat – gen - ins – com} \hfill \citep{caha2009}
-
-The result of that is that a PP can contain a preposition and a suffix, as in \ref{ex:loffel}. The dative suffix is used with a genitive preposition.
-
-\exg. (die Farbe) von ein -em Löffel\\
-the color of a -\tsc{dat.sg} spoon\\
-`(the color) of a spoon' \hfill (German)\label{ex:loffel}
-
-With the case hierarchy in Nanosyntax this can be modeled by letting the DP move as high as above the \tsc{datP} in the syntactic structure.
+\b. The case sequence: \tsc{nom – acc – dat – gen - ins – com} \hfill \citep{caha2009}
+
+The result of that is that a PP can contain a preposition and a suffix. In the German example in \ref{ex:loffel}, the dative suffix is used with a instrumental preposition.
+
+\exg. mit ein -em Löffel\\
+with a -\tsc{dat.sg} spoon\\
+`with a spoon' \hfill (German)\label{ex:loffel}
+
+With the case hierarchy in Nanosyntax this can be modeled by letting the DP move as high as above the \tsc{datP} in the syntactic structure in \ref{ex:casetree}.
 The features below the \tsc{datP} are realized as a suffix, and the features above \tsc{datP} are realized as a preposition.
@@
 There is variation with respect to how high a DP can move in the structure, both between languages and within languages.
-An example from the latter comes from Bulgarian.
+An example of the latter comes from Bulgarian.
 \ref{ex:bulpron} shows that pronouns can take the suffix \tit{-i} to realize dative, but full DPs need a preposition \tit{na} `to'.
@@
 that word is unfamiliar to son my\\
-`That word is unfamiliar to my son.'\label{ex:buldpto} \hfill \citep[39]{caha2009}
+`That word is unfamiliar to my son.'\label{ex:buldpto} \hfill (Bulgarian, \citealt[39]{caha2009})
 
@@
 To be more precise, the inanimate \tit{'t} is replaced by \tit{'r}, and this element can move as high as above the dative to combine with \tit{-mee}.
-Later I return to what it is that prevents animates and full DPs from being combined with \tit{-mee}.
-
-First I show to is what the lexical entry of \tit{-mee} looks like.
-This needs to capture three facts.
-\tit{-mee} combines with \tit{'r}, and it is a postposition.
-First, \tit{-mee} expresses instrumental (and comitative) case and it combines with \tit{'r}.\footnote{For reasons of space I leave \tsc{f6} out of the lexical entries and discussion, even though \tit{-mee} and \tit{met} can also express comitative.}
-So far, \tit{'r} `there' only realizes the feature \tsc{thing}. This leaves Σ and \tsc{f1} to \tsc{f5} to be realized by \tit{-mee}. I give the lexical tree of \tit{-mee} in \ref{ex:entrymee}.
-
-\ex. \begin{forest} boom
-    [\tsc{insP}
-        [\tsc{f6}]
-        [\tsc{genP}
-            [\tsc{f4}]
-            [\tsc{datP}
-                [\tsc{f3}]
-                [\tsc{accP}
-                    [\tsc{f2}]
-                    [\tsc{nomP}
-                        [\tsc{f1}]
-                        [ΣP
-                            [Σ]
-                        ]
-                    ]
-                ]
-            ]
-        ]
-    ]
-{\draw (.east) node[right]{⇔ \tit{-mee}}; }
-\end{forest}\label{ex:entrymee}
-
-This leads us to the second point: \tit{-mee} is a postposition.
-Notice that the foot of the structure has a singleton feature.
-Nanosyntax distinguishes pre-elements from post-elements by the shape of their lexical entry \citep{starke2018}.
-As a result, the whether an element is pre or post is lexically stored as follows from the spellout procedure.
-I illustrate this in Section \ref{sec:derivation}.
-Post-elements have a unary bottom (i.e.
-the foot of the tree is a single feature), so they can only appear as the result of movement.
-Post-elements have a binary bottom (i.e.
-the foot of the tree consists of two features), so they cannot be a candidate as a result of movement.
-
-Why does \tit{-mee} not combine with animates and full DPs?
-I claim that has to do with the bottom feature of the lexical entry of \tit{-mee}.
-Full DPs do not take features related to pronominal strength.
-According to the Superset Principle, a lexical tree can also match a syntactic tree with a subpart of the features, but a tree can only shrink from the top, so \tit{-mee} will always realize Σ.
-I have a less clear answer to why animates do not combine with \tit{-mee}.
-The crucial difference between animates and inanimates if gender features.
-For now I assume that gender features are situated between Σ and \tsc{f1}.
-The lexical entry of \tit{-mee} includes both these features, so any features are incompatible with \tit{-mee}.
-So far I do not have independent evidence for placing gender features between features of pronominal strength and case, and I leave this for future research.
-
-So far I discussed \tit{-mee} is a postposition, which follows \tit{'r} and is stored with a unary bottom.
-\tit{Met}, on the other hand, is a preposition, it precedes \tit{'t}, so it should be stored with a binary bottom.
-The highest case feature \tit{'t} can realize is \tsc{f3}, so the preposition realizes all higher cases up to \tsc{f5}.
-I give the lexical entry for \tit{met} in \ref{ex:entrymet}.
-
-\ex. \begin{forest} boom
-[\tsc{insP}
-    [\tsc{f5}]
-    [\tsc{f4}]
-]
-{\draw (.east) node[right]{⇔ \tit{met}}; }
-\end{forest}\label{ex:entrymet}
-
-In the next section I put all features back together in a derivation and I show how \tit{waar-mee} `with what' surfaces when all features form a constituent.
-\tit{Met wat} `with what' appears when the functional sequence is disrupted.
-
-\section{In a derivation}\label{sec:derivation}
-
-Before I show that \tit{waar-mee} `with what' is used when all features form a proper constituent, I need to make some assumptions about the spellout process in Nanosyntax explicit.
-Spellout happens in a cyclic derivation, following a spellout algorithm \citep{starke2018}.
-After each instance of merge, spellout takes place.
-If no spellout exists for the phrase created by the newly added feature, evacuation movements specified in the spellout algorithm take place.
-The algorithm is given in \ref{ex:spellout}.
-
-\ex. Merge F and \label{ex:spellout}
- \a. Spell out FP.
- \b. If (a) fails, attempt movement of the spec of the complement of \tsc{f}, and retry (a).
- \b. If (b) fails, move the complement of \tsc{f}, and retry (a).
-
-When a new match is found, it overrides previous spellouts.
-
-\ex. Cyclic Override \citep{starke2018}:\\
-Lexicalisation at a node XP overrides any previous match at a phrase contained in XP.
-
-If the spellout procedure in \ref{ex:spellout} fails, backtracking takes place.
-This is a crucial operation to get from the suppletive nominative, accusative and dative \tit{'t} to the base form \tit{'r}.
-
-\ex. Backtracking \citep{starke2018}:\\
-When spellout fails, go back to the previous cycle, and try the next option for that cycle.\label{ex:backtracking}
-
-If backtracking also does not help, a specifier is constructed. This is what happens when the preposition \tit{met} is inserted.
-
-\ex. Spec Formation \citep{starke2018}:\\
-If Merge F has failed to spell out (even after backtracking), try to spawn a new derivation providing the feature F and merge that with the current derivation, projecting the feature F at the top node.\label{ex:specformation}
-
-With this theoretical background in place, we can turn to the derivation.
-I first show how \tit{'rmee} `with it' is constructed.
-I leave out \tit{w} and \tit{a}, because it unnecessarily complicates the story.\footnote{I assume that the \tsc{wP} and \tsc{deixP} appear lower in the structure than the case features, so the functional sequence is as given in \ref{ex:fseq}.
-
-\ex. [ [ [ [ [ [ [ \tsc{thing} ] \tsc{deix} ] W ] \tsc{f1} ] \tsc{f2} ] \tsc{f3} ] \tsc{f4} ]\label{ex:fseq}
-\z.
-
-\phantom{x}
-
-}
-
-We start with \tsc{thing}.
-The two candidates here are \ref{ex:entryt} and \ref{ex:entryr}.
-Following the Elsewhere Condition, \ref{ex:entryr} wins the competition because it contains less unused material.
-
-\ex.
-\begin{forest} boom
- [\tsc{thingP}
-     [\tsc{thing}, roof]
- ]
-{\draw (.east) node[right]{⇒ \tit{'r}}; }
-\end{forest}\label{ex:thingspellout}
-
-In the next step, Σ is merged.
-\ref{ex:entryr} is no longer a candidate because it does not contain Σ.
-\ref{ex:entryt} still is a candidate, because it contains all features in \ref{ex:thingf1}.
-The spellout is overridden and the structure is realized as \tit{'t}.
-
-\ex. \begin{forest} boom
-[ΣP
-   [Σ]
-   [\tsc{thingP}
-       [\tsc{thing}, roof]
-   ]
-]
-{\draw (.east) node[right]{⇒ \tit{'t}}; }
-\end{forest}\label{ex:thingf1}
-
-Then \tsc{f1} is merged. This structure can still be realized by \tit{'t}.
-
-\ex. \begin{forest} boom
-[\tsc{nomP}
-   [\tsc{f1}]
-   [ΣP
-       [Σ]
-       [\tsc{thingP}
-           [\tsc{thing}, roof]
-       ]
-   ]
-]
-{\draw (.east) node[right]{⇒ \tit{'t}}; }
-\end{forest}
-
-The same holds for the next two steps in which \tsc{f2} and \tsc{f3} are merged: the structure can still be spelled out as \tit{'t}.
-
-\ex. \begin{forest} boom
-[\tsc{datP}
-    [\tsc{f3}]
-    [\tsc{accP}
-       [\tsc{f2}]
-       [\tsc{nomP}
-           [\tsc{f1}]
-           [ΣP
-               [Σ]
-               [\tsc{thingP}
-                   [\tsc{thing}, roof]
-               ]
-           ]
-       ]
-    ]
-]
-{\draw (.east) node[right]{⇒ \tit{'t}}; }
-\end{forest}
-
-Then \tsc{f4} is merged, as shown in \ref{ex:f4no}.
-\ref{ex:entryt} can no longer spell out the structure, because it does not contain \tsc{f4}.
-There is also no other candidate to spell out the structure as it is.
+I return to what it is that prevents animates and full DPs from being combined with \tit{-mee} shortly.
+
+First I show what the lexical entry of \tit{-mee} looks like.
+Two facts need to be captured.
+\tit{-mee} combines with \tit{'r} and is a postposition.
+First, \tit{-mee} expresses instrumental (and comitative) case and it combines with \tit{'r}.\footnote{For reasons of space I leave \tsc{comP} out of the lexical entries and discussion, even though \tit{-mee} `with' and \tit{met} `with' can also express comitative.}
+This means that the combination of \tit{'r} and \tit{-mee} has to realize \tsc{thing}, Σ and all case features up to \tsc{f4}.
+So far, \tit{'r} `there' only realizes the feature \tsc{thing}.
+This leaves Σ and \tsc{f1} to \tsc{f4} to be realized by \tit{-mee}.
+I give the lexical tree of \tit{-mee} in \ref{ex:entrymee}.
 
@@
                     [Σ]
+                ]
+            ]
+        ]
+    ]
+]
+{\draw (.east) node[right]{⇔ \tit{-mee}}; }
+\end{forest}\label{ex:entrymee}
+
+This leads me to the second point: \tit{-mee} is a postposition.
+Notice that the foot of the structure has a singleton feature.
+Nanosyntax distinguishes pre-elements from post-elements by the shape of their lexical entry \citep{starke2018}.
+As a result, it follows from the spellout procedure whether an element appears before or after the previously inserted element.
+Post-elements have a unary bottom (i.e.
+the foot of the tree is a single feature), so they can only appear as the result of movement.
+Post-elements have a binary bottom (i.e.
+the foot of the tree consists of two features), so they cannot be a candidate as a result of movement.
+I illustrate this in Section \ref{sec:derivation}.
+
+Why does \tit{-mee} not combine with animates and full DPs?
+I claim that has to do with the bottom feature of the lexical entry of \tit{-mee}.
+Full DPs do not take features related to pronominal strength.
+According to the Superset Principle, a lexical tree can match a syntactic tree with a subpart of the features, but a tree can only shrink from the top, so \tit{-mee} will always realize Σ.
+It is less clear to me why animates do not combine with \tit{-mee}.
+The crucial difference between animates and inanimates if gender features.
+For now I assume that gender features are situated between Σ and \tsc{f1}.
+The lexical entry of \tit{-mee} includes both these features, so any additional gender features are incompatible with \tit{-mee}.
+So far I do not have independent evidence for placing gender features between features of pronominal strength and case, and I leave this for future research.
+
+So far I discussed \tit{-mee} is a postposition, which follows \tit{'r} and is stored with a unary bottom.
+\tit{Met}, on the other hand, is a preposition, it precedes \tit{'t}, so it should be stored with a binary bottom.
+The highest case feature \tit{'t} can realize is \tsc{f3}, so the preposition realizes \tsc{f4}.
+I give the lexical entry for \tit{met} in \ref{ex:entrymet}.
+
+\ex. \begin{forest} boom
+[\tsc{insP}
+    [\tsc{f4},roof]
+]
+{\draw (.east) node[right]{⇔ \tit{met}}; }
+\end{forest}\label{ex:entrymet}
+
+In the next section I put all features back together in a derivation and I show how \tit{waar-mee} `with what' and not \tit{met wat} `with what' surfaces when all features form a constituent.
+
+\section{In a derivation}\label{sec:derivation}
+
+Before I show that \tit{waar-mee} `with what' is used when all features form a proper constituent, I need to make some assumptions about the spellout procedure in Nanosyntax explicit.
+Spellout happens in a cyclic derivation, following a spellout algorithm \citep{starke2018}.
+After each instance of merge, spellout takes place.
+If no spellout exists for the phrase created by the newly added feature, evacuation movements specified in the spellout algorithm take place.
+The algorithm is given in \ref{ex:spellout}.
+
+\ex. Merge F and \label{ex:spellout}
+ \a. Spell out FP.
+ \b. If (a) fails, attempt movement of the spec of the complement of \tsc{f}, and retry (a).
+ \b. If (b) fails, move the complement of \tsc{f}, and retry (a).
+
+When a new match is found, it overrides previous spellouts.
+
+\ex. Cyclic Override \citep{starke2018}:\\
+Lexicalisation at a node XP overrides any previous match at a phrase contained in XP.
+
+If the spellout procedure in \ref{ex:spellout} fails, backtracking takes place.
+This is the operation that leads from the suppletive nominative, accusative and dative \tit{'t} to the base form \tit{'r}.
+
+\ex. Backtracking \citep{starke2018}:\\
+When spellout fails, go back to the previous cycle, and try the next option for that cycle.\label{ex:backtracking}
+
+If backtracking also does not help, a specifier is constructed. This is what happens when the preposition \tit{met} `with' is inserted.
+
+\ex. Spec Formation \citep{starke2018}:\\
+If Merge F has failed to spell out (even after backtracking), try to spawn a new derivation providing the feature F and merge that with the current derivation, projecting the feature F at the top node.\label{ex:specformation}
+
+With this theoretical background in place, I can turn to the derivation.
+I first show how \tit{'rmee} `with it' is constructed.
+I leave out \tit{w} and \tit{a} to not unnecessarily complicate the story.\footnote{I assume that the \tsc{wP} and \tsc{deixP} appear lower in the structure than the case features, so the functional sequence is as given in \ref{ex:fseq}.
+
+\ex. [ [ [ [ [ [ [ \tsc{thing} ] \tsc{deix} ] W ] \tsc{f1} ] \tsc{f2} ] \tsc{f3} ] \tsc{f4} ]\label{ex:fseq}
+\z.
+
+\phantom{x}
+
+}
+
+I start with \tsc{thing}.
+The two candidates here are \ref{ex:entryt} and \ref{ex:entryr}.
+Following the Elsewhere Condition, \ref{ex:entryr} wins the competition because it contains less unused material.
+
+\ex.
+\begin{forest} boom
+ [\tsc{thingP}
+     [\tsc{thing}, roof]
+ ]
+{\draw (.east) node[right]{⇒ \tit{'r}}; }
+\end{forest}\label{ex:thingspellout}
+
+In the next step, Σ is merged.
+\ref{ex:entryr} is no longer a candidate because it does not contain Σ.
+\ref{ex:entryt} still is a candidate, because it contains all features in \ref{ex:thingf1}.
+The spellout is overridden and the structure is realized as \tit{'t}.
+
+\ex. \begin{forest} boom
+[ΣP
+   [Σ]
+   [\tsc{thingP}
+       [\tsc{thing}, roof]
+   ]
+]
+{\draw (.east) node[right]{⇒ \tit{'t}}; }
+\end{forest}\label{ex:thingf1}
+
+Then \tsc{f1} is merged. This structure can still be realized by \tit{'t}.
+
+\ex. \begin{forest} boom
+[\tsc{nomP}
+   [\tsc{f1}]
+   [ΣP
+       [Σ]
+       [\tsc{thingP}
+           [\tsc{thing}, roof]
+       ]
+   ]
+]
+{\draw (.east) node[right]{⇒ \tit{'t}}; }
+\end{forest}
+
+The same holds for the next two steps in which \tsc{f2} and \tsc{f3} are merged: the structure can still be spelled out as \tit{'t}.
+
+\ex. \begin{forest} boom
+[\tsc{datP}
+    [\tsc{f3}]
+    [\tsc{accP}
+       [\tsc{f2}]
+       [\tsc{nomP}
+           [\tsc{f1}]
+           [ΣP
+               [Σ]
+               [\tsc{thingP}
+                   [\tsc{thing}, roof]
+               ]
+           ]
+       ]
+    ]
+]
+{\draw (.east) node[right]{⇒ \tit{'t}}; }
+\end{forest}
+
+Then \tsc{f4} is merged, as shown in \ref{ex:f4no}.
+\ref{ex:entryt} can no longer spell out the structure, because it does not contain \tsc{f4}.
+There is also no other candidate to spell out the structure as it is.
+
+\ex. \begin{forest} boom
+[\tsc{insP}
+    [\tsc{f4}]
+    [\tsc{datP}
+        [\tsc{f3}]
+        [\tsc{accP}
+           [\tsc{f2}]
+           [\tsc{nomP}
+               [\tsc{f1}]
+               [ΣP
+                   [Σ]
                    [\tsc{thingP}
@@
 
-According to the spellout algorithm in \ref{ex:spellout}, it should be attempted to move of the spec of the complement of \tsc{f4}.
+According to the spellout algorithm in \ref{ex:spellout}, it should be attempted to move the spec of the complement of \tsc{f4}.
 However, there is no specifier in \ref{ex:f4no}, so this does not apply.
@@
 
-As I formulated in the introduction of this section, the operation called Backtracking is triggered (see \ref{ex:backtracking}).
+As I formulated in the introduction of this section, the operation called backtracking is triggered (see \ref{ex:backtracking}).
 This means that the derivation goes back to the previous cycle, and the next option for that cycle is tried.
@@
 At this stage, \tsc{thing} was realized as \tit{'r}.
-Again there was no specifier, no spec-to-spec movement does not apply.
-However, complement movement provides a structure that is a match for the lexical entry in \ref{ex:entrymee}: \tit{-mee}.\footnote{This picture resembles the proposal of \citep{abels2003diss} in that not the whole complement of P is moves but only a part is extracted.
+Again there was no specifier, spec-to-spec movement does not apply.
+However, complement movement provides a structure that is a match for the lexical entry in \ref{ex:entrymee}: \tit{-mee}.\footnote{This picture resembles the proposal of \citep{abels2003diss} in that not the whole complement of P is moved but only a part is subextracted.
 The current analysis differs in that the movement is not syntactically driven but by spellout.}
@@
 
-Following the spellout algorithm, the next step is spec-to-spec movement is tried. The result is shown in \ref{ex:f1spec}. In that configuration \tsc{f1} can be realized together with Σ as \tit{-mee}.
+Following the spellout algorithm, the next step is spec-to-spec movement. The result is shown in \ref{ex:f1spec}. In that configuration \tsc{f1} can be realized together with Σ as \tit{-mee}.
 
@@
 I skip over the details of how \tit{w} and \tit{a} end up in their positions.\footnote{I assume that \tsc{wP} and \tsc{deixP} are both complex specifiers that are created after \tsc{thing} is spelled out in \ref{ex:thingspellout}.
-After each instance of merge after that, backtracking takes place, the complex specifier is detached from the structure and the case features are spelled out together with or as a postposition on \tsc{thing}.} The final result of the structure for \tit{waar-mee} `with what' look as in \ref{ex:spelloutwaar-mee}.
+After each instance of merge after that, backtracking takes place, the complex specifier is detached from the structure and the case features are spelled out together with \tsc{thing} or as the postposition -\tit{mee}.} The final result of the structure for \tit{waar-mee} `with what' look as in \ref{ex:spelloutwaar-mee}.
 
@@
 
-A consequence of analyzing \tit{-mee} `with' as a postposition is that \tit{r} and \tit{-mee} always form a constituent to the exclusion of \tit{w} and \tit{a}.
-At first sight this seems problematic, because it is possible for \tit{waar} `where', stranding \tit{-mee} `with'.
+A consequence of analyzing \tit{-mee} `with' as a postposition is that \tit{'r} and \tit{-mee} always form a constituent to the exclusion of \tit{w} and \tit{a}.
+At first sight this seems problematic, because it is possible for \tit{waar} `where' to \tit{-mee} `with'.
 I repeat the relevant example in \ref{ex:meestranded}.
@@
 
-There is no constituent in \ref{ex:spelloutwaar-mee} that contains \tit{waar} but not \tit{-mee}.
-To resolve this situation I follow \citet{noonan2017dutch} in assuming that the phrase containing the adposition (here \tit{-mee}) can syntactically move to a position higher in the structure.
+There is no constituent in \ref{ex:spelloutwaar-mee} that contains \tit{waar} but not \tit{-mee}, so it is not possible to move \tit{waar} from \ref{ex:spelloutwaar-mee} and strand \tit{mee} in the process.
+To resolve this situation I follow \citet{noonan2017dutch} in assuming that the phrase containing the adposition (\tit{-mee}) can syntactically move to a position higher in the structure.
 Evidence that \tit{mee} `with' has moved comes from the ungrammaticality of \ref{ex:meeend}.
-This shows that \tit{mee} `with' cannot be stranded in its base position (see \ref{ex:const3stage}).
+This shows that \tit{mee} `with' cannot be stranded in its base position (see also \ref{ex:const3stage}).
 
@@
 The movement of the adposition has the typical distribution of that of verbal particles (cf.
-\citealt{riemsdijk1978,noonan2017dutch}, and it could possibly be triggered by the feature Σ (which is contained in \tit{mee} `with`), associated with weak pronouns.
+\citealt{riemsdijk1978,noonan2017dutch}.
+The trigger for the movement of \tit{mee} could be the feature Σ (which is contained in \tit{mee} `with`), associated with weak pronouns.
+Allowing \tit{mee} to subextract from the \tsc{w}P resolves the issue.
 With \tit{-mee} having moved out, the \tsc{wP} only contains features that are realized as \tit{waar}, and it moves to the left edge of the clause, resulting in the surface order in \ref{ex:meestranded}.
@@
 
-I start at the point on which \tit{wat} `what' is part of a syntactic structure with the rest of a relative clause as a sister.
+I start at the point at which \tit{wat} `what' is part of a syntactic structure with the rest of a relative clause as a sister.
 Even though \tsc{f3} is not part of the embedded clause, I already added it to the structure.
-While it is unclear why, syncretic forms seem to behave differently in that they seem to resolve case conflicts in free relatives and related phenomena (cf.
+While it is unclear why, syncretic forms behave differently in that they seem to resolve case conflicts in free relatives and related phenomena (cf.
 \citealt{groos1981,pullum1986,ingria1990}).
-I give the syntactic structure from which are start in \ref{ex:metwatst}.
+I give the syntactic structure from which I start in \ref{ex:metwatst}.
 
@@
     [CP
-        [...,roof]
+        [..,roof]
     ]
@@
 \ex. \begin{forest} boom
-[\tsc{genP}
+[\tsc{insP}
     [\tsc{f4}]
@@
         [CP
-            [...,roof]
+            [..,roof]
         ]
@@
     [\tsc{insP}
-        [\tsc{f5}]
-        [\tsc{f4}]
+        [\tsc{f4},roof]
     ]
@@
 
-This section showed how the instrumental inanimate relative pronoun is realized as \tit{waar-mee} `with what' when all syntactic features form a constituent.
-It also showed how \tit{met wat} `with what' appears when all features do not form a proper constituent, and other features intervene.
+This section showed how the instrumental inanimate relative pronoun is realized as \tit{waar-mee} `with what' when all relevant features form a constituent, and how \tit{met wat} `with what' appears when they do not.
 
@@
 In this paper, I discussed the instrumental \tsc{r}-pronoun and postposition \tit{waar-mee} `with what' in Dutch.
-The main intuition is that this form that appears when features of an instrumental inanimate object form a proper constituent.
-The form cannot appear, and \tit{met wat} `with what` surfaces instead, when all features do not form a proper constituent.
+The main intuition is that this form appears when features of an instrumental inanimate object form a proper constituent.
+The form cannot appear, and \tit{met wat} `with what` surfaces instead, when all relevant features do not form a proper constituent.
 The described pattern follows from a core assumption in Nanosyntax: phrasal spellout spells out constituents \citep{starke2009}.
-The distribution of \tit{r}-pronouns and postpositions and prepositions and pronouns follows from regular spellout mechanisms.
 
 Under this analysis, there is no need for a filter that rules out a combination of a preposition and an inanimate pronoun.
-As long as the to be spelled out features form a proper constituent, the spellout algorithm ensures the \tsc{r}-pronoun and postposition takes precedence over the other form.
-The fact that locatives are syncretic with \tsc{r}-pronouns is not a coincidence as well.
+As long as the relevant features form a proper constituent, the spellout algorithm ensures the \tsc{r}-pronoun and postposition takes precedence over the other form.
+The fact that locatives are syncretic with \tsc{r}-pronouns is not a coincidence.
 The lexicon contains a single entry for a locative, which is the one used for \tsc{r}-pronouns as well.
@@
 In all other cases the adposition does not change form when it combines with an \tsc{r}-pronoun, e.g.
-\tit{in}.
+\tit{in} `in'.
 If this proposal is on the right track, elements as \tit{in} can be used as either a preposition or as a postposition.
-The lexical entry should then be usable as pre-element and as post-element, so it needs to have a binary bottom and a unary foot at the same time.
+The lexical entry should then be usable as pre-element and as post-element, so it needs to have a binary bottom and a unary foot simultaneously.
 The lexical entry in \ref{ex:presuf} would be a candidate for such an element.
-YP can be inserted as a post-element, and XP can be inserted via the Superset Princple as a pre-element.
+YP can be inserted as a post-element, and XP can be inserted via the Superset Principle as a pre-element.
 
@@
 
-I leave it to future research to determine whether this is a feasible solution.
+I leave it to future research to investigate such a proposal.
 

### 2020-01-20 paper.tex
comments on bulgarian
maybe not that different after all

@@
 
+%%no complementary distribution in Bulgarian! So different! Nelli =b-example
+
 \ex.\label{ex:bulgarian}
 \ag. Tazi duma m -i e nepoznata.\\
-that word I -\tsc{dat} is unfamiliar\\
+that word I -\tsc{acc/dat.cl} is unfamiliar\\
 `That word is unfamiliar to me.'\label{ex:bulpron}
+\bg. Tazi duma e nepoznata na m -en.\\
+that word is unfamiliar to me -\tsc{acc/dat.full}\\
+`That word is unfamiliar to me. (with contrast)'
 \bg. Tazi duma e nepoznata na sina mi.\\
@@
 
+%%Maybe save the day: in Dutch you can also use \tit{dat} in that position. So here is another difference between Bulgarian and Dutch: not with clitics, but with weak pronouns
+
 \ex.
@@
  `I am painting with it.'\label{ex:dutchina}
-\bg. *Ik schilder met 't\\
+\bg. *Ik schilder met 't.\\
  I paint with it\\
  `I am painting with it.'\label{ex:dutchinmet}
+\bg. Ik schilder met dat.\\
+ I paint with that\\
+ `I am painting with it.'
 

### 2020-04-14 presentation nanolab/presentation.tex

--- 2020-01-16 paper.tex
@@
-\documentclass[12pt]{article}
+\documentclass[xcolor=dvipsnames,10pt]{beamer}
 
-\usepackage[margin=1in]{geometry}
-%\usepackage{setspace}
-%\doublespacing
+\usepackage{../fenna-files/packages}
+\usepackage{../fenna-files/commands}
+\bibliography{../fenna-files/references}{}
 
-\usepackage{fenna-files/packages}
-\usepackage{fenna-files/commands}
-\bibliography{fenna-files/references}{}
+\geometry{paperwidth=140mm,paperheight=105mm}
+%
+% Choose how your presentation looks.
+%
+% For more themes, color themes and font themes, see:
+% http://deic.uab.es/~iblanes/beamer_gallery/index_by_theme.html
+%
+\mode<presentation>
+{
+	\usetheme{Berlin}      % or try Darmstadt, Madrid, Warsaw, ...
+	\definecolor{goethe}{rgb}{0,0.37,0.66}
+	\usecolortheme[named=goethe]{structure}
+	%\usefonttheme{serif}  % or try serif, structurebold, ...
+	\setbeamertemplate{navigation symbols}{}
+	\setbeamertemplate{caption}[numbered]
+	\resetcounteronoverlays{exx}
+}
+
+%gets rid of bottom navigation bars
+\setbeamertemplate{footline}{}
+
+%gets rid of navigation symbols
+%\setbeamertemplate{navigation symbols}{}
+
+\addtobeamertemplate{navigation symbols}{}{%
+	\usebeamerfont{footline}%
+	\usebeamercolor[fg]{footline}%
+	\hspace{1em}%
+	\insertframenumber/\inserttotalframenumber
+}
 
 \title{The \tsc{r}-pronoun and postposition \tit{waar-mee} in Dutch}
-\author{Fenna Bergsma\\Goethe-Universität Frankfurt}
-\date{\today}
+\author{Fenna Bergsma}
+\date{Nanolab\\ \today}
+\institute{Goethe-Universität Frankfurt}
 
@@
 
-\maketitle
+\begin{frame}
+	\titlepage
 
-\section{Introduction}
+\centering{
+	\includegraphics[width=0.4\textwidth]{dfg-logo}
+	\hspace{2cm}
+	\includegraphics[width=0.3\textwidth]{goethe-logo}}
+\end{frame}
 
-Dutch has the preposition \tit{met} `with' that expresses the instrumental.
-In \ref{ex:metdp}, \tit{met} `with' is combined with a full DP.
-The inanimate pronoun in Dutch is \tit{'t} `it'.\footnote{The longer form that is mostly used in writing is \tit{het} `it'.
-I will use the spoken variant \tit{'t} throughout this paper.} \ref{ex:tverb} illustrates that \tit{'t} `it' can be used as the object of a verb.
+% \section{Introduction}
 
-\ex.
-\ag. Ik schilder met een kwast.\\
+\begin{frame}
+
+\exg. Ik schilder met een kwast.\\
  I paint with a brush\\
  `I am painting with a brush.'\label{ex:metdp}
- \bg. Ik zie 't.\\
+
+ \pause
+
+\exg. Ik zie 't.\\
  I see it\\
@@
 
-\tit{Met} `with' and \tit{'t} `it' do not appear together, as illustrated in \ref{ex:neemett}.
-Instead, Dutch uses the \tsc{r}-pronoun \tit{'r} `there' and the postposition \tit{mee} `with', as shown in \ref{ex:jarmee}.\footnote{The \tsc{r}-pronoun \tit{'r} in \ref{ex:jarmee} can be written as \tit{er}, \tit{der} and \tit{'r} and pronounced as respectively /ɛr/, /dər/ or /ər/.
-As far as I am aware, there is no clear meaning difference between these forms.
-See \citet{wesseling2018} for discussion.
-In my examples I use \tit{'r}, but the other two forms fit just as well.}$^,$\footnote{In this paper I do not make any claims about the distinction between prefixes and prepositions, or suffixes and postpositions.}
+\pause
 
-\ex.\label{ex:rmeeconst}
-\ag. *Ik schilder met 't.\\
+\exg. *Ik schilder met 't.\\
+ I paint with it\\
+ `I am painting with it.'
+
+\end{frame}
+
+\begin{frame}
+
+\exg. *Ik schilder met 't.\\
  I paint with it\\
  `I am painting with it.'\label{ex:neemett}
-\bg. Ik schilder 'r -mee.\\
+
+\pause
+
+\exg. Ik schilder r -mee.\\
  I paint there -with\\
@@
 
-\tsc{R}-pronouns \citep{riemsdijk1978,koopman1994} are nominal elements that are syncretic with locative pronouns, which in Dutch means they contain the morpheme \tit{r}.
-The adpositions they combine with obligatorily follow the \tsc{r}-pronoun, see \ref{ex:jarmee} and \ref{ex:neemeer}.
-Notice also that the preposition \tit{met} `with' differs phonologically from the postposition \tit{mee} `with` (see \ref{ex:metdp} and \ref{ex:jarmee}).
+\end{frame}
+
+\begin{frame}
+
+\centering{\Large{Why *\tit{met 't}?}}
+
+\end{frame}
+
+\begin{frame}
+
+Instrumental in Dutch
+\ex. *met t
+
+\ex. r mee
+
+\pause
+
+\begin{itemize}
+	\item r-pronouns and locatives syncretic \pause
+	\item \tit{met} becomes \tit{mee} \pause
+	\item position of adposition
+\end{itemize}
+
+\end{frame}
+
+% \section{R-pronouns and constituency}
+
+% \subsection{Distribution of \tsc{r}-pronouns}
+
+\begin{frame}
+
+\exg. Ik zie haar/hem.\\
+ I see her/him\\
+ `I see her/him.'\label{ex:aniobj}
+
+\exg. Ik zie 't.\\
+ I see it\\
+ `I see it.'\label{ex:inaniobj}
+
+\end{frame}
+
+\begin{frame}
+
+\exg. Ik schilder samen met haar/hem.\\
+ I paint together with her/him\\
+ `I am painting together with her/him.'\label{ex:prepani}
+
+\exg. *Ik schilder met 't.\\
+ I paint with it\\
+ `I am painting with it.'\label{ex:prephet}
+
+\exg. Ik schilder 'r -mee.\\
+ I paint there -with\\
+ `I am painting with it.'\label{ex:preper}
 
@@
  I paint with there\\
- `I am painting with it.'\label{ex:neemeer}
-
-The main question I address in this paper is how to correctly rule out \tit{met 't} `with it' in \ref{ex:neemett}, and let the \tsc{r}-pronoun and postposition in \ref{ex:jarmee} appear.
-I argue that \tsc{r}-pronouns are not something special, but a consequence of regular spellout mechanisms.
-Just like \citet{riemsdijk1978} I analyze an \tsc{r}-pronoun and postposition as a type of allomorph of the preposition and pronoun.
-The crucial difference in the current approach is that spellout rules out the ungrammaticality of the preposition and pronoun and not the stipulation of a filter.
-
-This paper is focuses on the instrumental \tsc{r}-pronoun and postposition \tit{'r-mee} `with it' and \tit{waar-mee} `with what' in Dutch.
-This instance is interesting for two reasons.
-First, just like for all \tsc{r}-pronouns, the \tsc{r}-pronoun is syncretic with the locative.
-In many of the \tsc{r}-pronouns and postpositions, the meaning component of the locative is intuitive, as many prepositions express locations, directions etc.
-However, an instrumental expresses an instrument, which does not have a meaning component associated with location.
-Ideally, an analysis treats the syncretism not as accidental but allows for the locative meaning to be absent.
-The second reason why I focus on this particular \tsc{r}-pronoun and postposition has to do with the form of the adposition.
-The preposition \tit{met} `with' does not only turn into a postposition, but it also changes into \tit{-mee} `with' when it is combined with an \tsc{r}-pronoun.
-This last observation has so far remained unexplained.
-
-The main generalization is that the instrumental \tsc{r}-pronoun and postposition \tit{waar-mee} `with what' takes precedence over the instrumental preposition and inanimate pronoun \tit{met wat} `with what'.
-This generalization is subject to an important condition: the instrumental object needs to form a proper constituent i.e.
-a constituent to the exclusion of other features.
-When this condition is not met, the preposition and pronoun appear.
-This can straightforwardly follow in a system in which spellout targets phrasal constituents: Nanosyntax \citep{starke2009}.
-I work this idea out capturing the following observations.
-First, \tsc{r}-pronouns are syncretic with locatives.
-Second, regular pronouns appear with prepositions, \tsc{r}-pronouns with postpositions.
-Third, the instrumental preposition and postposition differ in form (\tit{met} vs.
-\tit{mee}).
-
-This paper is structured as follows.
-In Section \ref{sec:distribution} I discuss the condition that \tsc{r}-pronouns and postpositions are subject too: they need to form a proper constituent.
-I show that \tsc{r}-pronouns and postpositions and prepositions and pronouns are in complementary distribution, depending on whether all features form a proper constituent or not.
-In Section \ref{sec:takingapart} I decompose \tit{waar-mee} `with what' and \tit{met wat} `with what', and I connect them to parts of syntactic structure.
-Section \ref{sec:derivation} shows in a derivation how \tit{waar-mee} `with what' is derived and the role that constituency plays.
-Section \ref{sec:conclusion} concludes and discusses possible extensions of the analysis.
-All examples in this paper are from Dutch, unless indicated otherwise.
-Unmarked examples are constructed and have been verified by native speakers.
-
-\section{\tsc{R}-pronouns are proper constituents}\label{sec:distribution}
-
-The goal of this section is to show that \tsc{r}-pronouns and postpositions appear when all relevant features form a proper constituent, i.e.
-that all features form a constituent to the exclusion of any other features.
-I start the section by showing that \tit{'rmee} `with it' and \tit{waar-mee} `with what` are the default, that normally they appear instead of \tit{met 't} `with it' and \tit{met wat} `with what`.
-Then I show an exception, in which \tit{met wat} `with what` has to be used and \tit{waar-mee} `with what` cannot.
-I argue that the crucial difference between the exception and other cases is that in the exception the relevant features do not form a proper constituent.
-
-\subsection{\tsc{R}-pronouns as default}\label{sec:rdefault}
-
-In what follows I discuss the distribution of \tsc{r}-pronouns and regular pronouns in general \citep{riemsdijk1978,koopman1994}. I start with the personal pronouns and then return to the wh-pronouns.
-
-Dutch has the accusative personal pronouns \tit{haar} `her', \tit{hem} `him' and \tit{'t} `it' that can be used as animate and inanimate objects of verbs, as illustrated in \ref{ex:objverb}.
-
- \ex. \label{ex:objverb}
- \ag. Ik zie haar/hem.\\
-  I see her/him\\
-  `I see her/him.'\label{ex:aniobj}
- \bg. Ik zie 't.\\
-  I see it\\
-  `I see it.'\label{ex:inaniobj}
-
-Example \ref{ex:prepani} shows that for animate objects the same pronouns (\tit{haar} `her' and \tit{hem} `him') appear as objects of prepositions.
-Repeating from the introduction, the inanimate personal pronoun \tit{'t} `it' cannot be used as an object of a preposition, shown in \ref{ex:prephet}.
-Instead, an \tsc{r}-pronoun appears.
-This is illustrated in \ref{ex:preper}.
-\ref{ex:erprep} shows that the \tsc{r}-pronoun has moved obligatorily to the left of the adposition.
-
-\ex. \label{ex:objprep}
-\ag. Ik schilder samen met haar/hem.\\
- I paint together with her/him\\
- `I am painting together with her/him.'\label{ex:prepani}
-\bg. *Ik schilder met 't.\\
- I paint with it\\
- `I am painting with it.'\label{ex:prephet}
-\bg. Ik schilder 'r -mee.\\
- I paint there -with\\
- `I am painting with it.'\label{ex:preper}
-\bg. *Ik schilder mee 'r.\\
- I paint with there\\
  `I am painting with it.'\label{ex:erprep}
 
-\tit{Met} is not the only preposition with which this happens.
-For example, \tit{op} `on' and \tit{in} `in' also do not combine with the inanimate personal pronoun \tit{'t}, but the \tsc{r}-pronoun and postposition are used obligatorily.
+\end{frame}
+
+\begin{frame}
 
@@
 
-The situation of the inanimate wh-pronouns resembles the one of the inanimate personal pronouns.
-\tit{Wat} `what' can function as an object of a verb (see \ref{ex:wat}), but not as an object of a preposition \ref{ex:metwat}.
-In that case, the \tsc{r}-pronoun and postposition \tit{waar-mee} `with what' appears, as shown in \ref{ex:waar-mee}.\footnote{The sentence in \ref{ex:metwat} is unacceptable with neutral intonation.
-It becomes acceptable if \tit{wat} `what' is stressed, for example in a context in which the speaker is highly surprised about the choice of the object the hearer is painting with.}
+\end{frame}
 
-\ex.
-\ag. Wat zie jij?\\
+\begin{frame}
+
+\exg. Wat zie jij?\\
  what see you\\
  `What do you see?'\label{ex:wat}
-\bg. *Met wat schilder jij?\\
+
+\exg. *Met wat schilder jij?\\
  with what paint you\\
  `What are you painting with?'\label{ex:metwat}
-\bg. Waar -mee schilder jij?\\
+
+\exg. Waar -mee schilder jij?\\
  where with paint you with\\
@@
 
-\tit{Waar-mee} `with what' and not \tit{met wat} `with what' does not only appear in wh-questions, but also in other contexts.
-\ref{ex:headed} gives an example of a headed relative, and \ref{ex:headless} shows a free relative in which both predicates combine with an instrumental object.
-The use of \tit{met wat} `with what' is ungrammatical in both contexts, and \tit{waar-mee} `with what' is used.
+\end{frame}
+
+\begin{frame}
 
@@
 
-In sum, \tit{'t} `it' and \tit{wat} `what' do not combine with prepositions. They are substituted by respectively \tit{'r} `there' and \tit{waar} `where'.
+\end{frame}
 
-\subsection{\tit{Met wat} `with what' shows up}
-
-This section discusses an exception to what is shown in the previous section.
-I show an instance in which \tit{met wat} `with what' has to be used instead of \tit{waar-mee} `with what'.
-This instance comes from a mismatching free relative construction.
-
-A mismatching free relative is a free relative construction in which the two predicates (the one in the main clause and the one in the embedded clause) combine with two different cases (i.e.
-the case requirements do not match).
-I give an example in which the \tsc{r}-pronoun and postposition appear before I get to the exception.
-Consider \ref{ex:gekochtwaar-mee}.
-The predicate in the embedded clause, \tit{schildert} `paint', combines with an instrumental object.
-The predicate in the main clause, \tit{gekocht} `bought' combines with an accusative object.
-The \tsc{r}-pronoun and postposition \tit{waar-mee} `with what' is used here.
-The use of \tit{met wat} `with what' is ungrammatical in this context, illustrated in \ref{ex:gekochtmetwat}.\footnote{In this example, \tit{waar} `where' takes \tit{-mee} `with' to the left edge of the embedded clause.
-It is also possible for \tit{-mee} `with' to be stranded, and \tit{waar} `where' to be moved to the left edge of the embedded clause on its own.
-
-\exg. Ik heb gekocht waar jij mee schildert.\\
- I have bought waar you with paint\\
- `I bought what you are painting with.'\label{ex:meealong}
-\z.
-
-\phantom{x}
-}
+\begin{frame}
 
@@
 
-If the predicates are switched between the clauses, the \tsc{r}-pronoun and postposition do not appear anymore.
-In \ref{ex:schildermet}, \tit{schilder} `paint' combines with an instrumental object in the main clause and \tit{gekocht} `bought' combines with an accusative object in the embedded clause.
-The use of an \tsc{r}-pronoun and postposition is ungrammatical, as indicated by \ref{ex:schilderwaar-mee}.
-Instead, a combination of the regular instrumental preposition \tit{met} `with' and the regular wh-pronoun \tit{wat} `what' in used.
+\pause
 
@@
 
-Table \ref{tbl:distribution} summarizes the pattern.
-When the main clause predicate combines with an accusative and the embedded clause predicate with an instrumental, \tit{waar-mee} `with what' is grammatical and \tit{met wat} `with what' is ungrammatical.
-When the main clause predicate combines with an instrumental and the embedded clause predicate with an accusative, \tit{waar-mee} `with what' is ungrammatical and \tit{met wat} `with what' is used.
+\end{frame}
 
-\begin{table}[ht]
-	\center
-	\caption {Distribution between \tit{waar-mee} and \tit{met wat}}
-	\begin{minipage}{0.45\linewidth}
-		\begin{tabularx}{\textwidth}{ccc}
-		\toprule
-                              & \tit{waar-mee} & \tit{met wat} \\
-		\midrule
-    m:\tsc{acc}, e:\tsc{ins}  & ✔             & *             \\
-    m:\tsc{ins}, e:\tsc{acc}  & *             & ✔             \\
-    \bottomrule
-\end{tabularx}
-\label{tbl:distribution}
-\end{minipage}
-\end{table}
-
-In the remainder of this section I argue that the crucial point of \ref{ex:schildermetwat} is that the instrumental object does not form a proper constituent, i.e.
-it is not a constituent to the exclusion of any other elements.
-The other side of the coin is that constructions with \tsc{r}-pronouns and postpositions contain an instrumental object that does form a proper constituent.
-
-Below I repeat the examples with instrumentals I discussed so far in this paper.
+\begin{frame}
 
@@
 
-In each of these examples the instrumental object forms a proper constituent at a certain point in the derivation.
-In \ref{ex:const1}, the instrumental object forms a proper constituent in the surface order, as shown in \ref{ex:const1stage}.
-In \ref{ex:const2}, the instrumental object forms a proper constituent before wh- and V2- movement, shown in \ref{ex:const2stage}.
-The structure in \ref{ex:const3stage} represents a stage in the derivation of the embedded clauses in \ref{ex:const3} and \ref{ex:const4}.
-Again, in the stage, which comes before relative movement of the pronoun to the left periphery of the relative clause, the instrumental object forms a proper constituent.
+\pause
 
@@
 
-Let me now show how this applies to the examples with the mismatching free relatives.
-The two predicates I used in the free relatives are \tit{kopen} `to buy' and \tit{schilderen}  `to paint'.
-\tit{Kopen} `to buy' takes an accusative object, illustrated in \ref{ex:kopen}.
-\tit{Schilderen} `to paint' can take an instrumental as its object, shown in \ref{ex:schilderen}.\footnote{\tit{Schilderen} also optionally takes an (accusative) object, but I am focusing on the instrumental object here.}
+\end{frame}
+
+\begin{frame}
 
@@
 
-I repeat the mismatching free relative in which \tit{waar-mee} `with what' appears in \ref{ex:mismatchwaar-mee}.
-The predicate \tit{schildert} `paints' combines in the embedded clause with the instrumental object.
-The instrumental object forms a proper constituent within the embedded clause, and the it can be realized as the \tsc{r}-pronoun and postposition \tit{waar-mee} `with what'.\footnote{I assume that the accusative case requirement of \tit{gekocht} `bought' is satisfying by grafting a subconstituent of \tit{waar-mee} `with what' \citep{bergsma2019}.}
+ \pause
+
+\end{frame}
+
+\ex.
+\ag. Ik koop het schilderij.\\
+ I buy the painting\\
+ `I am buying the painting.'\label{ex:kopen}
+\bg. Ik schilder met een kwast.\\
+ I paint with a brush\\
+ `I am painting with a brush.'\label{ex:schilderen}
+
+\pause
 
@@
 
-Next, I arrive at the mismatching free relative in which \tit{waar-mee} `with what' cannot be used, but \tit{met wat} `with what' appears.
-The embedded clause predicate \tit{gekocht} `bought' combines with an accusative object.
-The accusative object of a verb is always \tit{wat} `what', as I showed in \ref{ex:wat}.
-The instrumental only comes into the picture in the main clause, when \tit{schilder} `paint' combines with an instrumental object.
-At no point in the derivation does the instrumental object form a proper constituent, and \tit{waar-mee} `with what' does not surface.
+\pause
 
@@
 
- The mismatching free relative in \ref{ex:mismatchmetwat} is not the only construction in which the string \tit{met wat} `with what' appears.
-I give examples of two more occurrences in \ref{ex:moremetwat}.
-In \ref{ex:watwasfur}, \tit{wat} `what' is the \tit{wat} `what' in the so-called \tit{wat voor} `what for'-construction \citep[cf.][]{corver1991}.
- In \ref{ex:watindef}, \tit{wat} appears as a quantifier, and it means `some'.
-In both constructions \tit{wat} `what' takes a complement and \tit{met wat} `with what' do not form a proper constituent.
-The brackets within the examples indicate the constituency.
+\begin{frame}
 
- \ex.\label{ex:moremetwat}
- \ag. [Met [wat [voor [potloden]]] teken jij?\\
+\exg. [Met [wat [voor [potloden]]] teken jij?\\
  with what for pencils draw you\\
  `What kind of pencils do you with?'\label{ex:watwasfur}
- \bg. Ik wil graag thee [met [wat [suiker]]].\\
+\exg. Ik wil graag thee [met [wat [suiker]]].\\
  I want please tea with some sugar\\
@@
 
-\ref{ex:summaryconst} summarizes what I showed in this section.
-\tit{Met wat} `with what' can never surface when \tit{met} `with' and \tit{wat} `what' form a proper constituent.
-It always becomes \tit{waar-mee} `with what', as shown in \ref{ex:waar-meefr}.
-\tit{Met wat} `with what' can appear when the instrumental object does not form a proper constituent.
-This can be either when \tit{wat} `what' takes a complement before it combines with \tit{met} `with', as shown in \ref{ex:metwatx}, representing the examples in \ref{ex:moremetwat}.
-The other option is that \tit{wat} `what' is part of the a clause that \tit{met} `with' is not a part of, schematized as \ref{ex:metwatfr} as an illustration of \ref{ex:mismatchmetwat}.
+\pause
 
@@
 
-\section{Decomposing \tit{waar-mee} and \tit{met wat}}\label{sec:takingapart}
+\end{frame}
 
-In this section I decompose \tit{waar-mee} `with what' and \tit{met wat} `met wat' into smaller units, which I connect to parts of syntactic structure.
-\tit{Waar-mee} `with what' and \tit{met wat} `met wat' spell out the same set of features but the distribution is different.
-I decompose \tit{waar-mee} and \tit{met wat} as I show in \ref{ex:decompose}.
-Earlier works have decomposed these pronouns in similar ways (cf.
-\citealt{hachem2015,noonan2017dutch,wesseling2018}).
+\begin{frame}
 
@@
 
-In this section I first identify \tit{w} and \tit{a} as morphemes that appear in both expressions.
-Putting these two aside, I concentrate on \tit{'rmee} `with it' and \tit{met 't} `with it'.
-Along the way I introduce some necessary theoretical background on Nanosyntax.
+\end{frame}
 
-\subsection{Overlap: \tit{w-} and \tit{-a-}}
-
-Let me start with the morphemes \tit{w} and \tit{a} that appear in both \tit{waar-mee} `with what' and \tit{met wat} `met wat'.
-I assume that they correspond to the same syntactic structure in both.
-As I am interested in the differences between the two expressions, I do not discuss the featural content of \tit{w} and \tit{a} into depth.
-
-For \tit{w} I follow \citet{hachem2015} who investigated \tit{d} and \tit{w} elements in German and Dutch.
-In her work, \tit{d} establishes a definite reference and \tit{w} triggers the construction of a set of alternatives in the sense of \citet{rooth1992} (see \citealt{hachem2015} for discussion).\footnote{Throughout the paper, ⇔ indicates the pairing between a lexical tree and a phonological form in a lexical entry, and ⇒ indicates how a node in the syntactic structure is spelled out.}
+\begin{frame}
 
@@
 
-I follow several authors (cf.
-\citealt{lander2016,noonan2017dutch,wesseling2018}) that assume the morpheme \tit{a} is related to deixis.
-Dutch distinguishes between proximal by using \tit{ie} (/i:/) and \tit{i} (/ɪ/) and distal by using \tit{aa} (/aː/) and \tit{a} (/ɑ/), illustrated in \ref{ex:deixis}.\footnote{A question that remains open is why wh-elements combine with the distal marker \tit{a}, and they cannot with the proximal marker \tit{i/ie}.} I analyze the transformation from /ɪ/ into /i:/ and /ɑ/ into /aː/ as a result of the final r.
-
-\ex.\label{ex:deixis}
-\ag. h-ie-r\\
- here\\
-\bg. d-aa-r\\
- there\\
-\bg. d-i-t\\
- this\\
-\bg. d-a-t\\
- that\\
- \z.
- \z.
-
-For the purpose of this paper I let \tit{a} correspond to \tsc{deixP}.
-
 \ex. \begin{forest}
@@
 
-I put \tit{w} and \tit{a} aside for now, assuming they spell out the same syntactic structure in \tit{waar-mee} `with what' and \tit{met wat} `with what'.
-This leaves \tit{'r-mee} `with it' and \tit{met 't} `with it'.
+\end{frame}
 
-\ex.
-\ag. 'r -mee\\
-there with\\
-\b. met 't\\
-with it\\
-\z.
-\z.
-
-\subsection{Differences: \tit{'rmee} vs. \tit{met 't}}
-
-In this section I discuss the forms \tit{met 't} `with it` and \tit{'rmee} `with it'.
-I set up an account that makes the ungrammaticality of \tit{met 't} and the appearance of \tit{'rmee} follow from spellout.
-The analysis accounts for the following three observations, taking \tit{met 't} as the point of departure.
-First, \tit{met} `with' changes from being a preposition to being a postposition.
-This process is restricted to inanimate pronouns, and it does not apply to full DPs and animate pronouns.
-Second, \tit{met} changes form into \tit{-mee}.
-Third, \tit{'t} is replaced by \tit{'r}, a morpheme that is associated with the locative in Dutch.
-
-\subsubsection{\tit{'t} vs. \tit{'r}}
-
-In this section I give the lexical entries for \tit{'t} and \tit{'r}, and I show that \tit{'r} is actually the base form and \tit{'t} a suppletive nominative, accusative and dative.
-
-Let me start with the lexical entry for \tit{'t}.
-\tit{'t} `it' can be used as a subject (associated with nominative), direct object (associated in accusative) and indirect object (associated with dative), as shown in \ref{ex:tsubobj}.
+\begin{frame}{Case}
 
@@
 
- Pronouns in other genders alternate between nominative (non-oblique) and accusative/dative (oblique) in these contexts, illustrated in \ref{ex:hemsubobj}.
-
 \ex.\label{ex:hemsubobj}
@@
 
-For case, I follow \citet{caha2009} in that case features are organized as in the containment relation in \ref{ex:casetree}.
-The higher, more complex cases contain the smaller, less complex cases.
-For the purpose of this paper, I only show case features relevant for the argument.
+\end{frame}
 
- \ex. \label{ex:casetree}
- \begin{forest} boom
- [\tsc{insP}
-     [\tsc{f4}]
-     [\tsc{datP}
-         [\tsc{f3}]
-         [\tsc{accP}
-             [\tsc{f2}]
-             [\tsc{nomP}
-                 [\tsc{f1}]
-                 [DP
-                     [..,roof]
-                 ]
-             ]
-         ]
-     ]
- ]
- \end{forest}
-
- Following the distinctions from \citet{cardinaletti1996}, I assume \tit{'t} `it' is a weak pronoun.
-It is not a clitic, because it can occur in sentence initial position, shown in \ref{ex:tnoclitic}.
-It is not a strong pronoun, because it cannot be coordinated, as indicated in  \ref{ex:tcoordinated}.
-\ref{ex:datcoordinated} shows that \tit{'t} `it' needs to combine with \tit{da-}/\tit{di-} to be able to be coordinated.
+\begin{frame}
 
@@
 
-\ref{ex:entryt} shows the lexical entry for \tit{'t} `it'.
-I assume that the \tit{'t} contains the ontological category \tsc{thing} \citep{kayne2005}.
-The feature Σ indicates that the pronoun is a weak pronoun.
-For reasons of space I let singular be the absence of number and neuter the absence of gender.
-The morpheme \tit{'t} can act as nominative, accusative and dative, as I showed in \ref{ex:tsubobj}.\footnote{ Another possibility is to claim that \tit{'t} can only spell out \tsc{thing} and Σ and it combines with a zero suffix for the cases up to dative.
-This could be the same zero marker that full DPs combine with.
+\end{frame}
 
-\ex.
-\ag. De kast-∅ staat in de hal.\\
- the cabinet-\tsc{nom} stands in the hallway\\
- `The cabinet is standing in the hallway.'
-\bg. Ik zie de kast-∅.\\
- I see the cabinet-\tsc{acc}\\
- `I see the cabinet.'
-\bg. Ik heb de kast-∅ een klap gegeven.\\
- I have the cabinet-\tsc{dat} a hit given\\
- `I gave the cabinet a hit.'
-
-The proposed account fares equally well with both alternatives. I work the proposal out with \tit{'t} realizing the cases up to the dative.}
+\begin{frame}
 
@@
 
- This lexical entry can lexicalize the \tsc{datP}, but also the \tsc{accP} and \tsc{nomP}. This is due to the Superset Principle.
+\end{frame}
 
-  \ex. The Superset Principle \citet{starke2009}: \\
-  A lexically stored tree matches a syntactic node iff the lexically stored tree contains the syntactic node.
-
- In other words, a lexically stored structure does not have to be identical to the syntactic structure.
-It is enough if the syntactic structure is contained in the lexically stored tree.
-This has as a consequence that the lexical entry in \ref{ex:entryt} can also be inserted in \ref{ex:tacc} and \ref{ex:tnom}.
-
- \ex.
- \a. \begin{forest} boom
- [\tsc{accP}
-     [\tsc{f2}]
-     [\tsc{nomP}
-         [\tsc{f1}]
-         [ΣP
-             [Σ]
-             [\tsc{thingP}
-                 [\tsc{thing}, roof]
-             ]
-         ]
-     ]
- ]
- \end{forest}\label{ex:tacc}
- \b. \begin{forest} boom
- [\tsc{nomP}
-     [\tsc{f1}]
-     [ΣP
-         [Σ]
-         [\tsc{thingP}
-             [\tsc{thing}, roof]
-         ]
-     ]
- ]
- \end{forest}\label{ex:tnom}
-
-Let me move on to \tit{'r}. \tit{'r} `there' can be used as a locative.
+\begin{frame}
 
@@
  `I have already been there.'
-
-I follow \citet{baunaz2018} in assuming that the ontological category \tsc{location} contains \tsc{thing}.\footnote{\citet{baunaz2018} place in addition \tsc{person} between \tsc{thing} and \tsc{location}, which I have left out here.}
 
@@
 
-Notice here that, via the Superset Principle, \tit{'r} can be used to realize the feature \tsc{thing} as well, as it is contained in \tsc{locP}.
-Moreover, in a syntactic structure like in \ref{ex:rthing} the lexical entry \ref{ex:entryr} will be inserted and not \ref{ex:entryt}.
+\end{frame}
 
-\ex.
-\begin{forest} boom
- [\tsc{thingP}
-     [\tsc{thing}, roof]
- ]
-{\draw (.east) node[right]{⇒ \tit{'r}}; }
-\end{forest}\label{ex:rthing}
+\begin{frame}
 
-This is due to the Elsewhere Condition. The idea is that when two lexical entries are both candidates for spellout, the most specific is inserted.
-
-\ex. The Elsewhere Condition (\citealt{kiparsky1973}, formulated as in \citealt{caha2020}):\\
-When two entries can spell out a given node, the more specific entry wins. Under the Superset Principle governed insertion, the more specific entry is the one which has fewer unused features.
-
-The syntactic structure in \ref{ex:entryr} only has \tsc{loc} as an unused feature, whereas in \ref{ex:entryt} Σ up to \tsc{f3} remain unused.
-
-This means that the caseless base form of the neuter singular pronoun in Dutch is actually \tit{'r} and \tit{'t} should be analyzed as a suppletive nominative, accusative and dative.
-The base form only shows up in the higher cases, from instrumental on, see Table \ref{tbl:dutchcases}.
-
-\begin{table}[ht]
-	\center
-	\caption {Fragment Dutch \tsc{n.sg}}
-	\begin{minipage}{0.17\linewidth}
 	\begin{tabularx}{\textwidth}{ccccccc}
@@
 \end{tabularx}
-\label{tbl:dutchcases}
-\end{minipage}
-\end{table}
 
-A similar situation appears in Iron Ossetic, shown in Table \ref{tbl:ossetic}.
-In the first person singular of this language, it is only the nominative that is suppletive: \tit{æz}.
-The higher cases have the stem \tit{mæn} and they combine with the suffixes that nouns normally also combine with.
+\end{frame}
 
-\begin{table}[ht]
-	\center
-	\caption {Fragment Iron Ossetic 1.\tsc{sg} and noun \citep{erschler2012}}
-	\begin{minipage}{0.3\linewidth}
-		\begin{tabularx}{\textwidth}{ccccccc}
-		\toprule
-              & 1.\tsc{sg}  & head    \\
-		\midrule
-    \tsc{nom} & æz          & sær-∅   \\
-    \tsc{acc} & mæn-∅       & sær-∅   \\
-    \tsc{dat} & mæn-æn      & sær-æn  \\
-    \tsc{ins} & mæn-æj      & sær-æj  \\
-    \bottomrule
-\end{tabularx}
-\label{tbl:ossetic}
-\end{minipage}
-\end{table}
-
-\citet{caha2019competition} uses evidence from a phenomenon called suspended affixation to argue that \tit{mæn} is a caseless stem and and \tit{æz}.
-Consider the ordinary coordination in \ref{ex:horseoxboth}.
-Both conjuncts are marked by a plural marker and a case marker.
-Suspended affixation is shown in \ref{ex:horseoxone}.
-Here the case marker only appears on the second conjunct and not on the first one without changing the interpretation.
-\tit{Bæx-tæ} `horse-\tsc{pl}' in \ref{ex:horseoxone} does not carry any case marking here.
-
-\ex.
-\ag. bæx-t-imæ æmæ gæl-t-imæ\\
-horse-\tsc{pl-com} and ox-\tsc{pl-com}\\\label{ex:horseoxboth}
-\bg. bæx-tæ æmæ gæl-t-imæ\\
-horse-\tsc{pl} and ox-\tsc{pl-com}\\
-`with horses and oxen' \hfill (Iron Ossetic, \citealt[165]{erschler2012})\label{ex:horseoxone}
-
-\ref{ex:suspendedme} gives examples of the first person singular in a suspended affixation contexts.
-It shows that it is \tit{mæn} that appears as a caseless first conjunct and that the use of \tit{æz} is ungrammatical.
-This means that \tit{mæn} is the bare stem that combines with case markers, and \tit{æz} the suppletive nominative.
-In Section \ref{sec:derivation} I show how a derivation with this type of elements works in Nanosyntax.
-
-\ex.\label{ex:suspendedme}
-\ag. mæn æmæ Zauyr-æn\\
- 1.\tsc{sg} and Zaur-\tsc{dat}\\\label{ex:izaurboth}
-\bg. *æz æmæ Zauyr-æn\\
- 1.\tbf{sg} and Zaur-\tsc{dat}\\
- `me and Zaur' \hfill (Iron Ossetic, \citealt[39]{беляев2014} after \citealt{caha2019competition})\label{ex:izaurone}
-
-The point of showing the Ossetic example is that Dutch is not unique in having suppletive forms that are less marked (in this case nominative, accusative and dative), and higher cases that are a combination of a suffix and a caseless base form.
-
-\subsubsection{\tit{-mee} vs. \tit{met}}
-
-The last two forms to specify lexical entries for are \tit{-mee} `with' and \tit{met} `with'.
-An important distinction between these two is that \tit{-mee} appears after the element it combines with (\tsc{'r}), while \tit{met} appears before the element it combines with (\tit{'t}).
-I will analyze \tit{-mee} as a postposition and \tit{met} as a preposition.\footnote{A topic related to this paper is the different positioning of identical adpositions in Dutch (see \citet{caha2010} for an account of German and Dutch and \citet{pretorius2017} for Afrikaans).
-In \ref{ex:dutchin}, \tit{in} `in' changes meaning depending on whether it proceeds or follows the DP, it is respectively locational or directional.
-
-\ex.\label{ex:dutchin}
-\ag. Ik klim in de boom.\\
- I climb in the tree\\
- `I am climbing in the tree.'
-\bg. Ik klim de boom in.\\
- I climb the tree in\\
- `I am climbing into the tree.'
-
-In \ref{ex:dutchin}, the movement of the adposition is driven by movement, and it is meaningful.
-The movement of \tsc{r}-pronouns I discuss in this paper is driven by spellout, which is meaningless.} In this section I discuss the relation between prepositions and postpositions, and how this is modeled with the case hierarchy in Nanosyntax \citep{caha2009}.
-
-In the previous section I argued that \tit{'t} realizes case features up to \tsc{f3} (see \ref{ex:entryt}).
-However, case can also be expressed by prepositions (or prefixes) and postpositions (or suffixes).
-The division between which cases are expressed by prepositions and which are expressed by postpositions is not arbitrary.
-
-\ex. The preposition/postposition hierarchy
-\a. If the expression of a particular case in the case sequence (below) involves a preposition, then all cases to its right do as well.
-\b. The case sequence: \tsc{nom – acc – dat – gen - ins – com} \hfill \citep{caha2009}
-
-The result of that is that a PP can contain a preposition and a suffix. In the German example in \ref{ex:loffel}, the dative suffix is used with a instrumental preposition.
-
-\exg. mit ein -em Löffel\\
-with a -\tsc{dat.sg} spoon\\
-`with a spoon' \hfill (German)\label{ex:loffel}
-
-With the case hierarchy in Nanosyntax this can be modeled by letting the DP move as high as above the \tsc{datP} in the syntactic structure in \ref{ex:casetree}.
-The features below the \tsc{datP} are realized as a suffix, and the features above \tsc{datP} are realized as a preposition.
-
-There is variation with respect to how high a DP can move in the structure, both between languages and within languages.
-An example of the latter comes from Bulgarian.
-\ref{ex:bulpron} shows that pronouns can take the suffix \tit{-i} to realize dative, but full DPs need a preposition \tit{na} `to'.
-
-\ex.\label{ex:bulgarian}
-\ag. Tazi duma m -i e nepoznata.\\
-that word I -\tsc{dat} is unfamiliar\\
-`That word is unfamiliar to me.'\label{ex:bulpron}
-\bg. Tazi duma e nepoznata na sina mi.\\
-that word is unfamiliar to son my\\
-`That word is unfamiliar to my son.'\label{ex:buldpto} \hfill (Bulgarian, \citealt[39]{caha2009})
-
-In Dutch the split is not between pronouns and full DPs but between inanimate pronouns on the one hand and animates and full DPs on the other hand.
-In Dutch, inanimate pronouns combine with the postposition \tit{-mee} (see \ref{ex:dutchina} and not with the preposition \tit{met} (see \ref{ex:dutchinmet}).
-
-\ex.
-\ag. Ik schilder 'r -mee.\\
- I paint there -with\\
- `I am painting with it.'\label{ex:dutchina}
-\bg. *Ik schilder met 't\\
- I paint with it\\
- `I am painting with it.'\label{ex:dutchinmet}
-
-Animate pronouns and full DPs, however, combine with the preposition met, as shown in \ref{ex:dutchan} and \ref{ex:dutchdp}.
-The use of the postposition \tit{-mee} is ungrammatical (see \ref{ex:dutchanmee} and \ref{ex:dutchdpmee}).
-
-\ex.
-\ag. Ik schilder samen met hem.\\
- I paint together with him\\
- `I am painting with him.'\label{ex:dutchan}
-\bg. Ik schilder samen met de man.\\
- I paint together with the man\\
- `I am painting together with the man.'\label{ex:dutchdp}
-\bg. *Ik schilder samen 'm-mee.\\
- I paint together him-with\\
- `I am painting together with him.'\label{ex:dutchanmee}
-\bg. *Ik schilder samen de man-mee.\\
- I paint together the man-with\\
- `I am painting together with the man.'\label{ex:dutchdpmee}
-
- In other words, inanimates can move higher than animates and full DPs in Dutch.
-To be more precise, the inanimate \tit{'t} is replaced by \tit{'r}, and this element can move as high as above the dative to combine with \tit{-mee}.
-I return to what it is that prevents animates and full DPs from being combined with \tit{-mee} shortly.
-
-First I show what the lexical entry of \tit{-mee} looks like.
-Two facts need to be captured.
-\tit{-mee} combines with \tit{'r} and is a postposition.
-First, \tit{-mee} expresses instrumental (and comitative) case and it combines with \tit{'r}.\footnote{For reasons of space I leave \tsc{comP} out of the lexical entries and discussion, even though \tit{-mee} `with' and \tit{met} `with' can also express comitative.}
-This means that the combination of \tit{'r} and \tit{-mee} has to realize \tsc{thing}, Σ and all case features up to \tsc{f4}.
-So far, \tit{'r} `there' only realizes the feature \tsc{thing}.
-This leaves Σ and \tsc{f1} to \tsc{f4} to be realized by \tit{-mee}.
-I give the lexical tree of \tit{-mee} in \ref{ex:entrymee}.
+\begin{frame}
 
@@
 
-This leads me to the second point: \tit{-mee} is a postposition.
-Notice that the foot of the structure has a singleton feature.
-Nanosyntax distinguishes pre-elements from post-elements by the shape of their lexical entry \citep{starke2018}.
-As a result, it follows from the spellout procedure whether an element appears before or after the previously inserted element.
-Post-elements have a unary bottom (i.e.
-the foot of the tree is a single feature), so they can only appear as the result of movement.
-Post-elements have a binary bottom (i.e.
-the foot of the tree consists of two features), so they cannot be a candidate as a result of movement.
-I illustrate this in Section \ref{sec:derivation}.
+\end{frame}
 
-Why does \tit{-mee} not combine with animates and full DPs?
-I claim that has to do with the bottom feature of the lexical entry of \tit{-mee}.
-Full DPs do not take features related to pronominal strength.
-According to the Superset Principle, a lexical tree can match a syntactic tree with a subpart of the features, but a tree can only shrink from the top, so \tit{-mee} will always realize Σ.
-It is less clear to me why animates do not combine with \tit{-mee}.
-The crucial difference between animates and inanimates if gender features.
-For now I assume that gender features are situated between Σ and \tsc{f1}.
-The lexical entry of \tit{-mee} includes both these features, so any additional gender features are incompatible with \tit{-mee}.
-So far I do not have independent evidence for placing gender features between features of pronominal strength and case, and I leave this for future research.
-
-So far I discussed \tit{-mee} is a postposition, which follows \tit{'r} and is stored with a unary bottom.
-\tit{Met}, on the other hand, is a preposition, it precedes \tit{'t}, so it should be stored with a binary bottom.
-The highest case feature \tit{'t} can realize is \tsc{f3}, so the preposition realizes \tsc{f4}.
-I give the lexical entry for \tit{met} in \ref{ex:entrymet}.
+\begin{frame}
 
@@
 
-In the next section I put all features back together in a derivation and I show how \tit{waar-mee} `with what' and not \tit{met wat} `with what' surfaces when all features form a constituent.
+\end{frame}
 
-\section{In a derivation}\label{sec:derivation}
+\begin{frame}
 
-Before I show that \tit{waar-mee} `with what' is used when all features form a proper constituent, I need to make some assumptions about the spellout procedure in Nanosyntax explicit.
-Spellout happens in a cyclic derivation, following a spellout algorithm \citep{starke2018}.
-After each instance of merge, spellout takes place.
-If no spellout exists for the phrase created by the newly added feature, evacuation movements specified in the spellout algorithm take place.
-The algorithm is given in \ref{ex:spellout}.
-
-\ex. Merge F and \label{ex:spellout}
- \a. Spell out FP.
- \b. If (a) fails, attempt movement of the spec of the complement of \tsc{f}, and retry (a).
- \b. If (b) fails, move the complement of \tsc{f}, and retry (a).
-
-When a new match is found, it overrides previous spellouts.
-
-\ex. Cyclic Override \citep{starke2018}:\\
-Lexicalisation at a node XP overrides any previous match at a phrase contained in XP.
-
-If the spellout procedure in \ref{ex:spellout} fails, backtracking takes place.
-This is the operation that leads from the suppletive nominative, accusative and dative \tit{'t} to the base form \tit{'r}.
-
-\ex. Backtracking \citep{starke2018}:\\
-When spellout fails, go back to the previous cycle, and try the next option for that cycle.\label{ex:backtracking}
-
-If backtracking also does not help, a specifier is constructed. This is what happens when the preposition \tit{met} `with' is inserted.
-
-\ex. Spec Formation \citep{starke2018}:\\
-If Merge F has failed to spell out (even after backtracking), try to spawn a new derivation providing the feature F and merge that with the current derivation, projecting the feature F at the top node.\label{ex:specformation}
-
-With this theoretical background in place, I can turn to the derivation.
-I first show how \tit{'rmee} `with it' is constructed.
-I leave out \tit{w} and \tit{a} to not unnecessarily complicate the story.\footnote{I assume that the \tsc{wP} and \tsc{deixP} appear lower in the structure than the case features, so the functional sequence is as given in \ref{ex:fseq}.
-
-\ex. [ [ [ [ [ [ [ \tsc{thing} ] \tsc{deix} ] W ] \tsc{f1} ] \tsc{f2} ] \tsc{f3} ] \tsc{f4} ]\label{ex:fseq}
-\z.
-
-\phantom{x}
-
-}
-
-I start with \tsc{thing}.
-The two candidates here are \ref{ex:entryt} and \ref{ex:entryr}.
-Following the Elsewhere Condition, \ref{ex:entryr} wins the competition because it contains less unused material.
-
-\ex.
 \begin{forest} boom
@@
 
-In the next step, Σ is merged.
-\ref{ex:entryr} is no longer a candidate because it does not contain Σ.
-\ref{ex:entryt} still is a candidate, because it contains all features in \ref{ex:thingf1}.
-The spellout is overridden and the structure is realized as \tit{'t}.
+\pause
 
-\ex. \begin{forest} boom
+\begin{forest} boom
 [ΣP
@@
 
-Then \tsc{f1} is merged. This structure can still be realized by \tit{'t}.
+\end{frame}
 
-\ex. \begin{forest} boom
+\begin{frame}
+
+	\begin{forest} boom
 	[\tsc{nomP}
@@
 
-The same holds for the next two steps in which \tsc{f2} and \tsc{f3} are merged: the structure can still be spelled out as \tit{'t}.
+\end{frame}
 
-\ex. \begin{forest} boom
+\begin{frame}
+
+\begin{forest} boom
 [\tsc{datP}
@@
 
-Then \tsc{f4} is merged, as shown in \ref{ex:f4no}.
-\ref{ex:entryt} can no longer spell out the structure, because it does not contain \tsc{f4}.
-There is also no other candidate to spell out the structure as it is.
+\end{frame}
 
-\ex. \begin{forest} boom
+\begin{frame}
+
+\begin{forest} boom
 [\tsc{insP}
@@
 
-According to the spellout algorithm in \ref{ex:spellout}, it should be attempted to move the spec of the complement of \tsc{f4}.
-However, there is no specifier in \ref{ex:f4no}, so this does not apply.
-The second movement option is complement movement.
-The complement of \tsc{f4} moves to the specifier of \tsc{insP}, resulting in the structure in \ref{ex:f4comp}.
-The lexicon does not contain an entry with \tsc{insP} which contains only \tsc{f4}.\footnote{\tit{Met} `with' is not a candidate, because the syntactic structure has a unary bottom and the lexical structure has a binary bottom.}
+\end{frame}
 
-\ex. \begin{forest} boom
-[\tsc{datP}
-    [\tsc{datP}
-        [\tsc{f3}]
-        [\tsc{accP}
-           [\tsc{f2}]
-           [\tsc{nomP}
-               [\tsc{f1}]
-               [ΣP
-                   [Σ]
-                   [\tsc{thingP}
-                       [\tsc{thing}, roof]
-                   ]
-               ]
-           ]
-        ]
-    ]
-    {\draw (.east) node[right]{⇒ \tit{'t}}; }
-    [\tsc{insP}
-        [\tsc{f4}]
-    ]
-    {\draw (.east) node[right]{⇒ }; }
-]
-\end{forest}\label{ex:f4comp}
+\begin{frame}
 
-As I formulated in the introduction of this section, the operation called backtracking is triggered (see \ref{ex:backtracking}).
-This means that the derivation goes back to the previous cycle, and the next option for that cycle is tried.
-In this case, the previous cycle is the one in which \tsc{f3} is merged.
-The next option for that cycle is spec-to-spec movement.
-As there is no specifier, this does not apply.
-The option after that is complement movement, shown in \ref{ex:f3comp}.
-However, there is no match in the lexicon for an \tsc{datP} that contains only \tsc{f3}.
-
-\ex. \begin{forest} boom
-[\tsc{accP}
-    [\tsc{accP}
-       [\tsc{f2}]
-       [\tsc{nomP}
-           [\tsc{f1}]
-           [ΣP
-               [Σ]
-               [\tsc{thingP}
-                   [\tsc{thing}, roof]
-               ]
-           ]
-       ]
-    ]
-    {\draw (.east) node[right]{⇒ \tit{'t}}; }
-    [\tsc{datP}
-        [\tsc{f3}]
-    ]
-    {\draw (.east) node[right]{⇒ }; }
-]
-\end{forest}\label{ex:f3comp}
-
-This means that backtracking proceeds further, into the cycle in which \tsc{f2} was merged.
-Again, spec-to-spec movement does not apply because there is no specifier, and complement movement can be tried, but there is no fitting lexical entry available.
-The same holds for the cycle in which \tsc{f1} is merged.
-
-The situation changes when the derivation comes to the cycle in which Σ was merged.
-At this stage, \tsc{thing} was realized as \tit{'r}.
-Again there was no specifier, spec-to-spec movement does not apply.
-However, complement movement provides a structure that is a match for the lexical entry in \ref{ex:entrymee}: \tit{-mee}.\footnote{This picture resembles the proposal of \citep{abels2003diss} in that not the whole complement of P is moved but only a part is subextracted.
-The current analysis differs in that the movement is not syntactically driven but by spellout.}
-
-\ex. \begin{forest} boom
+\begin{forest} boom
 [ΣP
@@
 
-From this point on the previously unmerged features are merged again one by one. First, \tsc{f1} is merged again, shown in \ref{ex:f1again}. No match exists for this syntactic structure.
+\end{frame}
 
-\ex. \begin{forest} boom
+\begin{frame}
+
+\begin{forest} boom
 [\tsc{nomP}
@@
 
-Following the spellout algorithm, the next step is spec-to-spec movement. The result is shown in \ref{ex:f1spec}. In that configuration \tsc{f1} can be realized together with Σ as \tit{-mee}.
+\end{frame}
 
-\ex. \begin{forest} boom
+\begin{frame}
+
+\begin{forest} boom
 [\tsc{nomP}
@@
 
-The same happens for \tsc{f2}, \tsc{f3} and \tsc{f4}.
-The features are merged one at a time, there is no spellout after merging the feature, but there is a spellout after spec-to-spec movement.
-I show the situation after \tsc{f4} is realized as  \ref{ex:spellout'rmee}.
+\end{frame}
 
-\ex. \begin{forest} boom
+\begin{frame}
+
+\begin{forest} boom
 [\tsc{insP}
@@
 
-I skip over the details of how \tit{w} and \tit{a} end up in their positions.\footnote{I assume that \tsc{wP} and \tsc{deixP} are both complex specifiers that are created after \tsc{thing} is spelled out in \ref{ex:thingspellout}.
-After each instance of merge after that, backtracking takes place, the complex specifier is detached from the structure and the case features are spelled out together with \tsc{thing} or as the postposition -\tit{mee}.} The final result of the structure for \tit{waar-mee} `with what' look as in \ref{ex:spelloutwaar-mee}.
+\end{frame}
 
-\ex. \begin{forest} boom
+\begin{frame}
+
+\begin{forest} boom
 [\tsc{\tsc{wP}}
@@
 
-A consequence of analyzing \tit{-mee} `with' as a postposition is that \tit{'r} and \tit{-mee} always form a constituent to the exclusion of \tit{w} and \tit{a}.
-At first sight this seems problematic, because it is possible for \tit{waar} `where' to \tit{-mee} `with'.
-I repeat the relevant example in \ref{ex:meestranded}.
+\end{frame}
+
+\begin{frame}
 
@@
 
-There is no constituent in \ref{ex:spelloutwaar-mee} that contains \tit{waar} but not \tit{-mee}, so it is not possible to move \tit{waar} from \ref{ex:spelloutwaar-mee} and strand \tit{mee} in the process.
-To resolve this situation I follow \citet{noonan2017dutch} in assuming that the phrase containing the adposition (\tit{-mee}) can syntactically move to a position higher in the structure.
-Evidence that \tit{mee} `with' has moved comes from the ungrammaticality of \ref{ex:meeend}.
-This shows that \tit{mee} `with' cannot be stranded in its base position (see also \ref{ex:const3stage}).
-
 \exg. *Ik heb gekocht waar jij schildert mee.\\
@@
 
-The movement of the adposition has the typical distribution of that of verbal particles (cf.
-\citealt{riemsdijk1978,noonan2017dutch}.
-The trigger for the movement of \tit{mee} could be the feature Σ (which is contained in \tit{mee} `with`), associated with weak pronouns.
-Allowing \tit{mee} to subextract from the \tsc{w}P resolves the issue.
-With \tit{-mee} having moved out, the \tsc{wP} only contains features that are realized as \tit{waar}, and it moves to the left edge of the clause, resulting in the surface order in \ref{ex:meestranded}.
+\end{frame}
 
-So far I showed how \tit{waar-mee} `with what' is derived if all syntactic features form a constituent.
-Next I address how \tit{waar-mee} `with what' is blocked and \tit{met wat} `with what' appears when the features do not form a proper constituent is derived.
-An example of a situation in which all features do not form a constituent is given in \ref{ex:noconst}.
+\begin{frame}
 
-\exg. Ik schilder met wat jij hebt gekocht.\\
- I paint with what you have bought\\
- `I paint with what you bought.'\label{ex:noconst}
+\ex.
+\a. \tit{met} --- \tit{mee}
+\b. \tit{tot} --- \tit{toe}
 
-I start at the point at which \tit{wat} `what' is part of a syntactic structure with the rest of a relative clause as a sister.
-Even though \tsc{f3} is not part of the embedded clause, I already added it to the structure.
-While it is unclear why, syncretic forms behave differently in that they seem to resolve case conflicts in free relatives and related phenomena (cf.
-\citealt{groos1981,pullum1986,ingria1990}).
-I give the syntactic structure from which I start in \ref{ex:metwatst}.
+\ex. CVt
+\pause
 
-\ex. \begin{forest} boom
-[CP
-    [\tsc{\tsc{wP}}
-        [\tsc{\tsc{wP}}
-            [\tsc{w}, roof]
-        ]
-        {\draw (.east) node[right]{⇒ \tit{w}}; }
-        [\tsc{deixP}
-            [\tsc{deixP}
-                [\tsc{deix}, roof]
-            ]
-            {\draw (.east) node[right]{⇒ \tit{a}}; }
-            [\tsc{datP}
-                [\tsc{f3}]
-                [\tsc{accP}
-                   [\tsc{f2}]
-                   [\tsc{nomP}
-                       [\tsc{f1}]
-                       [ΣP
-                           [Σ]
-                           [\tsc{thingP}
-                               [\tsc{thing}, roof]
-                           ]
-                       ]
-                   ]
-                ]
-            ]
-            {\draw (.east) node[right]{⇒ \tit{'t}}; }
-        ]
-    ]
-    [CP
-        [..,roof]
-    ]
-]
-\end{forest}\label{ex:metwatst}
+\ex.
+\a. \tit{in} --- \tit{in}
+\b. \tit{van} --- \tit{van}
+\b. \tit{op} --- \tit{op}
 
-At this point \tsc{f4} is merged, as shown in \ref{ex:f4metwat}.
-Because of the presence of the CP, there is no possibility for \tsc{f4} to be spelled out, even after the regular movements and backtracking.
+\end{frame}
 
-\ex. \begin{forest} boom
-[\tsc{insP}
-    [\tsc{f4}]
-    [CP
-        [\tsc{\tsc{wP}}
-            [\tsc{\tsc{wP}}
-                [\tsc{w}, roof]
-            ]
-            {\draw (.east) node[right]{⇒ \tit{w}}; }
-            [\tsc{deixP}
-                [\tsc{deixP}
-                    [\tsc{deix}, roof]
-                ]
-                {\draw (.east) node[right]{⇒ \tit{a}}; }
-                [\tsc{accP}
-                   [\tsc{f2}]
-                   [\tsc{nomP}
-                       [\tsc{f1}]
-                       [ΣP
-                           [Σ]
-                           [\tsc{thingP}
-                               [\tsc{thing}, roof]
-                           ]
-                       ]
-                   ]
-                ]
-                {\draw (.east) node[right]{⇒ \tit{'t}}; }
-            ]
-        ]
-        [CP
-            [..,roof]
-        ]
-    ]
-]
-\end{forest}\label{ex:f4metwat}
+\appendix
 
-The last resort possibility to spell out features is set in motion: a complex specifier is created, as described in \ref{ex:specformation}. This is illustrated in \ref{ex:metmetwat}.
+\begin{frame}{References}
 
-\ex. \begin{forest} boom
-[\tsc{insP}
-    [\tsc{insP}
-        [\tsc{f4},roof]
-    ]
-    {\draw (.east) node[right]{⇒ \tit{met}}; }
-    [CP
-        [\tsc{\tsc{wP}}
-            [\tsc{\tsc{wP}}
-                [\tsc{w}, roof]
-            ]
-            {\draw (.east) node[right]{⇒ \tit{w}}; }
-            [\tsc{deixP}
-                [\tsc{deixP}
-                    [\tsc{deix}, roof]
-                ]
-                {\draw (.east) node[right]{⇒ \tit{a}}; }
-                [\tsc{accP}
-                   [\tsc{f2}]
-                   [\tsc{nomP}
-                       [\tsc{f1}]
-                       [ΣP
-                           [Σ]
-                           [\tsc{thingP}
-                               [\tsc{thing}, roof]
-                           ]
-                       ]
-                   ]
-                ]
-                {\draw (.east) node[right]{⇒ \tit{'t}}; }
-            ]
-        ]
-        [CP
-            [..,roof]
-        ]
-    ]
-]
-\end{forest}\label{ex:metmetwat}
+	\scriptsize{
+		\printbibliography
+	}
 
-This section showed how the instrumental inanimate relative pronoun is realized as \tit{waar-mee} `with what' when all relevant features form a constituent, and how \tit{met wat} `with what' appears when they do not.
-
-\section{Conclusion and discussion}\label{sec:conclusion}
-
-In this paper, I discussed the instrumental \tsc{r}-pronoun and postposition \tit{waar-mee} `with what' in Dutch.
-The main intuition is that this form appears when features of an instrumental inanimate object form a proper constituent.
-The form cannot appear, and \tit{met wat} `with what` surfaces instead, when all relevant features do not form a proper constituent.
-The described pattern follows from a core assumption in Nanosyntax: phrasal spellout spells out constituents \citep{starke2009}.
-
-Under this analysis, there is no need for a filter that rules out a combination of a preposition and an inanimate pronoun.
-As long as the relevant features form a proper constituent, the spellout algorithm ensures the \tsc{r}-pronoun and postposition takes precedence over the other form.
-The fact that locatives are syncretic with \tsc{r}-pronouns is not a coincidence.
-The lexicon contains a single entry for a locative, which is the one used for \tsc{r}-pronouns as well.
-The change in placement of the adposition is a consequence of spellout too.
-\tit{Mee} `with' is a postposition and is stored differently from the preposition \tit{met} `with', which leads to the correct placement with different constituency.
-The fact that \tit{met} `with' and \tit{mee} `with' differ phonologically can also be captured by storing them as two separate lexical entries.
-
-In the remainder of this section I discuss how this analysis can be extended to other adpositions in Dutch.
-Giving \tit{met} `with' and \tit{-mee} `with' two distinct lexical entries has as a consequence that the phonological overlap between them seems like a coincidence.
-This can be questioned, because there is only one more preposition that changes form when it appears postpositionally.
-This preposition is \tit{tot} `to', and it changes into \tit{toe} as a postposition.
-It has in common with \tit{met} `with' that it is the only preposition in Dutch that has the phonological structure CVt.
-For now I take the phonological resemblance to be a relic from the past without having any influence on the synchronic data.
-
-In all other cases the adposition does not change form when it combines with an \tsc{r}-pronoun, e.g.
-\tit{in} `in'.
-If this proposal is on the right track, elements as \tit{in} can be used as either a preposition or as a postposition.
-The lexical entry should then be usable as pre-element and as post-element, so it needs to have a binary bottom and a unary foot simultaneously.
-The lexical entry in \ref{ex:presuf} would be a candidate for such an element.
-YP can be inserted as a post-element, and XP can be inserted via the Superset Principle as a pre-element.
-
-\ex. \begin{forest} boom
-[YP
-    [XP
-        [X,roof]
-    ]
-    [YP
-        [Y]
-    ]
-]
-{\draw (.east) node[right]{⇔ \tit{in}}; }
-\end{forest}\label{ex:presuf}
-
-I leave it to future research to investigate such a proposal.
-
-\printbibliography
+\end{frame}
 

### 2020-04-16 presentation nanolab/presentation.tex
voo rnieuw starten

@@
 	\usecolortheme[named=goethe]{structure}
-	%\usefonttheme{serif}  % or try serif, structurebold, ...
+	% \usefonttheme{serif}  % or try serif, structurebold, ...
 	\setbeamertemplate{navigation symbols}{}
@@
 }
+
+\renewcommand{\eachwordone}{\sffamily}
+\renewcommand{\eachwordtwo}{\sffamily}
+\renewcommand{\eachwordthree}{\sffamily}
 
@@
 
-\exg. Ik schilder met een kwast.\\
+\exg. Ik schilder \tbf{met} een kwast.\\
  I paint with a brush\\
@@
 
-\exg. Ik zie 't.\\
+\exg. Ik zie \tbf{t}.\\
  I see it\\
@@
 
-\exg. *Ik schilder met 't.\\
+\exg. *Ik schilder \tbf{met} \tbf{t}.\\
  I paint with it\\
@@
 
-\exg. Ik schilder r -mee.\\
+\exg. Ik schilder \tbf{r} \tbf{-mee}.\\
  I paint there -with\\
@@
 
-\centering{\Large{Why *\tit{met 't}?}}
+\centering{\Large{Why *\tit{met t}?}}
 
@@
 
-Instrumental in Dutch
-\ex. *met t
+*\tit{met t} vs. \tit{r mee}
 
-\ex. r mee
+\vspace{1em}
 
@@
 \begin{itemize}
-	\item r-pronouns and locatives syncretic \pause
 	\item \tit{met} becomes \tit{mee} \pause
-	\item position of adposition
+	\item position of adposition differs \pause
+	\item \tsc{r}-pronouns and locatives are syncretic
 \end{itemize}
@@
 
-\exg. Ik zie haar/hem.\\
+\exg. Ik zie \tbf{haar/hem}.\\
  I see her/him\\
@@
 
-\exg. Ik schilder samen met haar/hem.\\
+\exg. Ik schilder samen \tbf{met} \tbf{haar/hem}.\\
  I paint together with her/him\\
@@
 
-\exg. Ik schilder 'r -mee.\\
+\exg. Ik schilder \tbf{r} \tbf{-mee}.\\
  I paint there -with\\
@@
 
-\exg. *Ik schilder mee 'r.\\
+\exg. *Ik schilder \tbf{mee} \tbf{r}.\\
  I paint with there\\
@@
 \ex.
-\ag. Ik zit 'r op.\\
+\ag. Ik zit \tbf{r} \tbf{op}.\\
  I sit there on\\
  `I am sitting on it.
-\bg. *Ik zit op 't.\\
+\bg. *Ik zit \tbf{op} \tbf{t}.\\
  I sit on it\\
@@
 \ex.
- \ag. Hij zwemt 'r in.\\
+ \ag. Hij zwemt \tbf{r} \tbf{in}.\\
   he swims it-in\\
   `He is swimming there it.'
- \bg. *Hij zwemt in 't.\\
+ \bg. *Hij zwemt \tbf{in} \tbf{t}.\\
   he swims in it\\
@@
 
-\exg. Wat zie jij?\\
+\exg. \tbf{Wat} zie jij?\\
  what see you\\
@@
 
-\exg. *Met wat schilder jij?\\
+\exg. *\tbf{Met} \tbf{wat} schilder jij?\\
  with what paint you\\
@@
 
-\exg. Waar -mee schilder jij?\\
+\exg. \tbf{Waar} \tbf{-mee} schilder jij?\\
  where with paint you with\\
@@
 \ex.\label{ex:headed}
-\ag. Ik schilder met de kwast waar -mee jij ook schildert.\\
+\ag. Ik schilder met de kwast \tbf{waar} \tbf{-mee} jij ook schildert.\\
  I paint with the brush where with you also paint\\
  `I am painting with the brush that you are painting with too.'
-\bg. *Ik schilder met de kwast met wat jij ook schildert.\\
+\bg. *Ik schilder met de kwast \tbf{met} \tbf{wat} jij ook schildert.\\
  I paint with the brush with what you also paint\\
@@
 \ex.\label{ex:headless}
-\ag. Ik schilder waar -mee jij ook schildert.\\
+\ag. Ik schilder \tbf{waar} \tbf{-mee} jij ook schildert.\\
  I paint where with you also paint\\
  `I am painting with what you are painting with too.'
-\bg. *Ik schilder met wat jij ook schildert.\\
+\bg. *Ik schilder \tbf{met} \tbf{wat} jij ook schildert.\\
  I paint with what you also paint\\
@@
 \ex.
-\ag. Ik heb gekocht waar -mee jij schildert.\\
+\ag. Ik heb gekocht \tbf{waar} \tbf{-mee} jij schildert.\\
  I have bought where with you paint\\
  `I bought what you are painting with.'\label{ex:gekochtwaar-mee}
-\bg. *Ik heb gekocht met wat jij schildert.\\
+\bg. *Ik heb gekocht \tbf{met} \tbf{wat} jij schildert.\\
  I have bought with what you paint\\
@@
 \ex.\label{ex:schildermet}
-\ag. *Ik schilder waar -mee jij hebt gekocht.\\
+\ag. *Ik schilder \tbf{waar} \tbf{-mee} jij hebt gekocht.\\
  I paint where with you have bought\\
  `I paint with what you bought.'\label{ex:schilderwaar-mee}
-\bg. Ik schilder met wat jij hebt gekocht.\\
+\bg. Ik schilder \tbf{met} \tbf{wat} jij hebt gekocht.\\
  I paint with what you have bought\\
@@
 \ex.
-\ag. Ik schilder 'r -mee.\\
+\ag. Ik schilder \tbf{r} \tbf{-mee}.\\
  I paint there with\\
  `I am painting with it.'\label{ex:const1}
-\bg. Waar -mee schilder jij?\\
+\bg. \tbf{Waar} \tbf{-mee} schilder jij?\\
 where with paint you with\\
  `What are you painting with?'\label{ex:const2}
-\bg. Ik schilder met de kwast [waar -mee jij ook schildert].\\
+\bg. Ik schilder met de kwast [\tbf{waar} \tbf{-mee} jij ook schildert].\\
  I paint with the brush where with you also paint\\
  `I am painting with the brush that you are painting with too.'\label{ex:const3}
-\bg. Ik schilder [waar -mee jij ook schildert].\\
+\bg. Ik schilder [\tbf{waar} \tbf{-mee} jij ook schildert].\\
  I paint where with you also paint\\
@@
 \ex.
-\a. [[ik] [[schilder] ['r -mee]]]\label{ex:const1stage}
-\b. [[jij] [[schilder] [waar-mee]]]\label{ex:const2stage}
-\b. [[jij] [[ook] [[schilder] [waar-mee]]]]\label{ex:const3stage}
+\a. [[ik] [[schilder] [\tbf{r -mee}]]]\label{ex:const1stage}
+\b. [[jij] [[schilder] [\tbf{waar-mee}]]]\label{ex:const2stage}
+\b. [[jij] [[ook] [[schilder] [\tbf{waar-mee}]]]]\label{ex:const3stage}
 
@@
 \ex.
-\ag. Ik koop het schilderij.\\
+\ag. Ik koop \tbf{het} \tbf{schilderij}.\\
  I buy the painting\\
  `I am buying the painting.'\label{ex:kopen}
-\bg. Ik schilder met een kwast.\\
+\bg. Ik schilder \tbf{met} \tbf{een} \tbf{kwast}.\\
  I paint with a brush\\
@@
 
-\end{frame}
-
-\ex.
-\ag. Ik koop het schilderij.\\
- I buy the painting\\
- `I am buying the painting.'\label{ex:kopen}
-\bg. Ik schilder met een kwast.\\
- I paint with a brush\\
- `I am painting with a brush.'\label{ex:schilderen}
-
-\pause
-
-\exg. Ik heb gekocht [waar -mee jij schildert].\\
+\exg. Ik heb gekocht [\tbf{waar} \tbf{-mee} jij schildert].\\
  I have bought where with you paint\\
@@
 
-\exg. Ik schilder met [wat jij hebt gekocht].\\
+\exg. Ik schilder \tbf{met} [\tbf{wat} jij hebt gekocht].\\
  I paint with what you have bought\\
@@
 
+\end{frame}
+
 \begin{frame}
 
-\exg. [Met [wat [voor [potloden]]] teken jij?\\
+\exg. [\tbf{Met} [\tbf{wat} [voor [potloden]]] teken jij?\\
  with what for pencils draw you\\
  `What kind of pencils do you with?'\label{ex:watwasfur}
-\exg. Ik wil graag thee [met [wat [suiker]]].\\
+\exg. Ik wil graag thee [\tbf{met} [\tbf{wat} [suiker]]].\\
  I want please tea with some sugar\\
@@
 
-\begin{frame}
+\begin{frame}{ \tit{w} and \tit{a}}
 
-\ex. \begin{forest}
+\begin{forest}
 [\tsc{wP}
@@
 
-\ex. \begin{forest}
+\pause
+
+\begin{forest}
 [\tsc{deixP}
@@
 
-\begin{frame}{Case}
+\begin{frame}{\tit{t}}
 
 \ex.\label{ex:tsubobj}
-\ag. 't Staat in de hal.\\
+\ag. t Staat in de hal.\\
  \tsc{3sg.n.nom} stands in the hallway\\
  `It is standing in the hallway.'\label{ex:tnoclitic}
-\bg. Ik zie 't.\\
+\bg. Ik zie t.\\
  I see \tsc{3sg.n.acc}\\
  `I see it.'
-\bg. Ik heb 't een klap gegeven.\\
+\bg. Ik heb t een klap gegeven.\\
  I have \tsc{3sg.n.dat} a hit given\\
@@
 
-\begin{frame}
+\begin{frame}{\tit{t}}
 
 \ex.
-\ag. *Hij en 't staan in de hoek.\\
+\ag. *Hij en t staan in de hoek.\\
  he and it stand in the corner\\
@@
 
-\begin{frame}
+\begin{frame}{\tit{t}}
 
-\ex. \begin{forest} boom
+\begin{forest} boom
  [\tsc{datP}
@@
  ]
- {\draw (.east) node[right]{⇔ \tit{'t}}; }
+ {\draw (.east) node[right]{⇔ \tit{t}}; }
  \end{forest}\label{ex:entryt}
@@
 
-\begin{frame}
+\begin{frame}{\tit{r}}
 
-\exg. Ik ben 'r al geweest.\\
+\exg. Ik ben r al geweest.\\
  I am there already been\\
@@
 
-\ex. \begin{forest} boom
+\begin{forest} boom
 [\tsc{loc}P
@@
 ]
-{\draw (.east) node[right]{⇔ \tit{'r}}; }
+{\draw (.east) node[right]{⇔ \tit{r}}; }
 \end{forest}\label{ex:entryr}
@@
 
-	\begin{tabularx}{\textwidth}{ccccccc}
+	\begin{tabular}{cc}
 	\toprule
@@
 	\midrule
-	\tsc{nom} & 't         \\
-	\tsc{acc} & 't         \\
-	\tsc{dat} & 't         \\
-	\tsc{ins} & -r -mee    \\
+	\tsc{nom} & t         \\
+	\tsc{acc} & t         \\
+	\tsc{dat} & t         \\
+	\tsc{ins} & r -mee    \\
 	\bottomrule
-\end{tabularx}
+\end{tabular}
 
@@
 
-\begin{frame}
+\begin{frame}{\tit{mee}}
 
-\ex. \begin{forest} boom
+\begin{forest} boom
 [\tsc{insP}
@@
 
-\begin{frame}
+\begin{frame}{\tit{met}}
 
-\ex. \begin{forest} boom
+\begin{forest} boom
 [\tsc{insP}
@@
  ]
-{\draw (.east) node[right]{⇒ \tit{'r}}; }
+{\draw (.east) node[right]{⇒ \tit{r}}; }
 \end{forest}\label{ex:thingspellout}
@@
 ]
-{\draw (.east) node[right]{⇒ \tit{'t}}; }
+{\draw (.east) node[right]{⇒ \tit{t}}; }
 \end{forest}\label{ex:thingf1}
@@
 	]
-	{\draw (.east) node[right]{⇒ \tit{'t}}; }
+	{\draw (.east) node[right]{⇒ \tit{t}}; }
 	\end{forest}
@@
 ]
-{\draw (.east) node[right]{⇒ \tit{'t}}; }
+{\draw (.east) node[right]{⇒ \tit{t}}; }
 \end{forest}
@@
 	 ]
-	 {\draw (.east) node[right]{⇒ \tit{'r}}; }
+	 {\draw (.east) node[right]{⇒ \tit{r}}; }
 	 [ΣP
@@
    ]
-   {\draw (.east) node[right]{⇒ \tit{'r}}; }
+   {\draw (.east) node[right]{⇒ \tit{r}}; }
    [\tsc{nomP}
@@
     ]
-    {\draw (.east) node[right]{⇒ \tit{'r}}; }
+    {\draw (.east) node[right]{⇒ \tit{r}}; }
     [\tsc{insP}
@@
 ]
-\end{forest}\label{ex:spellout'rmee}
+\end{forest}\label{ex:spelloutrmee}
 
@@
 						]
-						{\draw (.east) node[right]{⇒ \tit{'r}}; }
+						{\draw (.east) node[right]{⇒ \tit{r}}; }
 						[\tsc{insP}

### 2020-04-16 presentation nanolab/presentation.tex
presentation thursday
am ende noch ein bisschen

@@
 
-\end{frame}
-
-\begin{frame}
-
-\exg. *Ik schilder \tbf{met} \tbf{t}.\\
- I paint with it\\
- `I am painting with it.'\label{ex:neemett}
-
 \pause
@@
 \exg. Ik schilder \tbf{r} \tbf{-mee}.\\
- I paint there -with\\
+ I paint \tsc{r} -with\\
  `I am painting with it.'\label{ex:jarmee}
@@
 
-*\tit{met t} vs. \tit{r mee}
+\centering{
+*\tit{met t} \hspace{1em} | \hspace{1em} \tit{r mee}}
 
@@
 \begin{itemize}
+	\item positions are reversed \pause
 	\item \tit{met} becomes \tit{mee} \pause
-	\item position of adposition differs \pause
-	\item \tsc{r}-pronouns and locatives are syncretic
+	\item \tit{t} becomes \tit{r}, which is syncretic with locative
 \end{itemize}
+
+\vspace{1em}
+
+\tit{rmee} (and not \tit{met t}) appears when all features form a proper constituent
 
@@
 
-\exg. Ik zie \tbf{haar/hem}.\\
- I see her/him\\
- `I see her/him.'\label{ex:aniobj}
+\ex. rmee ⇒ waarmee
 
-\exg. Ik zie \tbf{t}.\\
- I see it\\
- `I see it.'\label{ex:inaniobj}
+\ex. met t ⇒ met wat
 
-\end{frame}
-
-\begin{frame}
-
-\exg. Ik schilder samen \tbf{met} \tbf{haar/hem}.\\
- I paint together with her/him\\
- `I am painting together with her/him.'\label{ex:prepani}
-
-\exg. *Ik schilder \tbf{met} \tbf{t}.\\
- I paint with it\\
- `I am painting with it.'\label{ex:prephet}
-
-\exg. Ik schilder \tbf{r} \tbf{-mee}.\\
- I paint there -with\\
- `I am painting with it.'\label{ex:preper}
-
-\exg. *Ik schilder \tbf{mee} \tbf{r}.\\
- I paint with there\\
- `I am painting with it.'\label{ex:erprep}
-
-\end{frame}
-
-\begin{frame}
-
-\ex.
-\ag. Ik zit \tbf{r} \tbf{op}.\\
- I sit there on\\
- `I am sitting on it.
-\bg. *Ik zit \tbf{op} \tbf{t}.\\
- I sit on it\\
- `I am sitting on it.
-
-\ex.
- \ag. Hij zwemt \tbf{r} \tbf{in}.\\
-  he swims it-in\\
-  `He is swimming there it.'
- \bg. *Hij zwemt \tbf{in} \tbf{t}.\\
-  he swims in it\\
-  `He is swimming in it.'
-
-\end{frame}
-
-\begin{frame}
+\pause
+\vspace{1em}
 
@@
 \exg. \tbf{Waar} \tbf{-mee} schilder jij?\\
- where with paint you with\\
+ \tsc{r} with paint you with\\
  `What are you painting with?'\label{ex:waar-mee}
@@
 \ag. Ik schilder met de kwast \tbf{waar} \tbf{-mee} jij ook schildert.\\
- I paint with the brush where with you also paint\\
+ I paint with the brush \tsc{r} with you also paint\\
  `I am painting with the brush that you are painting with too.'
@@
 
+ \pause
+
 \ex.\label{ex:headless}
 \ag. Ik schilder \tbf{waar} \tbf{-mee} jij ook schildert.\\
- I paint where with you also paint\\
+ I paint \tsc{r} with you also paint\\
  `I am painting with what you are painting with too.'
@@
 \ag. Ik heb gekocht \tbf{waar} \tbf{-mee} jij schildert.\\
- I have bought where with you paint\\
+ I have bought \tsc{r} with you paint\\
  `I bought what you are painting with.'\label{ex:gekochtwaar-mee}
@@
 \ag. *Ik schilder \tbf{waar} \tbf{-mee} jij hebt gekocht.\\
- I paint where with you have bought\\
+ I paint \tsc{r} with you have bought\\
  `I paint with what you bought.'\label{ex:schilderwaar-mee}
@@
 \ag. Ik schilder \tbf{r} \tbf{-mee}.\\
- I paint there with\\
+ I paint \tsc{r} with\\
  `I am painting with it.'\label{ex:const1}
 \bg. \tbf{Waar} \tbf{-mee} schilder jij?\\
-where with paint you with\\
+ \tsc{r} with paint you with\\
  `What are you painting with?'\label{ex:const2}
 \bg. Ik schilder met de kwast [\tbf{waar} \tbf{-mee} jij ook schildert].\\
- I paint with the brush where with you also paint\\
+ I paint with the brush \tsc{r} with you also paint\\
  `I am painting with the brush that you are painting with too.'\label{ex:const3}
 \bg. Ik schilder [\tbf{waar} \tbf{-mee} jij ook schildert].\\
- I paint where with you also paint\\
+ I paint \tsc{r} with you also paint\\
  `I am painting with what you are painting with too.'\label{ex:const4}
@@
 \exg. Ik heb gekocht [\tbf{waar} \tbf{-mee} jij schildert].\\
- I have bought where with you paint\\
+ I have bought \tsc{r} with you paint\\
  `I bought what you are painting with.'\label{ex:mismatchwaar-mee}
@@
  with what for pencils draw you\\
- `What kind of pencils do you with?'\label{ex:watwasfur}
+ `What kind of pencils are you drawing with?'\label{ex:watwasfur}
+
+\pause
+
 \exg. Ik wil graag thee [\tbf{met} [\tbf{wat} [suiker]]].\\
@@
 
-\ex.\label{ex:decompose}
-\ag. w -aa -r -mee\\
-\tsc{w} -\tsc{deix} -\tsc{loc} -\tsc{ins}\\
-\bg. met w -a -t\\
-\tsc{ins} \tsc{w} -\tsc{deix} -\tsc{n.sg}\\
-\z.
-\z.
+\ex. w -aa -r -mee
+
+\ex. met w -a -t
 
@@
 
-\begin{frame}{ \tit{w} and \tit{a}}
+\begin{frame}
 
@@
 
-\begin{frame}{\tit{t}}
+\begin{frame}
 
@@
 
-\begin{frame}{\tit{r}}
+\begin{frame}
 
 \exg. Ik ben r al geweest.\\
- I am there already been\\
+ I am \tsc{r} already been\\
  `I have already been there.'
@@
 
-\begin{frame}{\tit{mee}}
+\begin{frame}
 
@@
 
-\begin{frame}{\tit{met}}
+\begin{frame}
 
@@
 \begin{frame}
+
+	show fseq
 
@@
 
+	\begin{itemize}
+		\item rmee is nothing special anymore, just a result of spellout
+		\item r is ambiguous between thing and location, r is a caseless base
+		\item met and mee are separate lexical entries, so the system allows for them to phonologically differ
+		\item mee is a postposition, met is a preposition
+	\end{itemize}
+
+\end{frame}
+
+\begin{frame}
+
+	what happens to \tit{met wat}?
+
+	--give a tree of halfway there--
+
+\end{frame}
+
+\begin{frame}
+
+\exg. Ik zie \tbf{haar/hem}.\\
+ I see her/him\\
+ `I see her/him.'\label{ex:aniobj}
+
+\exg. Ik zie \tbf{t}.\\
+ I see it\\
+ `I see it.'\label{ex:inaniobj}
+
+\exg. Ik schilder samen \tbf{met} \tbf{haar/hem}.\\
+ I paint together with her/him\\
+ `I am painting together with her/him.'\label{ex:prepani}
+
+\exg. *Ik schilder \tbf{met} \tbf{t}.\\
+ I paint with it\\
+ `I am painting with it.'\label{ex:prephet}
+
+\exg. Ik schilder \tbf{r} \tbf{-mee}.\\
+ I paint \tsc{r} -with\\
+ `I am painting with it.'\label{ex:preper}
+
+gender and number between sigma and case -- make tree
+
+\end{frame}
+
+\begin{frame}
+
+list of postpositions and prepositions
+maybe i have a tree
+
+\ex.
+\ag. Ik zit \tbf{r} \tbf{op}.\\
+ I sit \tsc{r} on\\
+ `I am sitting on it.
+\bg. *Ik zit \tbf{op} \tbf{t}.\\
+ I sit on it\\
+ `I am sitting on it.
+
+\ex.
+ \ag. Hij zwemt \tbf{r} \tbf{in}.\\
+  he swims it-in\\
+  `He is swimming in it.'
+ \bg. *Hij zwemt \tbf{in} \tbf{t}.\\
+  he swims in it\\
+  `He is swimming in it.'
+
+\pause
+
+verbal particles
+
+\ex. CVt
+\a. \tit{met} --- \tit{mee}
+\b. \tit{tot} --- \tit{toe}
+
+\end{frame}
+
+\begin{frame}
+
+	repeat example i always use
+
 \exg. Ik heb gekocht waar jij mee schildert.\\
@@
  `I bought what you are painting with.'\label{ex:meestranded}
+
+	look at story again
 
@@
 
-\begin{frame}
-
-\ex.
-\a. \tit{met} --- \tit{mee}
-\b. \tit{tot} --- \tit{toe}
-
-\ex. CVt
-\pause
-
-\ex.
-\a. \tit{in} --- \tit{in}
-\b. \tit{van} --- \tit{van}
-\b. \tit{op} --- \tit{op}
-
-\end{frame}
-
-\appendix
-
-\begin{frame}{References}
-
-	\scriptsize{
-		\printbibliography
-	}
-
-\end{frame}
-
 \end{document}

### 2020-04-20 presentation nanolab/presentation.tex
toch nog
presentation for syntax colloquium

--- 2020-04-16 presentation nanolab/presentation.tex
@@
 \bibliography{../fenna-files/references}{}
+
+\usepackage{multicol}
 
@@
 \author{Fenna Bergsma}
-\date{Nanolab\\ \today}
+\date{Syntax colloquium\\ \today}
 \institute{Goethe-Universität Frankfurt}
@@
 
-\exg. Ik schilder \tbf{met} een kwast.\\
- I paint with a brush\\
- `I am painting with a brush.'\label{ex:metdp}
+\exg. Jij schildert \tbf{met} \tbf{een} \tbf{kwast}.\\
+ you paint with a brush\\
+ `You are painting with a brush.'\label{ex:metwat}
 
@@
 
-\exg. Ik zie \tbf{t}.\\
- I see it\\
- `I see it.'\label{ex:tverb}
+\exg. \tbf{Wat} zie jij?\\
+ what see you\\
+ `What do you see?'\label{ex:wat}
 
@@
 
-\exg. *Ik schilder \tbf{met} \tbf{t}.\\
- I paint with it\\
- `I am painting with it.'
+\exg. *\tbf{Met} \tbf{wat} schilder jij?\\
+ with what paint you\\
+ `What are you painting with?'\label{ex:metwat}
+
+\pause
+
+\exg. \tbf{Waarmee} schilder jij?\\
+ {where with} paint you with\\
+ `What are you painting with?'\label{ex:waar-mee}
+
+\end{frame}
+
+\begin{frame}
+
+\exg. Womit malst du?\\
+ {where with} paint you\\
+ `What are you painting with?'
+
+\pause
+
+\exg. Waa\tbf{r}mee schilder jij?\\
+ {where with} paint you with\\
+ `What are you painting with?'\label{ex:waar-mee}
+
+\end{frame}
+
+\begin{frame}
+
+\exg. Worauf kletterst du?\\
+ {where on} climb you\\
+ `What are you climbing onto?'
+
+\exg. Wo bist du \tbf{(d)r}auf geklettert?\\
+ where are you on climbed\\
+ `What did you climb on?'
+
+\pause
+
+\exg. Waa\tbf{r} ben jij op geklommen?\\
+ where are you on climbed\\
+ `What did you climb on?'
 
@@
  I paint with it\\
- `I am painting with it.'\label{ex:neemett}
+ `I am painting with it.'
 
@@
 
-\centering{\Large{Why *\tit{met t}?}}
+\centering{\Large{Why *\tit{met wat}?}}
+
+\vspace{3em} \citep{riemsdijk1978}
 
@@
 
-*\tit{met t} vs. \tit{r mee}
+\centering{
+*\tit{met wat} \hspace{1em} | \hspace{1em} \tit{waar-mee}}
 
@@
 \begin{itemize}
+\item positions are reversed \pause
 \item \tit{met} becomes \tit{mee} \pause
-	\item position of adposition differs \pause
-	\item \tsc{r}-pronouns and locatives are syncretic
+\item \tit{wat} becomes \tit{waar}, which is syncretic with locative \citep{koopman1994}
 \end{itemize}
 
-\end{frame}
+\vspace{1em}\pause
 
-% \section{R-pronouns and constituency}
+\tsc{r}-pronouns are the result of regular spellout mechanisms
 
-% \subsection{Distribution of \tsc{r}-pronouns}
+\pause
 
-\begin{frame}
-
-\exg. Ik zie \tbf{haar/hem}.\\
- I see her/him\\
- `I see her/him.'\label{ex:aniobj}
-
-\exg. Ik zie \tbf{t}.\\
- I see it\\
- `I see it.'\label{ex:inaniobj}
+as long as all features form a proper constituent
 
@@
 
-\exg. Ik schilder samen \tbf{met} \tbf{haar/hem}.\\
- I paint together with her/him\\
- `I am painting together with her/him.'\label{ex:prepani}
-
-\exg. *Ik schilder \tbf{met} \tbf{t}.\\
- I paint with it\\
- `I am painting with it.'\label{ex:prephet}
-
-\exg. Ik schilder \tbf{r} \tbf{-mee}.\\
- I paint there -with\\
- `I am painting with it.'\label{ex:preper}
-
-\exg. *Ik schilder \tbf{mee} \tbf{r}.\\
- I paint with there\\
- `I am painting with it.'\label{ex:erprep}
+\ex.\label{ex:headed}
+\ag. Ik koop de kwast \tbf{waar} \tbf{-mee} jij schildert.\\
+ I buy the brush where with you paint\\
+ `I buy the brush that you are painting with.'
+\bg. *Ik koop de kwast \tbf{met} \tbf{wat} jij schildert.\\
+ I koop the brush with what you paint\\
+ `I buy the brush that you are painting with.'
 
@@
 \ex.
-\ag. Ik zit \tbf{r} \tbf{op}.\\
- I sit there on\\
- `I am sitting on it.
-\bg. *Ik zit \tbf{op} \tbf{t}.\\
- I sit on it\\
- `I am sitting on it.
+\ag. \tbf{Waar} \tbf{-mee} schilder jij?\\
+ where with paint you with\\
+ `What are you painting with?'\label{ex:const2}
+\bg. Ik koop de kwast [\tbf{waar} \tbf{-mee} jij schildert].\\
+ I buy the brush where with you paint\\
+ `I koop the brush that you are painting with.'\label{ex:const3}
 
-\ex.
- \ag. Hij zwemt \tbf{r} \tbf{in}.\\
-  he swims it-in\\
-  `He is swimming there it.'
- \bg. *Hij zwemt \tbf{in} \tbf{t}.\\
-  he swims in it\\
-  `He is swimming in it.'
+\pause
 
-\end{frame}
-
-\begin{frame}
-
-\exg. \tbf{Wat} zie jij?\\
- what see you\\
- `What do you see?'\label{ex:wat}
-
-\exg. *\tbf{Met} \tbf{wat} schilder jij?\\
- with what paint you\\
- `What are you painting with?'\label{ex:metwat}
-
-\exg. \tbf{Waar} \tbf{-mee} schilder jij?\\
- where with paint you with\\
- `What are you painting with?'\label{ex:waar-mee}
-
-\end{frame}
-
-\begin{frame}
-
-\ex.\label{ex:headed}
-\ag. Ik schilder met de kwast \tbf{waar} \tbf{-mee} jij ook schildert.\\
- I paint with the brush where with you also paint\\
- `I am painting with the brush that you are painting with too.'
-\bg. *Ik schilder met de kwast \tbf{met} \tbf{wat} jij ook schildert.\\
- I paint with the brush with what you also paint\\
- `I am painting with the brush that you are painting with too.'
-
-\ex.\label{ex:headless}
-\ag. Ik schilder \tbf{waar} \tbf{-mee} jij ook schildert.\\
- I paint where with you also paint\\
- `I am painting with what you are painting with too.'
-\bg. *Ik schilder \tbf{met} \tbf{wat} jij ook schildert.\\
- I paint with what you also paint\\
- `I am painting with what you are painting with too.'
+\ex. [[jij] [[schilder] [\tbf{waar-mee}]]]\label{ex:const2stage}
 
@@
  `I paint with what you bought.'\label{ex:schildermetwat}
-
-\end{frame}
-
-\begin{frame}
-
-\ex.
-\ag. Ik schilder \tbf{r} \tbf{-mee}.\\
- I paint there with\\
- `I am painting with it.'\label{ex:const1}
-\bg. \tbf{Waar} \tbf{-mee} schilder jij?\\
-where with paint you with\\
- `What are you painting with?'\label{ex:const2}
-\bg. Ik schilder met de kwast [\tbf{waar} \tbf{-mee} jij ook schildert].\\
- I paint with the brush where with you also paint\\
- `I am painting with the brush that you are painting with too.'\label{ex:const3}
-\bg. Ik schilder [\tbf{waar} \tbf{-mee} jij ook schildert].\\
- I paint where with you also paint\\
- `I am painting with what you are painting with too.'\label{ex:const4}
-
-\pause
-
-\ex.
-\a. [[ik] [[schilder] [\tbf{r -mee}]]]\label{ex:const1stage}
-\b. [[jij] [[schilder] [\tbf{waar-mee}]]]\label{ex:const2stage}
-\b. [[jij] [[ook] [[schilder] [\tbf{waar-mee}]]]]\label{ex:const3stage}
 
@@
 
-\ex.\label{ex:decompose}
-\ag. w -aa -r -mee\\
-\tsc{w} -\tsc{deix} -\tsc{loc} -\tsc{ins}\\
-\bg. met w -a -t\\
-\tsc{ins} \tsc{w} -\tsc{deix} -\tsc{n.sg}\\
-\z.
-\z.
+\ex. w -aa \tbf{-r} \tbf{-mee}
+
+\ex. \tbf{met} w -a \tbf{-t}
+
+\pause
+
+\begin{itemize}
+\item late insertion (phonology after syntax)\pause
+\item individual features (no feature bundles)
+\end{itemize}
 
@@
 
-\begin{frame}{ \tit{w} and \tit{a}}
+\begin{frame}
 
-\begin{forest}
+\ex. \begin{forest}
 [\tsc{wP}
@@
 
+\citep{hachem2015}
+
 \pause
 
-\begin{forest}
+\ex. \begin{forest}
 [\tsc{deixP}
@@
 
+\citep[cf.][]{lander2016}
+
 \end{frame}
 
-\begin{frame}{\tit{t}}
+\begin{frame}
 
 \ex.\label{ex:tsubobj}
-\ag. t Staat in de hal.\\
+\ag. T staat in de hal.\\
  \tsc{3sg.n.nom} stands in the hallway\\
@@
 
-\ex.\label{ex:hemsubobj}
-\ag. Hij staat in de hal.\\
-\tsc{3sg.m.nom} stands in the hallway\\
-`He is standing in the hallway.'
-\bg. Ik zie hem.\\
-I see \tsc{3sg.m.acc}\\
-`I see it.'
-\bg. Ik heb hem een klap gegeven.\\
-I have \tsc{3sg.m.dat} a hit given\\
-`I gave him a hit.'
+\end{frame}
+
+\begin{frame}
+
+\label{ex:casetree}
+\ex. \begin{forest} boom
+	[\tsc{insP}
+			[\tsc{f4}]
+			[\tsc{datP}
+					[\tsc{f3}]
+					[\tsc{accP}
+							[\tsc{f2}]
+							[\tsc{nomP}
+									[\tsc{f1}]
+									[X
+											[..,roof]
+									]
+							]
+					]
+			]
+	]
+\end{forest}
+
+\citep{caha2009}
 
@@
 
+\pause
+
+\exg. T staat in de hal.\\
+ \tsc{3sg.n.nom} stands in the hallway\\
+ `It is standing in the hallway.'\label{ex:tnoclitic}
+
 \end{frame}
 
-\begin{frame}{\tit{t}}
+\begin{frame}
 
-\begin{forest} boom
+\label{ex:strengthtree}
+\ex. \begin{forest} boom
+			[CP
+					[C]
+					[ΣP
+							[Σ]
+							[IP
+									[I]
+									[X
+											[..,roof]
+									]
+							]
+					]
+			]
+\end{forest}
+
+\citep{cardinaletti1996}
+
+\end{frame}
+
+\begin{frame}
+
+\ex. \begin{forest} boom
  [\tsc{datP}
@@
                  [Σ]
+								 [IP
+								 		[I]
 		                 [\tsc{thingP}
 		                     [\tsc{thing}, roof]
+										]
                  ]
@@
 
+\citep{cardinaletti1996,kayne2005,caha2009}
+
 \end{frame}
 
-\begin{frame}{\tit{r}}
+\begin{frame}
+
+\ex. \tbf{The Superset Principle} \citep{starke2009}: \\
+	A lexically stored tree matches a syntactic node iff the lexically stored tree contains the syntactic node.
+
+\begin{multicols}{2}
+
+\ex. \begin{forest} boom
+	[\tsc{accP}
+			[\tsc{f2}]
+			[\tsc{nomP}
+					[\tsc{f1}]
+					[ΣP
+							[Σ]
+							[IP
+									[I]
+									[\tsc{thingP}
+											[\tsc{thing}, roof]
+									]
+							]
+					]
+			]
+	]
+\end{forest}\label{ex:tacc}
+
+\ex. \begin{forest} boom
+	[\tsc{nomP}
+			[\tsc{f1}]
+			[ΣP
+					[Σ]
+					[IP
+							[I]
+							[\tsc{thingP}
+									[\tsc{thing}, roof]
+							]
+					]
+			]
+	]
+\end{forest}\label{ex:tnom}
+
+\end{multicols}
+
+\end{frame}
+
+\begin{frame}
 
@@
 
-\begin{forest} boom
+\pause
+
+\ex. \begin{forest} boom
 [\tsc{loc}P
@@
 
+\citep{baunaz2018}
+
+\pause
+
+\ex. \tbf{The Elsewhere Condition} (\citealt{kiparsky1973}, formulated as in \citealt{caha2020}):\\
+When two entries can spell out a given node, the more specific entry wins. Under the Superset Principle governed insertion, the more specific entry is the one which has fewer unused features.
+
+\pause
+
+\ex. \begin{forest} boom
+ [\tsc{thingP}
+     [\tsc{thing}, roof]
+ ]
+{\draw (.east) node[right]{⇒ \tit{r}}; }
+\end{forest}
+
 \end{frame}
@@
 
+\centering{
 \begin{tabular}{cc}
@@
 \end{tabular}
+}
 
@@
 
-\begin{frame}{\tit{mee}}
+\begin{frame}
 
-\begin{forest} boom
+\ex. \begin{forest} boom
 [\tsc{insP}
@@
                     [Σ]
+										[IP
+												[I]
+										]
                 ]
@@
 
-\end{frame}
+\pause
 
-\begin{frame}{\tit{met}}
-
-\begin{forest} boom
+\ex. \begin{forest} boom
 [\tsc{insP}
@@
 
-\begin{forest} boom
+[W [\tsc{deix} [\tsc{f4} [\tsc{f3} [\tsc{f2} [\tsc{f1} [Σ [I [\tsc{thing}] ] ] ] ] ] ] ] ]
+
+\end{frame}
+
+\begin{frame}
+
+\ex. Merge F and \label{ex:spellout}
+	 \a. Spell out FP.
+	 \b. If (a) fails, attempt movement of the spec of the complement of \tsc{f}, and retry (a).
+	 \b. If (b) fails, move the complement of \tsc{f}, and retry (a).
+
+\pause
+
+\ex. \tbf{Cyclic Override} \citep{starke2018}:\\
+	Lexicalisation at a node XP overrides any previous match at a phrase contained in XP.
+
+\pause
+
+\ex. \tbf{Backtracking} \citep{starke2018}:\\
+	When spellout fails, go back to the previous cycle, and try the next option for that cycle.\label{ex:backtracking}
+
+\pause
+
+\ex. \tbf{Spec Formation} \citep{starke2018}:\\
+	If Merge F has failed to spell out (even after backtracking), try to spawn a new derivation providing the feature F and merge that with the current derivation, projecting the feature F at the top node.\label{ex:specformation}
+
+\end{frame}
+
+\begin{frame}
+
+\ex. \begin{forest} boom
  [\tsc{thingP}
@@
 
-\begin{forest} boom
-[ΣP
-   [Σ]
+\ex. \begin{forest} boom
+[IP
+   [I]
    [\tsc{thingP}
@@
 
-	\begin{forest} boom
-	[\tsc{nomP}
-	   [\tsc{f1}]
+\ex. \begin{forest} boom
 	   [ΣP
 	       [Σ]
+				 [IP
+				 		[I]
 			       [\tsc{thingP}
@@
 
-\begin{forest} boom
+\ex. \begin{forest} boom
+	[\tsc{nomP}
+	   [\tsc{f1}]
+	   [ΣP
+	       [Σ]
+				 [IP
+				 		[I]
+			       [\tsc{thingP}
+			           [\tsc{thing}, roof]
+			       ]
+					]
+	   ]
+	]
+	{\draw (.east) node[right]{⇒ \tit{t}}; }
+\end{forest}
+
+\end{frame}
+
+\begin{frame}
+
+\ex. \begin{forest} boom
 [\tsc{datP}
@@
                [Σ]
+							 [IP
+							 		[I]
 		               [\tsc{thingP}
 		                   [\tsc{thing}, roof]
+		               ]
 							 ]
@@
 
-\begin{forest} boom
+\ex. \begin{forest} boom
 [\tsc{insP}
@@
                    [Σ]
+									 [IP
+									 		[I]
 		                   [\tsc{thingP}
 		                       [\tsc{thing}, roof]
+		                   ]
 										]
@@
 
-\begin{forest} boom
+\ex. \begin{forest} boom
+	[\tsc{datP}
+	    [\tsc{datP}
+	        [\tsc{f3}]
+	        [\tsc{accP}
+	           [\tsc{f2}]
+	           [\tsc{nomP}
+	               [\tsc{f1}]
 	               [ΣP
+	                   [Σ]
+										 [IP
+										 		[I]
 			                   [\tsc{thingP}
@@
 												 ]
-	 {\draw (.east) node[right]{⇒ \tit{r}}; }
-	 [ΣP
-			 [Σ]
 	                   ]
-	 {\draw (.east) node[right]{⇒ \tit{-mee}}; }
+	               ]
+	           ]
+	        ]
+	    ]
+	    {\draw (.east) node[right]{⇒ \tit{'t}}; }
+	    [\tsc{insP}
+	        [\tsc{f4}]
+	    ]
+	    {\draw (.east) node[right]{⇒ }; }
 	]
@@
 
-\begin{forest} boom
-[\tsc{nomP}
-    [\tsc{f1}]
-    [ΣP
+\ex. \begin{forest} boom
+[IP
 	 [\tsc{thingP}
@@
 	 ]
+	 {\draw (.east) node[right]{⇒ \tit{r}}; }
+	 [IP
+			 [I]
+	 ]
+	 {\draw (.east) node[right]{⇒ \tit{-mee}}; }
+]
+\end{forest}
+
+\pause
+
+\citep{abels2003diss}
+
+\end{frame}
+
+\begin{frame}
+
+\ex. \begin{forest} boom
 [ΣP
     [Σ]
+    [IP
+       [\tsc{thingP}
+           [\tsc{thing}, roof]
+       ]
+       [IP
+           [I]
        ]
@@
 
-\begin{forest} boom
-[\tsc{nomP}
+\ex. \begin{forest} boom
+[ΣP
    [\tsc{thingP}
@@
    {\draw (.east) node[right]{⇒ \tit{r}}; }
-   [\tsc{nomP}
-       [\tsc{f1}]
    [ΣP
        [Σ]
+       [IP
+           [I]
        ]
@@
 									 		[Σ]
+		                   [IP
+		                       [I]
+											]
                    ]
@@
 
-\begin{forest} boom
+\ex. \begin{forest} boom
 [\tsc{\tsc{wP}}
@@
 													 		 [Σ]
+															 [IP
+																	 [I]
+															 ]
 													 ]
@@
 
-\exg. Ik heb gekocht waar jij mee schildert.\\
- I have bought waar you with paint\\
- `I bought what you are painting with.'\label{ex:meestranded}
-
-\exg. *Ik heb gekocht waar jij schildert mee.\\
- I have bought waar you paint with\\
- `I bought what you are painting with.'\label{ex:meeend}
+\ex. \begin{forest} boom
+[CP
+    [\tsc{\tsc{wP}}
+        [\tsc{\tsc{wP}}
+            [\tsc{w}, roof]
+        ]
+        {\draw (.east) node[right]{⇒ \tit{w}}; }
+        [\tsc{deixP}
+            [\tsc{deixP}
+                [\tsc{deix}, roof]
+            ]
+            {\draw (.east) node[right]{⇒ \tit{a}}; }
+            [\tsc{datP}
+                [\tsc{f3}]
+                [\tsc{accP}
+                   [\tsc{f2}]
+                   [\tsc{nomP}
+                       [\tsc{f1}]
+                       [ΣP
+                           [Σ]
+													 [IP
+													 		[I]
+		                           [\tsc{thingP}
+		                               [\tsc{thing}, roof]
+		                           ]
+														]
+                       ]
+                   ]
+                ]
+            ]
+            {\draw (.east) node[right]{⇒ \tit{t}}; }
+        ]
+    ]
+    [CP
+        [..,roof]
+    ]
+]
+\end{forest}
 
@@
 
-\ex.
-\a. \tit{met} --- \tit{mee}
-\b. \tit{tot} --- \tit{toe}
-
-\ex. CVt
-\pause
-
-\ex.
-\a. \tit{in} --- \tit{in}
-\b. \tit{van} --- \tit{van}
-\b. \tit{op} --- \tit{op}
+\begin{itemize}
+	\item \tsc{r}-pronouns are nothing special, but just a result of regular spellout \pause
+	\item \tit{r} is ambiguous between location and (caseless) thing \pause
+	\item \tit{met} and \tit{mee} are separate lexical entries
+		\begin{itemize}
+			\item so their phonological realization can differ
+			\item so they can differ between between being pre and post
+		\end{itemize}
+\end{itemize}
 
@@
 
-\appendix
+\begin{frame}
 
-\begin{frame}{References}
+\exg. Ik zie \tbf{t}.\\
+ I see it\\
+ `I see it.'\label{ex:inaniobj}
 
-	\scriptsize{
-		\printbibliography
+\exg. *Ik schilder \tbf{met} \tbf{t}.\\
+ I paint with it\\
+ `I am painting with it.'\label{ex:prephet}
+
+\exg. Ik schilder \tbf{r} \tbf{-mee}.\\
+ I paint where -with\\
+ `I am painting with it.'\label{ex:preper}
+
+\pause
+
+\exg. Ik zie \tbf{haar/hem}.\\
+ I see her/him\\
+ `I see her/him.'\label{ex:aniobj}
+
+\exg. Ik schilder samen \tbf{met} \tbf{haar/hem}.\\
+I paint together with her/him\\
+`I am painting together with her/him.'\label{ex:prepani}
+
+\pause
+
+\ex. [\tsc{f4} [\tsc{f3} [\tsc{f2} [\tsc{f1} [\tbf{phi} [Σ [I [\tsc{thing}] ] ] ] ] ] ] ]
+
+\end{frame}
+
+\begin{frame}
+
+\exg. Ik heb gekocht waar mee jij schildert.\\
+ I have bought where with you paint\\
+ `I bought what you are painting with.'\label{ex:meestranded}
+
+\pause
+
+\exg. Ik heb gekocht waar jij mee schildert.\\
+ I have bought where you paint\\
+ `I bought what you are painting with.'\label{ex:meestranded}
+
+\pause
+
+\ex. \begin{forest} boom
+[\tsc{insP}
+    [\tsc{thingP}
+       [\tsc{thing}, roof]
+    ]
+    {\draw (.east) node[right]{⇒ \tit{r}}; }
+    [\tsc{\tbf{insP}}
+       [\tsc{f4}]
+       [\tsc{datP}
+           [\tsc{f3}]
+           [\tsc{accP}
+               [\tsc{f2}]
+               [\tsc{nomP}
+                   [\tsc{f1}]
+									 [ΣP
+									 		[Σ]
+			                   [IP
+			                       [I]
+			                   ]
+			               ]
+								]
+           ]
+       ]
+    ]
+    {\draw (.east) node[right]{⇒ \tit{-mee}}; }
+]
+\end{forest}
+
+\citep{noonan2017dutch}
+
+\end{frame}
+
+\begin{frame}
+
+\begin{tabular}{ l | l | l }
+\textsc{prep} \textit{what} & \textit{where} \tsc{post} & translation \\
+\hline
+ aan wat & waar\textbf{aan} & `on whom/what' \\
+ achter wat & waar\textbf{achter} & `behind whom/what' \\
+ bij wat & waar\textbf{bij} & `at whom/what' \\
+ door wat & waar\textbf{door} & `by whom/what' \\
+ langs wat & waar\textbf{langs} & `alongside whom/what \\
+ met wat & waar\underline{\textbf{mee}} & `with whom/what' \\
+ naar wat & waar\textbf{naar} & `to whom/what' \\
+ op wat & waar\textbf{op} & `on whom/what' \\
+ over wat & waar\textbf{over} & `about whom/what' \\
+ tot wat & waar\underline{\textbf{toe}} & `to whom/what' \\
+ uit wat & waar\textbf{uit} & `out of whom/what' \\
+ van wat & waar\textbf{van} & `of whom/what' \\
+ voor wat & waar\textbf{voor} & `for whom/what' \\
+\end{tabular}
+
+\end{frame}
+
+\begin{frame}
+
+\ex.\label{ex:dutchin}
+\ag. Ik dans in het bos.\\
+ I dance in the forest\\
+ `I am dancing in the forest.'
+\bg. Ik dans het bos in.\\
+ I dance the forest in\\
+ `I am dancing into the forest.'
+
+\pause
+
+\exg. Ik dans r -in.\\
+ I dance \tsc{r} in\\
+ `I dance it in.'\\
+  *`I dance into it.'
+
+\pause
+
+\exg. *Ik ben r -in gedanst.\\
+ I am \tsc{r} in danced\\
+ `I dancing into it.'
+
+\pause
+
+\exg. Ik heb r -in gedanst.\\
+ I have \tsc{r} in danced\\
+ `I dancing in it.'
+
+\end{frame}
+
+\begin{frame}
+
+\centering{
+	\begin{tabular}{ccc}
+	\toprule
+					& DP				& \tsc{r}	\\
+	\midrule
+		pre		& \tsc{loc} & *     	\\
+		post	& \tsc{dir}	& \tsc{loc} \\
+	\bottomrule
+\end{tabular}
+		}
+
+\vspace{1em}
+\pause
+
+verbal particles in e.g. \tbf{mee}lopen `walk along', \tbf{mee}zingen `sing along'
+
+\vspace{1em}
+	\pause
+
+\centering{
+	\begin{tabular}{ccc}
+	\toprule
+					& \tit{mee}	& \tit{met}	\\
+	\midrule
+		pre		& verb		 	& noun     	\\
+		post	& noun			& *					 \\
+	\bottomrule
+	\end{tabular}
 	}

### 2020-04-23 daarmee.tex
waarmee > daarmee

\documentclass[12pt]{article}

\usepackage[margin=1in]{geometry}
%\usepackage{setspace}
%\doublespacing

\usepackage{fenna-files/packages}
\usepackage{fenna-files/commands}
\bibliography{fenna-files/references}{}

\title{The instrumental \tsc{r}-pronoun and postposition in Dutch}
\author{Fenna Bergsma\\Goethe-Universität Frankfurt}
\date{\today}

\begin{document}

\maketitle

\section{The problem}

Dutch has several types of inanimate pronouns.

\ex.
\ag. t\\
 it\\
 `it'
\bg. *dat\\
 that\\
 `that'
\bg. *wat\\
 what\\
 `what'
\bg. *iets\\
 something\\
 `something'
\bg. *alles\\
 everything\\
 `everything'

Dutch has a preposition for that expresses instrumental.

\exg. met een potlood\\
 with a pencil\\
 `with a pencil'

Inanimate pronouns in Dutch do not combine with the instrumental preposition.

\ex.
\ag. *met t\\
 with it\\
 `with it'
\bg. *met dat\\
 with that\\
 `with that'
\bg. *met wat\\
 with what\\
 `with what'
\bg. *met iets\\
 with something\\
 `with something'
\bg. *met alles\\
 with everything\\
 `with everything'

Instead, an \tsc{r}-pronoun plus postposition is used.

\ex.
\ag. (e)r mee\\
 there with\\
 `with it'
\bg. daar mee\\
 there with\\
 `with that'
\bg. waar mee\\
 where with\\
 `with what'
\bg. ergens mee\\
 somehwere with\\
 `with something'
\bg. overal mee\\
 everywhere with\\
 `with everything'

\section{This paper: questions and answers}

There is a big question to be asked:

\begin{itemize}
  \item Why *[P inanimate]?
\end{itemize}

And there are three questions with respect to the instrumental:

\begin{itemize}
  \item why is there an \tit{r}, even though there is no location involved
  \item why does the adposition change form?
  \item why does the adposition change position?
\end{itemize}

Answer to the big question:

\begin{itemize}
  \item the \tsc{r}-pronoun and postposition are the default spellout, as long as they form a proper constituent
\end{itemize}

Answers to the smaller questions:

\begin{itemize}
  \item the \tit{r} is ambiguous between location and (caseless) thing
  \item the preposition and postposition are two separate items in the lexcion so: (1) the form can be different, and (2) the position can be different
\end{itemize}

\section{Proof for proper constituent}

Let's compare a proper constituent vs. not a proper constituent

\ex.
\ag. Ze heeft (de brief) daar mee geschreven.\\
 she has the letter there with written\\
 `She wrote (the letter) with that.'
\bg. Ze heeft (de brief) met dat potlood geschreven\\
 she has the letter with that pencil written\\
 `She wrote (the letter) with that pencil.'

\tit{Daar mee} `there with' forms a proper constituent, \tit{met dat} `with that' does not.

\ex. topicalization
\a. Daar mee heeft ze (de brief) geschreven.
\b. *Met dat heeft ze (de brief) potlood geschreven.
\b. Met dat potlood heeft ze (de brief) geschreven.

\ex. coordination
\a. Ze heeft (de brief) hier mee en daar mee geschreven.
\b. *Ze heeft (de brief) met die en met dat potlood.
\b. Ze heeft (de brief) met die pen en met dat potlood geschreven.

\ex. fragment answer
\a. Waarmee heeft ze de brief geschreven?
\b. daarmee
\b. *met dat
\b. met dat potlood

\section{Technical implementation}

\ex. r = [loc [thing]]

\ex. met = binary entry

\ex. mee = unary entry

alternative fseq

\ex. [\tsc{f4} [\tsc{f3} [\tsc{f2} [\tsc{f1} [\tsc{thing} [ D [\tsc{deix}  ] ] ] ] ] ] ]

\subsection{Mobility of \tit{mee}}

\tit{daar} can move while stranding \tit{mee}. A consequence of letting \tit{mee} be a suffix makes it hard to only move \tit{daar}. Can \tit{d-} and \tit{a-} be lower in the hierarchy than \tit{r}? Then \tit{r} can be a suffix on \tit{da}. That way, \tit{d} and \tit{a} are not projecting as specifiers.

\subsection{Full DPs and animates}

Why do full DPs not take \tit{mee} as a suffix? Has to do with pronominal strength features and gaps. (?)

\section{Big-big question}

Should adpositions by default be able to be pre and post?

\subsection{pro}

lots are syncretic

\subsection{against}

several can only be pre or post

\ex. only pre: zonder, volgens

\ex. only post: vandaan

\subsection{two tables}

three instances of \tit{in}

\begin{table}[h]
  \begin{tabular}{ccc}
  \toprule
          & DP				& \tsc{r}	\\
  \midrule
    pre		& \tsc{loc} & *     	\\
    post	& \tsc{dir}	& \tsc{loc} \\
  \bottomrule
  \end{tabular}
\end{table}

twice \tit{mee} and once \tit{met}

\begin{table}[h]
  \begin{tabular}{ccc}
  \toprule
          & \tit{mee}	& \tit{met}	\\
  \midrule
    pre		& verb		 	& noun     	\\
    post	& noun			& *					 \\
  \bottomrule
  \end{tabular}
\end{table}

\printbibliography

\end{document}

### 2020-04-27 presentation nanolab/presentation.tex
klaar met daarmee voor nu
nog wel naar pavel sturen.. die zinnetjes

@@
 
+\begin{frame}{The data}
+
+\exg. Zij schrijft de brief \tbf{met} een potlood.\\
+ she writes the letter with a pencil\\
+ `She writes the letter with a pencil.'
+
+\pause
+
+\exg. Zij koopt \tbf{dat}.\\
+ she buys that\\
+ `She buys that.'
+
+\pause
+
+\exg. * Zij schrijft de brief \tbf{met} \tbf{dat}.\\
+ she writes the letter with that\\
+ `She writes the letter with that.'
+
+\pause
+
+\exg. Zij schrijft de brief \tbf{daar} \tbf{mee}.\\
+ she writes the letter there with\\
+ `She writes the letter with that.'
+
+\end{frame}
+
+\begin{frame}{Questions and answers}
+
+\centering{
+\tbf{met dat} | \tbf{daar mee} \pause
+}
+
+\vspace{1em}
+
+\begin{enumerate}
+  \item Q: why *\tit{met dat} (but \tit{daar mee})? \pause\\
+  A: \tit{daar mee} is the default, \tit{met dat} only appears under special circumstances (morphological derivation, cf. \tit{mice} and not \tit{mouse-s})\pause
+  \item Q: why does the adposition change form? \pause\\
+  A: \tit{mee} and \tit{met} are stored as different forms in the lexicon \pause
+  \item Q: why does the adposition change position? \pause\\
+  A: \tit{mee} and \tit{met} are stored as preposition or postposition in the lexicon \pause
+  \item Q: why is there an \tit{r}, even though there is no location involved? \pause\\
+  A: \tit{r} is ambiguous between \tsc{thing} and \tsc{location}
+\end{enumerate}
+
+\end{frame}
+
+\begin{frame}{Nanosyntax}
+
+\begin{itemize}
+  \item functional sequence is constant\pause
+  \item spellout algorithm is constant\pause
+  \item a single place for cross-linguistic differences: the postsyntactic lexicon\pause
+\end{itemize}
+
+\vspace{1em}
+
+\begin{enumerate}
+  \item spellout happens feature by feature and targets phrases
+  \item phonological forms are stored in the postsyntactic lexicon
+  \item postpositions are candidates for spellout before prepositions are
+  \item ambiguity comes from containment relations
+\end{enumerate}
+
+\end{frame}
+
+\begin{frame}{differing phonological forms}
+
+\begin{itemize}
+  \item \tit{mee} and \tit{met} are stored as different forms in the lexicon
+  \item phonological forms are stored in the lexicon \pause
+\end{itemize}
+
+  \ex. \begin{forest} boom
+  [\tsc{insP}
+      [\tsc{f4}]
+      [\tsc{datP}
+          [\tsc{f3}]
+          [\tsc{accP}
+              [\tsc{f2}]
+              [\tsc{nomP}
+                  [\tsc{f1}]
+                  [ΣP
+                      [Σ]
+  										[IP
+  												[I]
+  										]
+                  ]
+              ]
+          ]
+      ]
+  ]
+  {\draw (.east) node[right]{⇔ \tit{-mee}}; }
+  \end{forest}\label{ex:entrymee}
+
+  \pause
+
+  \ex. \begin{forest} boom
+  [\tsc{insP}
+      [\tsc{f4},roof]
+  ]
+  {\draw (.east) node[right]{⇔ \tit{met}}; }
+  \end{forest}\label{ex:entrymet}
+
+\end{frame}
+
+\begin{frame}{pre vs. post}
+
+\begin{itemize}
+  \item \tit{mee} and \tit{met} are stored as preposition or postposition in the lexicon \pause
+  \item postpositions are candidates for spellout before prepositions are \pause
+\end{itemize}
+
+  \ex. \begin{forest} boom
+  [\tsc{insP}
+      [\tsc{f4}]
+      [\tsc{datP}
+          [\tsc{f3}]
+          [\tsc{accP}
+              [\tsc{f2}]
+              [\tsc{nomP}
+                  [\tsc{f1}]
+                  [ΣP
+                      [Σ]
+  										[IP
+  												[I]
+  										]
+                  ]
+              ]
+          ]
+      ]
+  ]
+  {\draw (.east) node[right]{⇔ \tit{-mee}}; }
+  \end{forest}\label{ex:entrymee}
+
+  \pause
+
+  \ex. \begin{forest} boom
+  [\tsc{insP}
+      [\tsc{f4},roof]
+  ]
+  {\draw (.east) node[right]{⇔ \tit{met}}; }
+  \end{forest}\label{ex:entrymet}
+
+\end{frame}
+
+\begin{frame}{pre vs. post}
+
+  \ex. Merge F and \label{ex:spellout}
+  	 \a. Spell out FP.
+  	 \b. If (a) fails, attempt movement of the spec of the complement of \tsc{f}, and retry (a).
+  	 \b. If (b) fails, move the complement of \tsc{f}, and retry (a).
+
+  \ex. \tbf{Backtracking} \citep{starke2018}:\\
+  	When spellout fails, go back to the previous cycle, and try the next option for that cycle.\label{ex:backtracking}
+
+  \ex. \tbf{Spec Formation} \citep{starke2018}:\\
+  	If Merge F has failed to spell out (even after backtracking), try to spawn a new derivation providing the feature F and merge that with the current derivation, projecting the feature F at the top node.\label{ex:specformation}
+
+\end{frame}
+
+\begin{frame}{\tit{r} without location}
+
+  \begin{itemize}
+    \item \tit{r} is ambiguous between \tsc{thing} and \tsc{location}
+    \item ambiguity comes from containment relations
+  \end{itemize}
+
+\pause
+
+\ex. \tbf{The Superset Principle} \citep{starke2009}: \\
+	A lexically stored tree matches a syntactic node iff the lexically stored tree contains the syntactic node.
+
+\ex. \begin{forest} boom
+[\tsc{loc}P
+   [\tsc{location}]
+   [\tsc{thingP}
+       [\tsc{thing}, roof]
+   ]
+]
+{\draw (.east) node[right]{⇔ \tit{r}}; }
+\end{forest}\label{ex:entryr}
+
+\end{frame}
+
+\begin{frame}{Derivational system}
+
+\begin{itemize}
+  \item \tit{daar mee} is the default, \tit{met dat} only appears under special circumstances (morphological derivation, cf. \tit{mice} and not \tit{mouse-s}) \pause
+  \item spellout happens feature by feature and targets constituents
+\end{itemize}
+
+\pause
+
+\ex.
+\ag. Ze heeft de brief \tbf{daar} \tbf{mee} geschreven.\\
+ she has the letter there with written\\
+ `She wrote the letter with that.'
+\bg. Zij heeft de brief \tbf{met} \tbf{dat} potlood geschreven.\\
+ she has the letter with that pencil written\\
+ `She wrote the letter with that potlood.'
+
+\end{frame}
+
+\begin{frame}{\tit{daar mee} in a proper constituent}
+
+\exg. Ze heeft de brief \tbf{daar} \tbf{mee} geschreven.\\
+ she has the letter there with written\\
+ `She wrote (the letter) with that.'
+
+\pause
+
+\exg. \tbf{Daar} \tbf{mee} heeft ze de brief geschreven.\\
+ there with has she the letter written\\
+ `With that she has written the letter.' \hfill topicalization
+
+\pause
+
+\exg. Ze heeft de brief \tbf{hier} \tbf{mee} en \tbf{daar} \tbf{mee} geschreven.\\
+ she has the letter here with and there with written\\
+ `She has written the letter with this and with that' \hfill coordination
+
+\pause
+
+\ex.
+\a. With what did she write the letter?
+\bg. \tbf{daar} \tbf{mee}\\
+ there with\\
+ `with that' \hfill fragment answer
+
+\end{frame}
+
+\begin{frame}
+
+  \ex. \begin{forest} boom
+  [\tsc{insP}
+      [\tsc{f4}]
+  	    [\tsc{datP}
+  	        [\tsc{f3}]
+  	        [\tsc{accP}
+  	           [\tsc{f2}]
+  	           [\tsc{nomP}
+  	               [\tsc{f1}]
+  	               [ΣP
+  	                   [Σ]
+  										 [IP
+  										 		[I]
+  			                   [\tsc{thingP}
+  			                       [\tsc{thing}, roof]
+  												 ]
+  	                   ]
+  	               ]
+  	           ]
+  	        ]
+  	    ]
+  	    {\draw (.east) node[right]{⇒ \tit{'t}}; }
+    ]
+  \end{forest}
+
+\end{frame}
+
+\begin{frame}{\tit{met dat} in a non-constituent}
+
+\exg. Ze heeft de brief \tbf{met} \tbf{dat} potlood geschreven.\\
+she has the letter with the pencil written\\
+`She has written the letter with that pencil.'
+
+\pause
+
+\ex.
+\ag. *\tbf{Met} \tbf{dat} heeft ze de brief \tbf{potlood} geschreven.\\
+ with that has she the letter pencil written\\
+ `With that pencil she has written the letter.'
+\bg. \tbf{Met} \tbf{dat} \tbf{potlood} heeft ze de brief geschreven.\\
+ with that pencil has she the letter written\\
+ `With that pencil she has written the letter.' \hfill topicalization
+
+\pause
+
+% \ex.
+% \ag. *Ze heeft de brief met die en met dat potlood geschreven.\\
+%  she has the letter with this and with that pencil written\\
+%  `She has written the letter with this pencil and with that marker.' \hfill coordination
+% \bg. Ze heeft de brief met die pen en en dat potlood geschreven.\\
+%  she has the letter with this marker and with that pencil written\\
+%  `She has written the letter with this pencil and with that marker.' \hfill coordination
+%
+% \pause
+
+\ex.
+\a. With what did she write the letter?
+\bg. *\tbf{met} \tbf{dat}\\
+ with that\\
+ `with that'
+\bg. \tbf{met} \tbf{dat} \tbf{potlood}\\
+ with that pancil\\
+ `with that pencil'\hfill fragment answer
+
+\end{frame}
+
+\begin{frame}
+
+  \ex. \begin{forest} boom
+[\tsc{insP}
+    [\tsc{f4}]
+    [\tsc{datP}
+        [\tsc{datP}
+            [\tsc{f3}]
+            [\tsc{accP}
+               [\tsc{f2}]
+               [\tsc{nomP}
+                   [\tsc{f1}]
+                   [ΣP
+                       [Σ]
+  										 [IP
+  										 		[I]
+                           [\tsc{thingP}
+                               [\tsc{thing}, roof]
+                           ]
+  											]
+                   ]
+               ]
+            ]
+        ]
+        {\draw (.east) node[right]{⇒ \tit{t}}; }
+        [NP
+            [\tsc{pencil}, roof]
+        ]
+        {\draw (.east) node[right]{⇒ \tit{potlood}}; }
+    ]
+]
+    \end{forest}
+
+\end{frame}
+
+\begin{frame}{Summary}
+
+    \begin{enumerate}
+      \item Q: why *\tit{met dat} (but \tit{daar mee})? \pause\\
+      A: \tit{daar mee} is the default, \tit{met dat} only appears under special circumstances (morphological derivation, cf. \tit{mice} and not \tit{mouse-s})\pause
+      \item Q: why does the adposition change form? \pause\\
+      A: \tit{mee} and \tit{met} are stored as different forms in the lexicon \pause
+      \item Q: why does the adposition change position? \pause\\
+      A: \tit{mee} and \tit{met} are stored as preposition or postposition in the lexicon \pause
+      \item Q: why is there an \tit{r}, even though there is no location involved? \pause\\
+      A: \tit{r} is ambiguous between \tsc{thing} and \tsc{location}
+    \end{enumerate}
+
+\end{frame}
+
 \end{document}

### 2021-11-16 paper.tex
ok, alleen nog drivation + conclusion

--- 2020-01-16 paper.tex
@@
-\documentclass[12pt]{article}
+\documentclass[11pt,a4paper]{article}
 
@@
 
-\title{The \tsc{r}-pronoun and postposition \tit{waar-mee} in Dutch}
+\title{The \tsc{r}-pronoun plus postposition \tit{waar mee} in Dutch}
 \author{Fenna Bergsma\\Goethe-Universität Frankfurt}
@@
 In \ref{ex:metdp}, \tit{met} `with' is combined with a full DP.
-The inanimate pronoun in Dutch is \tit{'t} `it'.\footnote{The longer form that is mostly used in writing is \tit{het} `it'.
-I will use the spoken variant \tit{'t} throughout this paper.} \ref{ex:tverb} illustrates that \tit{'t} `it' can be used as the object of a verb.
+The inanimate pronoun in Dutch is \tit{t} `it'.\footnote{The longer form that is mostly used in writing is \tit{het} `it'.
+I will use the spoken variant \tit{t} throughout this paper.} \ref{ex:tverb} illustrates that \tit{t} `it' can be used as the object of a verb.
 
@@
  `I am painting with a brush.'\label{ex:metdp}
- \bg. Ik zie 't.\\
+ \bg. Ik zie t.\\
   I see it\\
@@
 
-\tit{Met} `with' and \tit{'t} `it' do not appear together, as illustrated in \ref{ex:neemett}.
-Instead, Dutch uses the \tsc{r}-pronoun \tit{'r} `there' and the postposition \tit{mee} `with', as shown in \ref{ex:jarmee}.\footnote{The \tsc{r}-pronoun \tit{'r} in \ref{ex:jarmee} can be written as \tit{er}, \tit{der} and \tit{'r} and pronounced as respectively /ɛr/, /dər/ or /ər/.
-As far as I am aware, there is no clear meaning difference between these forms.
-See \citet{wesseling2018} for discussion.
-In my examples I use \tit{'r}, but the other two forms fit just as well.}$^,$\footnote{In this paper I do not make any claims about the distinction between prefixes and prepositions, or suffixes and postpositions.}
-
-\ex.\label{ex:rmeeconst}
-\ag. *Ik schilder met 't.\\
+\tit{Met} `with' and \tit{t} `it' do not appear together, as illustrated in \ref{ex:neemett}.
+Instead, Dutch uses the \tsc{r}-pronoun \tit{r} `there' and the postposition \tit{mee} `with', as shown in \ref{ex:jar mee}.\footnote{The \tsc{r}-pronoun \tit{r} in \ref{ex:jar mee} can be written as \tit{er}, \tit{der} and \tit{r} and pronounced as respectively /ɛr/, /dər/ or /ər/.
+There is no clear meaning difference between these forms that is relevant for the discussion in this paper
+(see \citet{wesseling2018} for discussion).
+In my examples I use \tit{r}, but the other forms fit just as well.}$^,$\footnote{In this paper I do not make any claims about the distinction between prefixes and prepositions, or suffixes and postpositions.}
+
+\ex.\label{ex:r meeconst}
+\ag. *Ik schilder met t.\\
  I paint with it\\
  `I am painting with it.'\label{ex:neemett}
-\bg. Ik schilder 'r -mee.\\
- I paint there -with\\
- `I am painting with it.'\label{ex:jarmee}
-
-\tsc{R}-pronouns \citep{riemsdijk1978,koopman1994} are nominal elements that are syncretic with locative pronouns, which in Dutch means they contain the morpheme \tit{r}.
-The adpositions they combine with obligatorily follow the \tsc{r}-pronoun, see \ref{ex:jarmee} and \ref{ex:neemeer}.
-Notice also that the preposition \tit{met} `with' differs phonologically from the postposition \tit{mee} `with` (see \ref{ex:metdp} and \ref{ex:jarmee}).
-
-\exg. *Ik schilder mee 'r.\\
+\bg. Ik schilder r mee.\\
+ I paint there with\\
+ `I am painting with it.'\label{ex:jar mee}
+
+\tsc{R}-pronouns are nominal elements that are syncretic with locative pronouns, which in Dutch means they contain the morpheme \tit{r} \citep[cf.][]{riemsdijk1978,koopman1994}.
+The adpositions they combine with obligatorily follow the \tsc{r}-pronoun (compare \ref{ex:jar mee} and \ref{ex:neemeer}).
+Notice also that the preposition \tit{met} `with' differs phonologically from the postposition \tit{mee} `with` (see \ref{ex:metdp} and \ref{ex:jar mee}), although they express the same meaning.
+
+\exg. *Ik schilder mee r.\\
  I paint with there\\
@@
 
-The main question I address in this paper is how to correctly rule out \tit{met 't} `with it' in \ref{ex:neemett}, and let the \tsc{r}-pronoun and postposition in \ref{ex:jarmee} appear.
+The main question I address in this paper is how to correctly rule out \tit{met t} `with it' in \ref{ex:neemett}, and let the \tsc{r}-pronoun plus postposition \tit{r mee} `with it' in \ref{ex:jar mee} appear.
 I argue that \tsc{r}-pronouns are not something special, but a consequence of regular spellout mechanisms.
-Just like \citet{riemsdijk1978} I analyze an \tsc{r}-pronoun and postposition as a type of allomorph of the preposition and pronoun.
-The crucial difference in the current approach is that spellout rules out the ungrammaticality of the preposition and pronoun and not the stipulation of a filter.
-
-This paper is focuses on the instrumental \tsc{r}-pronoun and postposition \tit{'r-mee} `with it' and \tit{waar-mee} `with what' in Dutch.
+Just as \citet{riemsdijk1978} I analyze the \tsc{r}-pronoun plus postposition as a type of allomorph of the preposition plus pronoun.
+The crucial difference in the current approach is that spellout - not the stipulation of a filter - rules out the ungrammaticality of the preposition plus inanimate pronoun.
+
+This paper focuses on the instrumental \tsc{r}-pronoun plus postposition \tit{r mee} `with it' in Dutch.
 This instance is interesting for two reasons.
-First, just like for all \tsc{r}-pronouns, the \tsc{r}-pronoun is syncretic with the locative.
-In many of the \tsc{r}-pronouns and postpositions, the meaning component of the locative is intuitive, as many prepositions express locations, directions etc.
+First, just as for all \tsc{r}-pronouns, the \tsc{r}-pronoun is syncretic with the locative.
+In many of the \tsc{r}-pronouns and postpositions, the meaning component of the locative within the \tsc{r}-pronoun plus postposition is intuitive, as many adpositions express locations, directions, etc.
 However, an instrumental expresses an instrument, which does not have a meaning component associated with location.
-Ideally, an analysis treats the syncretism not as accidental but allows for the locative meaning to be absent.
-The second reason why I focus on this particular \tsc{r}-pronoun and postposition has to do with the form of the adposition.
-The preposition \tit{met} `with' does not only turn into a postposition, but it also changes into \tit{-mee} `with' when it is combined with an \tsc{r}-pronoun.
-This last observation has so far remained unexplained.
-
-The main generalization is that the instrumental \tsc{r}-pronoun and postposition \tit{waar-mee} `with what' takes precedence over the instrumental preposition and inanimate pronoun \tit{met wat} `with what'.
-This generalization is subject to an important condition: the instrumental object needs to form a proper constituent i.e.
+Ideally, a formal analysis would treat the syncretism as unaccidental but still allow the locative meaning to be absent.
+The second reason for focusing on this particular \tsc{r}-pronoun plus postposition is the form of the adposition.
+The preposition \tit{met} `with' does not only turn into a postposition, but it also changes into \tit{mee} `with' when it is combined with an \tsc{r}-pronoun.
+This last observation has so far remained unexplained in the literature on \tsc{r}-pronouns (cf.
+\citealt{koopman1994,riemsdijk1978,noonan2017dutch,abels2003diss}).
+
+The main generalization is that the instrumental \tsc{r}-pronoun plus postposition \tit{r mee} `with it' takes precedence over the instrumental preposition plus inanimate pronoun \tit{met t} `with it'.
+I show that a single requirement has to be satisfied: the instrumental object needs to form a proper constituent i.e.
 a constituent to the exclusion of other features.
-When this condition is not met, the preposition and pronoun appear.
+When this condition is not met, the preposition plus inanimate pronoun appear.
 This can straightforwardly follow in a system in which spellout targets phrasal constituents: Nanosyntax \citep{starke2009}.
-I work this idea out capturing the following observations.
+I work this idea out capturing the following three observations.
 First, \tsc{r}-pronouns are syncretic with locatives.
-Second, regular pronouns appear with prepositions, \tsc{r}-pronouns with postpositions.
-Third, the instrumental preposition and postposition differ in form (\tit{met} vs.
+Second, inanimate pronouns appear with prepositions, and \tsc{r}-pronouns appear with postpositions.
+And third, the instrumental preposition and postposition differ in form (\tit{met} vs.
 \tit{mee}).
@@
 This paper is structured as follows.
-In Section \ref{sec:distribution} I discuss the condition that \tsc{r}-pronouns and postpositions are subject too: they need to form a proper constituent.
-I show that \tsc{r}-pronouns and postpositions and prepositions and pronouns are in complementary distribution, depending on whether all features form a proper constituent or not.
-In Section \ref{sec:takingapart} I decompose \tit{waar-mee} `with what' and \tit{met wat} `with what', and I connect them to parts of syntactic structure.
-Section \ref{sec:derivation} shows in a derivation how \tit{waar-mee} `with what' is derived and the role that constituency plays.
-Section \ref{sec:conclusion} concludes and discusses possible extensions of the analysis.
-All examples in this paper are from Dutch, unless indicated otherwise.
-Unmarked examples are constructed and have been verified by native speakers.
+In Section \ref{sec:distribution} I show that \tsc{r}-pronouns plus postpositions and prepositions plus inanimate pronouns are in complementary distribution, depending on whether all features form a proper constituent or not.
+Besides discussing \tit{r mee} `with it' and \tit{met t} `with it', I introduce the \tit{wh}-pronouns \tit{waarmee} `with what' and \tit{met wat} `with what'.
+For these forms it is intuitive to see that proper constituency is the critical condition.
+In Section \ref{sec:takingapart} I decompose \tit{waar mee} `with what' and \tit{met wat} `with what', and I link the morphemes they consist of to specific syntactic structures.
+Section \ref{sec:derivation} shows in a derivation how \tit{waar mee} `with what' is derived when all features form a proper constituent.
+I also show how \tit{met wat} `with what' appears when the features do not form a proper constituent.
+Section \ref{sec:conclusion} concludes.
+All examples in this paper are from spoken Dutch, unless indicated otherwise.
+Examples without a reference are constructed and have been verified by native speakers.
 
@@
 that all features form a constituent to the exclusion of any other features.
-I start the section by showing that \tit{'rmee} `with it' and \tit{waar-mee} `with what` are the default, that normally they appear instead of \tit{met 't} `with it' and \tit{met wat} `with what`.
-Then I show an exception, in which \tit{met wat} `with what` has to be used and \tit{waar-mee} `with what` cannot.
-I argue that the crucial difference between the exception and other cases is that in the exception the relevant features do not form a proper constituent.
+I start the section by showing that \tit{r mee} `with it' and \tit{waar mee} `with what` are the default, which is to say that they normally appear and \tit{met t} `with it' and \tit{met wat} `with what' do not.
+There is one exception, in which \tit{met wat} `with what` has to be used and \tit{waar mee} `with what` cannot, which is when case the relevant features do not form a proper constituent.
 
@@
 
-In what follows I discuss the distribution of \tsc{r}-pronouns and regular pronouns in general \citep{riemsdijk1978,koopman1994}. I start with the personal pronouns and then return to the wh-pronouns.
-
-Dutch has the accusative personal pronouns \tit{haar} `her', \tit{hem} `him' and \tit{'t} `it' that can be used as animate and inanimate objects of verbs, as illustrated in \ref{ex:objverb}.
+In what follows I discuss the distribution of \tsc{r}-pronouns and regular pronouns in general \citep{riemsdijk1978,koopman1994}.
+I start with the personal pronouns and then turn to the \tsc{wh}-pronouns.
+
+Dutch has the accusative personal pronouns \tit{haar} `her', \tit{hem} `him' and \tit{t} `it' that can be used as animate and inanimate objects of verbs, as illustrated in \ref{ex:objverb}.
 
@@
   `I see her/him.'\label{ex:aniobj}
- \bg. Ik zie 't.\\
+ \bg. Ik zie t.\\
   I see it\\
@@
 Example \ref{ex:prepani} shows that for animate objects the same pronouns (\tit{haar} `her' and \tit{hem} `him') appear as objects of prepositions.
-Repeating from the introduction, the inanimate personal pronoun \tit{'t} `it' cannot be used as an object of a preposition, shown in \ref{ex:prephet}.
-Instead, an \tsc{r}-pronoun appears.
-This is illustrated in \ref{ex:preper}.
-\ref{ex:erprep} shows that the \tsc{r}-pronoun has moved obligatorily to the left of the adposition.
+Repeating from the introduction, the inanimate pronoun \tit{t} `it' cannot be used as an object of a preposition, shown in \ref{ex:prephet}.
+Instead, an \tsc{r}-pronoun appears, as is illustrated in \ref{ex:preper}.
+\ref{ex:erprep} shows that the \tsc{r}-pronoun must appear to the left of the adposition.
 
@@
  `I am painting together with her/him.'\label{ex:prepani}
-\bg. *Ik schilder met 't.\\
+\bg. *Ik schilder met t.\\
  I paint with it\\
  `I am painting with it.'\label{ex:prephet}
-\bg. Ik schilder 'r -mee.\\
- I paint there -with\\
+\bg. Ik schilder r mee.\\
+ I paint there with\\
  `I am painting with it.'\label{ex:preper}
-\bg. *Ik schilder mee 'r.\\
+\bg. *Ik schilder mee r.\\
  I paint with there\\
@@
 
-\tit{Met} is not the only preposition with which this happens.
-For example, \tit{op} `on' and \tit{in} `in' also do not combine with the inanimate personal pronoun \tit{'t}, but the \tsc{r}-pronoun and postposition are used obligatorily.
+\tit{Met} is not the only preposition this occurs with.
+For example, \tit{op} `on' and \tit{in} `in' cannot combine with the inanimate pronoun \tit{t} either, and the \tsc{r}-pronoun plus postposition are obligatorily used instead.
 
 \ex.
-\ag. Ik zit 'r op.\\
+\ag. Ik zit r op.\\
  I sit there on\\
  `I am sitting on it.
-\bg. *Ik zit op 't.\\
+\bg. *Ik zit op t.\\
  I sit on it\\
@@
 \ex.
- \ag. Hij zwemt 'r in.\\
-  he swims it-in\\
-  `He is swimming there it.'
- \bg. *Hij zwemt in 't.\\
-  he swims in it\\
-  `He is swimming in it.'
-
-The situation of the inanimate wh-pronouns resembles the one of the inanimate personal pronouns.
-\tit{Wat} `what' can function as an object of a verb (see \ref{ex:wat}), but not as an object of a preposition \ref{ex:metwat}.
-In that case, the \tsc{r}-pronoun and postposition \tit{waar-mee} `with what' appears, as shown in \ref{ex:waar-mee}.\footnote{The sentence in \ref{ex:metwat} is unacceptable with neutral intonation.
+ \ag. Ik zwem r in.\\
+  I swim there in\\
+  `I am swimming in it.'
+ \bg. *Ik zwemt in t.\\
+  I swim in it\\
+  `I am swimming in it.'
+
+The situation of the inanimate \tsc{wh}-pronouns resembles the one of the inanimate personal pronouns.
+\tit{Wat} `what' can function as the object of a verb (see \ref{ex:wat}), but not as the object of a preposition \ref{ex:metwat}.
+The \tsc{r}-pronoun plus postposition \tit{waar mee} `with what' appears, as shown in \ref{ex:waar mee}.\footnote{The sentence in \ref{ex:metwat} is unacceptable with neutral intonation.
 It becomes acceptable if \tit{wat} `what' is stressed, for example in a context in which the speaker is highly surprised about the choice of the object the hearer is painting with.}
@@
  `What are you painting with?'\label{ex:metwat}
-\bg. Waar -mee schilder jij?\\
- where with paint you with\\
- `What are you painting with?'\label{ex:waar-mee}
-
-\tit{Waar-mee} `with what' and not \tit{met wat} `with what' does not only appear in wh-questions, but also in other contexts.
+\bg. Waar mee schilder jij?\\
+ where with paint you\\
+ `What are you painting with?'\label{ex:waar mee}
+
+\tit{Waar mee} `with what' and not \tit{met wat} `with what' does not only appear in \tsc{wh}-questions, but also in other contexts.
 \ref{ex:headed} gives an example of a headed relative, and \ref{ex:headless} shows a free relative in which both predicates combine with an instrumental object.
-The use of \tit{met wat} `with what' is ungrammatical in both contexts, and \tit{waar-mee} `with what' is used.
+The use of \tit{met wat} `with what' is ungrammatical in both contexts, and \tit{waar mee} `with what' is used instead.\footnote{
+In this example, \tit{waar} `where' and \tit{mee} `with' are the two left-most elements of the relative clause.
+It is also possible for \tit{mee} `with' to appear more to the right in the clause and for \tit{waar} to appear as the left-most element on its own.
+
+\exg. Ik schilder waar jij ook mee schildert.\\
+ I paint where you also with paint\\
+ `I am painting with what you are painting with too.'\label{ex:meealong}
+
+I return to this variant in Section \ref{sec:derivation}.
+}
 
 \ex.\label{ex:headed}
-\ag. Ik schilder met de kwast waar -mee jij ook schildert.\\
+\ag. Ik schilder met de kwast waar mee jij ook schildert.\\
  I paint with the brush where with you also paint\\
@@
  \ex.\label{ex:headless}
- \ag. Ik schilder waar -mee jij ook schildert.\\
+ \ag. Ik schilder waar mee jij ook schildert.\\
   I paint where with you also paint\\
@@
 
-In sum, \tit{'t} `it' and \tit{wat} `what' do not combine with prepositions. They are substituted by respectively \tit{'r} `there' and \tit{waar} `where'.
-
-\subsection{\tit{Met wat} `with what' shows up}
-
-This section discusses an exception to what is shown in the previous section.
-I show an instance in which \tit{met wat} `with what' has to be used instead of \tit{waar-mee} `with what'.
-This instance comes from a mismatching free relative construction.
-
-A mismatching free relative is a free relative construction in which the two predicates (the one in the main clause and the one in the embedded clause) combine with two different cases (i.e.
-the case requirements do not match).
-I give an example in which the \tsc{r}-pronoun and postposition appear before I get to the exception.
-Consider \ref{ex:gekochtwaar-mee}.
-The predicate in the embedded clause, \tit{schildert} `paint', combines with an instrumental object.
+In sum, the inanimate pronouns \tit{t} `it' and \tit{wat} `what' do not combine with prepositions. They are substituted by, respectively, the \tsc{r}-pronouns \tit{r} `there' and \tit{waar} `where'.
+
+\subsection{When \tit{met wat} `with what' shows up}
+
+This section starts by showing that \tit{met wat} `with what' has to be used instead of \tit{waar mee} `with what' under certain circumstances in mismatching free relatives.
+Later in this section I argue that under these circumstances the relevant features that need to be spelled out do not form a proper constituent.
+
+A mismatching free relative is a free relative construction in which the two predicates (the one in the main clause and the one in the relative clause) combine with two different cases.
+In other words, the case requirements of the two clauses do not match.
+First consider \ref{ex:gekochtwaarmee}.
+The predicate in the relative clause, \tit{schildert} `paint', combines with an instrumental object.
 The predicate in the main clause, \tit{gekocht} `bought' combines with an accusative object.
-The \tsc{r}-pronoun and postposition \tit{waar-mee} `with what' is used here.
-The use of \tit{met wat} `with what' is ungrammatical in this context, illustrated in \ref{ex:gekochtmetwat}.\footnote{In this example, \tit{waar} `where' takes \tit{-mee} `with' to the left edge of the embedded clause.
-It is also possible for \tit{-mee} `with' to be stranded, and \tit{waar} `where' to be moved to the left edge of the embedded clause on its own.
-
-\exg. Ik heb gekocht waar jij mee schildert.\\
- I have bought waar you with paint\\
- `I bought what you are painting with.'\label{ex:meealong}
-\z.
-
-\phantom{x}
-}
+The \tsc{r}-pronoun plus postposition \tit{waar mee} `with what' is used here, shown in \ref{ex:gekochtwaarmee}.
+The use of \tit{met wat} `with what' is ungrammatical in this context, illustrated in \ref{ex:gekochtmetwat}.
 
 \ex.
-\ag. Ik heb gekocht waar -mee jij schildert.\\
+\ag. Ik heb gekocht waar mee jij schildert.\\
  I have bought where with you paint\\
- `I bought what you are painting with.'\label{ex:gekochtwaar-mee}
+ `I bought what you are painting with.'\label{ex:gekochtwaarmee}
 \bg. *Ik heb gekocht met wat jij schildert.\\
@@
 
-If the predicates are switched between the clauses, the \tsc{r}-pronoun and postposition do not appear anymore.
-In \ref{ex:schildermet}, \tit{schilder} `paint' combines with an instrumental object in the main clause and \tit{gekocht} `bought' combines with an accusative object in the embedded clause.
-The use of an \tsc{r}-pronoun and postposition is ungrammatical, as indicated by \ref{ex:schilderwaar-mee}.
-Instead, a combination of the regular instrumental preposition \tit{met} `with' and the regular wh-pronoun \tit{wat} `what' in used.
+If the predicates are switched between the clauses, the \tsc{r}-pronoun plus postposition cannot appear anymore.
+In \ref{ex:schildermet}, \tit{schilder} `paint' combines with an instrumental object in the main clause and \tit{gekocht} `bought' combines with an accusative object in the relative clause.
+The use of an \tsc{r}-pronoun plus postposition is ungrammatical, illustrated in \ref{ex:schilderwaarmee}.
+Instead, a combination of the instrumental preposition \tit{met} `with' and the \tsc{wh}-pronoun \tit{wat} `what' is used, shown in \ref{ex:schildermetwat}.
 
 \ex.\label{ex:schildermet}
-\ag. *Ik schilder waar -mee jij hebt gekocht.\\
+\ag. *Ik schilder waar mee jij hebt gekocht.\\
  I paint where with you have bought\\
- `I paint with what you bought.'\label{ex:schilderwaar-mee}
+ `I paint with what you bought.'\label{ex:schilderwaarmee}
 \bg. Ik schilder met wat jij hebt gekocht.\\
@@
 Table \ref{tbl:distribution} summarizes the pattern.
-When the main clause predicate combines with an accusative and the embedded clause predicate with an instrumental, \tit{waar-mee} `with what' is grammatical and \tit{met wat} `with what' is ungrammatical.
-When the main clause predicate combines with an instrumental and the embedded clause predicate with an accusative, \tit{waar-mee} `with what' is ungrammatical and \tit{met wat} `with what' is used.
+When the main clause predicate combines with an accusative and the relative clause predicate with an instrumental, \tit{waar mee} `with what' is grammatical and \tit{met wat} `with what' is ungrammatical.
+When the main clause predicate combines with an instrumental and the relative clause predicate with an accusative, \tit{waar mee} `with what' is ungrammatical and \tit{met wat} `with what' appears instead.
 
@@
   \center
-	\caption {Distribution between \tit{waar-mee} and \tit{met wat}}
-	\begin{minipage}{0.45\linewidth}
-		\begin{tabularx}{\textwidth}{ccc}
+	\caption {Distribution between \tit{waar mee} and \tit{met wat}}
+		\begin{tabular}{lll}
 		\toprule
-                              & \tit{waar-mee} & \tit{met wat} \\
+                              & \tit{waar mee} & \tit{met wat} \\
 		\midrule
-    m:\tsc{acc}, e:\tsc{ins}  & ✔             & *             \\
-    m:\tsc{ins}, e:\tsc{acc}  & *             & ✔             \\
+    m:\tsc{acc}, r:\tsc{ins}  & ✔             & *             \\
+    m:\tsc{ins}, r:\tsc{acc}  & *             & ✔             \\
     \bottomrule
-\end{tabularx}
+\end{tabular}
 \label{tbl:distribution}
-\end{minipage}
 \end{table}
@@
 In the remainder of this section I argue that the crucial point of \ref{ex:schildermetwat} is that the instrumental object does not form a proper constituent, i.e.
-it is not a constituent to the exclusion of any other elements.
+the instrumental object is not a constituent to the exclusion of any other elements.
 The other side of the coin is that constructions with \tsc{r}-pronouns and postpositions contain an instrumental object that does form a proper constituent.
 
-Below I repeat the examples with instrumentals I discussed so far in this paper.
+Below I repeat the examples with instrumental objects discussed in this paper so far.
+I placed square brackets around the relative clauses in \ref{ex:const3} and \ref{ex:const4}.
+In each of these examples the instrumental object forms a proper constituent at a certain point in the derivation.
 
 \ex.
-\ag. Ik schilder 'r -mee.\\
+\ag. Ik schilder r mee.\\
  I paint there with\\
  `I am painting with it.'\label{ex:const1}
-\bg. Waar -mee schilder jij?\\
+\bg. Waar mee schilder jij?\\
 where with paint you with\\
  `What are you painting with?'\label{ex:const2}
-\bg. Ik schilder met de kwast [waar -mee jij ook schildert].\\
+\bg. Ik schilder met de kwast [waar mee jij ook schildert].\\
  I paint with the brush where with you also paint\\
  `I am painting with the brush that you are painting with too.'\label{ex:const3}
-\bg. Ik schilder [waar -mee jij ook schildert].\\
+\bg. Ik schilder [waar mee jij ook schildert].\\
  I paint where with you also paint\\
@@
 
-In each of these examples the instrumental object forms a proper constituent at a certain point in the derivation.
-In \ref{ex:const1}, the instrumental object forms a proper constituent in the surface order, as shown in \ref{ex:const1stage}.
-In \ref{ex:const2}, the instrumental object forms a proper constituent before wh- and V2- movement, shown in \ref{ex:const2stage}.
-The structure in \ref{ex:const3stage} represents a stage in the derivation of the embedded clauses in \ref{ex:const3} and \ref{ex:const4}.
-Again, in the stage, which comes before relative movement of the pronoun to the left periphery of the relative clause, the instrumental object forms a proper constituent.
-
-\ex.
-\a. [[ik] [[schilder] ['r -mee]]]\label{ex:const1stage}
-\b. [[jij] [[schilder] [waar-mee]]]\label{ex:const2stage}
-\b. [[jij] [[ook] [[schilder] [waar-mee]]]]\label{ex:const3stage}
-
-Let me now show how this applies to the examples with the mismatching free relatives.
+Consider now the examples with the mismatching free relatives.
 The two predicates I used in the free relatives are \tit{kopen} `to buy' and \tit{schilderen} `to paint'.
-\tit{Kopen} `to buy' takes an accusative object, illustrated in \ref{ex:kopen}.
-\tit{Schilderen} `to paint' can take an instrumental as its object, shown in \ref{ex:schilderen}.\footnote{\tit{Schilderen} also optionally takes an (accusative) object, but I am focusing on the instrumental object here.}
+\tit{Kopen} `to buy' takes accusative objects, illustrated in \ref{ex:kopen}.
+\tit{Schilderen} `to paint' takes instrumental objects, shown in \ref{ex:schilderen}.\footnote{\tit{Schilderen} also optionally takes an (accusative) object, but I am focusing on the instrumental object here.}
 
@@
 
-I repeat the mismatching free relative in which \tit{waar-mee} `with what' appears in \ref{ex:mismatchwaar-mee}.
-The predicate \tit{schildert} `paints' combines in the embedded clause with the instrumental object.
-The instrumental object forms a proper constituent within the embedded clause, and the it can be realized as the \tsc{r}-pronoun and postposition \tit{waar-mee} `with what'.\footnote{I assume that the accusative case requirement of \tit{gekocht} `bought' is satisfying by grafting a subconstituent of \tit{waar-mee} `with what' \citep{bergsma2019}.}
-
-\exg. Ik heb gekocht [waar -mee jij schildert].\\
+In \ref{ex:mismatchwaarmee}, I repeat the mismatching free relative in which \tit{waar mee} `with what' appears.
+The predicate \tit{schildert} `paints' combines in the relative clause with the instrumental object.
+I placed square brackets around the relative clauses in \ref{ex:mismatchwaarmee}.
+The instrumental object forms a proper constituent within the relative clause, and it can be realized as the \tsc{r}-pronoun plus postposition \tit{waar mee} `with what'.
+
+\exg. Ik heb gekocht [waar mee jij schildert].\\
  I have bought where with you paint\\
- `I bought what you are painting with.'\label{ex:mismatchwaar-mee}
-
-Next, I arrive at the mismatching free relative in which \tit{waar-mee} `with what' cannot be used, but \tit{met wat} `with what' appears.
-The embedded clause predicate \tit{gekocht} `bought' combines with an accusative object.
-The accusative object of a verb is always \tit{wat} `what', as I showed in \ref{ex:wat}.
+ `I bought what you are painting with.'\label{ex:mismatchwaarmee}
+
+Consider now the other kind of mismatch.
+The relative clause predicate \tit{gekocht} `bought' combines with an accusative object.
+I placed square brackets around the relative clauses in \ref{ex:mismatchmetwat}.
+The accusative \tsc{wh}-object of a verb is always \tit{wat} `what', as I have shown earlier in \ref{ex:wat}.
 The instrumental only comes into the picture in the main clause, when \tit{schilder} `paint' combines with an instrumental object.
-At no point in the derivation does the instrumental object form a proper constituent, and \tit{waar-mee} `with what' does not surface.
+At no point in the derivation does the instrumental object form a proper constituent.
+\tit{Waar mee} `with what' cannot surface, and \tit{met wat} appears instead.
 
@@
 I give examples of two more occurrences in \ref{ex:moremetwat}.
-In \ref{ex:watwasfur}, \tit{wat} `what' is the \tit{wat} `what' in the so-called \tit{wat voor} `what for'-construction \citep[cf.][]{corver1991}.
+In \ref{ex:watwasfur}, \tit{wat} `what' is the \tit{wat} in the so-called \tit{wat voor} `what for'-construction \citep[cf.][]{corver1991}.
  In \ref{ex:watindef}, \tit{wat} appears as a quantifier, and it means `some'.
-In both constructions \tit{wat} `what' takes a complement and \tit{met wat} `with what' do not form a proper constituent.
+In both constructions \tit{wat} `what' takes a complement and \tit{met wat} `with what' is not a proper constituent.
 The brackets within the examples indicate the constituency.
@@
 
-\ref{ex:summaryconst} summarizes what I showed in this section.
-\tit{Met wat} `with what' can never surface when \tit{met} `with' and \tit{wat} `what' form a proper constituent.
-It always becomes \tit{waar-mee} `with what', as shown in \ref{ex:waar-meefr}.
+\ref{ex:summaryconst} summarizes the main results of this section.
+\tit{Met wat} `with what' can not surface when the features that correspond to \tit{met wat} form a proper constituent.
+It is always \tit{waar mee} `with what' that appears, as shown in \ref{ex:waar meefr}.
 \tit{Met wat} `with what' can appear when the instrumental object does not form a proper constituent.
-This can be either when \tit{wat} `what' takes a complement before it combines with \tit{met} `with', as shown in \ref{ex:metwatx}, representing the examples in \ref{ex:moremetwat}.
-The other option is that \tit{wat} `what' is part of the a clause that \tit{met} `with' is not a part of, schematized as \ref{ex:metwatfr} as an illustration of \ref{ex:mismatchmetwat}.
+This can be either when \tit{wat} `what' takes a complement before it combines with \tit{met} `with', as shown in \ref{ex:metwatx}, corresponding to the examples in \ref{ex:moremetwat}.
+The other option is that \tit{wat} `what' is part of a clause that \tit{met} `with' is not a part of, schematized as \ref{ex:metwatfr} and corresponding to \ref{ex:mismatchmetwat}.
 
 \ex.\label{ex:summaryconst}
-\a. [[met] [wat]] → [waar-mee]\label{ex:waar-meefr}
+\a. [[met] [wat]] → [waar mee]\label{ex:waar meefr}
 \b. [met [wat [X]]]\label{ex:metwatx}
@@
 
-\section{Decomposing \tit{waar-mee} and \tit{met wat}}\label{sec:takingapart}
-
-In this section I decompose \tit{waar-mee} `with what' and \tit{met wat} `met wat' into smaller units, which I connect to parts of syntactic structure.
-\tit{Waar-mee} `with what' and \tit{met wat} `met wat' spell out the same set of features but the distribution is different.
-I decompose \tit{waar-mee} and \tit{met wat} as I show in \ref{ex:decompose}.
+In sum, \tit{waar mee} `with what' is the default, and \tit{met wat} `with what' only appears if the features that spell out an instrumental object do not form a proper constituent.
+
+\section{Decomposing \tit{waar mee} and \tit{met wat}}\label{sec:takingapart}
+
+In this section I decompose \tit{waar mee} `with what' and \tit{met wat} `with what' into morphemes.
+I connect these morphemes to parts of syntactic structure.
+\tit{Waar mee} `with what' and \tit{met wat} `with what' spell out the same set of features, but the distribution is different.
+I decompose \tit{waar mee} and \tit{met wat} as in \ref{ex:decompose}.
 Earlier works have decomposed these pronouns in similar ways (cf.
@@
 \ex.\label{ex:decompose}
-\ag. w -aa -r -mee\\
-\tsc{w} -\tsc{deix} -\tsc{loc} -\tsc{ins}\\
-\bg. met w -a -t\\
-\tsc{ins} \tsc{w} -\tsc{deix} -\tsc{n.sg}\\
-\z.
-\z.
-
-In this section I first identify \tit{w} and \tit{a} as morphemes that appear in both expressions.
-Putting these two aside, I concentrate on \tit{'rmee} `with it' and \tit{met 't} `with it'.
-Along the way I introduce some necessary theoretical background on Nanosyntax.
-
-\subsection{Overlap: \tit{w-} and \tit{-a-}}
-
-Let me start with the morphemes \tit{w} and \tit{a} that appear in both \tit{waar-mee} `with what' and \tit{met wat} `met wat'.
+\a. w-aa-r mee
+\b. met w-a-t
+
+In this section I first identify \tit{w} and \tit{a(a)} as morphemes that appear in both expressions. Putting these two aside, I then concentrate on \tit{r mee} `with it' and \tit{met t} `with it'.
+I propose an account that makes the ungrammaticality of \tit{met t} and the appearance of \tit{r mee} follow from spellout.
+The analysis accounts for the following three observations, taking \tit{met t} as the point of departure.
+First, \tit{met} `with' changes from being a preposition to being a postposition.
+This process is restricted to inanimate pronouns, and it does not apply to full noun phrases and animate pronouns.
+Second, \tit{met} changes form to \tit{mee}.
+Third, \tit{t} is replaced by \tit{r}, a morpheme that is associated with the locative in Dutch.
+Along the way I introduce some necessary theoretical background on lexicalization in Nanosyntax.
+
+\subsection{\tit{w} and \tit{a(a)}}
+
+Let me start with the morphemes \tit{w} and \tit{a(a)} that appear in both \tit{waar mee} `with what' and \tit{met wat} `with what'.
 I assume that they correspond to the same syntactic structure in both.
-As I am interested in the differences between the two expressions, I do not discuss the featural content of \tit{w} and \tit{a} into depth.
-
-For \tit{w} I follow \citet{hachem2015} who investigated \tit{d} and \tit{w} elements in German and Dutch.
+As I am interested in the differences between the two expressions, I do not discuss the featural content of \tit{w} and \tit{a(a)} in depth.
+
+For \tit{w} I follow \posscitet{hachem2015} work on \tit{d} and \tit{w} elements in German and Dutch.
 In her work, \tit{d} establishes a definite reference and \tit{w} triggers the construction of a set of alternatives in the sense of \citet{rooth1992} (see \citealt{hachem2015} for discussion).\footnote{Throughout the paper, ⇔ indicates the pairing between a lexical tree and a phonological form in a lexical entry, and ⇒ indicates how a node in the syntactic structure is spelled out.}
@@
 I follow several authors (cf.
-\citealt{lander2016,noonan2017dutch,wesseling2018}) that assume the morpheme \tit{a} is related to deixis.
-Dutch distinguishes between proximal by using \tit{ie} (/i:/) and \tit{i} (/ɪ/) and distal by using \tit{aa} (/aː/) and \tit{a} (/ɑ/), illustrated in \ref{ex:deixis}.\footnote{A question that remains open is why wh-elements combine with the distal marker \tit{a}, and they cannot with the proximal marker \tit{i/ie}.} I analyze the transformation from /ɪ/ into /i:/ and /ɑ/ into /aː/ as a result of the final r.
+\citealt{lander2016,noonan2017dutch,wesseling2018}) in the assumption that the morpheme \tit{a(a)} is related to deixis.
+Dutch distinguishes between proximal by using \tit{ie} (/i:/) and \tit{i} (/ɪ/) and distal by using \tit{aa} (/aː/) and \tit{a} (/ɑ/), illustrated in \ref{ex:deixis}.\footnote{
+\tsc{Wh}-elements combine with the distal marker \tit{a(a)}, and they cannot with the proximal marker \tit{i/ie}.
+Conceptually, this can be understood if spatial deixis is connected to discourse deixis \citep[cf.][]{colasanti2019}.
+Proximal is spatially near the speaker and refers to knowledge that the speaker possesses.
+Distal is spatially away from the speaker and refers to knowledge that the speaker does not possess.
+In \tsc{wh}-pronouns, the speaker does not have the knowledge, so the distal is used and not the proximal.
+}
+I assume that the changes from from /ɪ/ into /i:/ and /ɑ/ into /aː/ is due to phonology, possibly as a result of the final /r/.\footnote{I leave the description of the exact phonological process for future research.}\footnote{
+Note that in the proximal the initial \tit{d} is also replaced by an \tit{h}.
+This could indicate that (1) there must be some difference between \tit{hier} `here' and \tit{daar} `there' besides proximal and distal or (2) there is a different distribution between \tit{h} plus \tit{ie} and \tit{d} plus \tit{i} and the difference in vowels is not a matter of phonology.
+As this is not the focus of this paper, I put this aside for now.
+}
 
@@
 
-For the purpose of this paper I let \tit{a} correspond to \tsc{deixP}.
+For the purpose of this paper I let \tit{a(a)} correspond to \tsc{deixP}.
 
@@
 ]
-{\draw (.east) node[right]{⇔ \tit{a}}; }
+{\draw (.east) node[right]{⇔ \tit{a(a)}}; }
 \end{forest}\label{ex:entrya}
 
-I put \tit{w} and \tit{a} aside for now, assuming they spell out the same syntactic structure in \tit{waar-mee} `with what' and \tit{met wat} `with what'.
-This leaves \tit{'r-mee} `with it' and \tit{met 't} `with it'.
-
-\ex.
-\ag. 'r -mee\\
-there with\\
-\b. met 't\\
-with it\\
-\z.
-\z.
-
-\subsection{Differences: \tit{'rmee} vs. \tit{met 't}}
-
-In this section I discuss the forms \tit{met 't} `with it` and \tit{'rmee} `with it'.
-I set up an account that makes the ungrammaticality of \tit{met 't} and the appearance of \tit{'rmee} follow from spellout.
-The analysis accounts for the following three observations, taking \tit{met 't} as the point of departure.
-First, \tit{met} `with' changes from being a preposition to being a postposition.
-This process is restricted to inanimate pronouns, and it does not apply to full DPs and animate pronouns.
-Second, \tit{met} changes form into \tit{-mee}.
-Third, \tit{'t} is replaced by \tit{'r}, a morpheme that is associated with the locative in Dutch.
-
-\subsubsection{\tit{'t} vs. \tit{'r}}
-
-In this section I give the lexical entries for \tit{'t} and \tit{'r}, and I show that \tit{'r} is actually the base form and \tit{'t} a suppletive nominative, accusative and dative.
-
-Let me start with the lexical entry for \tit{'t}.
-\tit{'t} `it' can be used as a subject (associated with nominative), direct object (associated in accusative) and indirect object (associated with dative), as shown in \ref{ex:tsubobj}.
+I put \tit{w} and \tit{a(a)} aside for now, assuming they spell out the same syntactic structure in \tit{waar mee} `with what' and \tit{met wat} `with what'.
+This leaves \tit{r mee} `with it' and \tit{met t} `with it'.
+
+\subsection{\tit{r mee} vs. \tit{met t}}
+
+In this section I discuss the forms \tit{r mee} `with it' and \tit{met t} `with it`.
+I argue that both forms spell out the same features.
+Whether or not the features form a proper constituent determines which form appears.
+
+\subsubsection{\tit{t} vs. \tit{r}}
+
+In this section I give the lexical entries for \tit{t} and \tit{r}. I show that \tit{r} is the base form and \tit{t} a suppletive form that additionally encodes nominative, accusative or dative.
+
+I start with the lexical entry for \tit{t}.
+The element \tit{t} `it' can be used as a subject (associated with nominative), direct object (associated with accusative) and indirect object (associated with dative), as shown in \ref{ex:tsubobj}.
 
 \ex.\label{ex:tsubobj}
-\ag. 't Staat in de hal.\\
+\ag. T staat in de hal.\\
  \tsc{3sg.n.nom} stands in the hallway\\
  `It is standing in the hallway.'\label{ex:tnoclitic}
-\bg. Ik zie 't.\\
+\bg. Ik zie t.\\
  I see \tsc{3sg.n.acc}\\
  `I see it.'
-\bg. Ik heb 't een klap gegeven.\\
+\bg. Ik heb t een klap gegeven.\\
  I have \tsc{3sg.n.dat} a hit given\\
@@
 
- Pronouns in other genders alternate between nominative (non-oblique) and accusative/dative (oblique) in these contexts, illustrated in \ref{ex:hemsubobj}.
-
- \ex.\label{ex:hemsubobj}
- \ag. Hij staat in de hal.\\
-  \tsc{3sg.m.nom} stands in the hallway\\
-  `He is standing in the hallway.'
- \bg. Ik zie hem.\\
-  I see \tsc{3sg.m.acc}\\
-  `I see it.'
- \bg. Ik heb hem een klap gegeven.\\
-  I have \tsc{3sg.m.dat} a hit given\\
-  `I gave him a hit.'
-
-For case, I follow \citet{caha2009} in that case features are organized as in the containment relation in \ref{ex:casetree}.
-The higher, more complex cases contain the smaller, less complex cases.
-For the purpose of this paper, I only show case features relevant for the argument.
+For case, I follow \citet{caha2009} in that case features are organized in a containment relation as in \ref{ex:casetree}.
+The higher, more complex cases contain the lower, less complex cases.
+For the purpose of this paper, I only show the case features relevant to my analysis.
 
@@
  [\tsc{insP}
-     [\tsc{f4}]
+     [\tsc{k4}]
      [\tsc{datP}
-         [\tsc{f3}]
+         [\tsc{k3}]
          [\tsc{accP}
-             [\tsc{f2}]
-             [\tsc{nomP}
-                 [\tsc{f1}]
+             [\tsc{k2}]
+             [\tsc{nomP}
+                 [\tsc{k1}]
                  [DP
-                     [..,roof]
+                     [\phantom{xxx},roof]
                  ]
@@
 
- Following the distinctions from \citet{cardinaletti1996}, I assume \tit{'t} `it' is a weak pronoun.
+ The morpheme \tit{t} can act as nominative, accusative and dative, so it spells out \tit{k}1, \tsc{k}2 and \tsc{k}3.
+
+ Following the distinctions from \citet{cardinaletti1996}, I assume \tit{t} `it' is a weak pronoun.
 It is not a clitic, because it can occur in sentence initial position, shown in \ref{ex:tnoclitic}.
 It is not a strong pronoun, because it cannot be coordinated, as indicated in  \ref{ex:tcoordinated}.
-\ref{ex:datcoordinated} shows that \tit{'t} `it' needs to combine with \tit{da-}/\tit{di-} to be able to be coordinated.
+\ref{ex:datcoordinated} shows that \tit{t} `it' needs to combine with \tit{da-}/\tit{di-} to be able to be coordinated.
 
  \ex.
- \ag. *Hij en 't staan in de hoek.\\
+ \ag. *Hij en t staan in de hoek.\\
   he and it stand in the corner\\
@@
 
-\ref{ex:entryt} shows the lexical entry for \tit{'t} `it'.
-I assume that the \tit{'t} contains the ontological category \tsc{thing} \citep{kayne2005}.
 The feature Σ indicates that the pronoun is a weak pronoun.
-For reasons of space I let singular be the absence of number and neuter the absence of gender.
-The morpheme \tit{'t} can act as nominative, accusative and dative, as I showed in \ref{ex:tsubobj}.\footnote{ Another possibility is to claim that \tit{'t} can only spell out \tsc{thing} and Σ and it combines with a zero suffix for the cases up to dative.
-This could be the same zero marker that full DPs combine with.
-
-\ex.
-\ag. De kast-∅ staat in de hal.\\
- the cabinet-\tsc{nom} stands in the hallway\\
- `The cabinet is standing in the hallway.'
-\bg. Ik zie de kast-∅.\\
- I see the cabinet-\tsc{acc}\\
- `I see the cabinet.'
-\bg. Ik heb de kast-∅ een klap gegeven.\\
- I have the cabinet-\tsc{dat} a hit given\\
- `I gave the cabinet a hit.'
-
-The proposed account fares equally well with both alternatives. I work the proposal out with \tit{'t} realizing the cases up to the dative.}
+
+In addition to the pronominal and case features, I assume that the \tit{t} contains the ontological category \tsc{thing} \citep{kayne2005}.
+For reasons of space I will assume singular to be the absence of number and neuter the absence of gender.
+
+\ref{ex:entryt} shows the lexical entry for \tit{t} `it'.
 
@@
  [\tsc{datP}
-     [\tsc{f3}]
+     [\tsc{k3}]
      [\tsc{accP}
-         [\tsc{f2}]
-         [\tsc{nomP}
-             [\tsc{f1}]
-             [ΣP
-                 [Σ]
-                 [\tsc{thingP}
-                     [\tsc{thing}, roof]
-                 ]
-             ]
-         ]
-     ]
- ]
- {\draw (.east) node[right]{⇔ \tit{'t}}; }
+         [\tsc{k2}]
+         [\tsc{nomP}
+             [\tsc{k1}]
+             [ΣP
+                 [Σ]
+                 [\tsc{thingP}
+                     [\tsc{thing}, roof]
+                 ]
+             ]
+         ]
+     ]
+ ]
+ {\draw (.east) node[right]{⇔ \tit{t}}; }
  \end{forest}\label{ex:entryt}
 
- This lexical entry can lexicalize the \tsc{datP}, but also the \tsc{accP} and \tsc{nomP}. This is due to the Superset Principle.
-
-  \ex. The Superset Principle \citet{starke2009}: \\
+ This lexical entry can lexicalize the \tsc{datP}, but also the \tsc{accP} and \tsc{nomP}. This is due to the Superset Principle, given in \ref{ex:superset-principle}.
+
+  \ex.\label{ex:superset-principle} The Superset Principle \citet{starke2009}: \\
   A lexically stored tree matches a syntactic node iff the lexically stored tree contains the syntactic node.
 
- In other words, a lexically stored structure does not have to be identical to the syntactic structure.
-It is enough if the syntactic structure is contained in the lexically stored tree.
+ In other words, a lexically stored structure does not have to be identical to the syntactic structure it spells out.
+The crucial requirement is that the syntactic structure is contained within the lexically stored tree.
 This has as a consequence that the lexical entry in \ref{ex:entryt} can also be inserted in \ref{ex:tacc} and \ref{ex:tnom}.
@@
  [\tsc{accP}
-     [\tsc{f2}]
-     [\tsc{nomP}
-         [\tsc{f1}]
-         [ΣP
-             [Σ]
-             [\tsc{thingP}
-                 [\tsc{thing}, roof]
-             ]
-         ]
-     ]
- ]
+     [\tsc{k2}]
+     [\tsc{nomP}
+         [\tsc{k1}]
+         [ΣP
+             [Σ]
+             [\tsc{thingP}
+                 [\tsc{thing}, roof]
+             ]
+         ]
+     ]
+ ]
+ {\draw (.east) node[right]{⇔ \tit{t}}; }
  \end{forest}\label{ex:tacc}
@@
  [\tsc{nomP}
-     [\tsc{f1}]
-     [ΣP
-         [Σ]
-         [\tsc{thingP}
-             [\tsc{thing}, roof]
-         ]
-     ]
- ]
+     [\tsc{k1}]
+     [ΣP
+         [Σ]
+         [\tsc{thingP}
+             [\tsc{thing}, roof]
+         ]
+     ]
+ ]
+ {\draw (.east) node[right]{⇔ \tit{t}}; }
  \end{forest}\label{ex:tnom}
 
-Let me move on to \tit{'r}. \tit{'r} `there' can be used as a locative.
-
- \exg. Ik ben 'r al geweest.\\
+I continue with \tit{r}. The \tsc{r}-pronoun \tit{r} can be used as a locative.
+
+ \exg. Ik ben r al geweest.\\
   I am there already been\\
@@
 
-I follow \citet{baunaz2018} in assuming that the ontological category \tsc{location} contains \tsc{thing}.\footnote{\citet{baunaz2018} place in addition \tsc{person} between \tsc{thing} and \tsc{location}, which I have left out here.}
-
-\ex. \begin{forest} boom
-[\tsc{loc}P
+I follow \citet{baunaz2018} in assuming that the ontological category \tsc{location} contains \tsc{thing}.\footnote{\citet{baunaz2018} place in addition \tsc{person} between \tsc{thing} and \tsc{location}, which I leave out here.} I give the lexical entry for \tit{r} `there' in \ref{ex:entryr}.
+
+\ex. \begin{forest} boom
+[\tsc{location}P
     [\tsc{location}]
@@
 ]
-{\draw (.east) node[right]{⇔ \tit{'r}}; }
+{\draw (.east) node[right]{⇔ \tit{r}}; }
 \end{forest}\label{ex:entryr}
 
-Notice here that, via the Superset Principle, \tit{'r} can be used to realize the feature \tsc{thing} as well, as it is contained in \tsc{locP}.
-Moreover, in a syntactic structure like in \ref{ex:rthing} the lexical entry \ref{ex:entryr} will be inserted and not \ref{ex:entryt}.
+Notice here that, via the Superset Principle, \tit{r} can also realize the feature \tsc{thing}, as it is contained in \tsc{locationP}.
+Moreover, for a syntactic structure like \ref{ex:rthing} the lexical entry \ref{ex:entryr} will be inserted and not \ref{ex:entryt}.
 
@@
  ]
-{\draw (.east) node[right]{⇒ \tit{'r}}; }
+{\draw (.east) node[right]{⇒ \tit{r}}; }
 \end{forest}\label{ex:rthing}
 
-This is due to the Elsewhere Condition. The idea is that when two lexical entries are both candidates for spellout, the most specific is inserted.
-
-\ex. The Elsewhere Condition (\citealt{kiparsky1973}, formulated as in \citealt{caha2020}):\\
+The choice of \ref{ex:entryt} over \ref{ex:entryr} is due to the Elsewhere Condition, given in \ref{ex:elswhere-condition}.
+
+\ex.\label{ex:elswhere-condition} The Elsewhere Condition (\citealt{kiparsky1973}, formulated as in \citealt{caha2020}):\\
 When two entries can spell out a given node, the more specific entry wins. Under the Superset Principle governed insertion, the more specific entry is the one which has fewer unused features.
 
-The syntactic structure in \ref{ex:entryr} only has \tsc{loc} as an unused feature, whereas in \ref{ex:entryt} Σ up to \tsc{f3} remain unused.
-
-This means that the caseless base form of the neuter singular pronoun in Dutch is actually \tit{'r} and \tit{'t} should be analyzed as a suppletive nominative, accusative and dative.
-The base form only shows up in the higher cases, from instrumental on, see Table \ref{tbl:dutchcases}.
+In other words, when two lexical entries are both candidates for spellout, the more specific one is inserted.
+The syntactic structure in \ref{ex:entryr} only has \tsc{location} as an unused feature, while in \ref{ex:entryt} all features from Σ up to \tsc{k3} remain unused.
+
+Under this analysis, the caseless base form of the neuter singular pronoun in Dutch is actually \tit{r} and \tit{t} is a suppletive nominative, accusative and dative form.
+The base form only shows up in the higher cases, from instrumental on.
+I show this in Table \ref{tbl:dutchcases}.
 
@@
 	\caption {Fragment Dutch \tsc{n.sg}}
-	\begin{minipage}{0.17\linewidth}
-		\begin{tabularx}{\textwidth}{ccccccc}
+		\begin{tabular}{ll}
 		\toprule
@@
 		\midrule
-    \tsc{nom} & 't         \\
-    \tsc{acc} & 't         \\
-    \tsc{dat} & 't         \\
-    \tsc{ins} & -r -mee    \\
+    \tsc{nom} & t         \\
+    \tsc{acc} & t         \\
+    \tsc{dat} & t         \\
+    \tsc{ins} & r-mee    \\
     \bottomrule
-\end{tabularx}
+\end{tabular}
 \label{tbl:dutchcases}
-\end{minipage}
 \end{table}
 
-A similar situation appears in Iron Ossetic, shown in Table \ref{tbl:ossetic}.
-In the first person singular of this language, it is only the nominative that is suppletive: \tit{æz}.
-The higher cases have the stem \tit{mæn} and they combine with the suffixes that nouns normally also combine with.
+A similar pattern appears in Iron Ossetic, shown in Table \ref{tbl:ossetic}.
+In the first person singular of this language, it is only the nominative that is suppletive form (\tit{æz}).
+The higher cases have the stem \tit{mæn} and they combine with the suffixes that nouns normally combine with.
 
@@
 	\center
-	\caption {Fragment Iron Ossetic 1.\tsc{sg} and noun \citep{erschler2012}}
-	\begin{minipage}{0.3\linewidth}
-		\begin{tabularx}{\textwidth}{ccccccc}
+	\caption {Partial paradigm of Iron Ossetic 1\tsc{sg} and noun \citep{erschler2012}}
+		\begin{tabular}{lll}
 		\toprule
-              & 1.\tsc{sg}  & head    \\
+              & 1\tsc{sg}  & head    \\
 		\midrule
@@
     \bottomrule
-\end{tabularx}
+\end{tabular}
 \label{tbl:ossetic}
-\end{minipage}
 \end{table}
 
-\citet{caha2019competition} uses evidence from a phenomenon called suspended affixation to argue that \tit{mæn} is a caseless stem and and \tit{æz}.
-Consider the ordinary coordination in \ref{ex:horseoxboth}.
+\citet{caha2019competition} uses evidence from a phenomenon called suspended affixation to argue that \tit{mæn} is a caseless stem and \tit{æz} is a suppletive nominative form.
+Consider the ordinary coordination of two full noun phrases in \ref{ex:horseoxboth}.
 Both conjuncts are marked by a plural marker and a case marker.
 Suspended affixation is shown in \ref{ex:horseoxone}.
-Here the case marker only appears on the second conjunct and not on the first one without changing the interpretation.
+Here the case marker only appears on the second conjunct and not on the first one, without changing the interpretation.
 \tit{Bæx-tæ} `horse-\tsc{pl}' in \ref{ex:horseoxone} does not carry any case marking here.
@@
 
-\ref{ex:suspendedme} gives examples of the first person singular in a suspended affixation contexts.
+\ref{ex:suspendedme} gives examples of the first person singular in suspended affixation contexts.
 It shows that it is \tit{mæn} that appears as a caseless first conjunct and that the use of \tit{æz} is ungrammatical.
-This means that \tit{mæn} is the bare stem that combines with case markers, and \tit{æz} the suppletive nominative.
-In Section \ref{sec:derivation} I show how a derivation with this type of elements works in Nanosyntax.
+This means that \tit{mæn} is the bare stem that combines with case markers, and \tit{æz} the suppletive nominative form.
 
@@
 \ag. mæn æmæ Zauyr-æn\\
- 1.\tsc{sg} and Zaur-\tsc{dat}\\\label{ex:izaurboth}
+ 1\tsc{sg} and Zaur-\tsc{dat}\\\label{ex:izaurboth}
 \bg. *æz æmæ Zauyr-æn\\
- 1.\tbf{sg} and Zaur-\tsc{dat}\\
+ 1\tsc{sg} and Zaur-\tsc{dat}\\
  `me and Zaur' \hfill (Iron Ossetic, \citealt[39]{беляев2014} after \citealt{caha2019competition})\label{ex:izaurone}
 
-The point of showing the Ossetic example is that Dutch is not unique in having suppletive forms that are less marked (in this case nominative, accusative and dative), and higher cases that are a combination of a suffix and a caseless base form.
-
-\subsubsection{\tit{-mee} vs. \tit{met}}
-
-The last two forms to specify lexical entries for are \tit{-mee} `with' and \tit{met} `with'.
-An important distinction between these two is that \tit{-mee} appears after the element it combines with (\tsc{'r}), while \tit{met} appears before the element it combines with (\tit{'t}).
-I will analyze \tit{-mee} as a postposition and \tit{met} as a preposition.\footnote{A topic related to this paper is the different positioning of identical adpositions in Dutch (see \citet{caha2010} for an account of German and Dutch and \citet{pretorius2017} for Afrikaans).
-In \ref{ex:dutchin}, \tit{in} `in' changes meaning depending on whether it proceeds or follows the DP, it is respectively locational or directional.
+The take-away message from the Ossetic example is that Dutch is not unique.
+Dutch and Ossetic both have a suppletive form that is less marked (in Dutch nominative, accusative and dative and in Ossetic nominative), and higher cases that are expressed by a combination of a suffix and a caseless base form.
+
+\subsubsection{\tit{mee} vs. \tit{met}}
+
+The last two forms for which I specify lexical entries are \tit{mee} `with' and \tit{met} `with'.
+An important distinction between these two is that \tit{mee} appears after the element it combines with, while \tit{met} appears before the element it combines with.
+In other words, \tit{mee} is a postposition and \tit{met} is a preposition.\footnote{
+A topic related to this paper is the different positioning of syncretic adpositions in Dutch (see \citet{caha2010} for an account of German and Dutch and see \citet{pretorius2017} for Afrikaans).
+In \ref{ex:dutchin}, \tit{in} `in' changes meaning depending on whether it proceeds or follows the DP.
+In \ref{ex:dutch-in-loc}, \tit{in} `in' carries a locational meaning, and in \ref{ex:dutch-in-dir}, \tit{in} `in' carries a directional meaning.
 
@@
  I climb in the tree\\
- `I am climbing in the tree.'
+ `I am climbing in the tree.'\label{ex:dutch-in-loc}
 \bg. Ik klim de boom in.\\
  I climb the tree in\\
- `I am climbing into the tree.'
-
-In \ref{ex:dutchin}, the movement of the adposition is driven by movement, and it is meaningful.
-The movement of \tsc{r}-pronouns I discuss in this paper is driven by spellout, which is meaningless.} In this section I discuss the relation between prepositions and postpositions, and how this is modeled with the case hierarchy in Nanosyntax \citep{caha2009}.
-
-In the previous section I argued that \tit{'t} realizes case features up to \tsc{f3} (see \ref{ex:entryt}).
+ `I am climbing into the tree.'\label{ex:dutch-in-dir}
+
+In \ref{ex:dutchin}, the movement of the adposition is driven by movement, and it is meaningful. The movement of \tsc{r}-pronouns I discuss in this paper is driven by spellout, which is meaningless.}
+In this section I discuss the difference between prepositions and postpositions, and how this is modeled with the case hierarchy in Nanosyntax \citep{caha2009}.
+
+In the previous section I argued that \tit{t} realizes case features up to \tsc{k3} (see \ref{ex:entryt}).
 However, case can also be expressed by prepositions (or prefixes) and postpositions (or suffixes).
 The division between which cases are expressed by prepositions and which are expressed by postpositions is not arbitrary.
-
-\ex. The preposition/postposition hierarchy
-\a. If the expression of a particular case in the case sequence (below) involves a preposition, then all cases to its right do as well.
-\b. The case sequence: \tsc{nom – acc – dat – gen - ins – com} \hfill \citep{caha2009}
-
-The result of that is that a PP can contain a preposition and a suffix. In the German example in \ref{ex:loffel}, the dative suffix is used with a instrumental preposition.
+If a particular case in the case sequence (see \ref{ex:casetree}) is expressed by a preposition, then all higher cases are too (the preposition/postposition hierarchy, \pgcitealt{caha2010}{36}).
+The lower cases are expressed by the DP, either as a suffix or by the DP itself.
+The result of that is that a PP can contain a preposition and a suffix. In the German example in \ref{ex:loffel}, the dative suffix is used with an instrumental preposition.
 
 \exg. mit ein -em Löffel\\
-with a -\tsc{dat.sg} spoon\\
+with a \tsc{dat.m.sg} spoon\\
 `with a spoon' \hfill (German)\label{ex:loffel}
 
-With the case hierarchy in Nanosyntax this can be modeled by letting the DP move as high as above the \tsc{datP} in the syntactic structure in \ref{ex:casetree}.
-The features below the \tsc{datP} are realized as a suffix, and the features above \tsc{datP} are realized as a preposition.
-
-There is variation with respect to how high a DP can move in the structure, both between languages and within languages.
-An example of the latter comes from Bulgarian.
-\ref{ex:bulpron} shows that pronouns can take the suffix \tit{-i} to realize dative, but full DPs need a preposition \tit{na} `to'.
+The features up to the \tsc{datP} are realized as a suffix, and the features above \tsc{datP} are realized as a preposition (see \ref{ex:casetree}).
+
+It varies between and within languages which cases are spelled out by prepositions and which ones are spelled out by suffixes.
+In other words, there is variation in how many case features a suffix can spell out, and how many it leaves for the preposition to spell out.
+An example of variation within a language comes from Bulgarian.
+\ref{ex:bulpron} shows that pronouns can take the suffix \tit{-i} to realize dative, and \ref{ex:buldpto} shows that full noun phrases (such as the proper name \tit{Kamen}) need a preposition \tit{na} `to'.
 
@@
 \ag. Tazi duma m -i e nepoznata.\\
-that word I -\tsc{dat} is unfamiliar\\
+that word I -\tsc{acc/dat.cl} is unfamiliar\\
 `That word is unfamiliar to me.'\label{ex:bulpron}
-\bg. Tazi duma e nepoznata na sina mi.\\
-that word is unfamiliar to son my\\
-`That word is unfamiliar to my son.'\label{ex:buldpto} \hfill (Bulgarian, \citealt[39]{caha2009})
-
-In Dutch the split is not between pronouns and full DPs but between inanimate pronouns on the one hand and animates and full DPs on the other hand.
-In Dutch, inanimate pronouns combine with the postposition \tit{-mee} (see \ref{ex:dutchina} and not with the preposition \tit{met} (see \ref{ex:dutchinmet}).
+\bg. Tazi duma e nepoznata na Kamen.\\
+that word is unfamiliar to Kamen\\
+`That word is unfamiliar to Kamen.'\label{ex:buldpto} \hfill (Bulgarian, \citealt[39]{caha2009})
+
+The example in \ref{ex:bulpron} indicates that the suffix \tit{-i} can spell out features up to the dative case.
+However, for some reason this suffix cannot combine with a full DP to spell out these dative features.
+Instead, the preposition \tit{na} is used, as shown in \ref{ex:buldpto}.
+
+In Dutch, the split between the use of a preposition and the use of a postposition is not between pronouns and full noun phrases but between inanimate pronouns and animate pronouns plus full noun phrases.
+In Dutch, inanimate pronouns combine with the postposition \tit{mee} and not with the preposition \tit{met} (compare \ref{ex:dutchina} and \ref{ex:dutchinmet}).
 
 \ex.
-\ag. Ik schilder 'r -mee.\\
- I paint there -with\\
+\ag. Ik schilder r mee.\\
+ I paint there with\\
  `I am painting with it.'\label{ex:dutchina}
-\bg. *Ik schilder met 't\\
+\bg. *Ik schilder met t.\\
  I paint with it\\
@@
 
-Animate pronouns and full DPs, however, combine with the preposition met, as shown in \ref{ex:dutchan} and \ref{ex:dutchdp}.
-The use of the postposition \tit{-mee} is ungrammatical (see \ref{ex:dutchanmee} and \ref{ex:dutchdpmee}).
+Animate pronouns and full noun phrases, however, combine with the preposition \tit{met}, and the use of the postposition \tit{mee} is ungrammatical (compare \ref{ex:dutchan} and \ref{ex:dutchdp} to \ref{ex:dutchanmee} and \ref{ex:dutchdpmee}).
 
 \ex.
-\ag. Ik schilder samen met hem.\\
- I paint together with him\\
- `I am painting with him.'\label{ex:dutchan}
-\bg. Ik schilder samen met de man.\\
- I paint together with the man\\
- `I am painting together with the man.'\label{ex:dutchdp}
-\bg. *Ik schilder samen 'm-mee.\\
- I paint together him-with\\
- `I am painting together with him.'\label{ex:dutchanmee}
-\bg. *Ik schilder samen de man-mee.\\
- I paint together the man-with\\
- `I am painting together with the man.'\label{ex:dutchdpmee}
-
- In other words, inanimates can move higher than animates and full DPs in Dutch.
-To be more precise, the inanimate \tit{'t} is replaced by \tit{'r}, and this element can move as high as above the dative to combine with \tit{-mee}.
-I return to what it is that prevents animates and full DPs from being combined with \tit{-mee} shortly.
-
-First I show what the lexical entry of \tit{-mee} looks like.
-Two facts need to be captured.
-\tit{-mee} combines with \tit{'r} and is a postposition.
-First, \tit{-mee} expresses instrumental (and comitative) case and it combines with \tit{'r}.\footnote{For reasons of space I leave \tsc{comP} out of the lexical entries and discussion, even though \tit{-mee} `with' and \tit{met} `with' can also express comitative.}
-This means that the combination of \tit{'r} and \tit{-mee} has to realize \tsc{thing}, Σ and all case features up to \tsc{f4}.
-So far, \tit{'r} `there' only realizes the feature \tsc{thing}.
-This leaves Σ and \tsc{f1} to \tsc{f4} to be realized by \tit{-mee}.
-I give the lexical tree of \tit{-mee} in \ref{ex:entrymee}.
+\ag. Ik schilder samen met de kunstenares.\\
+ I paint together with the artist\\
+ `I am painting together with the artist.'\label{ex:dutchan}
+\bg. Ik schilder samen met de kunstenares.\\
+ I paint together with the artist\\
+ `I am painting together with the artist.'\label{ex:dutchdp}
+\bg. *Ik schilder samen de kunstenares mee.\\
+ I paint together the artist with\\
+ `I am painting together with the artist.'\label{ex:dutchanmee}
+\bg. *Ik schilder samen de kunstenares mee.\\
+ I paint together the artist with\\
+ `I am painting together with the artist.'\label{ex:dutchdpmee}
+
+The example in \ref{ex:dutchina} indicates that the postposition \tit{mee} can spell out features up to the instrumental case when there is an inanimate pronoun.
+However, for some reason this suffix cannot combine with an animate pronouns or a full DP to spell out these dative features, as shown in \ref{ex:dutchanmee} and \ref{ex:dutchdpmee}.
+Instead, the preposition \tit{met} is used, as shown in \ref{ex:dutchan} and \ref{ex:dutchdp}.
+In what follows, I give lexical entries that are in line with these observations.
+
+I start by giving the lexical entry for \tit{mee}.
+Two facts need to be captured: \tit{mee} combines with \tit{r} and it is a postposition.
+The combination of \tit{r} and \tit{mee} expresses an inanimate instrumental.
+This means that the combination of \tit{r} and \tit{mee} has to realize \tsc{thing}, Σ and all case features up to \tsc{k4}.
+So far, the \tsc{r}-pronoun \tit{r} only realizes the feature \tsc{thing}.
+This leaves Σ and \tsc{k1} to \tsc{k4} to be realized by \tit{mee}.
+
+This brings me to the second point: \tit{mee} is a postposition.
+Nanosyntax distinguishes pre-elements from post-elements by the shape of their lexical entry \citep{starke2018}.
+Doing so, it follows from the spellout procedure whether an element appears before or after the previously inserted element.
+Post-elements have a unary bottom (i.e.
+the foot of the tree is a single feature), so they can only appear as the result of movement of their complement.
+Pre-elements have a binary bottom (i.e.
+the foot of the tree consists of two features), so they cannot be the inserted after complement movement.
+I illustrate this in a derivation in Section \ref{sec:derivation}.
+I give the lexical tree of \tit{mee} in \ref{ex:entrymee}.
 
@@
 [\tsc{insP}
-    [\tsc{f4}]
+    [\tsc{k4}]
     [\tsc{datP}
-        [\tsc{f3}]
+        [\tsc{k3}]
         [\tsc{accP}
-            [\tsc{f2}]
-            [\tsc{nomP}
-                [\tsc{f1}]
-                [ΣP
-                    [Σ]
-                ]
-            ]
-        ]
-    ]
-]
-{\draw (.east) node[right]{⇔ \tit{-mee}}; }
+            [\tsc{k2}]
+            [\tsc{nomP}
+                [\tsc{k1}]
+                [ΣP
+                    [Σ]
+                ]
+            ]
+        ]
+    ]
+]
+{\draw (.east) node[right]{⇔ \tit{mee}}; }
 \end{forest}\label{ex:entrymee}
 
-This leads me to the second point: \tit{-mee} is a postposition.
-Notice that the foot of the structure has a singleton feature.
-Nanosyntax distinguishes pre-elements from post-elements by the shape of their lexical entry \citep{starke2018}.
-As a result, it follows from the spellout procedure whether an element appears before or after the previously inserted element.
-Post-elements have a unary bottom (i.e.
-the foot of the tree is a single feature), so they can only appear as the result of movement.
-Post-elements have a binary bottom (i.e.
-the foot of the tree consists of two features), so they cannot be a candidate as a result of movement.
-I illustrate this in Section \ref{sec:derivation}.
-
-Why does \tit{-mee} not combine with animates and full DPs?
-I claim that has to do with the bottom feature of the lexical entry of \tit{-mee}.
-Full DPs do not take features related to pronominal strength.
-According to the Superset Principle, a lexical tree can match a syntactic tree with a subpart of the features, but a tree can only shrink from the top, so \tit{-mee} will always realize Σ.
-It is less clear to me why animates do not combine with \tit{-mee}.
-The crucial difference between animates and inanimates if gender features.
-For now I assume that gender features are situated between Σ and \tsc{f1}.
-The lexical entry of \tit{-mee} includes both these features, so any additional gender features are incompatible with \tit{-mee}.
-So far I do not have independent evidence for placing gender features between features of pronominal strength and case, and I leave this for future research.
-
-So far I discussed \tit{-mee} is a postposition, which follows \tit{'r} and is stored with a unary bottom.
-\tit{Met}, on the other hand, is a preposition, it precedes \tit{'t}, so it should be stored with a binary bottom.
-The highest case feature \tit{'t} can realize is \tsc{f3}, so the preposition realizes \tsc{f4}.
+Throughout the paper I have been mentioning that \tit{mee} cannot combine with animate pronouns and full noun phrases.
+This is not surprising with a lexical entry as the one in \ref{ex:entrymee}.
+Animate pronouns contain, in addition the features of inanimate pronouns, gender features.
+I assume that gender features are situated between pronominal features (so Σ) and case features.
+The syntactic structure of an animate instrumental contains gender features that the lexical entry for \tit{mee} does not contain, so \tit{mee} cannot be inserted and a different lexical entry will be chosen.
+Full nouns phrases do not take features related to pronominal strength.
+According to the Superset Principle, a lexical tree can match a syntactic tree with a subpart of the features, but a tree can only shrink from the top, so \tit{mee} will always realize the feature Σ.
+
+I just showed that \tit{mee} is a postposition that follows \tit{r}.
+This follows from the idea that its lexical tree has a unary bottom.
+\tit{Met} is a preposition, meaning it precedes \tit{t}, and it should be stored with a binary bottom.
+The highest case feature that \tit{t} can realize is \tsc{k3}, so the preposition must correspond to the feature that remains: \tsc{k4}.
+However, since the lexical tree should be stored with a binary bottom, the preposition must correspond to an additional feature.
+This cannot be just any feature, but it needs to be the feature that precedes it in the functional sequence, which is \tsc{f}3.\footnote{
+There are different proposals regarding this overlap of features.
+\citet{caha2019competition} argues that there can only be a single feature overlap, \citet{starke2018} claims that the overlap can be more than one feature, and according to \citet{de2018}, there cannot be
+any overlap at all. The proposal in this paper is compatible with the first two ideas.}
 I give the lexical entry for \tit{met} in \ref{ex:entrymet}.
@@
 [\tsc{insP}
-    [\tsc{f4},roof]
+    [\tsc{k4}]
+    [\tsc{k3}]
 ]
@@
 
-In the next section I put all features back together in a derivation and I show how \tit{waar-mee} `with what' and not \tit{met wat} `with what' surfaces when all features form a constituent.
+In the next section I put all features back together in a derivation and I show how \tit{waar mee} `with what' and not \tit{met wat} `with what' surfaces when all features form a constituent.
 
@@
 
-Before I show that \tit{waar-mee} `with what' is used when all features form a proper constituent, I need to make some assumptions about the spellout procedure in Nanosyntax explicit.
+Before I show that \tit{waar mee} `with what' is used when all features form a proper constituent, I need to make some assumptions about the spellout procedure in Nanosyntax explicit.
 Spellout happens in a cyclic derivation, following a spellout algorithm \citep{starke2018}.
@@
  \a. Spell out FP.
- \b. If (a) fails, attempt movement of the spec of the complement of \tsc{f}, and retry (a).
+ \b. If (a) fails, attempt movement of the specifier of the complement of \tsc{f}, and retry (a).
  \b. If (b) fails, move the complement of \tsc{f}, and retry (a).
@@
 If the spellout procedure in \ref{ex:spellout} fails, backtracking takes place.
-This is the operation that leads from the suppletive nominative, accusative and dative \tit{'t} to the base form \tit{'r}.
+This, in my analysis, is the operation that ultimately leads from the suppletive nominative, accusative and dative form \tit{t} to the base form \tit{r}.
 
 \ex. Backtracking \citep{starke2018}:\\
-When spellout fails, go back to the previous cycle, and try the next option for that cycle.\label{ex:backtracking}
+When spellout fails, go back tothe previous cycle, and try the next option for that cycle.\label{ex:backtracking}
 
@@
 With this theoretical background in place, I can turn to the derivation.
-I first show how \tit{'rmee} `with it' is constructed.
-I leave out \tit{w} and \tit{a} to not unnecessarily complicate the story.\footnote{I assume that the \tsc{wP} and \tsc{deixP} appear lower in the structure than the case features, so the functional sequence is as given in \ref{ex:fseq}.
-
-\ex. [ [ [ [ [ [ [ \tsc{thing} ] \tsc{deix} ] W ] \tsc{f1} ] \tsc{f2} ] \tsc{f3} ] \tsc{f4} ]\label{ex:fseq}
+I first show how \tit{r mee} `with it' is constructed.
+I leave out \tit{w} and \tit{a(a)} in order to not unnecessarily complicate the story.\footnote{I assume that the \tsc{wP} and \tsc{deixP} appear lower in the structure than the case features, so the functional sequence is as given in \ref{ex:fseq}.
+
+\ex. [ [ [ [ [ [ [ \tsc{thing} ] \tsc{deix} ] W ] \tsc{k1} ] \tsc{k2} ] \tsc{k3} ] \tsc{k4} ]\label{ex:fseq}
 \z.
@@
 \ref{ex:entryt} still is a candidate, because it contains all features in \ref{ex:thingf1}.
-The spellout is overridden and the structure is realized as \tit{'t}.
-
-\ex. \begin{forest} boom
-[ΣP
-   [Σ]
-   [\tsc{thingP}
-       [\tsc{thing}, roof]
-   ]
-]
-{\draw (.east) node[right]{⇒ \tit{'t}}; }
+The spellout is overridden and the structure is realized as \tit{t}.
+
+\ex. \begin{forest} boom
+[ΣP
+   [Σ]
+   [\tsc{thingP}
+       [\tsc{thing}, roof]
+   ]
+]
+{\draw (.east) node[right]{⇒ \tit{t}}; }
 \end{forest}\label{ex:thingf1}
 
-Then \tsc{f1} is merged. This structure can still be realized by \tit{'t}.
-
-\ex. \begin{forest} boom
-[\tsc{nomP}
-   [\tsc{f1}]
-   [ΣP
-       [Σ]
-       [\tsc{thingP}
-           [\tsc{thing}, roof]
-       ]
-   ]
-]
-{\draw (.east) node[right]{⇒ \tit{'t}}; }
+Then \tsc{k1} is merged. This structure can still be realized by \tit{t}.
+
+\ex. \begin{forest} boom
+[\tsc{nomP}
+   [\tsc{k1}]
+   [ΣP
+       [Σ]
+       [\tsc{thingP}
+           [\tsc{thing}, roof]
+       ]
+   ]
+]
+{\draw (.east) node[right]{⇒ \tit{t}}; }
 \end{forest}
 
-The same holds for the next two steps in which \tsc{f2} and \tsc{f3} are merged: the structure can still be spelled out as \tit{'t}.
+The same holds for the next two steps in which \tsc{k2} and \tsc{k3} are merged: the structure can still be spelled out as \tit{t} due to the Superset Principle.
 
@@
 [\tsc{datP}
-    [\tsc{f3}]
+    [\tsc{k3}]
     [\tsc{accP}
-       [\tsc{f2}]
-       [\tsc{nomP}
-           [\tsc{f1}]
-           [ΣP
-               [Σ]
-               [\tsc{thingP}
-                   [\tsc{thing}, roof]
-               ]
-           ]
-       ]
-    ]
-]
-{\draw (.east) node[right]{⇒ \tit{'t}}; }
+       [\tsc{k2}]
+       [\tsc{nomP}
+           [\tsc{k1}]
+           [ΣP
+               [Σ]
+               [\tsc{thingP}
+                   [\tsc{thing}, roof]
+               ]
+           ]
+       ]
+    ]
+]
+{\draw (.east) node[right]{⇒ \tit{t}}; }
 \end{forest}
 
-Then \tsc{f4} is merged, as shown in \ref{ex:f4no}.
-\ref{ex:entryt} can no longer spell out the structure, because it does not contain \tsc{f4}.
-There is also no other candidate to spell out the structure as it is.
+Then \tsc{k4} is merged, as shown in \ref{ex:f4no}.
+\ref{ex:entryt} can no longer spell out the structure, because it does not contain \tsc{k4}.
+There is no other candidate to spell out the structure as it is.
 
@@
 [\tsc{insP}
-    [\tsc{f4}]
+    [\tsc{k4}]
     [\tsc{datP}
-        [\tsc{f3}]
+        [\tsc{k3}]
         [\tsc{accP}
-           [\tsc{f2}]
-           [\tsc{nomP}
-               [\tsc{f1}]
+           [\tsc{k2}]
+           [\tsc{nomP}
+               [\tsc{k1}]
                [ΣP
@@
 
-According to the spellout algorithm in \ref{ex:spellout}, it should be attempted to move the spec of the complement of \tsc{f4}.
+According to the spellout algorithm in \ref{ex:spellout}, the next step is to move the specifier of the complement of \tsc{k4}.
 However, there is no specifier in \ref{ex:f4no}, so this does not apply.
 The second movement option is complement movement.
-The complement of \tsc{f4} moves to the specifier of \tsc{insP}, resulting in the structure in \ref{ex:f4comp}.
-The lexicon does not contain an entry with \tsc{insP} which contains only \tsc{f4}.\footnote{\tit{Met} `with' is not a candidate, because the syntactic structure has a unary bottom and the lexical structure has a binary bottom.}
+The complement of \tsc{k4} moves to the specifier of \tsc{insP}, resulting in the structure in \ref{ex:f4comp}.
+The lexicon does not contain an entry with \tsc{insP} which contains only \tsc{k4}.\footnote{\tit{Met} is not a candidate, because the syntactic structure has a unary bottom whereas the lexical structure of \tit{met} has a binary bottom.}
 
@@
     [\tsc{datP}
-        [\tsc{f3}]
+        [\tsc{k3}]
         [\tsc{accP}
-           [\tsc{f2}]
-           [\tsc{nomP}
-               [\tsc{f1}]
-               [ΣP
-                   [Σ]
-                   [\tsc{thingP}
-                       [\tsc{thing}, roof]
-                   ]
-               ]
-           ]
-        ]
-    ]
-    {\draw (.east) node[right]{⇒ \tit{'t}}; }
+           [\tsc{k2}]
+           [\tsc{nomP}
+               [\tsc{k1}]
+               [ΣP
+                   [Σ]
+                   [\tsc{thingP}
+                       [\tsc{thing}, roof]
+                   ]
+               ]
+           ]
+        ]
+    ]
+    {\draw (.east) node[right]{⇒ \tit{t}}; }
     [\tsc{insP}
-        [\tsc{f4}]
+        [\tsc{k4}]
     ]
@@
 This means that the derivation goes back to the previous cycle, and the next option for that cycle is tried.
-In this case, the previous cycle is the one in which \tsc{f3} is merged.
+In this case, the previous cycle is the one in which \tsc{k3} is merged.
 The next option for that cycle is spec-to-spec movement.
@@
 The option after that is complement movement, shown in \ref{ex:f3comp}.
-However, there is no match in the lexicon for an \tsc{datP} that contains only \tsc{f3}.
+However, there is no match in the lexicon for a \tsc{datP} that contains only \tsc{k3}.
 
@@
     [\tsc{accP}
-       [\tsc{f2}]
-       [\tsc{nomP}
-           [\tsc{f1}]
-           [ΣP
-               [Σ]
-               [\tsc{thingP}
-                   [\tsc{thing}, roof]
-               ]
-           ]
-       ]
-    ]
-    {\draw (.east) node[right]{⇒ \tit{'t}}; }
+       [\tsc{k2}]
+       [\tsc{nomP}
+           [\tsc{k1}]
+           [ΣP
+               [Σ]
+               [\tsc{thingP}
+                   [\tsc{thing}, roof]
+               ]
+           ]
+       ]
+    ]
+    {\draw (.east) node[right]{⇒ \tit{t}}; }
     [\tsc{datP}
-        [\tsc{f3}]
+        [\tsc{k3}]
     ]
@@
 
-This means that backtracking proceeds further, into the cycle in which \tsc{f2} was merged.
-Again, spec-to-spec movement does not apply because there is no specifier, and complement movement can be tried, but there is no fitting lexical entry available.
-The same holds for the cycle in which \tsc{f1} is merged.
+This means that backtracking proceeds further, into the cycle in which \tsc{k2} was merged.
+Again, spec-to-spec movement does not apply because there is no specifier, and complement movement can be tried, but there is no appropriate lexical entry available for the remaining structure.
+The same holds for the cycle in which \tsc{k1} is merged.
 
 The situation changes when the derivation comes to the cycle in which Σ was merged.
-At this stage, \tsc{thing} was realized as \tit{'r}.
-Again there was no specifier, spec-to-spec movement does not apply.
-However, complement movement provides a structure that is a match for the lexical entry in \ref{ex:entrymee}: \tit{-mee}.\footnote{This picture resembles the proposal of \citep{abels2003diss} in that not the whole complement of P is moved but only a part is subextracted.
-The current analysis differs in that the movement is not syntactically driven but by spellout.}
-
-\ex. \begin{forest} boom
-[ΣP
-   [\tsc{thingP}
-       [\tsc{thing}, roof]
-   ]
-   {\draw (.east) node[right]{⇒ \tit{'r}}; }
-   [ΣP
-       [Σ]
-   ]
-   {\draw (.east) node[right]{⇒ \tit{-mee}}; }
+At this stage, \tsc{thing} was realized as \tit{r}.
+Again there was no specifier, so spec-to-spec movement does not apply.
+However, complement movement provides a structure that is a match for the lexical entry in \ref{ex:entrymee}: \tit{mee}.\footnote{This picture resembles the proposal of \citep{abels2003diss} in that not the whole complement of P is moved but only a part is subextracted.
+The current analysis differs in that the movement is not syntactically driven but spellout-driven.
+
+%not too local? anti-locality is avoided becuase..
+}
+
+\ex. \begin{forest} boom
+[ΣP
+   [\tsc{thingP}
+       [\tsc{thing}, roof]
+   ]
+   {\draw (.east) node[right]{⇒ \tit{r}}; }
+   [ΣP
+       [Σ]
+   ]
+   {\draw (.east) node[right]{⇒ \tit{mee}}; }
 ]
@@
 
-From this point on the previously unmerged features are merged again one by one. First, \tsc{f1} is merged again, shown in \ref{ex:f1again}. No match exists for this syntactic structure.
-
-\ex. \begin{forest} boom
-[\tsc{nomP}
-    [\tsc{f1}]
+From this point on the previously unmerged features are merged again one by one. First, \tsc{k1} is merged, shown in \ref{ex:f1again}. No match exists for this syntactic structure.
+
+\ex. \begin{forest} boom
+[\tsc{nomP}
+    [\tsc{k1}]
     [ΣP
@@
 
-Following the spellout algorithm, the next step is spec-to-spec movement. The result is shown in \ref{ex:f1spec}. In that configuration \tsc{f1} can be realized together with Σ as \tit{-mee}.
-
-\ex. \begin{forest} boom
-[\tsc{nomP}
-   [\tsc{thingP}
-       [\tsc{thing}, roof]
-   ]
-   {\draw (.east) node[right]{⇒ \tit{'r}}; }
-   [\tsc{nomP}
-       [\tsc{f1}]
-       [ΣP
-           [Σ]
-       ]
-   ]
-   {\draw (.east) node[right]{⇒ \tit{-mee}}; }
+Following the spellout algorithm, the next step is spec-to-spec movement. The result is shown in \ref{ex:f1spec}. \tsc{k1} can be spelled out together with Σ as \tit{mee}.
+
+\ex. \begin{forest} boom
+[\tsc{nomP}
+   [\tsc{thingP}
+       [\tsc{thing}, roof]
+   ]
+   {\draw (.east) node[right]{⇒ \tit{r}}; }
+   [\tsc{nomP}
+       [\tsc{k1}]
+       [ΣP
+           [Σ]
+       ]
+   ]
+   {\draw (.east) node[right]{⇒ \tit{mee}}; }
  ]
@@
 
-The same happens for \tsc{f2}, \tsc{f3} and \tsc{f4}.
-The features are merged one at a time, there is no spellout after merging the feature, but there is a spellout after spec-to-spec movement.
-I show the situation after \tsc{f4} is realized as  \ref{ex:spellout'rmee}.
+The same happens for \tsc{k2}, \tsc{k3} and \tsc{k4}.
+The features are merged one at a time, there is no spellout immediately after merging the feature, but there is a spellout after spec-to-spec movement.
+I show the situation after \tsc{k4} in \ref{ex:spelloutr mee}.
 
@@
     ]
-    {\draw (.east) node[right]{⇒ \tit{'r}}; }
+    {\draw (.east) node[right]{⇒ \tit{r}}; }
     [\tsc{insP}
-       [\tsc{f4}]
+       [\tsc{k4}]
        [\tsc{datP}
-           [\tsc{f3}]
+           [\tsc{k3}]
            [\tsc{accP}
-               [\tsc{f2}]
-               [\tsc{nomP}
-                   [\tsc{f1}]
-                   [ΣP
-                       [Σ]
-                   ]
-               ]
-           ]
-       ]
-    ]
-    {\draw (.east) node[right]{⇒ \tit{-mee}}; }
-]
-\end{forest}\label{ex:spellout'rmee}
-
-I skip over the details of how \tit{w} and \tit{a} end up in their positions.\footnote{I assume that \tsc{wP} and \tsc{deixP} are both complex specifiers that are created after \tsc{thing} is spelled out in \ref{ex:thingspellout}.
-After each instance of merge after that, backtracking takes place, the complex specifier is detached from the structure and the case features are spelled out together with \tsc{thing} or as the postposition -\tit{mee}.} The final result of the structure for \tit{waar-mee} `with what' look as in \ref{ex:spelloutwaar-mee}.
+               [\tsc{k2}]
+               [\tsc{nomP}
+                   [\tsc{k1}]
+                   [ΣP
+                       [Σ]
+                   ]
+               ]
+           ]
+       ]
+    ]
+    {\draw (.east) node[right]{⇒ \tit{mee}}; }
+]
+\end{forest}\label{ex:spelloutr mee}
+
+I skip over the details of how \tit{w} and \tit{a(a)} end up in their positions.\footnote{
+I assume that \tsc{wP} and \tsc{deixP} are both complex specifiers that are created after \tsc{thing} is spelled out in \ref{ex:thingspellout}.
+After each instance of merge after that, backtracking takes place, the complex specifiers are detached from the structure,and the new feature is merged in all workspaces.
+The new feature is successfully spelled out in the workspace that contains the feature \tsc{thing}, and the workspaces are merged back together.
+} The final result of the structure for \tit{waar mee} `with what' appears in \ref{ex:spelloutwaar mee}.
 
@@
         ]
-        {\draw (.east) node[right]{⇒ \tit{a}}; }
+        {\draw (.east) node[right]{⇒ \tit{a(a)}}; }
         [\tsc{insP}
@@
             ]
-            {\draw (.east) node[right]{⇒ \tit{'r}}; }
+            {\draw (.east) node[right]{⇒ \tit{r}}; }
             [\tsc{insP}
-               [\tsc{f4}]
+               [\tsc{k4}]
                [\tsc{datP}
-                   [\tsc{f3}]
+                   [\tsc{k3}]
                    [\tsc{accP}
-                       [\tsc{f2}]
-                       [\tsc{nomP}
-                           [\tsc{f1}]
-                           [ΣP
-                               [Σ]
-                           ]
-                       ]
-                   ]
-               ]
-            ]
-            {\draw (.east) node[right]{⇒ \tit{-mee}}; }
-        ]
-    ]
-]
-\end{forest}\label{ex:spelloutwaar-mee}
-
-A consequence of analyzing \tit{-mee} `with' as a postposition is that \tit{'r} and \tit{-mee} always form a constituent to the exclusion of \tit{w} and \tit{a}.
-At first sight this seems problematic, because it is possible for \tit{waar} `where' to \tit{-mee} `with'.
+                       [\tsc{k2}]
+                       [\tsc{nomP}
+                           [\tsc{k1}]
+                           [ΣP
+                               [Σ]
+                           ]
+                       ]
+                   ]
+               ]
+            ]
+            {\draw (.east) node[right]{⇒ \tit{mee}}; }
+        ]
+    ]
+]
+\end{forest}\label{ex:spelloutwaar mee}
+
+A consequence of analyzing \tit{mee} `with' as a postposition is that \tit{r} and \tit{mee} always form a constituent to the exclusion of \tit{w} and \tit{a(a)}.
+At first sight this seems problematic, because it is possible for \tit{waar} `where' to not directly precede \tit{mee} `with'.
 I repeat the relevant example in \ref{ex:meestranded}.
@@
 
-There is no constituent in \ref{ex:spelloutwaar-mee} that contains \tit{waar} but not \tit{-mee}, so it is not possible to move \tit{waar} from \ref{ex:spelloutwaar-mee} and strand \tit{mee} in the process.
-To resolve this situation I follow \citet{noonan2017dutch} in assuming that the phrase containing the adposition (\tit{-mee}) can syntactically move to a position higher in the structure.
-Evidence that \tit{mee} `with' has moved comes from the ungrammaticality of \ref{ex:meeend}.
-This shows that \tit{mee} `with' cannot be stranded in its base position (see also \ref{ex:const3stage}).
-
-\exg. *Ik heb gekocht waar jij schildert mee.\\
- I have bought waar you paint with\\
- `I bought what you are painting with.'\label{ex:meeend}
-
-The movement of the adposition has the typical distribution of that of verbal particles (cf.
-\citealt{riemsdijk1978,noonan2017dutch}.
+There is no constituent in \ref{ex:spelloutwaar mee} that contains \tit{waar} but not \tit{mee}, so it is not possible to move \tit{waar} from \ref{ex:spelloutwaar mee} and strand \tit{mee} in the process.
+To resolve this situation I follow \citet{noonan2017dutch} in assuming that the phrase containing the adposition (\tit{mee}) can syntactically move to a position higher in the structure.
+
+The movement of the adposition has a distribution typical of verbal particles (cf.
+\citealt{riemsdijk1978,noonan2017dutch}).
 The trigger for the movement of \tit{mee} could be the feature Σ (which is contained in \tit{mee} `with`), associated with weak pronouns.
 Allowing \tit{mee} to subextract from the \tsc{w}P resolves the issue.
-With \tit{-mee} having moved out, the \tsc{wP} only contains features that are realized as \tit{waar}, and it moves to the left edge of the clause, resulting in the surface order in \ref{ex:meestranded}.
-
-So far I showed how \tit{waar-mee} `with what' is derived if all syntactic features form a constituent.
-Next I address how \tit{waar-mee} `with what' is blocked and \tit{met wat} `with what' appears when the features do not form a proper constituent is derived.
-An example of a situation in which all features do not form a constituent is given in \ref{ex:noconst}.
+With \tit{mee} having moved out, the remnant \tsc{wP} only contains features that are realized as \tit{waar}, and it moves to the left edge of the clause, resulting in the surface order in \ref{ex:meestranded}.
+
+So far I showed how \tit{waar mee} `with what' is derived if all syntactic features form a constituent.
+Next I address how \tit{waar mee} `with what' is blocked and \tit{met wat} `with what' appears when the features do not form a proper constituent.
+An example of a situation in which the features do not form a constituent is given in \ref{ex:noconst}.
 
@@
 
-I start at the point at which \tit{wat} `what' is part of a syntactic structure with the rest of a relative clause as a sister.
-Even though \tsc{f3} is not part of the embedded clause, I already added it to the structure.
-While it is unclear why, syncretic forms behave differently in that they seem to resolve case conflicts in free relatives and related phenomena (cf.
-\citealt{groos1981,pullum1986,ingria1990}).
-I give the syntactic structure from which I start in \ref{ex:metwatst}.
+\ref{ex:metwatst} shows the syntactic structure of the relative clause \tit{wat je hebt gekocht} `what you bought' in \ref{ex:noconst}. \tit{Wat} `what' is the element in the specifier of the CP.
 
@@
             ]
-            {\draw (.east) node[right]{⇒ \tit{a}}; }
-            [\tsc{datP}
-                [\tsc{f3}]
+            {\draw (.east) node[right]{⇒ \tit{a(a)}}; }
             [\tsc{accP}
-                   [\tsc{f2}]
-                   [\tsc{nomP}
-                       [\tsc{f1}]
-                       [ΣP
-                           [Σ]
-                           [\tsc{thingP}
-                               [\tsc{thing}, roof]
-                           ]
-                       ]
-                   ]
-                ]
-            ]
-            {\draw (.east) node[right]{⇒ \tit{'t}}; }
+               [\tsc{k2}]
+               [\tsc{nomP}
+                   [\tsc{k1}]
+                   [ΣP
+                       [Σ]
+                       [\tsc{thingP}
+                           [\tsc{thing}, roof]
+                       ]
+                   ]
+                ]
+            ]
+            {\draw (.east) node[right]{⇒ \tit{t}}; }
         ]
@@
 
-At this point \tsc{f4} is merged, as shown in \ref{ex:f4metwat}.
-Because of the presence of the CP, there is no possibility for \tsc{f4} to be spelled out, even after the regular movements and backtracking.
+At this point \tsc{k4} is merged, as shown in \ref{ex:f4metwat}.
+Because of the presence of the CP, backtracking cannot take place and the additional features cannot be spelled out as the postposition \tit{mee}.
+\footnote{
+Here I assume that backtracking is prohibited once syntactic movement has taken place (in this case \tsc{wh}-movement of the \tsc{wh}-element to the specCP position).
+I am not aware of any research about the interaction between backtracking and syntactic movement.
+Future research on the interaction between the two will show whether my assumption holds.
+}
 
@@
 [\tsc{insP}
-    [\tsc{f4}]
+    [\tsc{k4}]
     [CP
@@
                 ]
-                {\draw (.east) node[right]{⇒ \tit{a}}; }
+                {\draw (.east) node[right]{⇒ \tit{a(a)}}; }
                 [\tsc{accP}
-                   [\tsc{f2}]
-                   [\tsc{nomP}
-                       [\tsc{f1}]
-                       [ΣP
-                           [Σ]
-                           [\tsc{thingP}
-                               [\tsc{thing}, roof]
-                           ]
-                       ]
-                   ]
-                ]
-                {\draw (.east) node[right]{⇒ \tit{'t}}; }
+                   [\tsc{k2}]
+                   [\tsc{nomP}
+                       [\tsc{k1}]
+                       [ΣP
+                           [Σ]
+                           [\tsc{thingP}
+                               [\tsc{thing}, roof]
+                           ]
+                       ]
+                   ]
+                ]
+                {\draw (.east) node[right]{⇒ \tit{t}}; }
             ]
@@
 
-The last resort possibility to spell out features is set in motion: a complex specifier is created, as described in \ref{ex:specformation}. This is illustrated in \ref{ex:metmetwat}.
+Instead, the last resort possibility to spell out features is set in motion: a complex specifier is created, as described in \ref{ex:specformation}.
+This is illustrated in \ref{ex:metmetwat}.\footnote{
+I added the feature \tsc{k3} that creates a \tsc{dat}P in the relative clause.
+It is unclear why, but syncretic forms behave differently in that they seem to resolve case conflicts in free relatives and related phenomena (cf.
+\citealt{groos1981,pullum1986,ingria1990}).
+It seems that the syntax only sees the phonological form (in this case \tit{t}) and it is irrelevant whether the feature \tsc{k3} was already present in the relative clause.
+Syntactically, we expect the feature to be there because the feature \tsc{k4} can only be merged if the feature \tsc{k3} has been.
+}
 
@@
     [\tsc{insP}
-        [\tsc{f4},roof]
+        [\tsc{k4}]
+        [\tsc{k3}]
     ]
@@
                 ]
-                {\draw (.east) node[right]{⇒ \tit{a}}; }
+                {\draw (.east) node[right]{⇒ \tit{a(a)}}; }
+                [\tsc{dat}P
+                    [\tsc{k3}]
                     [\tsc{accP}
-                   [\tsc{f2}]
-                   [\tsc{nomP}
-                       [\tsc{f1}]
-                       [ΣP
-                           [Σ]
-                           [\tsc{thingP}
-                               [\tsc{thing}, roof]
-                           ]
-                       ]
-                   ]
-                ]
-                {\draw (.east) node[right]{⇒ \tit{'t}}; }
+                       [\tsc{k2}]
+                       [\tsc{nomP}
+                           [\tsc{k1}]
+                           [ΣP
+                               [Σ]
+                               [\tsc{thingP}
+                                   [\tsc{thing}, roof]
+                               ]
+                           ]
+                        ]
+                    ]
+                ]
+                {\draw (.east) node[right]{⇒ \tit{t}}; }
             ]
@@
 
-This section showed how the instrumental inanimate relative pronoun is realized as \tit{waar-mee} `with what' when all relevant features form a constituent, and how \tit{met wat} `with what' appears when they do not.
+This section showed how the instrumental inanimate relative pronoun is realized as \tit{waar mee} `with what' when all relevant features form a constituent, and how \tit{met wat} `with what' appears when they do not.
 
@@
 
-In this paper, I discussed the instrumental \tsc{r}-pronoun and postposition \tit{waar-mee} `with what' in Dutch.
+In this paper, I discussed the instrumental \tsc{r}-pronoun plus postposition \tit{waar mee} `with what' in Dutch.
 The main intuition is that this form appears when features of an instrumental inanimate object form a proper constituent.
 The form cannot appear, and \tit{met wat} `with what` surfaces instead, when all relevant features do not form a proper constituent.
-The described pattern follows from a core assumption in Nanosyntax: phrasal spellout spells out constituents \citep{starke2009}.
-
-Under this analysis, there is no need for a filter that rules out a combination of a preposition and an inanimate pronoun.
-As long as the relevant features form a proper constituent, the spellout algorithm ensures the \tsc{r}-pronoun and postposition takes precedence over the other form.
+The described pattern follows from a core assumption in Nanosyntax: only constituents can be targeted for spellout \citep{starke2009}.
+
+Under this analysis, there is no need for a filter that rules out a combination of a preposition plus an inanimate pronoun.
+As long as the relevant features form a proper constituent, the spellout algorithm ensures that the \tsc{r}-pronoun plus postposition takes precedence over the preposition plus inanimate pronoun.
 The fact that locatives are syncretic with \tsc{r}-pronouns is not a coincidence.
-The lexicon contains a single entry for a locative, which is the one used for \tsc{r}-pronouns as well.
+The lexicon contains a single entry that can spell out the features that refer to a locative and features that refer to a thing.
 The change in placement of the adposition is a consequence of spellout too.
-\tit{Mee} `with' is a postposition and is stored differently from the preposition \tit{met} `with', which leads to the correct placement with different constituency.
+\tit{Mee} `with' is a postposition and is stored differently from the preposition \tit{met} `with', which leads them to either appear before or after the previously spelled out element.
 The fact that \tit{met} `with' and \tit{mee} `with' differ phonologically can also be captured by storing them as two separate lexical entries.
 
-In the remainder of this section I discuss how this analysis can be extended to other adpositions in Dutch.
-Giving \tit{met} `with' and \tit{-mee} `with' two distinct lexical entries has as a consequence that the phonological overlap between them seems like a coincidence.
-This can be questioned, because there is only one more preposition that changes form when it appears postpositionally.
-This preposition is \tit{tot} `to', and it changes into \tit{toe} as a postposition.
-It has in common with \tit{met} `with' that it is the only preposition in Dutch that has the phonological structure CVt.
+Giving \tit{met} `with' and \tit{mee} `with' two distinct lexical entries has as a consequence that the phonological overlap between them seems like a coincidence.
+This can be questioned, because there is only one other preposition that changes form when it appears postpositionally.
+This preposition is \tit{tot} `to', which changes to \tit{toe} as a postposition.
+It has in common with \tit{met} `with' that it is the only preposition in Dutch with the phonological structure CVt.
 For now I take the phonological resemblance to be a relic from the past without having any influence on the synchronic data.
-
 In all other cases the adposition does not change form when it combines with an \tsc{r}-pronoun, e.g.
 \tit{in} `in'.
-If this proposal is on the right track, elements as \tit{in} can be used as either a preposition or as a postposition.
-The lexical entry should then be usable as pre-element and as post-element, so it needs to have a binary bottom and a unary foot simultaneously.
-The lexical entry in \ref{ex:presuf} would be a candidate for such an element.
-YP can be inserted as a post-element, and XP can be inserted via the Superset Principle as a pre-element.
-
-\ex. \begin{forest} boom
-[YP
-    [XP
-        [X,roof]
-    ]
-    [YP
-        [Y]
-    ]
-]
-{\draw (.east) node[right]{⇔ \tit{in}}; }
-\end{forest}\label{ex:presuf}
-
-I leave it to future research to investigate such a proposal.
+This raises the question of whether the preposition \tit{in} `in' and the postposition \tit{in} `in' are stored as separate lexical entries in the lexicon or whether they refer to a single entry.
+Connected to this are the verbal particles that appear in dutch.
+They have the form of the postposition and not of the preposition: it is \tit{mee-lopen} `walk along' and not *\tit{met-lopen} `walk along'.
+Ideally, an analysis derives all these observations.
+For now, I leave this for future research.
 
@@
 
+\section*{Acknowledgements}
+
+Thanks to Pavel, two anonymous reviewers, to the organizers of PlaCiG, nanolab, especially Pavel, Guido, Karen, Michal and Hagen Blix.
+
 \end{document}

### 2021-11-17 paper.tex
sent revised version

@@
 
-\title{The \tsc{r}-pronoun plus postposition \tit{waar mee} in Dutch}
+\title{The \tsc{r}-pronoun and postposition \tit{waar mee} in Dutch}
 \author{Fenna Bergsma\\Goethe-Universität Frankfurt}
@@
 Dutch has the preposition \tit{met} `with' that expresses the instrumental.
-In \ref{ex:metdp}, \tit{met} `with' is combined with a full DP.
+In \ref{ex:metdp}, \tit{met} `with' is combined with a full noun phrase.
 The inanimate pronoun in Dutch is \tit{t} `it'.\footnote{The longer form that is mostly used in writing is \tit{het} `it'.
@@
 \tit{Met} `with' and \tit{t} `it' do not appear together, as illustrated in \ref{ex:neemett}.
-Instead, Dutch uses the \tsc{r}-pronoun \tit{r} `there' and the postposition \tit{mee} `with', as shown in \ref{ex:jar mee}.\footnote{The \tsc{r}-pronoun \tit{r} in \ref{ex:jar mee} can be written as \tit{er}, \tit{der} and \tit{r} and pronounced as respectively /ɛr/, /dər/ or /ər/.
+Instead, Dutch uses the \tsc{r}-pronoun \tit{r} `there' and the postposition \tit{mee} `with', as shown in \ref{ex:jarmee}.\footnote{The \tsc{r}-pronoun \tit{r} in \ref{ex:jarmee} can be written as \tit{er}, \tit{der} and \tit{r} and pronounced as respectively /ɛr/, /dər/ or /ər/.
 There is no clear meaning difference between these forms that is relevant for the discussion in this paper
-(see \citet{wesseling2018} for discussion).
-In my examples I use \tit{r}, but the other forms fit just as well.}$^,$\footnote{In this paper I do not make any claims about the distinction between prefixes and prepositions, or suffixes and postpositions.}
+(see \citealt{wesseling2018} for discussion).
+In my examples I use \tit{r}, but the other forms fit just as well.}$^,$\footnote{In this paper I do not make a distinction between prefixes and prepositions, or between suffixes and postpositions.}
 
@@
  I paint there with\\
- `I am painting with it.'\label{ex:jar mee}
+ `I am painting with it.'\label{ex:jarmee}
 
 \tsc{R}-pronouns are nominal elements that are syncretic with locative pronouns, which in Dutch means they contain the morpheme \tit{r} \citep[cf.][]{riemsdijk1978,koopman1994}.
-The adpositions they combine with obligatorily follow the \tsc{r}-pronoun (compare \ref{ex:jar mee} and \ref{ex:neemeer}).
-Notice also that the preposition \tit{met} `with' differs phonologically from the postposition \tit{mee} `with` (see \ref{ex:metdp} and \ref{ex:jar mee}), although they express the same meaning.
+The adpositions they combine with obligatorily follow the \tsc{r}-pronoun (compare \ref{ex:jarmee} and \ref{ex:neemeer}).
+Notice also that the preposition \tit{met} `with' differs phonologically from the postposition \tit{mee} `with` (see \ref{ex:metdp} and \ref{ex:jarmee}), although they express the same meaning.
 
@@
 
-The main question I address in this paper is how to correctly rule out \tit{met t} `with it' in \ref{ex:neemett}, and let the \tsc{r}-pronoun plus postposition \tit{r mee} `with it' in \ref{ex:jar mee} appear.
+The main question I address in this paper is how to correctly rule out \tit{met t} `with it' in \ref{ex:neemett}, and let the \tsc{r}-pronoun plus postposition \tit{r mee} `with it' in \ref{ex:jarmee} appear.
 I argue that \tsc{r}-pronouns are not something special, but a consequence of regular spellout mechanisms.
-Just as \citet{riemsdijk1978} I analyze the \tsc{r}-pronoun plus postposition as a type of allomorph of the preposition plus pronoun.
+Just as \citet{riemsdijk1978}, I analyze the \tsc{r}-pronoun plus postposition as a type of allomorph of the preposition plus pronoun.
 The crucial difference in the current approach is that spellout - not the stipulation of a filter - rules out the ungrammaticality of the preposition plus inanimate pronoun.
@@
 The second reason for focusing on this particular \tsc{r}-pronoun plus postposition is the form of the adposition.
-The preposition \tit{met} `with' does not only turn into a postposition, but it also changes into \tit{mee} `with' when it is combined with an \tsc{r}-pronoun.
+The preposition \tit{met} does not only turn into a postposition, but it also changes into \tit{mee} when it is combined with an \tsc{r}-pronoun.
 This last observation has so far remained unexplained in the literature on \tsc{r}-pronouns (cf.
-\citealt{koopman1994,riemsdijk1978,noonan2017dutch,abels2003diss}).
-
-The main generalization is that the instrumental \tsc{r}-pronoun plus postposition \tit{r mee} `with it' takes precedence over the instrumental preposition plus inanimate pronoun \tit{met t} `with it'.
+\citealt{riemsdijk1978,koopman1994,abels2003diss,noonan2017dutch}).
+
+The main generalization is that the instrumental \tsc{r}-pronoun plus postposition \tit{r mee} `with it' by default takes precedence over the instrumental preposition plus inanimate pronoun \tit{met t} `with it'.
 I show that a single requirement has to be satisfied: the instrumental object needs to form a proper constituent i.e.
 a constituent to the exclusion of other features.
-When this condition is not met, the preposition plus inanimate pronoun appear.
-This can straightforwardly follow in a system in which spellout targets phrasal constituents: Nanosyntax \citep{starke2009}.
-I work this idea out capturing the following three observations.
+When this condition is not met, the preposition plus inanimate pronoun appear after all.
+This follows straightforwardly in a system in which spellout targets phrasal constituents: Nanosyntax \citep{starke2009}.
+I work out this idea capturing the following three observations.
 First, \tsc{r}-pronouns are syncretic with locatives.
@@
 In Section \ref{sec:distribution} I show that \tsc{r}-pronouns plus postpositions and prepositions plus inanimate pronouns are in complementary distribution, depending on whether all features form a proper constituent or not.
-Besides discussing \tit{r mee} `with it' and \tit{met t} `with it', I introduce the \tit{wh}-pronouns \tit{waarmee} `with what' and \tit{met wat} `with what'.
-For these forms it is intuitive to see that proper constituency is the critical condition.
-In Section \ref{sec:takingapart} I decompose \tit{waar mee} `with what' and \tit{met wat} `with what', and I link the morphemes they consist of to specific syntactic structures.
-Section \ref{sec:derivation} shows in a derivation how \tit{waar mee} `with what' is derived when all features form a proper constituent.
-I also show how \tit{met wat} `with what' appears when the features do not form a proper constituent.
+Besides discussing \tit{r mee} `with it' and \tit{met t} `with it', I introduce the \tsc{wh}-pronouns \tit{waarmee} `with what' and \tit{met wat} `with what'.
+Examples with these forms allow me illustrate that proper constituency is the critical condition.
+In Section \ref{sec:takingapart} I decompose \tit{waar mee} and \tit{met wat}, and I link the morphemes they consist of to specific syntactic structures.
+Section \ref{sec:derivation} shows the derivation of \tit{waar mee} when all relevant features form a proper constituent and the derivation of \tit{met wat} when the features do not.
 Section \ref{sec:conclusion} concludes.
-All examples in this paper are from spoken Dutch, unless indicated otherwise.
-Examples without a reference are constructed and have been verified by native speakers.
+
+All examples in this paper are from spoken Dutch, unless indicated otherwise. Examples without a reference are constructed and have been verified by native speakers.
 
@@
 that all features form a constituent to the exclusion of any other features.
-I start the section by showing that \tit{r mee} `with it' and \tit{waar mee} `with what` are the default, which is to say that they normally appear and \tit{met t} `with it' and \tit{met wat} `with what' do not.
-There is one exception, in which \tit{met wat} `with what` has to be used and \tit{waar mee} `with what` cannot, which is when case the relevant features do not form a proper constituent.
+I start the section by showing that \tit{r mee} `with it' and \tit{waar mee} `with what` are the default, which is to say that they normally appear (and \tit{met t} `with it' and \tit{met wat} `with what' do not).
+There is one exception, in which \tit{met wat} `with what` has to be used (and \tit{waar mee} `with what` cannot), which is when the relevant features do not form a proper constituent.
 
@@
 \tit{Met} is not the only preposition this occurs with.
-For example, \tit{op} `on' and \tit{in} `in' cannot combine with the inanimate pronoun \tit{t} either, and the \tsc{r}-pronoun plus postposition are obligatorily used instead.
+For example, \tit{op} `on' and \tit{in} `in' cannot combine with the inanimate pronoun \tit{t} `it' either, and the \tsc{r}-pronoun plus postposition are obligatorily used instead.
 
@@
 \tit{Wat} `what' can function as the object of a verb (see \ref{ex:wat}), but not as the object of a preposition \ref{ex:metwat}.
-The \tsc{r}-pronoun plus postposition \tit{waar mee} `with what' appears, as shown in \ref{ex:waar mee}.\footnote{The sentence in \ref{ex:metwat} is unacceptable with neutral intonation.
+The \tsc{r}-pronoun plus postposition \tit{waar mee} `with what' appears instead, as shown in \ref{ex:waarmee}.\footnote{The sentence in \ref{ex:metwat} is unacceptable with neutral intonation.
 It becomes acceptable if \tit{wat} `what' is stressed, for example in a context in which the speaker is highly surprised about the choice of the object the hearer is painting with.}
@@
  where with paint you\\
- `What are you painting with?'\label{ex:waar mee}
+ `What are you painting with?'\label{ex:waarmee}
 
@@
 The use of \tit{met wat} `with what' is ungrammatical in both contexts, and \tit{waar mee} `with what' is used instead.\footnote{
-In this example, \tit{waar} `where' and \tit{mee} `with' are the two left-most elements of the relative clause.
-It is also possible for \tit{mee} `with' to appear more to the right in the clause and for \tit{waar} to appear as the left-most element on its own.
+In this example, \tit{waar} and \tit{mee} are the two left-most elements of the relative clause.
+It is also possible for \tit{mee} to appear more to the right in the clause and for \tit{waar} to appear as the left-most element on its own.
 
@@
 
-I return to this variant in Section \ref{sec:derivation}.
+I return to this variant in Section \ref{sec:waarmee}.
 }
@@
 
-In sum, the inanimate pronouns \tit{t} `it' and \tit{wat} `what' do not combine with prepositions. They are substituted by, respectively, the \tsc{r}-pronouns \tit{r} `there' and \tit{waar} `where'.
+In sum, the inanimate pronouns \tit{t} `it' and \tit{wat} `what' do not combine with prepositions.
+They are substituted by the \tsc{r}-pronouns \tit{r} `there' and \tit{waar} `where' and combine with postpositions.
 
@@
 
-A mismatching free relative is a free relative construction in which the two predicates (the one in the main clause and the one in the relative clause) combine with two different cases.
+A mismatching free relative is a free relative construction in which the two predicates (the one in the main clause and the one in the relative clause) require arguments with different cases.
 In other words, the case requirements of the two clauses do not match.
@@
 Table \ref{tbl:distribution} summarizes the pattern.
-When the main clause predicate combines with an accusative and the relative clause predicate with an instrumental, \tit{waar mee} `with what' is grammatical and \tit{met wat} `with what' is ungrammatical.
-When the main clause predicate combines with an instrumental and the relative clause predicate with an accusative, \tit{waar mee} `with what' is ungrammatical and \tit{met wat} `with what' appears instead.
+When the main clause predicate combines with an accusative and the relative clause predicate with an instrumental, \tit{waar mee} is grammatical and \tit{met wat} is ungrammatical.
+When the main clause predicate combines with an instrumental and the relative clause predicate with an accusative, \tit{waar mee} is ungrammatical and \tit{met wat} appears instead.
 
@@
 
-Below I repeat the examples with instrumental objects discussed in this paper so far.
-I placed square brackets around the relative clauses in \ref{ex:const3} and \ref{ex:const4}.
+Below I repeat the examples with instrumental objects discussed in this paper so far, except for the mismatching free relatives.
+I place square brackets around the relative clauses in \ref{ex:const3} and \ref{ex:const4}.
 In each of these examples the instrumental object forms a proper constituent at a certain point in the derivation.
@@
 The predicate \tit{schildert} `paints' combines in the relative clause with the instrumental object.
-I placed square brackets around the relative clauses in \ref{ex:mismatchwaarmee}.
+I place square brackets around the relative clauses in \ref{ex:mismatchwaarmee}.
 The instrumental object forms a proper constituent within the relative clause, and it can be realized as the \tsc{r}-pronoun plus postposition \tit{waar mee} `with what'.
@@
 The relative clause predicate \tit{gekocht} `bought' combines with an accusative object.
-I placed square brackets around the relative clauses in \ref{ex:mismatchmetwat}.
+I place square brackets around the relative clauses in \ref{ex:mismatchmetwat}.
 The accusative \tsc{wh}-object of a verb is always \tit{wat} `what', as I have shown earlier in \ref{ex:wat}.
@@
 \ref{ex:summaryconst} summarizes the main results of this section.
-\tit{Met wat} `with what' can not surface when the features that correspond to \tit{met wat} form a proper constituent.
-It is always \tit{waar mee} `with what' that appears, as shown in \ref{ex:waar meefr}.
-\tit{Met wat} `with what' can appear when the instrumental object does not form a proper constituent.
-This can be either when \tit{wat} `what' takes a complement before it combines with \tit{met} `with', as shown in \ref{ex:metwatx}, corresponding to the examples in \ref{ex:moremetwat}.
-The other option is that \tit{wat} `what' is part of a clause that \tit{met} `with' is not a part of, schematized as \ref{ex:metwatfr} and corresponding to \ref{ex:mismatchmetwat}.
+\tit{Met wat} can not surface when the features that correspond to \tit{met wat} form a proper constituent.
+It is always \tit{waar mee} that appears, as shown in \ref{ex:waar meefr}.
+\tit{Met wat} can appear when the instrumental object does not form a proper constituent.
+This can be when \tit{wat} takes a complement before it combines with \tit{met}, as shown in \ref{ex:metwatx}, corresponding to the examples in \ref{ex:moremetwat}.
+The other option is that \tit{wat} is part of a clause that \tit{met} is not a part of, schematized as \ref{ex:metwatfr} and corresponding to \ref{ex:mismatchmetwat}.
 
@@
 I connect these morphemes to parts of syntactic structure.
-\tit{Waar mee} `with what' and \tit{met wat} `with what' spell out the same set of features, but the distribution is different.
+\tit{Waar mee} and \tit{met wat} spell out the same set of features, but the distribution is different.
 I decompose \tit{waar mee} and \tit{met wat} as in \ref{ex:decompose}.
@@
 
-In this section I first identify \tit{w} and \tit{a(a)} as morphemes that appear in both expressions. Putting these two aside, I then concentrate on \tit{r mee} `with it' and \tit{met t} `with it'.
+In this section I first identify \tit{w} and \tit{a(a)} as morphemes that appear in both expressions. Putting these two aside, I then concentrate on \tit{r mee} and \tit{met t}.
 I propose an account that makes the ungrammaticality of \tit{met t} and the appearance of \tit{r mee} follow from spellout.
 The analysis accounts for the following three observations, taking \tit{met t} as the point of departure.
-First, \tit{met} `with' changes from being a preposition to being a postposition.
+First, \tit{met} changes from being a preposition to being a postposition.
 This process is restricted to inanimate pronouns, and it does not apply to full noun phrases and animate pronouns.
@@
 Let me start with the morphemes \tit{w} and \tit{a(a)} that appear in both \tit{waar mee} `with what' and \tit{met wat} `with what'.
-I assume that they correspond to the same syntactic structure in both.
-As I am interested in the differences between the two expressions, I do not discuss the featural content of \tit{w} and \tit{a(a)} in depth.
-
-For \tit{w} I follow \posscitet{hachem2015} work on \tit{d} and \tit{w} elements in German and Dutch.
+I assume that they correspond to the same syntactic structure in both expressions, As I am interested in the differences between the two expressions, I do not discuss the featural content of \tit{w} and \tit{a(a)} in depth.
+
+For \tit{w}, I follow \posscitet{hachem2015} work on \tit{d} and \tit{w} elements in German and Dutch.
 In her work, \tit{d} establishes a definite reference and \tit{w} triggers the construction of a set of alternatives in the sense of \citet{rooth1992} (see \citealt{hachem2015} for discussion).\footnote{Throughout the paper, ⇔ indicates the pairing between a lexical tree and a phonological form in a lexical entry, and ⇒ indicates how a node in the syntactic structure is spelled out.}
@@
 Note that in the proximal the initial \tit{d} is also replaced by an \tit{h}.
-This could indicate that (1) there must be some difference between \tit{hier} `here' and \tit{daar} `there' besides proximal and distal or (2) there is a different distribution between \tit{h} plus \tit{ie} and \tit{d} plus \tit{i} and the difference in vowels is not a matter of phonology.
+This could indicate that (1) there must be some difference between \tit{hier} `here' and \tit{daar} `there' besides proximal and distal, or (2) there is a different distribution between \tit{h} plus \tit{ie} and \tit{d} plus \tit{i} and the difference in vowels is not a matter of phonology.
 As this is not the focus of this paper, I put this aside for now.
@@
 
- The morpheme \tit{t} can act as nominative, accusative and dative, so it spells out \tit{k}1, \tsc{k}2 and \tsc{k}3.
+ The morpheme \tit{t} can act as nominative, accusative and dative, so it spells out \tsc{k}1, \tsc{k}2 and \tsc{k}3.
 
@@
 In addition to the pronominal and case features, I assume that the \tit{t} contains the ontological category \tsc{thing} \citep{kayne2005}.
-For reasons of space I will assume singular to be the absence of number and neuter the absence of gender.
+For reasons of space I will assume singular to be the absence of number and inanimate or neuter the absence of gender.
 
@@
 
- In other words, a lexically stored structure does not have to be identical to the syntactic structure it spells out.
+ In other words, a lexically stored tree does not have to be identical to the syntactic structure it spells out.
 The crucial requirement is that the syntactic structure is contained within the lexically stored tree.
@@
  ]
- {\draw (.east) node[right]{⇔ \tit{t}}; }
+ {\draw (.east) node[right]{⇒ \tit{t}}; }
  \end{forest}\label{ex:tacc}
@@
  ]
- {\draw (.east) node[right]{⇔ \tit{t}}; }
+ {\draw (.east) node[right]{⇒ \tit{t}}; }
  \end{forest}\label{ex:tnom}
@@
 Notice here that, via the Superset Principle, \tit{r} can also realize the feature \tsc{thing}, as it is contained in \tsc{locationP}.
-Moreover, for a syntactic structure like \ref{ex:rthing} the lexical entry \ref{ex:entryr} will be inserted and not \ref{ex:entryt}.
+Moreover, for a syntactic structure as \ref{ex:rthing} the lexical entry \ref{ex:entryr} will be inserted and not \ref{ex:entryt}.
 
@@
 
-Under this analysis, the caseless base form of the neuter singular pronoun in Dutch is actually \tit{r} and \tit{t} is a suppletive nominative, accusative and dative form.
-The base form only shows up in the higher cases, from instrumental on.
+Under this analysis, the caseless base form of the inanimate singular pronoun in Dutch is actually \tit{r}, and \tit{t} is a suppletive nominative, accusative and dative form.
+The base form only shows up in the higher cases, from the instrumental on.
 I show this in Table \ref{tbl:dutchcases}.
@@
 
-A similar pattern appears in Iron Ossetic, shown in Table \ref{tbl:ossetic}.
-In the first person singular of this language, it is only the nominative that is suppletive form (\tit{æz}).
+A similar pattern appears in Ossetic, shown in Table \ref{tbl:ossetic}.
+In the first person singular of this language, it is only the nominative that is suppletive: \tit{æz}.
 The higher cases have the stem \tit{mæn} and they combine with the suffixes that nouns normally combine with.
@@
 	\center
-	\caption {Partial paradigm of Iron Ossetic 1\tsc{sg} and noun \citep{erschler2012}}
+	\caption {Partial paradigm of Ossetic 1\tsc{sg} and noun \citep{erschler2012}}
 		\begin{tabular}{lll}
@@
 horse-\tsc{pl} and ox-\tsc{pl-com}\\
-`with horses and oxen' \hfill (Iron Ossetic, \citealt[165]{erschler2012})\label{ex:horseoxone}
+`with horses and oxen' \hfill (Ossetic, \citealt[165]{erschler2012} after \citealt{caha2019competition})\label{ex:horseoxone}
 
@@
  1\tsc{sg} and Zaur-\tsc{dat}\\
- `me and Zaur' \hfill (Iron Ossetic, \citealt[39]{беляев2014} after \citealt{caha2019competition})\label{ex:izaurone}
+ `me and Zaur' \hfill (Ossetic, \citealt[39]{беляев2014} after \citealt{caha2019competition})\label{ex:izaurone}
 
 The take-away message from the Ossetic example is that Dutch is not unique.
-Dutch and Ossetic both have a suppletive form that is less marked (in Dutch nominative, accusative and dative and in Ossetic nominative), and higher cases that are expressed by a combination of a suffix and a caseless base form.
+Dutch and Ossetic both have a suppletive form that is less marked (in Dutch nominative, accusative and dative and in Ossetic nominative), and higher cases that are expressed by a combination a caseless base form and a suffix or postposition.
 
@@
 
-The last two forms for which I specify lexical entries are \tit{mee} `with' and \tit{met} `with'.
+The last two forms for which I specify lexical entries are \tit{mee} and \tit{met}.
 An important distinction between these two is that \tit{mee} appears after the element it combines with, while \tit{met} appears before the element it combines with.
 In other words, \tit{mee} is a postposition and \tit{met} is a preposition.\footnote{
-A topic related to this paper is the different positioning of syncretic adpositions in Dutch (see \citet{caha2010} for an account of German and Dutch and see \citet{pretorius2017} for Afrikaans).
-In \ref{ex:dutchin}, \tit{in} `in' changes meaning depending on whether it proceeds or follows the DP.
+A topic related to this paper is the different positioning of syncretic adpositions in Dutch (see \citealt{caha2010} for an account of German and Dutch and see \citealt{pretorius2017} for Afrikaans).
+In \ref{ex:dutchin}, \tit{in} `in' changes meaning depending on whether it proceeds or follows the noun phrase.
 In \ref{ex:dutch-in-loc}, \tit{in} `in' carries a locational meaning, and in \ref{ex:dutch-in-dir}, \tit{in} `in' carries a directional meaning.
@@
 
-In \ref{ex:dutchin}, the movement of the adposition is driven by movement, and it is meaningful. The movement of \tsc{r}-pronouns I discuss in this paper is driven by spellout, which is meaningless.}
+\citet{caha2010} argues that the movement of the adposition is driven by movement, and it is meaningful.
+The movement of \tsc{r}-pronouns I discuss in this paper is driven by spellout, which is meaningless.}
 In this section I discuss the difference between prepositions and postpositions, and how this is modeled with the case hierarchy in Nanosyntax \citep{caha2009}.
@@
 The division between which cases are expressed by prepositions and which are expressed by postpositions is not arbitrary.
-If a particular case in the case sequence (see \ref{ex:casetree}) is expressed by a preposition, then all higher cases are too (the preposition/postposition hierarchy, \pgcitealt{caha2010}{36}).
-The lower cases are expressed by the DP, either as a suffix or by the DP itself.
-The result of that is that a PP can contain a preposition and a suffix. In the German example in \ref{ex:loffel}, the dative suffix is used with an instrumental preposition.
+If a particular case in the case sequence (see \ref{ex:casetree}) is expressed by a preposition, then all higher cases are too (the preposition/suffix hierarchy, \pgcitealt{caha2010}{36}).
+The lower cases are expressed by the noun phrase, either as a suffix or by the noun phrase itself.
+The result of that is that a prepositional phrase can contain a preposition and a suffix. In the German example in \ref{ex:loffel}, the dative suffix is used with an instrumental preposition.
 
@@
 The example in \ref{ex:bulpron} indicates that the suffix \tit{-i} can spell out features up to the dative case.
-However, for some reason this suffix cannot combine with a full DP to spell out these dative features.
+However, for some reason this suffix cannot combine with a full noun phrase to spell out these dative features.
 Instead, the preposition \tit{na} is used, as shown in \ref{ex:buldpto}.
@@
 The example in \ref{ex:dutchina} indicates that the postposition \tit{mee} can spell out features up to the instrumental case when there is an inanimate pronoun.
-However, for some reason this suffix cannot combine with an animate pronouns or a full DP to spell out these dative features, as shown in \ref{ex:dutchanmee} and \ref{ex:dutchdpmee}.
+However, for some reason this postposition cannot combine with an animate pronoun or a full noun phrase to spell out these dative features, as shown in \ref{ex:dutchanmee} and \ref{ex:dutchdpmee}.
 Instead, the preposition \tit{met} is used, as shown in \ref{ex:dutchan} and \ref{ex:dutchdp}.
@@
 So far, the \tsc{r}-pronoun \tit{r} only realizes the feature \tsc{thing}.
-This leaves Σ and \tsc{k1} to \tsc{k4} to be realized by \tit{mee}.
+This leaves Σ and \tsc{k1} to \tsc{k4} to be realized as \tit{mee}.
 
 This brings me to the second point: \tit{mee} is a postposition.
-Nanosyntax distinguishes pre-elements from post-elements by the shape of their lexical entry \citep{starke2018}.
+Nanosyntax distinguishes pre-elements (so prepositions and prefixes) from post-elements (so postpositions and suffixes) by the shape of their lexical entry \citep{starke2018}.
 Doing so, it follows from the spellout procedure whether an element appears before or after the previously inserted element.
@@
 the foot of the tree consists of two features), so they cannot be the inserted after complement movement.
-I illustrate this in a derivation in Section \ref{sec:derivation}.
-I give the lexical tree of \tit{mee} in \ref{ex:entrymee}.
+In Section \ref{sec:spellout} I come back to the complement movement I am referring to, and I illustrate it in a derivation.
+I give the lexical tree of \tit{mee} `with' in \ref{ex:entrymee}.
 
@@
 This is not surprising with a lexical entry as the one in \ref{ex:entrymee}.
-Animate pronouns contain, in addition the features of inanimate pronouns, gender features.
+Animate pronouns contain, in addition to the features of inanimate pronouns, gender (or animacy) features.
 I assume that gender features are situated between pronominal features (so Σ) and case features.
-The syntactic structure of an animate instrumental contains gender features that the lexical entry for \tit{mee} does not contain, so \tit{mee} cannot be inserted and a different lexical entry will be chosen.
-Full nouns phrases do not take features related to pronominal strength.
+The syntactic structure of an animate instrumental contains gender features that the lexical entry for \tit{mee} does not contain, so \tit{mee} cannot be inserted and a different lexical entries will be chosen (namely an alternative to \tit{r} that spells out gender features and the preposition \tit{met}).
+Full nouns phrases do not combine with \tit{mee} because its lexical entry contains the pronominal feature Σ.
+Full noun phrases generally do not take features related to pronominal strength.
 According to the Superset Principle, a lexical tree can match a syntactic tree with a subpart of the features, but a tree can only shrink from the top, so \tit{mee} will always realize the feature Σ.
@@
 any overlap at all. The proposal in this paper is compatible with the first two ideas.}
-I give the lexical entry for \tit{met} in \ref{ex:entrymet}.
+I give the lexical entry for \tit{met} `with' in \ref{ex:entrymet}.
 
@@
 
-Before I show that \tit{waar mee} `with what' is used when all features form a proper constituent, I need to make some assumptions about the spellout procedure in Nanosyntax explicit.
+In this section I show derivations in which \tit{waar mee} appears when all features form a proper constituent and that \tit{met wat} appears when the features do not.
+Before I do that, I need to make some assumptions about the spellout procedure in Nanosyntax explicit.
+For a more complete  I do so in Section \ref{sec:spellout}.
+Section \ref{sec:waarmee} derives \tit{waarmee}, and Section \ref{sec:metwat} derives \tit{met wat}.
+
+\subsection{The spellout procedure}\label{sec:spellout}
+
 Spellout happens in a cyclic derivation, following a spellout algorithm \citep{starke2018}.
@@
 
-When a new match is found, it overrides previous spellouts.
+When a new match is found, it overrides previous spellouts, as described in \ref{ex:override}.
 
 \ex. Cyclic Override \citep{starke2018}:\\
-Lexicalisation at a node XP overrides any previous match at a phrase contained in XP.
+Lexicalisation at a node XP overrides any previous match at a phrase contained in XP.\label{ex:override}
 
 If the spellout procedure in \ref{ex:spellout} fails, backtracking takes place.
-This, in my analysis, is the operation that ultimately leads from the suppletive nominative, accusative and dative form \tit{t} to the base form \tit{r}.
+This is described in \ref{ex:backtracking}.
+In my analysis, backtracking is the operation that ultimately leads from the suppletive nominative, accusative and dative form \tit{t} to the base form \tit{r}.
 
@@
 
-If backtracking also does not help, a specifier is constructed. This is what happens when the preposition \tit{met} `with' is inserted.
+If backtracking also does not help, a specifier is constructed, as described in \ref{ex:specformation}. This is what happens when the preposition \tit{met} is inserted.
 
@@
 With this theoretical background in place, I can turn to the derivation.
-I first show how \tit{r mee} `with it' is constructed.
+
+\subsection{Deriving \tit{waarmee}}\label{sec:waarmee}
+
+I first show how \tit{r mee} is constructed.
 I leave out \tit{w} and \tit{a(a)} in order to not unnecessarily complicate the story.\footnote{I assume that the \tsc{wP} and \tsc{deixP} appear lower in the structure than the case features, so the functional sequence is as given in \ref{ex:fseq}.
@@
 
-Then \tsc{k1} is merged. This structure can still be realized by \tit{t}.
+Then \tsc{k1} is merged. This structure can still be realized as \tit{t}.
 
@@
 
-As I formulated in the introduction of this section, the operation called backtracking is triggered (see \ref{ex:backtracking}).
+As I mentioned in Section \ref{sec:spellout}, the following operation that is triggered is backtracking (see \ref{ex:backtracking}).
 This means that the derivation goes back to the previous cycle, and the next option for that cycle is tried.
@@
 
-This means that backtracking proceeds further, into the cycle in which \tsc{k2} was merged.
+This means that backtracking proceeds further, into the cycle in which \tsc{k2} is merged.
 Again, spec-to-spec movement does not apply because there is no specifier, and complement movement can be tried, but there is no appropriate lexical entry available for the remaining structure.
@@
 
-The situation changes when the derivation comes to the cycle in which Σ was merged.
-At this stage, \tsc{thing} was realized as \tit{r}.
-Again there was no specifier, so spec-to-spec movement does not apply.
-However, complement movement provides a structure that is a match for the lexical entry in \ref{ex:entrymee}: \tit{mee}.\footnote{This picture resembles the proposal of \citep{abels2003diss} in that not the whole complement of P is moved but only a part is subextracted.
+The situation changes when the derivation comes to the cycle in which Σ is merged.
+At this stage, \tsc{thing} is realized as \tit{r}.
+Again, there is no specifier, so spec-to-spec movement does not apply.
+However, complement movement provides a structure that is a match for the lexical entry in \ref{ex:entrymee}: \tit{mee}.\footnote{This picture resembles \posscitet{abels2003diss} analysis of \tsc{r}-pronouns in that not the whole complement of the preposition is moved but only a part is subextracted.
 The current analysis differs in that the movement is not syntactically driven but spellout-driven.
-
-%not too local? anti-locality is avoided becuase..
 }
@@
 The features are merged one at a time, there is no spellout immediately after merging the feature, but there is a spellout after spec-to-spec movement.
-I show the situation after \tsc{k4} in \ref{ex:spelloutr mee}.
+I show the situation after \tsc{k4} in \ref{ex:spelloutrmee}.
 
@@
 ]
-\end{forest}\label{ex:spelloutr mee}
+\end{forest}\label{ex:spelloutrmee}
 
@@
 I assume that \tsc{wP} and \tsc{deixP} are both complex specifiers that are created after \tsc{thing} is spelled out in \ref{ex:thingspellout}.
-After each instance of merge after that, backtracking takes place, the complex specifiers are detached from the structure,and the new feature is merged in all workspaces.
+After each instance of merge after that, backtracking takes place, the complex specifiers are detached from the structure, and the new feature is merged in all workspaces (see Multiple Merge, \pgcitealt{caha2019competition}{227}).
 The new feature is successfully spelled out in the workspace that contains the feature \tsc{thing}, and the workspaces are merged back together.
-} The final result of the structure for \tit{waar mee} `with what' appears in \ref{ex:spelloutwaar mee}.
+} The final result of the structure for \tit{waar mee} appears in \ref{ex:spelloutwaarmee}.
 
@@
 ]
-\end{forest}\label{ex:spelloutwaar mee}
-
-A consequence of analyzing \tit{mee} `with' as a postposition is that \tit{r} and \tit{mee} always form a constituent to the exclusion of \tit{w} and \tit{a(a)}.
-At first sight this seems problematic, because it is possible for \tit{waar} `where' to not directly precede \tit{mee} `with'.
+\end{forest}\label{ex:spelloutwaarmee}
+
+A consequence of analyzing \tit{mee} as a postposition is that \tit{r} and \tit{mee} always form a constituent to the exclusion of \tit{w} and \tit{a(a)}.
+At first sight this seems problematic, because it is possible for \tit{waar} `where' to not directly precede \tit{mee}.
 I repeat the relevant example in \ref{ex:meestranded}.
@@
 
-There is no constituent in \ref{ex:spelloutwaar mee} that contains \tit{waar} but not \tit{mee}, so it is not possible to move \tit{waar} from \ref{ex:spelloutwaar mee} and strand \tit{mee} in the process.
+There is no constituent in \ref{ex:spelloutwaarmee} that contains \tit{waar} but not \tit{mee}, so it is not possible to move \tit{waar} from \ref{ex:spelloutwaarmee} and strand \tit{mee} in the process.
 To resolve this situation I follow \citet{noonan2017dutch} in assuming that the phrase containing the adposition (\tit{mee}) can syntactically move to a position higher in the structure.
@@
 \citealt{riemsdijk1978,noonan2017dutch}).
-The trigger for the movement of \tit{mee} could be the feature Σ (which is contained in \tit{mee} `with`), associated with weak pronouns.
-Allowing \tit{mee} to subextract from the \tsc{w}P resolves the issue.
-With \tit{mee} having moved out, the remnant \tsc{wP} only contains features that are realized as \tit{waar}, and it moves to the left edge of the clause, resulting in the surface order in \ref{ex:meestranded}.
-
-So far I showed how \tit{waar mee} `with what' is derived if all syntactic features form a constituent.
-Next I address how \tit{waar mee} `with what' is blocked and \tit{met wat} `with what' appears when the features do not form a proper constituent.
-An example of a situation in which the features do not form a constituent is given in \ref{ex:noconst}.
+The trigger for the movement of \tit{mee} could be the feature Σ (which is contained in \tit{mee}), associated with weak pronouns.
+Allowing \tit{mee} to subextract from the \tsc{w}P resolves the issue of the surface order in \ref{ex:meestranded}.
+With \tit{mee} having moved out, the remnant \tsc{wP} only contains features that are realized as \tit{waar}, and it can move to the left edge of the clause, resulting in the surface order in \ref{ex:meestranded}.
+
+In this section I showed how \tit{waar mee} `with what' is derived if all syntactic features form a proper constituent.
+In the following section I address how \tit{waar mee} `with what' is blocked and \tit{met wat} `with what' appears when the features do not.
+
+\subsection{Deriving \tit{met wat}}\label{sec:metwat}
+
+An example of a situation in which the relevant features do not form a constituent and \tit{met wat} appears is given in \ref{ex:noconst}.
 
@@
 
-\ref{ex:metwatst} shows the syntactic structure of the relative clause \tit{wat je hebt gekocht} `what you bought' in \ref{ex:noconst}. \tit{Wat} `what' is the element in the specifier of the CP.
+\ref{ex:metwatst} shows the syntactic structure of the relative clause \tit{wat jij hebt gekocht} `what you bought' in \ref{ex:noconst}.
+\tit{Wat} `what' is the element in the specifier of the CP.\footnote{
+I added the feature \tsc{k3} that creates a \tsc{dat}P in the relative clause.
+It is unclear why, but syncretic forms seem to resolve case conflicts in free relatives and related phenomena (cf.
+\citealt{groos1981,pullum1986,ingria1990}).
+It seems that the syntax only sees the phonological form (in this case \tit{t}) and it is irrelevant whether the feature \tsc{k3} is present in the relative clause or not.
+Only considering the relative clause in \ref{ex:noconst}, we do not expect \tsc{k}3 to be present in the relative clause.
+However, also taking the instrumental case requirement from the main clause into account, we expect the feature to be present because the feature \tsc{k4} can only be merged if the feature \tsc{k3} has been.
+}
 
@@
             {\draw (.east) node[right]{⇒ \tit{a(a)}}; }
+            [\tsc{dat}P
+                [\tsc{k3}]
                 [\tsc{accP}
@@
                 ]
+            ]
             {\draw (.east) node[right]{⇒ \tit{t}}; }
@@
     [CP
-        [..,roof]
+        [\tit{jij hebt gekocht},roof]
     ]
@@
 At this point \tsc{k4} is merged, as shown in \ref{ex:f4metwat}.
-Because of the presence of the CP, backtracking cannot take place and the additional features cannot be spelled out as the postposition \tit{mee}.
-\footnote{
+Because of the presence of the CP, backtracking cannot take place and the additional features cannot be spelled out as the postposition \tit{mee}.\footnote{
 Here I assume that backtracking is prohibited once syntactic movement has taken place (in this case \tsc{wh}-movement of the \tsc{wh}-element to the specCP position).
@@
         [CP
-            [..,roof]
+            [\tit{jij hebt gekocht},roof]
         ]
@@
 Instead, the last resort possibility to spell out features is set in motion: a complex specifier is created, as described in \ref{ex:specformation}.
-This is illustrated in \ref{ex:metmetwat}.\footnote{
-I added the feature \tsc{k3} that creates a \tsc{dat}P in the relative clause.
-It is unclear why, but syncretic forms behave differently in that they seem to resolve case conflicts in free relatives and related phenomena (cf.
-\citealt{groos1981,pullum1986,ingria1990}).
-It seems that the syntax only sees the phonological form (in this case \tit{t}) and it is irrelevant whether the feature \tsc{k3} was already present in the relative clause.
-Syntactically, we expect the feature to be there because the feature \tsc{k4} can only be merged if the feature \tsc{k3} has been.
-}
+The newly merged feature merges with the previous feature in the functional sequence (\tsc{k}3), and together they form a complex specifier.
+This is illustrated in \ref{ex:metmetwat}.
 
@@
 
-This section showed how the instrumental inanimate relative pronoun is realized as \tit{waar mee} `with what' when all relevant features form a constituent, and how \tit{met wat} `with what' appears when they do not.
+In sum, \tit{met wat} appears when the relevant features that form an instrumental inanimate relative pronoun do not form a proper constituent.
 
@@
 The main intuition is that this form appears when features of an instrumental inanimate object form a proper constituent.
-The form cannot appear, and \tit{met wat} `with what` surfaces instead, when all relevant features do not form a proper constituent.
+The form cannot appear, and \tit{met wat} `with what` surfaces instead, when the relevant features do not form a proper constituent.
 The described pattern follows from a core assumption in Nanosyntax: only constituents can be targeted for spellout \citep{starke2009}.
@@
 As long as the relevant features form a proper constituent, the spellout algorithm ensures that the \tsc{r}-pronoun plus postposition takes precedence over the preposition plus inanimate pronoun.
-The fact that locatives are syncretic with \tsc{r}-pronouns is not a coincidence.
+The fact that locatives are syncretic with \tsc{r}-pronouns is not a coincidence either.
 The lexicon contains a single entry that can spell out the features that refer to a locative and features that refer to a thing.
 The change in placement of the adposition is a consequence of spellout too.
-\tit{Mee} `with' is a postposition and is stored differently from the preposition \tit{met} `with', which leads them to either appear before or after the previously spelled out element.
-The fact that \tit{met} `with' and \tit{mee} `with' differ phonologically can also be captured by storing them as two separate lexical entries.
-
-Giving \tit{met} `with' and \tit{mee} `with' two distinct lexical entries has as a consequence that the phonological overlap between them seems like a coincidence.
-This can be questioned, because there is only one other preposition that changes form when it appears postpositionally.
+\tit{Mee} is a postposition and is stored besides and shaped differently from the preposition \tit{met}, which leads them to either appear before or after the previously spelled out element.
+The fact that \tit{met} and \tit{mee} differ phonologically can also be captured by storing them as two separate lexical entries.
+
+Giving \tit{met} and \tit{mee} two distinct lexical entries has as the consequence that the phonological overlap between them seems like a coincidence.
+This can be questioned, because there is only one other preposition that changes form when it appears as a postposition.
 This preposition is \tit{tot} `to', which changes to \tit{toe} as a postposition.
-It has in common with \tit{met} `with' that it is the only preposition in Dutch with the phonological structure CVt.
+It has in common with \tit{met} that it is the only preposition in Dutch with the phonological structure CVt.
 For now I take the phonological resemblance to be a relic from the past without having any influence on the synchronic data.
-In all other cases the adposition does not change form when it combines with an \tsc{r}-pronoun, e.g.
+Other Dutch adpositions do not change form when they combine with an \tsc{r}-pronoun, e.g.
 \tit{in} `in'.
 This raises the question of whether the preposition \tit{in} `in' and the postposition \tit{in} `in' are stored as separate lexical entries in the lexicon or whether they refer to a single entry.
-Connected to this are the verbal particles that appear in dutch.
+Connected to this are the verbal particles that appear in Dutch.
 They have the form of the postposition and not of the preposition: it is \tit{mee-lopen} `walk along' and not *\tit{met-lopen} `walk along'.
 Ideally, an analysis derives all these observations.
-For now, I leave this for future research.
+For now, I leave these matters for future research.
 
@@
 
-Thanks to Pavel, two anonymous reviewers, to the organizers of PlaCiG, nanolab, especially Pavel, Guido, Karen, Michal and Hagen Blix.
+I am grateful for the feedback of audiences at On the place of case in grammar, Universität Leizpig, Georg-August-Universität Göttingen and Goethe-Universität Frankfurt, Pavel Caha, Hagen Blix, Karen De Clercq, Francesco Pinzin, Michal Starke and Guido Vanden Wyngaerd.
+I also wish to thank two anonymous reviewers for their constructive and helpful comments.
 
